### 2021-11-12 rmd/manuscript.Rmd
add: rmd files

---
title: "Excessive release of captive-bred animals destabilizes ecological communities"
output:
  word_document:
    reference_docx: word_format.docx
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Authors:** Akira Terui^1,\*^, Hirokazu Urabe^2^, Masayuki Senzaki^3^, Bungo Nishizawa^4^

\*Corresponding author: hanabi0111\@gmail.com

**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Department of Ecology, Evolution and Behavior, University of Minnesota, St. Paul, MN 55108, USA ^3^ National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan ^4^ Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan

## Maintext

## Methods

### Theory

We developed a multispecies Ricker model to simulate community dynamics with selective enhancement of a particular species. SUPPLEMENTAL EXPLANATION HERE. Population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:

$$
N_{i,t+1} = [N_{i,t}+\phi R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t})
$$

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient (intraspecific if $i=j$, interspecific otherwise), $K_i$ the carrying capacity, $R_t$ the number of released individuals for enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations. The parameter $\phi$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species.

### Empirical analysis

#### Data

#### Statistical analysis

## Data availability

## Acknowledgments

## References

### 2021-11-12 rmd/summary_slides.Rmd
add: rmd files

---
title: "8/6 Meeting"
author: Akira Terui
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

## Captive breeding

- Form of conservation of critically endangered species
- Restore declining natural populations
- Effective in certain circumstances

![](image/img-florida-panther.jpg)
Photo - Wikipedia

- Increased awareness of "downside"

## Knowledge gap

Community-level impact of captive breeding is unknown

- Effects spread through species interactions?
- Enhancement with captive-reared organisms sometimes excessive
- Fish stocking is an example

## Question

How does fish stocking influence long-term stability of fish communities?

- Theory: community model with a Ricker formula + stocking
- Data: empirical test with long term data

## Question

How does fish stocking influence long-term stability of fish communities?

- **Theory: community model with a Ricker formula + stocking**
- Data: empirical test with long term data

## Theory

Community Ricker model

$$
N_{i,t+1} = N_{i,t}exp(r_i[1-\frac{\sum_{j=1}^n\alpha_{ij}N_{j,t}}{K}])
$$
$N$ - density  
$r$ - intrinsic population growth rate  
$K$ - carrying capacity  
$\alpha$ - competition coefficient  
$i,j$ - species  
$t$ - time

## Theory

Community Ricker model + stocking

$$
N_{i,t+1} = (N_{i,t} + s_t)exp(r_i[1-\frac{\sum_{j=1}^n\alpha_{ij}N_{j,t} + \alpha_{i1}s_t}{K}])
$$

$N$ - density  
$r$ - intrinsic population growth rate  
$K$ - carrying capacity  
$\alpha$ - competition coefficient  
$i,j$ - species  
$t$ - time

## Theoretical prediction

Community-level CV increased with stocking even with weak species interactions

```{r figure1, fig.width = 7, fig.height = 4}
source("code_theory/figure_theory.R")
```

## Question

How does fish stocking influence long-term stability of fish communities?

- Theory: community model with a Ricker formula + stocking
- **Data: empirical test with long term data**

## Data

- Fish data collected in protected watersheds in Hokkaido
- Data compiled for 1999-2019

---

```{r figure2, fig.width = 8, fig.height = 6}
source("code_empirical/figure_time_series.R")
```

## Results

Community-level CV increased with stocking

```{r figure3, fig.width = 7, fig.height = 5}
source("code_empirical/figure_cv_stock.R")
```

### 2021-11-15 code_theory/function_sim.R
edit: minor edit to simulation function

@@ -1,4 +1,6 @@
 
+library(tidyverse)
+
 dynsim <- function(n_timestep = 1000,
                    n_warmup = 100,
                    n_burnin = 100,

### 2021-11-15 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Excessive release of captive-bred animals destabilizes ecological communities"
+title: "Selective enhancement of an exploited species destabilizes ecological communities"
 output:
@@
 knitr::opts_chunk$set(echo = TRUE)
+pacman::p_load(tidyverse)
+
+# theory infomation
+df_theory <- read_csv(here::here("code_theory/result/result_ricker.csv"))
+
+param_set <- df_theory %>% 
+  filter(r_min == 0.5) %>% 
+  distinct(n_species,
+           k,
+           r_type,
+           r_min,
+           r_max,
+           sd_env,
+           phi,
+           int_type,
+           alpha,
+           model,
+           seed)
+
 ```
@@
 
-We developed a multispecies Ricker model to simulate community dynamics with selective enhancement of a particular species.
-SUPPLEMENTAL EXPLANATION HERE.
-Population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+We developed a multispecies Ricker model to simulate community dynamics with selective enhancement of a particular species. Population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
 $$
-N_{i,t+1} = [N_{i,t}+\phi R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t})
+N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t})
 $$
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient (intraspecific if $i=j$, interspecific otherwise), $K_i$ the carrying capacity, $R_t$ the number of released individuals for enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
-The parameter $\phi$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
+The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species.
+The species-specific intrinsic growth rates and competition coefficients were drawn randomly from a uniform and exponential distribution, respectively, to allow for interspecific variation as $r_i \sim Unif(0.5, r_{max})$ and $\alpha_{ij, i \ne j} \sim Exp(\mu_{\alpha})$.
+Environmental stochasticity is random and was expressed as $\epsilon_{i,t} \sim Normal(\mu_{\epsilon}, \sigma_{\epsilon}^2)$
+
+We varied values of `r sum(unlist(lapply(sapply(param_set, unique), length)) > 1)` parameters: $S =$ `r unique(param_set$n_species)`; $r_{max}=$ `r unique(param_set$r_max)`; $\mu_{\alpha} =$ `r unique(param_set$alpha)`; $\sigma_\epsilon =$ `r unique(param_set$sd_env)`.
+For simplicity, we assumed identical carrying capacities among simulated species as $K_i =$ `r unique(param_set$k)`.
+This setup results in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
+
+Under each parameter combination, we ran 1400 generations to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).
+We also calculated temporal means and standard deviations for each species group.
 

### 2021-11-18 code_theory/run_simulation.R
edit: run simulation

@@ -28,7 +28,8 @@ df_param <- expand.grid(n_timestep = 1000,
                         int_type = "random",
                         alpha = c(0.1, 0.3, 0.5),
                         model = "ricker",
-                        seed = 5) %>% 
+                        seed = 5,
+                        seed_interval = 10) %>% 
   filter(r_max >= r_min)
 
 n_rep <- 1000

### 2021-11-18 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 The species-specific intrinsic growth rates and competition coefficients were drawn randomly from a uniform and exponential distribution, respectively, to allow for interspecific variation as $r_i \sim Unif(0.5, r_{max})$ and $\alpha_{ij, i \ne j} \sim Exp(\mu_{\alpha})$.
-Environmental stochasticity is random and was expressed as $\epsilon_{i,t} \sim Normal(\mu_{\epsilon}, \sigma_{\epsilon}^2)$
+The number of released individuals was assumed to be constant across time steps ($R_t = R$).
+Environmental stochasticity was drawn from a normal distribution as $\epsilon_{i,t} \sim Normal(\mu_{\epsilon}, \sigma_{\epsilon}^2)$
 
-We varied values of `r sum(unlist(lapply(sapply(param_set, unique), length)) > 1)` parameters: $S =$ `r unique(param_set$n_species)`; $r_{max}=$ `r unique(param_set$r_max)`; $\mu_{\alpha} =$ `r unique(param_set$alpha)`; $\sigma_\epsilon =$ `r unique(param_set$sd_env)`.
+We varied values of four parameters: $S =$ `r unique(param_set$n_species)`; $r_{max}=$ `r unique(param_set$r_max)`; $\mu_{\alpha} =$ `r unique(param_set$alpha)`; $\sigma_\epsilon =$ `r unique(param_set$sd_env)`.
 For simplicity, we assumed identical carrying capacities among simulated species as $K_i =$ `r unique(param_set$k)`.
-This setup results in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
+This setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
 
-Under each parameter combination, we ran 1400 generations to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).
+Under each parameter combination, we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with the gradient of the number of released individuals $R$ (0 - 500).
+We initialized the community with populations of each species drawn from a poisson distribution with a mean of five.
+We repeated the seeding procedure every 10 time steps over the first 200 time steps to allow species to establish populations and reach an equilibrium without (initialization period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next 200 time steps to reach a new equilibrium with selective enhancement (burn-in period).
+We saved the last 1000 time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).
 We also calculated temporal means and standard deviations for each species group.
+Values of simulation parameters were summarized in XXX.
+We performed simulations using R version XXX.
 
@@
 
+**Time-series data of fish abundance.** We assembled time-series data across XX sites within XX protected watersheds of Hokkaido Island, Japan.
+At these sites, long-term monitoring of fish abundance began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999.
+Data were collected in summer to fall with irregular sampling intervals (0 to 3 year intervals for most cases).
+After careful data selection (Supporting Information), we used time-series data of fish abundance at XX sites during a period of 1999-2019.
+
+**Fish stocking data of masu salmon.** Ask Urabe to write this part
+
+**Environmental data.** At each sampling site,we collected the following data as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture, urban), local species richness, local climates (annual mean air temperature [unit] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
+
 #### Statistical analysis
+
+We quantified the coefficient of variation (CV), temporal mean ($\mu$) and standard deviation ($\sigma$) of these local fish communities through the following procedure.
 

### 2021-11-24 rmd/manuscript.Rmd
edit: manuscript

@@
 ---
-title: "Selective enhancement of an exploited species destabilizes ecological communities"
+title: "Selective enhancement of an exploited species undermines the long-term stability of ecological communities"
 output:
@@
 
+Anthropogenic influences have caused global biodiversity crisis, such that active human interventions are critical to sustainable ecosystem management.
+Captive breeding is a pervasive method aiming to conserve or enhance wild populations of diverse plant and animal taxa.
+In fisheries for example, XXX have been spent annually to support hatchery programs globally.
+While there is growing recognition that the selective enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still widespread in conservation and fisheries perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
+However, a crucial yet overlooked perspective in this research area is the community-wide impact of selective enhancement through species interaction networks.
+Species are all embedded in the web of interacting organisms.
+Excessive release of particular species may therefore have unforeseen consequences for ecological communities in the long term.
+We lack quantitative evidence for this hypothesis, however.
+
+Here, we use a simple, general theory to show that selective enhancement of a particular species undermines the long-term stability of ecological communities.
+We then demonstrate the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, in which an exploited species, masu salmon (*Oncorhynchus masou masou*), is selectively enhanced through captive breeding programs.
+
+We developed...
+
 ## Methods
@@
 
-**Time-series data of fish abundance.** We assembled time-series data across XX sites within XX protected watersheds of Hokkaido Island, Japan.
-At these sites, long-term monitoring of fish abundance began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999.
+**Time-series data.** We assembled time-series data of fish abundance across XX sites within XX protected watersheds of Hokkaido Island, Japan.
+In these watersheds, aquatic species are protected and no harvest is allowed.
+At these sites, the long-term monitoring program began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999.
 Data were collected in summer to fall with irregular sampling intervals (0 to 3 year intervals for most cases).
 After careful data selection (Supporting Information), we used time-series data of fish abundance at XX sites during a period of 1999-2019.
+ADD SOME DETAILS
 
-**Fish stocking data of masu salmon.** Ask Urabe to write this part
+**Fish stocking.** At the protected watersheds, masu salmon were stocked to enhance the wild populations since XXX.
+A mixture of captive-bred and wild-born individuals were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
+We examined historical records of fish stocking and obtained annual stocking data (the number of individuals released) for a period of 1999-2019 at each watershed.
+We were unable to extract stocking data at the site level.
 
@@
 
-We quantified the coefficient of variation (CV), temporal mean ($\mu$) and standard deviation ($\sigma$) of these local fish communities through the following procedure.
+Our goal is to compare temporal dynamics of fish communities across sites.
+However, the data are not directly comparable because of artificial observation errors (e.g., different observers) and missing observations.
+To confront this challenge, we developed Bayesian state space models for three species groups separately: (1) whole community, summed abundance of all species, (2) enhanced species, abundance of masu salmon, (3) unenhanced species, summed abundance of all species except masu salmon.
+Bayesian state space models is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at the site.
+The model is composed of observation and state models as described below.
+
+In the observation model, we model observation processes.
+Summed fish abundance of either whole community, enhanced species (masu salmon only), and unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
+
+$$
+N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t})
+$$
+
+where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
+Since fish sampling was conducted after the spring stocking of masu salmon, captured fish may include individuals released in the observation year.
+To avoid biases in estimating temporal community trends, we explicitly modeled this observation process:
+
+$$
+\lambda_{s,t} = n_{s,t}e^{\epsilon_{s,t}^{obs}} + \psi \beta_s~Fry_{w(s),t}
+$$
+
+$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
+The parameter $e^{\epsilon_{s,t}^{obs}}$ is a random error variable drawn from a log-normal distribution as $\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$.
+The inclusion of this random variable allows us to account for site-specific and year-specific observation errors.
+The parameter $\psi$ equals one when we model the unenhanced species group (otherwise $\psi = 1$).
+We included $\psi$ to exclude the term $\beta~Fry_{w(j),t}$ because the unenhanced species group does not include masu salmon.
+
+In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
+
+$$
+ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
+$$where $ln~r_{s}$ is the average rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
+The site-specific rate of change is random draws from a normal distribution as $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).
+This hierarchical structure allows for improved estimates of $ln~r_s$ by sharing information across sites.
+We used median estimates of fish density $n_{s,t}$ to calculate temporal CV, mean ($\mu$), and SD ($\sigma$).
+
+We developed the following linear regression models taking either log-transformed CV, mean, or SD as a response variable $ln~y_s$ with a normal error distribution.
+
+$$
+\begin{aligned}
+ln~y_s &\sim Normal(\mu_{y,s},\sigma_y^2)\\
+\mu_{y,s} &= \beta_{0,w(s)} + \sum_k \beta_kx_{k,s}
+\end{aligned}
+$$
+
+where $\beta_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\beta_k (k > 0)$ is the regression coefficient of site-level predictor $x_k$.
+The site-level predictors include upstream watershed area, air temperature, precipitation, forest land use, and local species richness (we excluded local species richness from the masu salmon model).
+The watershed-specific intercept was related to watershed-level predictors as:
+
+$$
+\begin{aligned}
+\beta_{0,w} &\sim Normal(\mu_{\beta,w},\sigma_{\beta}^2)\\
+\mu_{\beta,w} &=\gamma_0+\sum_k\gamma_k z_{k,w}
+\end{aligned}
+$$
+
+The watershed-level predictors include the number of released masu salmon and ocean productivity (sea surface chlorophyll a).
+
+We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R. Priors were summarized in XXX. Data manipulation and analysis were performed in R version 4.1.0.
 

### 2021-11-26 rmd/manuscript.Rmd
edit: manuscript

@@
 ---
-title: "Selective enhancement of an exploited species undermines the long-term stability of ecological communities"
+title: "Selective enhancement of an exploited species undermines the community stability"
 output:
@@
 
-Anthropogenic influences have caused global biodiversity crisis, such that active human interventions are critical to sustainable ecosystem management.
-Captive breeding is a pervasive method aiming to conserve or enhance wild populations of diverse plant and animal taxa.
+Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to sustainable management of natural resources.
+Captive breeding is a pervasive method to conserve or enhance wild populations of diverse plant and animal taxa.
 In fisheries for example, XXX have been spent annually to support hatchery programs globally.
-While there is growing recognition that the selective enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still widespread in conservation and fisheries perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
+There is growing recognition that the selective enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles); nevertheless, captive breeding is still widespread in conservation and fisheries perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
 However, a crucial yet overlooked perspective in this research area is the community-wide impact of selective enhancement through species interaction networks.
-Species are all embedded in the web of interacting organisms.
-Excessive release of particular species may therefore have unforeseen consequences for ecological communities in the long term.
-We lack quantitative evidence for this hypothesis, however.
+Species are all embedded in the web of interacting organisms, and excessive release of particular species may have cascading consequences for ecological communities in the long term.
+Evidence for this hypothesis is lacking, however.
 
-Here, we use a simple, general theory to show that selective enhancement of a particular species undermines the long-term stability of ecological communities.
-We then demonstrate the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, in which an exploited species, masu salmon (*Oncorhynchus masou masou*), is selectively enhanced through captive breeding programs.
+Here, we use a simple, general theory to show that the selective enhancement of a particular species undermines the community stability, which is defined here by the relative size of fluctuations in summed community density over time.
+The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, in which an exploited species, masu salmon (*Oncorhynchus masou masou*), is supplemented through captive breeding programs.
 

### 2021-11-30 rmd/manuscript.Rmd
edit: manuscript

@@
 ---
-title: "Selective enhancement of an exploited species undermines the community stability"
+title: "Selective enhancement of an exploited species undermines community stability"
 output:
@@
 Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to sustainable management of natural resources.
-Captive breeding is a pervasive method to conserve or enhance wild populations of diverse plant and animal taxa.
+Captive breeding - DEFINE CAPTIVE BREEDING - is a common method to conserve or enhance wild populations of diverse plant and animal taxa.
+Although there is growing recognition that the selective enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still pervasive in conservation and fisheries.
 In fisheries for example, XXX have been spent annually to support hatchery programs globally.
-There is growing recognition that the selective enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles); nevertheless, captive breeding is still widespread in conservation and fisheries perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
-However, a crucial yet overlooked perspective in this research area is the community-wide impact of selective enhancement through species interaction networks.
-Species are all embedded in the web of interacting organisms, and excessive release of particular species may have cascading consequences for ecological communities in the long term.
+This is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
+The current debate, however, overlooks the fact that we have rarely assessed the community-wide impact of selective enhancement.
+Species are all embedded in the complex web of interacting organisms, and excessive release of particular species may have unforeseen consequences for ecological communities in the long term.
 Evidence for this hypothesis is lacking, however.
 
-Here, we use a simple, general theory to show that the selective enhancement of a particular species undermines the community stability, which is defined here by the relative size of fluctuations in summed community density over time.
-The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, in which an exploited species, masu salmon (*Oncorhynchus masou masou*), is supplemented through captive breeding programs.
+Here, we use a simple, general theory to show that the selective enhancement of a particular species undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time.
+The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with stream fish communities, in which an exploited species, masu salmon (*Oncorhynchus masou masou*), is supplemented by hatchery programs.
+Our findings paint a bleak picture for this form of ecosystem management, reinforcing the recurrent calls for alternative strategies.
 
-We developed...
+We use a multispecies Ricker model to simulate community dynamics with selective enhancement of a particular species.
+Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
-## Methods
+$$
+N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t})
+$$
+
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species (species 1; set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
+The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species.
+XX parameter combinations were used to represent ecological scenarios with different strength of competition and XX.
+Under each simulation scenario, we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with varying $R$, of which the last 1000 time steps were used to obtain the coefficient of variation, mean, and standard deviation of community density ($\sum_i^SN_j$).
+Temporal means and standard deviations were calculated for the enhanced species $N_1$ and the unenhanced species $\sum_{i,i \ne 1}^S N_i$ separately to infer mechanisms that underlie community-level responses.
+
+Our model predicted a destabilizing effect of selective enhancement on ecological communities.
+With increasing released individuals $R$, communities showed greater temporal fluctuations as illustrated by increased CV (Figure XX).
+Since CV is a ratio of SD to mean, the increase of CV can be driven by a decreased mean, an increased SD, or both.
+In our case, the group-level analysis depicted a major influence of the decreased means of enhanced and unenhanced species groups (Figure XX).
+For enhanced species, intraspecific competition is responsible for the decreased mean.
+That is, released individuals induce strong overcompensation, where the negative effect of reduced per-capita reproduction exceeds the numerical benefit (increased reproducing individuals) of released individuals.
+Meanwhile, the decreased mean of unenhanced species is caused by interspecific competition between enhanced and unenhanced species.
+This negative effect of released individuals through competition was noticeable even with weak interspecific competition that would otherwise allow stable coexistence.
+Combined, the total community density decreased more sharply than individual species groups with increased numbers of released individuals (XX).
+The SDs showed a similar trend, but the relationship was flatter than the means.
+CONCLUDING SENTENCE
+
+ADDITIONAL PARAGRAPH ABOUT EXTERNAL CONTROL OF RELEASED INDIVIDUALS
+
+EMPIRICAL ANALYSIS
+
+### Methods
 

### 2021-11-30 rmd/manuscript.Rmd
edit: manuscript

@@
 
-We use a multispecies Ricker model to simulate community dynamics with selective enhancement of a particular species.
+We use a multispecies Ricker model to simulate community dynamics with selective enhancement of a constituent species.
 Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 Our model predicted a destabilizing effect of selective enhancement on ecological communities.
-With increasing released individuals $R$, communities showed greater temporal fluctuations as illustrated by increased CV (Figure XX).
-Since CV is a ratio of SD to mean, the increase of CV can be driven by a decreased mean, an increased SD, or both.
-In our case, the group-level analysis depicted a major influence of the decreased means of enhanced and unenhanced species groups (Figure XX).
-For enhanced species, intraspecific competition is responsible for the decreased mean.
-That is, released individuals induce strong overcompensation, where the negative effect of reduced per-capita reproduction exceeds the numerical benefit (increased reproducing individuals) of released individuals.
-Meanwhile, the decreased mean of unenhanced species is caused by interspecific competition between enhanced and unenhanced species.
+Increasing numbers of released individuals $R$ led to greater temporal fluctuations of communities as illustrated by increased CV (Figure XX).
+This pattern stemmed mainly from the reduced means of enhanced and unenhanced species groups (Figure XX) that are driven by different mechanisms.
+For enhanced species, released individuals induced strong overcompensation, where the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals (increased reproducing individuals).
+Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals.
+Meanwhile, the reduced mean of unenhanced species is caused by interspecific competition between enhanced and unenhanced species.
 This negative effect of released individuals through competition was noticeable even with weak interspecific competition that would otherwise allow stable coexistence.
-Combined, the total community density decreased more sharply than individual species groups with increased numbers of released individuals (XX).
-The SDs showed a similar trend, but the relationship was flatter than the means.
-CONCLUDING SENTENCE
+Combined, the long-term average of the total community density decreased more sharply than individual species groups with increased numbers of released individuals (XX).
+The SDs showed a similar trend, but the relationship was flatter than the mean at the community level.
+Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density has led to the increased CV.
 
-ADDITIONAL PARAGRAPH ABOUT EXTERNAL CONTROL OF RELEASED INDIVIDUALS
+The phenomena of the decreased long-term means should arise as long as humans control the number of released individuals (i.e., donor-control).
+The released individuals are free from any density dependent feedback in natural communities and therefore undermine the internal regulation of self-sustaining communities.
+
+These results were qualitatively consistent across ecological scenarios (XX).
+
+The desta
 

### 2021-11-30 rmd/manuscript.Rmd
edit: manuscript

@@
 
-## Maintext
+# Maintext
 
@@
 Meanwhile, the reduced mean of unenhanced species is caused by interspecific competition between enhanced and unenhanced species.
-This negative effect of released individuals through competition was noticeable even with weak interspecific competition that would otherwise allow stable coexistence.
 Combined, the long-term average of the total community density decreased more sharply than individual species groups with increased numbers of released individuals (XX).
@@
 Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density has led to the increased CV.
+These patterns were qualitatively similar across ecological scenarios.
 
-The phenomena of the decreased long-term means should arise as long as humans control the number of released individuals (i.e., donor-control).
-The released individuals are free from any density dependent feedback in natural communities and therefore undermine the internal regulation of self-sustaining communities.
-
-These results were qualitatively consistent across ecological scenarios (XX).
-
-The desta
+Importantly, the reduced mean of community density may arise as long as humans control the number of releases.
+The stability of ecological communities rests on internal density regulation that allows for stable coexistence of competing species.
+For example, significant niche difference in resource use ($\alpha_{ij, i \ne j} < 1$) enables competing species to grow from low population densities because the numerically dominant species undergoes stronger intraspecific competition.
+However, the number of release is not subject to density-dependent feedback.
+The excessive individuals released by humans impose competition that would otherwise not exist and undermine the self-regulation process of stable communities.
+This argument is supported by the fact that the destabilizing effect of selective enhancement manifested even with weak interspecific competition that allows for stable coexistence of competing species.
+Perhaps, the only exception would be a scenario in which the species of interest is on the verge of local extinction with little or no density regulation (i.e., very large carrying capacity).
 
@@
 
-### Methods
+# Methods
 
-### Theory
+## Theory
 
@@
 
-### Empirical analysis
+## Empirical analysis
 
-#### Data
+### Data
 
@@
 
-#### Statistical analysis
+### Statistical analysis
 
@@
 
-## Data availability
+# Data availability
 
-## Acknowledgments
+# Acknowledgments
 
-## References
+# References

### 2021-12-01 rmd/manuscript.Rmd
edit: manuscript

@@
 
+## Theory
+
 We use a multispecies Ricker model to simulate community dynamics with selective enhancement of a constituent species.
@@
 
-EMPIRICAL ANALYSIS
+## Empirical evidence
+
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective enhancement of masu salmon on long-term stability of stream fish communities.
+Masu salmon represents one of the most valuable freshwater resources in Hokkaido Island, Japan, and XX leads extensive hatchery programs across the island.
+In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted over the past two decades along with official records of the number of released fish.
+Hence, this dataset provides an excellent opportunity to evaluate how the selective enhancement influences long-term stability of stream fish communities.
+In this study, we assembled long-term data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).
+
+## Implications
 

### 2021-12-06 rmd/manuscript.Rmd
edit: manuscript

--- 2021-11-30 rmd/manuscript.Rmd
@@
 ---
-title: "Selective enhancement of an exploited species undermines community stability"
+title: "Selective stock enhancement of an exploited species undermines community stability"
 output:
@@
 Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to sustainable management of natural resources.
-Captive breeding - DEFINE CAPTIVE BREEDING - is a common method to conserve or enhance wild populations of diverse plant and animal taxa.
-Although there is growing recognition that the selective enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still pervasive in conservation and fisheries.
-In fisheries for example, XXX have been spent annually to support hatchery programs globally.
+Captive breeding is a common practice to conserve or enhance wild populations of diverse plant and animal taxa.
+Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still pervasive in conservation and fisheries.
+In fisheries for example, XXX have been spent annually to release billions of hatchery-reared individuals globally.
 This is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
-The current debate, however, overlooks the fact that we have rarely assessed the community-wide impact of selective enhancement.
+The current debate, however, overlooks the fact that we have rarely assessed the community-wide impact of selective stock enhancement.
 Species are all embedded in the complex web of interacting organisms, and excessive release of particular species may have unforeseen consequences for ecological communities in the long term.
@@
 
-Here, we use a simple, general theory to show that the selective enhancement of a particular species undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time.
-The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with stream fish communities, in which an exploited species, masu salmon (*Oncorhynchus masou masou*), is supplemented by hatchery programs.
+Here, we use a simple, general theory to show that the selective stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time.
+The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, where XXX of hatchery masu salmon (*Oncorhynchus masou masou*) are released for fisheries, recreation, and conservation purposes.
 Our findings paint a bleak picture for this form of ecosystem management, reinforcing the recurrent calls for alternative strategies.
 
-We use a multispecies Ricker model to simulate community dynamics with selective enhancement of a constituent species.
+## Theory
+
+We use a multispecies Ricker model to simulate community dynamics with selective stock enhancement of a constituent species.
 Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species (species 1; set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1 (set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
 The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species.
@@
 
-Our model predicted a destabilizing effect of selective enhancement on ecological communities.
+Our model predicted a destabilizing effect of selective stock enhancement on ecological communities.
 Increasing numbers of released individuals $R$ led to greater temporal fluctuations of communities as illustrated by increased CV (Figure XX).
@@
 The excessive individuals released by humans impose competition that would otherwise not exist and undermine the self-regulation process of stable communities.
-This argument is supported by the fact that the destabilizing effect of selective enhancement manifested even with weak interspecific competition that allows for stable coexistence of competing species.
+This argument is supported by the fact that the destabilizing effect of selective stock enhancement manifested even with weak interspecific competition that allows for stable coexistence of competing species.
 Perhaps, the only exception would be a scenario in which the species of interest is on the verge of local extinction with little or no density regulation (i.e., very large carrying capacity).
 
-EMPIRICAL ANALYSIS
+## Empirical evidence
+
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon on long-term stability of stream fish communities.
+Masu salmon represents one of the most valuable freshwater resources in Hokkaido Island, Japan, and XX leads extensive hatchery programs across the island.
+In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted with consistent sampling methods over the past two decades along with official records of the number of fish released.
+Therefore, the data set the stage for a "natural experiment" to test the theoretical predictions.
+In this study, we assembled time-series data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).
+Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for other potential confounding factors.
+
+As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released.
+The positive relationship between the CV and the number of fish released was strongly supported by a hierarchical linear model, in which the probability of the regression coefficient being positive was XXX.
+This was associated with the reduced long-term averages of population densities of enhanced (masu salmon) and unenhanced fish groups.
+Both fish groups showed low population densities with high numbers of fish released (STATS), although statistical support for this relationship in the individual fish groups was weak to moderate (STATS).
+In the meantime, the SDs of population densities had vague relationships with the number of fish released, and neither positive or negative relationship was supported by statistical analysis.
+
+Our study system satisfies key theoretical assumptions that are required for the destabilizing effect of selective stock enhancement to emerge.
+The first assumption is that released fish compete with wild fish.
+This type of competition is very likely to occur in the study streams.
+Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that this species compete with other species of stream fish communities.
+In particular, masu salmon raised in hatchery environments are more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild.
+Second, our theory predicts the emergence of destabilizing effect when the number of fish released is externally controlled.
+This is exactly what was observed in our study system.
+In the protected watersheds, there was no apparent congruence between the number of fish released and the population density of masu salmon (XX).
+Instead, these released fish are likely controlled by socioeconomic factors, such as budget allocation to hatchery programs in this region.
+As such, released fish are probably "excessive" given the density-dependent regulation of natural communities, imposing intense resource competition that otherwise would not exist.
+
+Genetic effect XXX
+
+## Implications
+
+Although captive breeding programs carefully consider the fitness of captive-bred individuals in the wild, the debate often ignores the capacity of recipient ecosystems to support biodiversity.
+The results of this study suggest that the ignorance of the ecosystem capacity is critical, undermining the long-term stability of natural communities.
+Our research has two important implications to improve captive breeding programs.
+First, release of captive-bred individuals should be avoided when strong density-dependence operates in the recipient ecosystem.
+Second, we should prioritize the preservation and restoration of recipient ecosystems, which are rapidly degraded due to myriads of human influences.
+Without this integrative management framework that recognizes the fundamental process of biodiversity maintenance, selective stock enhancement will never be effective but will impair biodiversity.
 
@@
 
-We developed a multispecies Ricker model to simulate community dynamics with selective enhancement of a particular species. Population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+We developed a multispecies Ricker model to simulate community dynamics with selective stock enhancement of a particular species.
+Population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
@@
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the stock enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
 The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species.
@@
 We repeated the seeding procedure every 10 time steps over the first 200 time steps to allow species to establish populations and reach an equilibrium without (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next 200 time steps to reach a new equilibrium with selective enhancement (burn-in period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next 200 time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
 We saved the last 1000 time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).

### 2021-12-06 rmd/manuscript.Rmd
edit: manuscript

@@
 Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still pervasive in conservation and fisheries.
-In fisheries for example, XXX have been spent annually to release billions of hatchery-reared individuals globally.
-This is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
+In fisheries for example, XXX have been spent to produce and release XXX billions of hatchery-reared individuals globally.
+The widespread use of captive breeding is perhaps built upon the "myth" that numerical benefits of released individuals may exceed the associated risks.
 The current debate, however, overlooks the fact that we have rarely assessed the community-wide impact of selective stock enhancement.
@@
 Meanwhile, the reduced mean of unenhanced species is caused by interspecific competition between enhanced and unenhanced species.
-Combined, the long-term average of the total community density decreased more sharply than individual species groups with increased numbers of released individuals (XX).
+Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (XX).
 The SDs showed a similar trend, but the relationship was flatter than the mean at the community level.
@@
 
-Importantly, the reduced mean of community density may arise as long as humans control the number of releases.
+Importantly, the reduced mean of community density may arise as long as humans control stock enhancement.
 The stability of ecological communities rests on internal density regulation that allows for stable coexistence of competing species.
@@
 However, the number of release is not subject to density-dependent feedback.
-The excessive individuals released by humans impose competition that would otherwise not exist and undermine the self-regulation process of stable communities.
-This argument is supported by the fact that the destabilizing effect of selective stock enhancement manifested even with weak interspecific competition that allows for stable coexistence of competing species.
-Perhaps, the only exception would be a scenario in which the species of interest is on the verge of local extinction with little or no density regulation (i.e., very large carrying capacity).
-
-## Empirical evidence
+The excessive individuals released by humans impose additional competition that undermines the self-regulation process of stable communities.
+This argument is supported by the fact that the destabilizing effect of selective stock enhancement manifested even with weak interspecific competition that otherwise allows for stable coexistence of competing species.
+Perhaps, the only exception would be a scenario in which the species of interest is on the verge of local extinction with little or no density regulation, i.e., very large carrying capacity relative to the current population density.
 
@@
 Masu salmon represents one of the most valuable freshwater resources in Hokkaido Island, Japan, and XX leads extensive hatchery programs across the island.
-In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted with consistent sampling methods over the past two decades along with official records of the number of fish released.
+In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted with consistent sampling methods over the past two decades along with official records of stock enhancement.
 Therefore, the data set the stage for a "natural experiment" to test the theoretical predictions.
 In this study, we assembled time-series data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).
-Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for other potential confounding factors.
+Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for effects of climates and local abiotic factors.
 
@@
 This type of competition is very likely to occur in the study streams.
-Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that this species compete with other species of stream fish communities.
+Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that this species compete with other species of stream fish.
 In particular, masu salmon raised in hatchery environments are more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild.
@@
 
-Although captive breeding programs carefully consider the fitness of captive-bred individuals in the wild, the debate often ignores the capacity of recipient ecosystems to support biodiversity.
+Although captive breeding programs carefully consider the fitness of captive-bred individuals in the wild, the debate ignores the capacity of recipient ecosystems to support biodiversity.
 The results of this study suggest that the ignorance of the ecosystem capacity is critical, undermining the long-term stability of natural communities.
@@
 First, release of captive-bred individuals should be avoided when strong density-dependence operates in the recipient ecosystem.
-Second, we should prioritize the preservation and restoration of recipient ecosystems, which are rapidly degraded due to myriads of human influences.
-Without this integrative management framework that recognizes the fundamental process of biodiversity maintenance, selective stock enhancement will never be effective but will impair biodiversity.
+XXX Second, we should prioritize the preservation and restoration of recipient ecosystems, which are rapidly degraded due to myriads of human influences.
+XXX Without this integrative framework that recognizes the fundamental process of biodiversity maintenance, selective stock enhancement will never be effective but impairs biodiversity.
 

### 2021-12-16 figure_theory_example.R
Create figure_theory_example.R

@@ -1,0 +1,24 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls(all.names = TRUE))
+
+pacman::p_load(cdyns,
+               tidyverse)
+
+
+# simulation example ------------------------------------------------------
+
+re <- cdynsim(n_species = 3,
+              stock = 150,
+              int_type = "manual",
+              alpha = rbind(c(1.0, 0.1, 0.1),
+                            c(0.4, 1.0, 0.1),
+                            c(0.3, 0.1, 1.0)))
+
+re$df_dyn %>% 
+  filter(timestep < 101) %>% 
+  ggplot(aes(x = timestep,
+             y = density,
+             color = factor(species))) +
+  geom_line()

### 2021-12-16 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Selective stock enhancement of an exploited species undermines community stability"
+title: "Selective stock enhancement undermines community stability"
 output:
@@
 
-Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to sustainable management of natural resources.
+Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to the sustainable management of natural resources.
 Captive breeding is a common practice to conserve or enhance wild populations of diverse plant and animal taxa.
 Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still pervasive in conservation and fisheries.
-In fisheries for example, XXX have been spent to produce and release XXX billions of hatchery-reared individuals globally.
-The widespread use of captive breeding is perhaps built upon the "myth" that numerical benefits of released individuals may exceed the associated risks.
-The current debate, however, overlooks the fact that we have rarely assessed the community-wide impact of selective stock enhancement.
-Species are all embedded in the complex web of interacting organisms, and excessive release of particular species may have unforeseen consequences for ecological communities in the long term.
+In fisheries for example, billions of hatchery-reared individuals are produced and released annually across the globe.
+The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
+
+Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
+Species are all embedded in the complex web of interacting organisms, and excessive release of particular species may have unforeseen consequences for ecological communities by disrupting the sensitive balance of species interactions.
 Evidence for this hypothesis is lacking, however.
 
-Here, we use a simple, general theory to show that the selective stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time.
-The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, where XXX of hatchery masu salmon (*Oncorhynchus masou masou*) are released for fisheries, recreation, and conservation purposes.
-Our findings paint a bleak picture for this form of ecosystem management, reinforcing the recurrent calls for alternative strategies.
+Here, we use a simple, general theory to show that stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time.
+The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, where \>10 millions of hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes.
+Our findings paint a bleak picture for this form of ecosystem management, reinforcing the recurrent calls for alternative management strategies.
 
-## Theory
-
-We use a multispecies Ricker model to simulate community dynamics with selective stock enhancement of a constituent species.
+We used a multispecies Ricker model to simulate community dynamics with selective stock enhancement of a constituent species (species 1).
 Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 $$
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K})]~exp(\epsilon_{i,t})
 $$
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1 (set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
-The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species.
-XX parameter combinations were used to represent ecological scenarios with different strength of competition and XX.
-Under each simulation scenario, we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with varying $R$, of which the last 1000 time steps were used to obtain the coefficient of variation, mean, and standard deviation of community density ($\sum_i^SN_j$).
-Temporal means and standard deviations were calculated for the enhanced species $N_1$ and the unenhanced species $\sum_{i,i \ne 1}^S N_i$ separately to infer mechanisms that underlie community-level responses.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K$ the community-level carrying capacity in the absence of niche difference, $R_t$ the number of released individuals for the enhancement of species 1 (set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
+The parameter $\phi_i$ takes the following values:
 
-Our model predicted a destabilizing effect of selective stock enhancement on ecological communities.
-Increasing numbers of released individuals $R$ led to greater temporal fluctuations of communities as illustrated by increased CV (Figure XX).
+$$
+\phi_i = \left\{
+\begin{array}{}
+f_R & (i = 1)\\
+0 & (i \ne 1)
+\end{array}
+\right.
+$$
+
+$f_R~(\ge 0)$ is the density-independent survival of released individuals relative to wild individuals (the relative fitness).
+Therefore, the model accounts for the reduced fitness of captive-bred individuals due to genetic effects and/or phenotypic plasticity while considering the reproductive contribution of released individuals to the next generation of the enhanced species.
+
+In our simulation, we used XX parameter combinations that represent ecological scenarios with different strength of competition and XX.
+Under each scenario (i.e., parameter combination), we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with varying $R$.
+The last 1000 time steps were used to obtain the coefficient of variation, temporal mean, and temporal standard deviation of total community density ($\sum_i^SN_i$).
+Temporal means and standard deviations were calculated separately for the enhanced species $N_1$ and the unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie community-level responses.
+
+Our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (Figure XX).
 This pattern stemmed mainly from the reduced means of enhanced and unenhanced species groups (Figure XX) that are driven by different mechanisms.
@@
 Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (XX).
-The SDs showed a similar trend, but the relationship was flatter than the mean at the community level.
+The SDs showed a similar trend, but the relationship was flatter at the community level.
 Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density has led to the increased CV.
-These patterns were qualitatively similar across ecological scenarios.
+These patterns were qualitatively similar across ecological scenarios, even when the interspecific competition is sufficiently weak to allow for stable coexistence of competing species in the absence of stock enhancement.
 
-Importantly, the reduced mean of community density may arise as long as humans control stock enhancement.
-The stability of ecological communities rests on internal density regulation that allows for stable coexistence of competing species.
-For example, significant niche difference in resource use ($\alpha_{ij, i \ne j} < 1$) enables competing species to grow from low population densities because the numerically dominant species undergoes stronger intraspecific competition.
-However, the number of release is not subject to density-dependent feedback.
-The excessive individuals released by humans impose additional competition that undermines the self-regulation process of stable communities.
-This argument is supported by the fact that the destabilizing effect of selective stock enhancement manifested even with weak interspecific competition that otherwise allows for stable coexistence of competing species.
-Perhaps, the only exception would be a scenario in which the species of interest is on the verge of local extinction with little or no density regulation, i.e., very large carrying capacity relative to the current population density.
+The destabilizing effect emerges because stock enhancement undermines the balance of species interactions that underpin community stability.
+Stable coexistence of competing species rests largely on niche difference in consumable resource use ($\alpha_{ij, i \ne j} < 1$) because it creates a situation where numerically dominant species undergoes stronger intraspecific competition.
+However, stock enhancement is externally controlled and the number of release is not subject to density-dependent regulation.
+Such excessive individuals impose additional intra- and interspecific competition.
+Consequently, stock enhancement compromises the ecological process giving rise to "overyielding", in which total community density of an ecologically diverse community exceeds what would be expected in a single species community ($\sum_i^SN_i > K$).
+In an extreme scenario, intensive stock enhancement extirpates competing species, reducing biodiversity in the recipient community.
+
+We must note that stock enhancement helps increase the density of the enhanced species when the intrinsic population growth rate is significantly small.
+This result is reasonable because some of the best evidence for successful stock enhancement comes from critically endangered species.
+Even so, community level response was XXX, limiting the .
 
 To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon on long-term stability of stream fish communities.
-Masu salmon represents one of the most valuable freshwater resources in Hokkaido Island, Japan, and XX leads extensive hatchery programs across the island.
+Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and XX leads extensive hatchery programs across the island.
 In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted with consistent sampling methods over the past two decades along with official records of stock enhancement.
-Therefore, the data set the stage for a "natural experiment" to test the theoretical predictions.
+Therefore, the dataset sets the stage for a "natural experiment" to test the theoretical predictions.
 In this study, we assembled time-series data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).
-Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for effects of climates and local abiotic factors.
+Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for confounding effects of climates and local abiotic factors.
 
@@
 Instead, these released fish are likely controlled by socioeconomic factors, such as budget allocation to hatchery programs in this region.
-As such, released fish are probably "excessive" given the density-dependent regulation of natural communities, imposing intense resource competition that otherwise would not exist.
+As such, released fish are probably "excessive" given the density-dependent regulation of natural communities, imposing intense resource competition that would otherwise not exist.
 
-Genetic effect XXX
-
-## Implications
-
-Although captive breeding programs carefully consider the fitness of captive-bred individuals in the wild, the debate ignores the capacity of recipient ecosystems to support biodiversity.
-The results of this study suggest that the ignorance of the ecosystem capacity is critical, undermining the long-term stability of natural communities.
-Our research has two important implications to improve captive breeding programs.
+The results of this study point to two important avenues for biodiversity conservation.
 First, release of captive-bred individuals should be avoided when strong density-dependence operates in the recipient ecosystem.
-XXX Second, we should prioritize the preservation and restoration of recipient ecosystems, which are rapidly degraded due to myriads of human influences.
-XXX Without this integrative framework that recognizes the fundamental process of biodiversity maintenance, selective stock enhancement will never be effective but impairs biodiversity.
+Although captive breeding programs carefully consider the fitness of captive-bred individuals in the wild, it often fails to account for the capacity of recipient ecosystems to support biodiversity.
+Negative density dependence is a general regulating mechanism of biodiversity, and the ignorance of the ecosystem capacity may deteriorate biodiversity, including the supplemented species.
+Therefore, considering this aspect is crucial for saving biodiversity from unexpected effects of stock enhancement.
+Second, we should prioritize the preservation and restoration of ecosystems.
+Myriads of human influences have caused substantial loss and degradation of natural habitats.
+The lack of conservation actions that ameliorate these pressures will impose wild individuals to compete with captive-bred individuals for limited resources, further worsening the current ecosystem state.
+Collectively, without the broader framework that recognizes the regulation process of biodiversity, stock enhancement will never be effective but leads to biodiversity loss.
 

### 2021-12-27 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
-Species are all embedded in the complex web of interacting organisms, and excessive release of particular species may have unforeseen consequences for ecological communities by disrupting the sensitive balance of species interactions.
+Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species underpins emergent stability of ecological communities.
+In this context, stock enhancement represents excessive individuals that deviate from the internal regulation process of self-sustaining communities; therefore, it may disrupt the sensitive balance of species interactions with unforeseen consequences for community dynamics.
 Evidence for this hypothesis is lacking, however.
@@
 Our findings paint a bleak picture for this form of ecosystem management, reinforcing the recurrent calls for alternative management strategies.
+
+## Theoretical prediction
 
@@
 $f_R~(\ge 0)$ is the density-independent survival of released individuals relative to wild individuals (the relative fitness).
-Therefore, the model accounts for the reduced fitness of captive-bred individuals due to genetic effects and/or phenotypic plasticity while considering the reproductive contribution of released individuals to the next generation of the enhanced species.
+Therefore, the model accounts for fitness difference of captive-bred individuals due to genetic effects and/or phenotypic plasticity when considering the reproductive contribution of released individuals to the next generation of the enhanced species.
 
@@
 This pattern stemmed mainly from the reduced means of enhanced and unenhanced species groups (Figure XX) that are driven by different mechanisms.
-For enhanced species, released individuals induced strong overcompensation, where the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals (increased reproducing individuals).
+For enhanced species, released individuals induced strong overcompensation, where the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
 Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals.
@@
 Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density has led to the increased CV.
-These patterns were qualitatively similar across ecological scenarios, even when the interspecific competition is sufficiently weak to allow for stable coexistence of competing species in the absence of stock enhancement.
+These patterns were qualitatively similar across ecological scenarios, even when the interspecific competition is very weak.
 
@@
 Consequently, stock enhancement compromises the ecological process giving rise to "overyielding", in which total community density of an ecologically diverse community exceeds what would be expected in a single species community ($\sum_i^SN_i > K$).
-In an extreme scenario, intensive stock enhancement extirpates competing species, reducing biodiversity in the recipient community.
+In an extreme scenario, intensive stock enhancement extirpated competing species, reducing biodiversity in the recipient community.
 
-We must note that stock enhancement helps increase the density of the enhanced species when the intrinsic population growth rate is significantly small.
+We must note that stock enhancement helps increase the density of the enhanced species when the intrinsic population growth rate is significantly small ($r_1 < 0.5$).
 This result is reasonable because some of the best evidence for successful stock enhancement comes from critically endangered species.
-Even so, community level response was XXX, limiting the .
+Yet, the community-level effect is still destabilizing due to the intensified competition with unenhanced species.
+Therefore, managers should consider the propagating effect of captive breeding when implementing their programs.
+
+## Empirical evidence
 
@@
 In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted with consistent sampling methods over the past two decades along with official records of stock enhancement.
-Therefore, the dataset sets the stage for a "natural experiment" to test the theoretical predictions.
-In this study, we assembled time-series data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).
-Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for confounding effects of climates and local abiotic factors.
+Therefore, the dataset sets the stage for a "natural experiment" to test our theoretical predictions.
+In this study, we used time-series data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).
+Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for potential confounding factors (climates and local abiotic factors).
 
@@
 The positive relationship between the CV and the number of fish released was strongly supported by a hierarchical linear model, in which the probability of the regression coefficient being positive was XXX.
-This was associated with the reduced long-term averages of population densities of enhanced (masu salmon) and unenhanced fish groups.
+This result was associated with the reduced long-term averages of population densities of enhanced (masu salmon) and unenhanced fish groups.
 Both fish groups showed low population densities with high numbers of fish released (STATS), although statistical support for this relationship in the individual fish groups was weak to moderate (STATS).
@@
 
-Our study system satisfies key theoretical assumptions that are required for the destabilizing effect of selective stock enhancement to emerge.
+Our study system satisfies key theoretical assumptions that are required for the destabilizing effect of stock enhancement to emerge.
 The first assumption is that released fish compete with wild fish.
@@
 
-The results of this study point to two important avenues for biodiversity conservation.
-First, release of captive-bred individuals should be avoided when strong density-dependence operates in the recipient ecosystem.
-Although captive breeding programs carefully consider the fitness of captive-bred individuals in the wild, it often fails to account for the capacity of recipient ecosystems to support biodiversity.
-Negative density dependence is a general regulating mechanism of biodiversity, and the ignorance of the ecosystem capacity may deteriorate biodiversity, including the supplemented species.
-Therefore, considering this aspect is crucial for saving biodiversity from unexpected effects of stock enhancement.
-Second, we should prioritize the preservation and restoration of ecosystems.
-Myriads of human influences have caused substantial loss and degradation of natural habitats.
-The lack of conservation actions that ameliorate these pressures will impose wild individuals to compete with captive-bred individuals for limited resources, further worsening the current ecosystem state.
-Collectively, without the broader framework that recognizes the regulation process of biodiversity, stock enhancement will never be effective but leads to biodiversity loss.
+Like any non-experimental studies, we cannot exclude the possibility that our results were driven by spurious correlations.
+However, this is very unlikely because we have controlled potential confounding factors, including climatic and land use variables.
+In addition, our results were in close agreement with theoretical predictions, which are free from any confounding factors.
+Hence, our empirical results are sufficiently reliable.
+
+Although captive breeding programs pay close attention to the fate of captive-bred individuals in the wild, it is rare to consider the ecosystem's capacity to support biodiversity.
+We anticipate that the destabilizing effect of stock enhancement is pervasive across taxa because negative density dependence is a general regulating mechanism of biodiversity.
+In particular, resource competition may be intensified in the Anthropocene because human influences have caused substantial loss and degradation of natural habitats.
+Therefore, one important implication of this study is that priorities should be given to the preservation and restoration of natural habitats with a broader focus on biodiversity.
+For example, recent research underscores the importance of conserving a diverse habitat portfolio that may buffer the impacts of rapid environmental changes.
+Without a comprehensive framework that appreciates the ecological integrity of self-sustaining communities, stock enhancement will never be effective but impairs biodiversity.
 

### 2021-12-29 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 
-Although captive breeding programs pay close attention to the fate of captive-bred individuals in the wild, it is rare to consider the ecosystem's capacity to support biodiversity.
-We anticipate that the destabilizing effect of stock enhancement is pervasive across taxa because negative density dependence is a general regulating mechanism of biodiversity.
-In particular, resource competition may be intensified in the Anthropocene because human influences have caused substantial loss and degradation of natural habitats.
-Therefore, one important implication of this study is that priorities should be given to the preservation and restoration of natural habitats with a broader focus on biodiversity.
-For example, recent research underscores the importance of conserving a diverse habitat portfolio that may buffer the impacts of rapid environmental changes.
-Without a comprehensive framework that appreciates the ecological integrity of self-sustaining communities, stock enhancement will never be effective but impairs biodiversity.
+## Implications
+
+Although captive breeding programs pay close attention to the fate of captive-bred individuals in the wild, it is rare to consider the self-regulation process of biodiversity.
+The results of this study demonstrate that the ignorance of this critical process will erode the long-term persistence of the recipient community.
+The destabilizing effect of stock enhancement is likely to be pervasive across terrestrial and aquatic taxa because negative density dependence is a general regulating mechanism of biodiversity.
+We anticipate that the undesired influence of stock enhancement may be even more apparent in degraded habitats due to the compromised capacity to support biodiversity.
+Therefore, it is essential for us to shift our focus to the preservation and restoration efforts of natural habitats.
+For example, a modern conservation initiative underscores the importance of conserving a diverse habitat portfolio that may buffer the impacts of rapid environmental changes.
+Without a broader framework that appreciates the ecological integrity of self-sustaining communities, stock enhancement will never be effective but impairs biodiversity.
 

### 2021-12-29 figure_theory_example.R
Delete figure_theory_example.R

@@ -1,24 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-rm(list = ls(all.names = TRUE))
-
-pacman::p_load(cdyns,
-               tidyverse)
-
-
-# simulation example ------------------------------------------------------
-
-re <- cdynsim(n_species = 3,
-              stock = 150,
-              int_type = "manual",
-              alpha = rbind(c(1.0, 0.1, 0.1),
-                            c(0.4, 1.0, 0.1),
-                            c(0.3, 0.1, 1.0)))
-
-re$df_dyn %>% 
-  filter(timestep < 101) %>% 
-  ggplot(aes(x = timestep,
-             y = density,
-             color = factor(species))) +
-  geom_line()

### 2022-01-05 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 param_set <- df_theory %>% 
-  filter(r_min == 0.5) %>% 
+  filter(r_max == 2,
+         alpha != 0.3) %>% 
   distinct(n_species,
@@
            r_type,
+           r1,
            r_min,
@@
 Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
-Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species underpins emergent stability of ecological communities.
-In this context, stock enhancement represents excessive individuals that deviate from the internal regulation process of self-sustaining communities; therefore, it may disrupt the sensitive balance of species interactions with unforeseen consequences for community dynamics.
+Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities.
+Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild.
+Hence, this form of species management may have significant consequences for community dynamics.
 Evidence for this hypothesis is lacking, however.
 
-Here, we use a simple, general theory to show that stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time.
+Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time.
+Our theory illuminates that stock enhancement interferes the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche difference.
 The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, where \>10 millions of hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes.
-Our findings paint a bleak picture for this form of ecosystem management, reinforcing the recurrent calls for alternative management strategies.
-
-## Theoretical prediction
+Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
 
@@
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K$ the community-level carrying capacity in the absence of niche difference, $R_t$ the number of released individuals for the enhancement of species 1 (set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (interspecific competition drawn from an exponential distribution as $\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$ whereas $\alpha_{ii}=1$), $K$ the community-level carrying capacity in the absence of niche difference, $R_t$ the number of released individuals for the enhancement of species 1 (set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that follow an normal distribution with a mean of zero and a standard deviation of $\sigma_{\epsilon}$.
 The parameter $\phi_i$ takes the following values:
@@
 
-In our simulation, we used XX parameter combinations that represent ecological scenarios with different strength of competition and XX.
+In our simulation, we used `r nrow(param_set)` simulation scenarios with varied values of the following ecological parameters: mean strength of interspecific competition $\bar{\alpha}$, intrinsic growth of the enhanced species $r_1$, relative fitness of captive-bred individuals $f_R$, and degree of environmental stochasticity $\sigma_{\epsilon}$.
 Under each scenario (i.e., parameter combination), we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with varying $R$.
@@
 This pattern stemmed mainly from the reduced means of enhanced and unenhanced species groups (Figure XX) that are driven by different mechanisms.
-For enhanced species, released individuals induced strong overcompensation, where the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
+For enhanced species, released individuals induced overcompensation, where the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
 Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals.

### 2022-01-05 code_theory/figure_theory.R
Update figure_theory.R

@@ -14,7 +14,7 @@ df0 <- read_csv("result/result_ricker.csv") %>%
                names_to = "param",
                values_to = "value") %>% 
   filter(r_max == 2,
-         r_min == 0.3,
+         r1 == 1,
          sd_env == 0.5,
          alpha == 0.5,
          phi == 0.8,
@@ -40,10 +40,10 @@ g_theory <- df0 %>%
              x = stock,
              color = factor(status_name),
              fill = factor(status_name))) +
-  geom_point(data = filter(df0, status == "stocked"),
+  geom_point(data = filter(df0, status == "enhanced"),
              size = 0.25,
              color = "darkseagreen2") +
-  geom_point(data = filter(df0, status == "unstocked"),
+  geom_point(data = filter(df0, status == "unenhanced"),
              size = 0.25,
              color = "lightskyblue2") +
   geom_point(data = filter(df0, status == "all"),

### 2022-01-14 rmd/manuscript.Rmd
edit: manuscript

@@
 df_theory <- read_csv(here::here("code_theory/result/result_ricker.csv"))
+
+n_sim <- df_theory %>% 
+  mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
+  pull(n_sim) %>% 
+  unique()
 
@@
 
-Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to the sustainable management of natural resources.
-Captive breeding is a common practice to conserve or enhance wild populations of diverse plant and animal taxa.
-Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still pervasive in conservation and fisheries.
-In fisheries for example, billions of hatchery-reared individuals are produced and released annually across the globe.
+Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to the sustainable management of natural resources [@cardinaleBiodiversityLossIts2012].
+Captive breeding is a common practice to conserve or enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996].
+Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007a; @snyderLimitationsCaptiveBreeding1996; @griffithsCaptiveBreedingReintroduction2008], this method is still pervasive in conservation and fisheries.
+In fisheries for example, billions of hatchery-reared individuals are produced and released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
 The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
@@
 Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
-Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities.
+Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a].
 Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild.
@@
 
-Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time.
-Our theory illuminates that stock enhancement interferes the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche difference.
-The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, where \>10 millions of hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes.
+Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a].
+Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences.
+The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, where \>10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes.
 Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
 
-We used a multispecies Ricker model to simulate community dynamics with selective stock enhancement of a constituent species (species 1).
+## Theoretical predictions
+
+We used a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with selective stock enhancement of a constituent species (species 1).
 Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (interspecific competition drawn from an exponential distribution as $\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$ whereas $\alpha_{ii}=1$), $K$ the community-level carrying capacity in the absence of niche difference, $R_t$ the number of released individuals for the enhancement of species 1 (set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that follow an normal distribution with a mean of zero and a standard deviation of $\sigma_{\epsilon}$.
-The parameter $\phi_i$ takes the following values:
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (interspecific competition drawn from an exponential distribution as $\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$ whereas intraspecific competition $\alpha_{ii}=1$), $K$ the community-level carrying capacity in the absence of niche difference, $R_t$ the number of released individuals for the enhancement of species 1 (set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that follow an normal distribution with a mean of zero and a standard deviation of $\sigma_{\epsilon}$.
+The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
 
@@
 
-$f_R~(\ge 0)$ is the density-independent survival of released individuals relative to wild individuals (the relative fitness).
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals.
 Therefore, the model accounts for fitness difference of captive-bred individuals due to genetic effects and/or phenotypic plasticity when considering the reproductive contribution of released individuals to the next generation of the enhanced species.
@@
 In our simulation, we used `r nrow(param_set)` simulation scenarios with varied values of the following ecological parameters: mean strength of interspecific competition $\bar{\alpha}$, intrinsic growth of the enhanced species $r_1$, relative fitness of captive-bred individuals $f_R$, and degree of environmental stochasticity $\sigma_{\epsilon}$.
-Under each scenario (i.e., parameter combination), we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with varying $R$.
-The last 1000 time steps were used to obtain the coefficient of variation, temporal mean, and temporal standard deviation of total community density ($\sum_i^SN_i$).
+Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(df_theory$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$.
+The last `r unique(df_theory$n_timestep)` time steps were used to obtain the coefficient of variation, temporal mean, and temporal standard deviation of total community density ($\sum_i^SN_i$).
 Temporal means and standard deviations were calculated separately for the enhanced species $N_1$ and the unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie community-level responses.
@@
 This pattern stemmed mainly from the reduced means of enhanced and unenhanced species groups (Figure XX) that are driven by different mechanisms.
-For enhanced species, released individuals induced overcompensation, where the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
+For enhanced species, released individuals induced overcompensation, where the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals [@satakeStockingCaptivebredFish2012].
 Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals.
-Meanwhile, the reduced mean of unenhanced species is caused by interspecific competition between enhanced and unenhanced species.
+Meanwhile, interspecific competition between enhanced and unenhanced species caused the reduced mean of unenhanced species, leading to decreased numbers of persisting species at high levels of stock enhancement.
 Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (XX).
@@
 The destabilizing effect emerges because stock enhancement undermines the balance of species interactions that underpin community stability.
-Stable coexistence of competing species rests largely on niche difference in consumable resource use ($\alpha_{ij, i \ne j} < 1$) because it creates a situation where numerically dominant species undergoes stronger intraspecific competition.
+Stable coexistence of competing species rests largely on niche difference in consumable resource use ($\alpha_{ij, i \ne j} < 1$) because it creates a situation where numerically dominant species undergoes stronger intraspecific competition [@lettenLinkingModernCoexistence2017].
 However, stock enhancement is externally controlled and the number of release is not subject to density-dependent regulation.
 Such excessive individuals impose additional intra- and interspecific competition.
-Consequently, stock enhancement compromises the ecological process giving rise to "overyielding", in which total community density of an ecologically diverse community exceeds what would be expected in a single species community ($\sum_i^SN_i > K$).
-In an extreme scenario, intensive stock enhancement extirpated competing species, reducing biodiversity in the recipient community.
+Consequently, stock enhancement compromised the ecological process giving rise to "overyielding" [@tilmanEcologicalConsequencesChanges1999a], in which total community density of an ecologically diverse community exceeds what would be expected in a single species community ($\sum_i^SN_i > K$).
 
-We must note that stock enhancement helps increase the density of the enhanced species when the intrinsic population growth rate is significantly small ($r_1 < 0.5$).
-This result is reasonable because some of the best evidence for successful stock enhancement comes from critically endangered species.
+We must note that stock enhancement helps increase the density of the enhanced species when the intrinsic population growth rate is significantly small ($r_1 = 0.5$).
+This result is reasonable because some of the best evidence for successful stock enhancement comes from critically endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
 Yet, the community-level effect is still destabilizing due to the intensified competition with unenhanced species.
-Therefore, managers should consider the propagating effect of captive breeding when implementing their programs.
+It is therefore critical to consider the propagating effect when implementing captive breeding programs.
 
@@
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon on long-term stability of stream fish communities.
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon on the long-term stability of stream fish communities.
 Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and XX leads extensive hatchery programs across the island.
-In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted with consistent sampling methods over the past two decades along with official records of stock enhancement.
-Therefore, the dataset sets the stage for a "natural experiment" to test our theoretical predictions.
+In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted with consistent sampling methods over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018].
+Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
 In this study, we used time-series data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).
-Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for potential confounding factors (climates and local abiotic factors).
+Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for potential confounding effects of climates and local abiotic factors.
 
@@
 The positive relationship between the CV and the number of fish released was strongly supported by a hierarchical linear model, in which the probability of the regression coefficient being positive was XXX.
-This result was associated with the reduced long-term averages of population densities of enhanced (masu salmon) and unenhanced fish groups.
-Both fish groups showed low population densities with high numbers of fish released (STATS), although statistical support for this relationship in the individual fish groups was weak to moderate (STATS).
+This pattern was associated with the reduced long-term averages of population densities of enhanced (masu salmon) and unenhanced fish groups, although statistical support for this relationship was weak to moderate (STATS).
 In the meantime, the SDs of population densities had vague relationships with the number of fish released, and neither positive or negative relationship was supported by statistical analysis.
+These results are in good agreement with previous studies.
+Negative or vague population response to stock enhancement has been widely observed in other fish and invertebrate species, implying limited effectiveness of this method as a management tool.
+Our analysis of long-term community data further illuminated the potential negative impact of stock enhancement on unenhanced species and expanded our understanding to community-level response to stock enhancement.
 
-Our study system satisfies key theoretical assumptions that are required for the destabilizing effect of stock enhancement to emerge.
-The first assumption is that released fish compete with wild fish.
-This type of competition is very likely to occur in the study streams.
-Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that this species compete with other species of stream fish.
-In particular, masu salmon raised in hatchery environments are more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild.
-Second, our theory predicts the emergence of destabilizing effect when the number of fish released is externally controlled.
-This is exactly what was observed in our study system.
-In the protected watersheds, there was no apparent congruence between the number of fish released and the population density of masu salmon (XX).
-Instead, these released fish are likely controlled by socioeconomic factors, such as budget allocation to hatchery programs in this region.
-As such, released fish are probably "excessive" given the density-dependent regulation of natural communities, imposing intense resource competition that would otherwise not exist.
+In our theory, the observed pattern emerges when negative density dependence operates in the recipient community, and this assumption is well supported by previous observations.
+Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that released masu salmon compete with wild individuals of masu salmon [@sahashiEvaluationContributionHatchery2015a] and other stream fishes [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018].
+In particular, masu salmon raised in hatchery environments are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018].
+Importantly, the number of fish released is likely controlled by socioeconomic factors (e.g., budget allocation) because there was no apparent congruence between the number of fish released and the population density of masu salmon (XX).
+As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may impose resource competition that would otherwise not exist.
+
+Reduced fitness of captive-bred individuals may also play a role in producing the observed community response.
+As with other salmonid species, ocean-migrating adults of captive-bred masu salmon show lower return rates to the spawning river and therefore less contribute to the next generation (miyakoshi?).
+These processes, i.e., negative density dependence and fitness disadvantage of captive-bred fish, may act in concert to reduce the long-term average of community density, undermining community stability in the long term.
 
 Like any non-experimental studies, we cannot exclude the possibility that our results were driven by spurious correlations.
-However, this is very unlikely because we have controlled potential confounding factors, including climatic and land use variables.
-In addition, our results were in close agreement with theoretical predictions, which are free from any confounding factors.
-Hence, our empirical results are sufficiently reliable.
+However, in the protected watersheds, any exploitation of aquatic species and alteration of in-stream habitats (e.g., construction of river-crossing structure) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences played a major role in the observed relationships.
+Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables.
+Hence, we are confident in our statistical inference, and this unique study setup may have helped produce the close agreement between theory and empirical patterns.
 
@@
 The results of this study demonstrate that the ignorance of this critical process will erode the long-term persistence of the recipient community.
-The destabilizing effect of stock enhancement is likely to be pervasive across terrestrial and aquatic taxa because negative density dependence is a general regulating mechanism of biodiversity.
-We anticipate that the undesired influence of stock enhancement may be even more apparent in degraded habitats due to the compromised capacity to support biodiversity.
-Therefore, it is essential for us to shift our focus to the preservation and restoration efforts of natural habitats.
+The destabilizing effect of stock enhancement is likely to be pervasive across terrestrial and aquatic taxa because negative density dependence is a general regulating mechanism of ecological communities.
+
+We anticipate that the undesired influence of stock enhancement may be more apparent in degraded habitats as the compromised capacity to support biodiversity may impose greater competition among constituent species.
+Therefore, we should shift our management efforts to the preservation and restoration of natural habitats with a broader scope to conserve biodiversity.
 For example, a modern conservation initiative underscores the importance of conserving a diverse habitat portfolio that may buffer the impacts of rapid environmental changes.
-Without a broader framework that appreciates the ecological integrity of self-sustaining communities, stock enhancement will never be effective but impairs biodiversity.
+Without a comprehensive framework that appreciates the ecological integrity of self-sustaining communities, stock enhancement will never be effective but impairs biodiversity.
 
@@
 
-We developed a multispecies Ricker model to simulate community dynamics with selective stock enhancement of a particular species.
+We developed a multispecies Ricker model to simulate community dynamics with selective stock enhancement of a constituent species (species 1).
 Population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 $$
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t})
+N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K})]exp(\epsilon_{i,t})
 $$
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the stock enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations.
-The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species.
-The species-specific intrinsic growth rates and competition coefficients were drawn randomly from a uniform and exponential distribution, respectively, to allow for interspecific variation as $r_i \sim Unif(0.5, r_{max})$ and $\alpha_{ij, i \ne j} \sim Exp(\mu_{\alpha})$.
-The number of released individuals was assumed to be constant across time steps ($R_t = R$).
-Environmental stochasticity was drawn from a normal distribution as $\epsilon_{i,t} \sim Normal(\mu_{\epsilon}, \sigma_{\epsilon}^2)$
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K$ the community-level carrying capacity in the absence of niche difference, $R_t$ the number of released individuals for the stock enhancement of species 1 (set constant as $R_t = R$), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that obey an normal distribution with a mean of zero and a standard deviation of $\sigma_{\epsilon}$.
+The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
 
-We varied values of four parameters: $S =$ `r unique(param_set$n_species)`; $r_{max}=$ `r unique(param_set$r_max)`; $\mu_{\alpha} =$ `r unique(param_set$alpha)`; $\sigma_\epsilon =$ `r unique(param_set$sd_env)`.
-For simplicity, we assumed identical carrying capacities among simulated species as $K_i =$ `r unique(param_set$k)`.
-This setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
+$$
+\phi_i = \left\{
+\begin{array}{}
+f_R & (i = 1)\\
+0 & (i \ne 1)
+\end{array}
+\right.
+$$
 
-Under each parameter combination, we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with the gradient of the number of released individuals $R$ (0 - 500).
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals.
+
+We varied values of the following ecological parameters: mean strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), intrinsic growth of the enhanced species ($r_1 =$ `r unique(param_set$r1)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`), and degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).
+Other parameters were set constant or drawn randomly from a probability distribution: $S=$ `r unique(param_set$n_species)` , $K=$ `r unique(param_set$k)` , $r_i =$ $Unif$(`r unique(param_set$r_min)` , `r unique(param_set$r_max)`) ($i \ne 1$), $\alpha_{ii} = 1$, $\alpha_{ij,i \ne j} \sim Exp(\bar{\alpha})$.
+This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
+
+Under each parameter combination, we ran `r n_sim` time steps of `r max(df_theory$n_rep)` independent communities (i.e., simulation replicates).
+The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
 We initialized the community with populations of each species drawn from a poisson distribution with a mean of five.
-We repeated the seeding procedure every 10 time steps over the first 200 time steps to allow species to establish populations and reach an equilibrium without (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next 200 time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
-We saved the last 1000 time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).
+We repeated the seeding procedure every 10 time steps over the first `r unique(df_theory$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(df_theory$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
+After the burn-in period, we continued the simulation run with stock enhancement and saved the last `r unique(df_theory$n_timestep)` time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).
 We also calculated temporal means and standard deviations for each species group.
@@
 After careful data selection (Supporting Information), we used time-series data of fish abundance at XX sites during a period of 1999-2019.
-ADD SOME DETAILS
 
@@
 We examined historical records of fish stocking and obtained annual stocking data (the number of individuals released) for a period of 1999-2019 at each watershed.
-We were unable to extract stocking data at the site level.
+Although fish were released at multiple locations within a watershed, we were unable to extract stocking data at the site level.
 
-**Environmental data.** At each sampling site,we collected the following data as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture, urban), local species richness, local climates (annual mean air temperature [unit] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
+**Environmental data.** At each sampling site, we collected the following data as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture, urban), local climates (annual mean air temperature [unit] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
+Annual data of ocean productivity (2003-2019) were extracted from OceanColor (<https://oceancolor.gsfc.nasa.gov/>) and the averaged value within the 30-km radius of each river mouth was calculated.
 
@@
 Our goal is to compare temporal dynamics of fish communities across sites.
-However, the data are not directly comparable because of artificial observation errors (e.g., different observers) and missing observations.
+However, the data are not directly comparable because of observation errors (e.g., different observers) and missing observations.
 To confront this challenge, we developed Bayesian state space models for three species groups separately: (1) whole community, summed abundance of all species, (2) enhanced species, abundance of masu salmon, (3) unenhanced species, summed abundance of all species except masu salmon.
-Bayesian state space models is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at the site.
+Bayesian state space models is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site.
 The model is composed of observation and state models as described below.
@@
 The inclusion of this random variable allows us to account for site-specific and year-specific observation errors.
-The parameter $\psi$ equals one when we model the unenhanced species group (otherwise $\psi = 1$).
-We included $\psi$ to exclude the term $\beta~Fry_{w(j),t}$ because the unenhanced species group does not include masu salmon.
+The parameter $\psi$ equals zero when we model the unenhanced species group (otherwise $\psi = 1$).
+We included $\psi$ to exclude the term $\beta_s~Fry_{w(j),t}$ because the unenhanced species group does not include masu salmon.
 
@@
 ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
-$$where $ln~r_{s}$ is the average rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
+$$where $ln~r_{s}$ is the site-specific rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
 The site-specific rate of change is random draws from a normal distribution as $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).

### 2022-01-19 rmd/manuscript.Rmd
edit: manuscript

@@
 # theory infomation
-df_theory <- read_csv(here::here("code_theory/result/result_ricker.csv"))
+df_theory <- read_csv(here::here("result/result_ricker.csv"))
 
@@
 Captive breeding is a common practice to conserve or enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996].
-Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007a; @snyderLimitationsCaptiveBreeding1996; @griffithsCaptiveBreedingReintroduction2008], this method is still pervasive in conservation and fisheries.
-In fisheries for example, billions of hatchery-reared individuals are produced and released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
+Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007a; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996; @griffithsCaptiveBreedingReintroduction2008; @haagNorthAmericanFreshwater2012] and fisheries [@kitadaEconomicEcologicalGenetic2018; @arakiHatcheryStockingHelp2010].
+In fisheries for example, billions of hatchery-reared individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
 The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
@@
 Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
-Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a].
-Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild.
-Hence, this form of species management may have significant consequences for community dynamics.
+Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
+Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012].
+Hence, this form of species management may have significant consequences for community dynamics in the long term.
 Evidence for this hypothesis is lacking, however.
@@
 Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences.
-The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, where \>10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes.
+The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \>10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].
 Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
@@
 $$
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K})]~exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]~exp(\epsilon_{i,t})
 $$
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (interspecific competition drawn from an exponential distribution as $\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$ whereas intraspecific competition $\alpha_{ii}=1$), $K$ the community-level carrying capacity in the absence of niche difference, $R_t$ the number of released individuals for the enhancement of species 1 (set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that follow an normal distribution with a mean of zero and a standard deviation of $\sigma_{\epsilon}$.
+where $r_i$ is the intrinsic growth rate (drawn from a uniform distribution as $r_i \sim Unif(0,2)$ except $r_1$), $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ [drawn from an exponential distribution as $\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$; intraspecific competition $\alpha_{ii}=1$], $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that follow an normal distribution with a mean of zero and a standard deviation of $\sigma_{\epsilon}$.
 The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
@@
 $f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals.
-Therefore, the model accounts for fitness difference of captive-bred individuals due to genetic effects and/or phenotypic plasticity when considering the reproductive contribution of released individuals to the next generation of the enhanced species.
+Therefore, the model accounts for fitness difference of captive-bred individuals due to genetic effects and/or plasticity [@weberInteractionsHatcheryWild2003; @snyderLimitationsCaptiveBreeding1996; @arakiHatcheryStockingHelp2010] when considering the reproductive contribution of released individuals to the next generation of the enhanced species.
+Without loss of generality, we assumed constant $K_i$ ($K_i = K$) and $R_t$ ($R_t = R$) across species and time, respectively.
 
-In our simulation, we used `r nrow(param_set)` simulation scenarios with varied values of the following ecological parameters: mean strength of interspecific competition $\bar{\alpha}$, intrinsic growth of the enhanced species $r_1$, relative fitness of captive-bred individuals $f_R$, and degree of environmental stochasticity $\sigma_{\epsilon}$.
-Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(df_theory$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$.
+In our simulation, we used `r nrow(param_set)` simulation scenarios with varied values of the following ecological parameters: intrinsic growth of the enhanced species $r_1$, mean strength of interspecific competition $\bar{\alpha}$, carrying capacity $K$, relative fitness of captive-bred individuals $f_R$, and degree of environmental stochasticity $\sigma_{\epsilon}$.
+Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(df_theory$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$).
 The last `r unique(df_theory$n_timestep)` time steps were used to obtain the coefficient of variation, temporal mean, and temporal standard deviation of total community density ($\sum_i^SN_i$).
-Temporal means and standard deviations were calculated separately for the enhanced species $N_1$ and the unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie community-level responses.
+Temporal means and standard deviations were calculated separately for the enhanced species $N_1$ and unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie the community-level response.
 
-Our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (Figure XX).
-This pattern stemmed mainly from the reduced means of enhanced and unenhanced species groups (Figure XX) that are driven by different mechanisms.
-For enhanced species, released individuals induced overcompensation, where the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals [@satakeStockingCaptivebredFish2012].
-Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals.
-Meanwhile, interspecific competition between enhanced and unenhanced species caused the reduced mean of unenhanced species, leading to decreased numbers of persisting species at high levels of stock enhancement.
+In general, our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (Figure XX).
+This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible for this result.
+For enhanced species, released individuals induced overcompensation, in which the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
+Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals, confirming previous theoretical predictions [@satakeStockingCaptivebredFish2012].
+Meanwhile, interspecific competition caused the reduced mean density of unenhanced species and led to decreased numbers of persisting species at high levels of stock enhancement.
 Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (XX).
 The SDs showed a similar trend, but the relationship was flatter at the community level.
-Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density has led to the increased CV.
-These patterns were qualitatively similar across ecological scenarios, even when the interspecific competition is very weak.
+Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density resulted in the increased CV.
+These patterns were qualitatively similar across most ecological scenarios, even when the interspecific competition is very weak (XX).
 
 The destabilizing effect emerges because stock enhancement undermines the balance of species interactions that underpin community stability.
-Stable coexistence of competing species rests largely on niche difference in consumable resource use ($\alpha_{ij, i \ne j} < 1$) because it creates a situation where numerically dominant species undergoes stronger intraspecific competition [@lettenLinkingModernCoexistence2017].
+Ecological theory suggests that stable coexistence of competing species requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a].
+Under this condition, competing species can grow from small populations because numerically dominant species undergoes stronger intraspecific competition [@carrollNicheFitnessDifferences2011a].
+Such stable coexistence increases the likelihood of stabilizing temporal dynamics of species rich communities [@tilmanEcologicalConsequencesChanges1999a] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], that is, total community density of a multi-species community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$).
 However, stock enhancement is externally controlled and the number of release is not subject to density-dependent regulation.
-Such excessive individuals impose additional intra- and interspecific competition.
-Consequently, stock enhancement compromised the ecological process giving rise to "overyielding" [@tilmanEcologicalConsequencesChanges1999a], in which total community density of an ecologically diverse community exceeds what would be expected in a single species community ($\sum_i^SN_i > K$).
+Therefore, excessive individuals supplemented through stock enhancement impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.
 
-We must note that stock enhancement helps increase the density of the enhanced species when the intrinsic population growth rate is significantly small ($r_1 = 0.5$).
+The only scenario where stock enhancement had little influences on community dynamics was when carrying capacity was sufficiently large ($K=500$).
+In particular, stock enhancement increased, albeit slightly, the average density of the enhanced species with low population growth rate ($r_1=0.5$).
 This result is reasonable because some of the best evidence for successful stock enhancement comes from critically endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
-Yet, the community-level effect is still destabilizing due to the intensified competition with unenhanced species.
-It is therefore critical to consider the propagating effect when implementing captive breeding programs.
+In the meantime, our theoretical analysis also illuminates limitation of stock enhancement as a primary tool of ecosystem management.
+Habitat loss and fragmentation have severely reduced biodiversity, and one of the primary motivations for stock enhancement is to mitigate or reverse such a trend.
+However, stock enhancement will not bring desired ecological outcomes unless we address the root causes of habitat degradation and restore environmental capacity to support biodiversity.
 
@@
 Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that released masu salmon compete with wild individuals of masu salmon [@sahashiEvaluationContributionHatchery2015a] and other stream fishes [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018].
-In particular, masu salmon raised in hatchery environments are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018].
+Hatchery-reared salmons are larger and more aggressive than wild individuals, further increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003].
 Importantly, the number of fish released is likely controlled by socioeconomic factors (e.g., budget allocation) because there was no apparent congruence between the number of fish released and the population density of masu salmon (XX).
@@
 As with other salmonid species, ocean-migrating adults of captive-bred masu salmon show lower return rates to the spawning river and therefore less contribute to the next generation (miyakoshi?).
-These processes, i.e., negative density dependence and fitness disadvantage of captive-bred fish, may act in concert to reduce the long-term average of community density, undermining community stability in the long term.
+It has also been shown that hatchery-reared salmons are more susceptible to predation than wild salmons [@weberInteractionsHatcheryWild2003].
+The fitness disadvantage of captive-bred fish may interact with negative density dependence to reduce the long-term average of community density, undermining community stability in the long term.
 
@@
 
-Although captive breeding programs pay close attention to the fate of captive-bred individuals in the wild, it is rare to consider the self-regulation process of biodiversity.
-The results of this study demonstrate that the ignorance of this critical process will erode the long-term persistence of the recipient community.
-The destabilizing effect of stock enhancement is likely to be pervasive across terrestrial and aquatic taxa because negative density dependence is a general regulating mechanism of ecological communities.
+The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996].
+As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations of enhanced species [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007a].
+Despite the significant attention to the fate of captive-bred individuals, it is rare to consider the self-regulation process of biodiversity.
+The results of this study suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community.
+While our empirical example is limited to stream fish communities, the consistent emergence of destabilizing effect across simulated ecological scenarios implies that this ecological phenomenon is pervasive across terrestrial and aquatic taxa.
 
-We anticipate that the undesired influence of stock enhancement may be more apparent in degraded habitats as the compromised capacity to support biodiversity may impose greater competition among constituent species.
-Therefore, we should shift our management efforts to the preservation and restoration of natural habitats with a broader scope to conserve biodiversity.
-For example, a modern conservation initiative underscores the importance of conserving a diverse habitat portfolio that may buffer the impacts of rapid environmental changes.
-Without a comprehensive framework that appreciates the ecological integrity of self-sustaining communities, stock enhancement will never be effective but impairs biodiversity.
+We should prioritize the preservation and restoration efforts of natural habitats with a broader scope of biodiversity conservation.
+In particular, such efforts are crucial given that the undesired influence of stock enhancement is predicted to be exacerbated in degraded habitats due to the compromised capacity to support biodiversity (XX).
+It has been shown that protected areas and environmental restoration are promising tools to conserve biodiversity, and the effective spatial design is a key to achieve successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017].
+For example, coordinated placement of conservation sites considering spatial biodiversity patterns is of critical importance in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013].
+Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
+These considerable potentials indicate that we have viable management options for the sustainable future of biodiversity and natural resources before blindly accepting stock enhancement programs.
+Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.
 

### 2022-01-21 rmd/supporting_info.Rmd
Create supporting_info.Rmd

---
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
bibliography: reference.bib
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
header-includes:
  \pagenumbering{gobble}
---

```{r setup, include=FALSE}

pacman::p_load(knitr)

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE)
options(knitr.kable.NA = '')

```

\newpage

# Tables

```{r table_set1}

## load data for tables
source(here::here("code/table_reg.R"))

table_legend <- "Median estimates and standard errors (SEs) are shown. Pr(> 0) and Pr(< 0) represent the proportion of parameter estimates (MCMC samples) being positive and negative, respectively (i.e., posterior probability)."

table_reg <- NULL

for(i in seq_len(length(df_est))) {

  if(name[i] == "all") {
    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of whole community \n",
                         table_legend,
                         "\n```{r table_s", i,"}
                         \n\n
                         kable(df_est[[",i,"]], format = 'markdown')
                         \n\n
                         ```\n",
                         "\n\\pagebreak\n")
  }

  if(name[i] == "masu") {
    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of masu salmon \n",
                         table_legend,
                         "\n```{r table_s", i,"}
                         \n\n
                         kable(df_est[[",i,"]], format = 'markdown')
                         \n\n
                         ```\n",
                         "\n\\pagebreak\n")
  }

  if(name[i] == "other") {
    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of unenhanced species \n",
                         table_legend,
                         "\n```{r table_s", i,"}
                         \n\n
                         kable(df_est[[",i,"]], format = 'markdown')
                         \n\n```
                         \n",
                         "\n\\pagebreak\n")
  }

  table_reg <- c(table_reg, knit_chunk)
}

```

`r paste(knit(text = table_reg), collapse = '\n')`

# Figures

### 2022-01-21 rmd/title.tex
Create title.tex

%\begin{titlepage}
\begin{flushleft}
\LARGE{\textbf{Supporting Information for: \newline Selective stock enhancement undermines community stability}}\\
\vspace*{\baselineskip}
\large{Akira Terui$^{*,1}$, Hirokazu Urabe$^2$, Masayuki Senzaki$^3$, Bungo Nishizawa$^4$}\\
\vspace*{1\baselineskip}
\normalsize{*Corresponding author \newline Email: hanabi0111@gmail.com}\\
\vspace*{1\baselineskip}
\normalsize{
$^1$ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA \newline
$^2$ XXX \newline
$^3$ XXX \newline
$^4$ XXX}\\
\vspace*{2\baselineskip}
\textbf{This PDF file includes:}
\begin{itemize}
\item Supplementary text
\item XX
\item XX
\item SI References
\end{itemize}
\end{flushleft}
% \end{titlepage}

\newpage

### 2022-01-21 code/table_reg.R
Update table_reg.R

@@ -1,0 +1,71 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+pacman::p_load(tidyverse)
+
+op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x) 
+
+
+# data for tables ---------------------------------------------------------
+
+filename <- list.files(path = here::here("result"),
+                       full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "reg")) %>% 
+  pull()
+
+name <- str_extract(filename, pattern = "all|masu|other")
+
+df_est <- lapply(filename, function(x) {
+  
+  if (str_detect(x, pattern = "masu|other")) {
+    df0 <- read_csv(x) %>% 
+      filter(response != "cv")
+  } else {
+    df0 <- read_csv(x)
+  }
+  
+  df_m <- df0 %>% 
+    filter(!(str_detect(string = .$parameter,
+                        pattern = "sigma|b_raw"))) %>% 
+    dplyr::select(response,
+                  parameter,
+                  median,
+                  sd,
+                  prob_positive) %>% 
+    mutate(prob_negative = 1 - prob_positive,
+           Parameter = case_when(parameter == "a[1]" ~ "$\\beta_1$",
+                                 parameter == "a[2]" ~ "$\\beta_2$",
+                                 parameter == "a[3]" ~ "$\\beta_3$",
+                                 parameter == "a[4]" ~ "$\\beta_4$",
+                                 parameter == "b[1]" ~ "$\\gamma_0$",
+                                 parameter == "b[2]" ~ "$\\gamma_1$",
+                                 parameter == "b[3]" ~ "$\\gamma_2$"),
+           Effect = case_when(parameter == "a[1]" ~ "Watershed area",
+                              parameter == "a[2]" ~ "Air temperature",
+                              parameter == "a[3]" ~ "Precipitation",
+                              parameter == "a[4]" ~ "Forest fraction",
+                              parameter == "a[5]" ~ "Forest fraction",
+                              parameter == "b[1]" ~ "Intercept",
+                              parameter == "b[2]" ~ "Stock enhancement",
+                              parameter == "b[3]" ~ "Ocean productivity"),
+           Response = ifelse(parameter == "b[1]", response, NA),
+           Response = case_when(Response == "cv" ~ "CV",
[…]

### 2022-01-21 code/run_sensitivity.R
Create run_sensitivity.R

@@ -1,0 +1,109 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls(all.names = TRUE))
+
+pacman::p_load(here,
+               cdyns,
+               tidyverse,
+               foreach,
+               doParallel,
+               doSNOW)
+
+cl <- makeCluster(detectCores())
+registerDoSNOW(cl)
+
+# set parameters ----------------------------------------------------------
+
+n_para <- 500
+df_param <- tibble(n_timestep = 1000,
+                   n_warmup = 200,
+                   n_burnin = 400,
+                   n_species = round(runif(n_para, 5, 20)),
+                   k = runif(n_para, 100, 1000),
+                   r_type = "constant",
+                   r1 = runif(n_para, 0.5, 2.5),
+                   r_min = 0.5,
+                   r_max = runif(n_para, 0.5, 2.5),
+                   sd_env = runif(n_para, 0.05, 0.5),
+                   phi = runif(n_para, 0.5, 1),
+                   int_type = "random",
+                   alpha = runif(n_para, 0.01, 0.5),
+                   model = "ricker",
+                   seed = 5,
+                   seed_interval = 10)
+
+n_rep <- 100
+repeat {
+  stock <- round(runif(n_rep, min = 0, max = 500))
+  if(min(stock) == 0 & max(stock) == 500) break    
+}
+
+# run simulation ----------------------------------------------------------
+
+pb <- txtProgressBar(max = nrow(df_param), style = 3)
+fun_progress <- function(n) setTxtProgressBar(pb, n)
+opts <- list(progress = fun_progress)
+
+result <- foreach(x = iter(df_param, by = 'row'),
+                  .combine = "bind_rows",
+                  .packages = c("foreach", "dplyr", "cdyns"),
+                  .options.snow = opts) %dopar% {
+                    
+                    df_set <- foreach(j = seq_len(n_rep),
+                                      .combine = "bind_rows") %do% {
+                                        
+                                        dyn <- cdynsim(n_timestep = x$n_timestep,
+                                                       n_warmup = x$n_warmup,
+                                                       n_burnin = x$n_burnin,
+                                                       n_species = x$n_species,
+                                                       k = x$k,
+                                                       r_type = x$r_type,
+                                                       r = c(x$r1, runif(n = x$n_species - 1,
+                                                                         x$r_min, x$r_max)),
+                                                       sd_env = x$sd_env,
+                                                       stock = stock[j],
+                                                       phi = x$phi,
+                                                       int_type = x$int_type,
[…]

### 2022-01-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
+source(here::here("code/table_stvy_analysis.R"))
+
 ```
@@
 
-```{r table_set1}
+```{r table_sensitivity, results="asis"}
+
+conditional_text <- c("whole community",
+                      "enhanced species",
+                      "unenhanced species")
+
+table_sense <- knit_chunk <- NULL
+
+for(i in 1:length(table_stvy)) {
+
+  table_legend <- paste0("Sensitivity analysis of the community simulation.
+Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
+Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", conditional_text[i],".
+Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.")
+
+  knit_chunk <- paste0("## Table S", i, " Sensitivity analysis (", conditional_text[i],") \n",
+                       table_legend,
+                       "\n```{r table_s", i,", results='asis'}
+                       \n\n
+                       cat(table_stvy[[", i,"]], sep = '\n')
+                       \n\n
+                       ```\n",
+                       "\n\\pagebreak\n")
+
+  table_sense <- c(table_sense, knit_chunk)
+
+}
+
+```
+
+`r paste(knit(text = table_sense), collapse = '\n')`
+
+```{r table_reg}
 
@@
 table_legend <- "Median estimates and standard errors (SEs) are shown.
-Pr(> 0) and Pr(< 0) represent the proportion of parameter estimates (MCMC samples) being positive and negative, respectively (i.e., posterior probability)."
+Pr(> 0) and Pr(< 0) represent the proportion of positive and negative estimates (MCMC samples), respectively (i.e., posterior probability)."
 
-table_reg <- NULL
+table_reg <- knit_chunk <- NULL
 

### 2022-01-22 code/table_param_set.R
edit: table

@@ -4,6 +4,9 @@
 rm(list = ls())
 pacman::p_load(tidyverse)
 
+
+# table for main simulation -----------------------------------------------
+
 load(file = here::here("result/result_ricker.RData"))
 
 df_param <- sim_result %>% 
@@ -47,4 +50,14 @@ df_param <- sim_result %>%
   dplyr::select(-id) %>% 
   relocate(Parameter, Interpretation)
 
+
+# table for sensitivity analysis ------------------------------------------
             
+df_param_stvy <- df_param %>% 
+  mutate(Value = case_when(Parameter == "$S$" ~ "Unif(5, 20)",
+                           Parameter == "$K$" ~ "Unif(100, 1000)",
+                           Parameter == "$r_1$" ~ "Unif(0.5, 2.5)",
+                           Parameter == "$r_{max}$" ~ "Unif(0.5, 2.5)",
+                           Parameter == "$\\sigma_{env}$" ~ "Unif(0.05, 0.5)",
+                           Parameter == "$f_R$" ~ "Unif(0.5, 1)",
+                           Parameter == "$\\bar{\\alpha}$" ~ "Unif(0.05, 0.5)"))

### 2022-01-22 code/table_reg.R

@@ -3,7 +3,6 @@
 
 rm(list = ls())
 pacman::p_load(tidyverse)
-
 op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x) 
 
 

### 2022-01-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

--- 2022-01-21 rmd/supporting_info.Rmd
@@
 
+```{=tex}
+\newpage
+\pagenumbering{arabic}
+```
+# Tables
+
+## Table S1 Parameter values used in the main simulation
+See Methods for model description.
+
+```{r table_param_main_sim}
+
+source(here::here("code/table_param_set.R"))
+kable(df_param, format = "markdown")
+
+```
+
 \newpage
 
-# Tables
+## Table S2 Parameter values used in the sensitivity analysis
+In the sensitivity analysis, parameter values were randomly drawn from uniform distributions.
+Discrete parameters (number of species, carrying capacity) were rounded to the nearest integer prior to the analysis.
 
-```{r table_set1}
+```{r table_param_stvy}
 
-## load data for tables
+source(here::here("code/table_param_set.R"))
+kable(df_param_stvy, format = "markdown")
+
+```
+
+\newpage
+
+```{r data_stvy, include=FALSE}
+
+## load table for sensitivity analysis
+source(here::here("code/table_stvy_analysis.R"))
+
+```
+
+```{r table_sensitivity, results="asis"}
+
+j <- 2
+
+## conditional text
+c_text <- c("whole community",
+            "enhanced species",
+            "unenhanced species")
+
+table_stvy_chunk <- knit_chunk <- NULL
+
+for(i in 1:length(table_stvy)) {
+
+  table_legend <- paste0("Sensitivity analysis of the community simulation.
+Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
+Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],".
+Both response and explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.")
+
+  knit_chunk <- paste0("## Table S", i + j, " Sensitivity analysis (", c_text[i],") \n",
+                       table_legend,
+                       "\n```{r table_s", i + j,", results='asis'}
+                       \n\n
+                       cat(table_stvy[[", i,"]], sep = '\n')
+                       \n\n
+                       ```\n",
+                       "\n\\pagebreak\n")
+
+  table_stvy_chunk <- c(table_stvy_chunk, knit_chunk)
+
+}
+
+```
+
+`r paste(knit(text = table_stvy_chunk), collapse = '\n')`
+
+```{r table_reg}
+
+j <- 5
+
+## load regression tables
 source(here::here("code/table_reg.R"))
 
-table_legend <- "Median estimates and standard errors (SEs) are shown.
-Pr(> 0) and Pr(< 0) represent the proportion of parameter estimates (MCMC samples) being positive and negative, respectively (i.e., posterior probability)."
+## conditional text
+c_text <- case_when(name == "all" ~ "whole community",
+                    name == "masu" ~ "masu salmon",
+                    name == "other" ~ "unenhanced species")
 
-table_reg <- NULL
+## common text
+table_legend <- "Median estimates and standard errors (SEs) of regression coefficients are shown.
+Pr(> 0) and Pr(< 0) represent the proportion of positive and negative estimates (MCMC samples), respectively (i.e., posterior probability)."
+
+table_reg_chunk <- knit_chunk <- NULL
 
@@
 
-  if(name[i] == "all") {
-    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of whole community \n",
+  knit_chunk <- paste0("## Table S", i + j, " Parameter estimates for the regression model of ", c_text[i], " \n",
                        table_legend,
-                         "\n```{r table_s", i,"}
+                       "\n```{r table_s", i + j,"}
                        \n\n
@@
                        "\n\\pagebreak\n")
-  }
 
-  if(name[i] == "masu") {
-    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of masu salmon \n",
-                         table_legend,
-                         "\n```{r table_s", i,"}
-                         \n\n
-                         kable(df_est[[",i,"]], format = 'markdown')
-                         \n\n
-                         ```\n",
-                         "\n\\pagebreak\n")
-  }
+  table_reg_chunk <- c(table_reg_chunk, knit_chunk)
 
-  if(name[i] == "other") {
-    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of unenhanced species \n",
-                         table_legend,
-                         "\n```{r table_s", i,"}
-                         \n\n
-                         kable(df_est[[",i,"]], format = 'markdown')
-                         \n\n```
-                         \n",
-                         "\n\\pagebreak\n")
-  }
-
-  table_reg <- c(table_reg, knit_chunk)
 }
@@
 
-`r paste(knit(text = table_reg), collapse = '\n')`
+`r paste(knit(text = table_reg_chunk), collapse = '\n')`
 

### 2022-01-23 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 knitr::opts_chunk$set(echo = FALSE,
-                      message = FALSE)
+                      message = FALSE,
+                      warning = FALSE)
 options(knitr.kable.NA = '')
@@
 ```
+
 # Tables
@@
 
-j <- 5
-
 ## load regression tables
 source(here::here("code/table_reg.R"))
+j <- 5
 
@@
 # Figures
+
+```{r figure_main}
+
+## load figures
+source(here::here("code/figure_suppl.R"))
+
+j <- 0
+figure_sim_chunk <- knit_chunk <- NULL
+
+for(i in seq_len(nrow(df_param))) {
+
+  knit_chunk <- paste0("## Figure S", i + j,
+                       " Theoretical prediction (",
+                       "$r_1$ = `r df_param$r1[",i,"]`, ",
+                       "$\\sigma_{env}$ = `r df_param$sd_env[",i,"]`, ",
+                       "$K$ = `r df_param$k[",i,"]`) \n",
+
+                       "\n```{r figure_s", i + j,", fig.width = 9.5, fig.height = 8}
+                       \n\n
+                       list_g[[",i,"]]
+                       \n\n
+                       ```\n",
+
+                       "Theoretical predictions for the stocking effect on community dynamics.
+Rows represent different response varaibles, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
+Other parameters used in this analysis is the following: ",
+                       "intrinsic growth rate of enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
+                        "environmental variability $\\sigma_{env}$ = `r df_param$sd_env[",i,"]`; ",
+                        "carrying capacity $K$ = `r df_param$k[",i,"]`.",
+                        "\n\\pagebreak\n")
+
+  figure_sim_chunk <- c(figure_sim_chunk, knit_chunk)
+
+}
+
+```
+
+`r paste(knit(text = figure_sim_chunk), collapse = '\n')`

### 2022-01-24 code/table_param_set.R
edit: tables

@@ -19,9 +19,9 @@ df_param <- sim_result %>%
                 alpha) %>% 
   pivot_longer(cols = everything(),
                names_to = "Parameter",
-               values_to = "Value") %>% 
+               values_to = "Main") %>% 
   group_by(Parameter) %>% 
-  summarize(Value = list(unique(Value))) %>% 
+  summarize(Main = list(unique(Main))) %>% 
   ungroup() %>% 
   mutate(
     id = case_when(Parameter == "n_species" ~ "a",
@@ -38,26 +38,21 @@ df_param <- sim_result %>%
                                Parameter == "sd_env" ~ "Environmental variability",
                                Parameter == "phi" ~ "Relative fitness of captive-bred individuals",
                                Parameter == "alpha" ~ "Average strength of interspecific competition"),
+    Sensitivity = case_when(Parameter == "n_species" ~ "Unif(5, 20)",
+                            Parameter == "k" ~ "Unif(100, 1000)",
+                            Parameter == "r1" ~ "Unif(0.5, 2.5)",
+                            Parameter == "r_max" ~ "Unif(0.5, 2.5)",
+                            Parameter == "sd_env" ~ "Unif(0.05, 0.5)",
+                            Parameter == "phi" ~ "Unif(0.5, 1)",
+                            Parameter == "alpha" ~ "Unif(0.05, 0.5)"),
     Parameter = case_when(Parameter == "n_species" ~ "$S$",
                           Parameter == "k" ~ "$K$",
                           Parameter == "r1" ~ "$r_1$",
                           Parameter == "r_max" ~ "$r_{max}$",
-                          Parameter == "sd_env" ~ "$\\sigma_{env}$",
+                          Parameter == "sd_env" ~ "$\\sigma_{\\epsilon}$",
                           Parameter == "phi" ~ "$f_R$",
                           Parameter == "alpha" ~ "$\\bar{\\alpha}$")
   ) %>% 
   arrange(id) %>% 
   dplyr::select(-id) %>% 
   relocate(Parameter, Interpretation)
-
-
-# table for sensitivity analysis ------------------------------------------
-            
-df_param_stvy <- df_param %>% 
-  mutate(Value = case_when(Parameter == "$S$" ~ "Unif(5, 20)",
-                           Parameter == "$K$" ~ "Unif(100, 1000)",
[…]

### 2022-01-24 code/table_species_list.R

@@ -1,0 +1,27 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+pacman::p_load(tidyverse)
+
+
+# data --------------------------------------------------------------------
+
+source(here::here("code/data_fmt_fishdata.R"))
+
+df_sp_list <- d0 %>% 
+  filter(abundance > 0) %>% 
+  group_by(taxon) %>% 
+  summarise(n_site = n_distinct(site_id)) %>% 
+  mutate(taxon = str_replace_all(taxon,
+                                 pattern = "_",
+                                 replacement = " "),
+         taxon = str_replace(taxon,
+                             pattern = "\\sspp",
+                             replacement = " spp."),
+         taxon = paste0("*", taxon, "*"),
+         taxon = str_replace(taxon,
+                             pattern = "\\sspp.*",
+                             replacement = "* spp.")) %>% 
+  rename(Taxon = taxon,
+         'Number of sites observed' = n_site)

### 2022-01-24 code/table_stvy_analysis.R

@@ -22,7 +22,7 @@ for(i in seq_len(length(text_match))) {
                                                     "Carrying capacity $K$",
                                                     "Intrinsic growth rate $r_1$",
                                                     "Maximum intrinsic growth rate $r_{max}$",
-                                                    "Environmental variability $\\sigma_{env}$",
+                                                    "Environmental variability $\\sigma_{\\epsilon}$",
                                                     "Relative fitness $f_R$",
                                                     "Competition coefficient $\\bar{\\alpha}$",
                                                     "Intercept"),

### 2022-01-24 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 # theory infomation
-df_theory <- read_csv(here::here("result/result_ricker.csv"))
+load(here::here("result/result_ricker.RData"))
 
-n_sim <- df_theory %>% 
+n_sim <- sim_result %>% 
   mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
@@
 
-param_set <- df_theory %>% 
+param_set <- sim_result %>% 
   filter(r_max == 2,
@@
 
-We used a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with selective stock enhancement of a constituent species (species 1).
+We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with selective stock enhancement of a constituent species (species 1).
 Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 In our simulation, we used `r nrow(param_set)` simulation scenarios with varied values of the following ecological parameters: intrinsic growth of the enhanced species $r_1$, mean strength of interspecific competition $\bar{\alpha}$, carrying capacity $K$, relative fitness of captive-bred individuals $f_R$, and degree of environmental stochasticity $\sigma_{\epsilon}$.
-Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(df_theory$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$).
-The last `r unique(df_theory$n_timestep)` time steps were used to obtain the coefficient of variation, temporal mean, and temporal standard deviation of total community density ($\sum_i^SN_i$).
-Temporal means and standard deviations were calculated separately for the enhanced species $N_1$ and unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie the community-level response.
+Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$).
+The last `r unique(sim_result$n_timestep)` time steps were used to obtain the number of species persist (defined as $N_i > 0.01$ at $t=1000$), the coefficient of variation (CV), the temporal mean, and the temporal SD of total community density ($\sum_i^SN_i$).
+In addition, temporal means and SDs were calculated separately for the enhanced species $N_1$ and unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie the community-level response.
 
-In general, our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (Figure XX).
-This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible for this result.
+In general, our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (**Figure 1A**).
+This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible for this result (**Figure 1A**).
 For enhanced species, released individuals induced overcompensation, in which the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
 Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals, confirming previous theoretical predictions [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition caused the reduced mean density of unenhanced species and led to decreased numbers of persisting species at high levels of stock enhancement.
-Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (XX).
-The SDs showed a similar trend, but the relationship was flatter at the community level.
+Meanwhile, interspecific competition caused the reduced mean density of unenhanced species and led to decreased numbers of persisting species at high levels of stock enhancement (**Figure 1A**).
+Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (**Figure 1A**).
+The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure 1A**).
 Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density resulted in the increased CV.
-These patterns were qualitatively similar across most ecological scenarios, even when the interspecific competition is very weak (XX).
+These patterns were qualitatively similar across most ecological scenarios, even when interspecific competition is very weak (**Figure S1-6**).
 
-The destabilizing effect emerges because stock enhancement undermines the balance of species interactions that underpin community stability.
+The destabilizing effect emerges because stock enhancement undermines the balance of species interactions that underpins community stability.
 Ecological theory suggests that stable coexistence of competing species requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a].
@@
 
-The only scenario where stock enhancement had little influences on community dynamics was when carrying capacity was sufficiently large ($K=500$).
-In particular, stock enhancement increased, albeit slightly, the average density of the enhanced species with low population growth rate ($r_1=0.5$).
-This result is reasonable because some of the best evidence for successful stock enhancement comes from critically endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
-In the meantime, our theoretical analysis also illuminates limitation of stock enhancement as a primary tool of ecosystem management.
-Habitat loss and fragmentation have severely reduced biodiversity, and one of the primary motivations for stock enhancement is to mitigate or reverse such a trend.
-However, stock enhancement will not bring desired ecological outcomes unless we address the root causes of habitat degradation and restore environmental capacity to support biodiversity.
+The only scenario where stock enhancement had a little influence on community dynamics was when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**).
+In particular, stock enhancement increased, albeit slightly, the average density of the enhanced species with low population growth rate ($r_1=0.5$; **Figures S7 and S8**).
+This result may explain why some of the best evidence for successful stock enhancement comes from endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021], which typically suffer from increased mortality.
+At the same time, our theoretical analysis illuminates limitation of stock enhancement as a primary tool of ecosystem management.
+One of the primary motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020].
+However, our results suggest that stock enhancement will not bring desired ecological outcomes unless we restore high levels of environmental capacity to support biodiversity.
 
@@
 
-Under each parameter combination, we ran `r n_sim` time steps of `r max(df_theory$n_rep)` independent communities (i.e., simulation replicates).
+Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates).
 The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
 We initialized the community with populations of each species drawn from a poisson distribution with a mean of five.
-We repeated the seeding procedure every 10 time steps over the first `r unique(df_theory$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(df_theory$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
-After the burn-in period, we continued the simulation run with stock enhancement and saved the last `r unique(df_theory$n_timestep)` time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).
+We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
+After the burn-in period, we continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).
 We also calculated temporal means and standard deviations for each species group.

### 2022-01-24 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
+# Supplementary text
+
+## Sensitivity analysis
+
+We performed a sensitivity analysis of the community simulation to identify key simulation parameters that strongly affect the relationships between community dynamics (temporal mean and SD of density) and stock enhancement.
+We generated 500 sets of parameter combinations by randomly drawing values of 7 simulation parameters from uniform distributions (**Table S1**).
+For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of stock enhancement $R$ (drawn randomly from $Unif(0, 500)$).
+This yields a total of 50000 simulation replicates.
+In each simulation replicate, we ran 1600 time steps of community dynamics and obtained temporal means and SDs of whole community ($\sum_i^SN_i$), enhanced species ($N_1$), and unenhanced species ($\sum_{i, i\ne1}^SN_i$) using the last 1000 time steps.
+The first 600 time steps were discarded as initialization and burn-in periods.
+
+For each parameter combination, we regressed mean densities and SDs of whole community, enhanced species, and unenhanced species $y_j$ on the number of release $R$ as:
+
+```{=tex}
+\begin{equation}
+\begin{aligned}
+  y_j &\sim Normal(\mu_j, \sigma^2)\\
+  \mu_j &= \psi_0 + \psi_1~R_j
+\end{aligned}
+\end{equation}
+```
+
+where $\psi_k$ ($k = 0-1$) are the intercept ($\psi_0$) and regression coefficient ($\psi_1$).
+We extracted 500 estimates of $\psi_1$, each of which represents the effect of stock enhancement $R$ on community dynamics under a given parameter combination.
+To examine influences of simulation parameters (**Table S1**) on $\psi_1$, we developed the following regression model taking $\psi_1$ as a response variable (parameter combination $n$):
+
+```{=tex}
+\begin{equation}
+\begin{aligned}
+  \psi_{n} &\sim Normal(\mu_n, \sigma^2)\\
+  \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 K_n + \zeta_3 r_{1,n} + \zeta_4 r_{max,n} + \zeta_5 \sigma_{\epsilon,n} + \zeta_6 f_{R, n} + \zeta_7 \bar{\alpha}_n
+\end{aligned}
+\end{equation}
+```
+
+where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$).
+Both response and explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.
+
+We found that regression coefficients of the following parameters ($\zeta$) never exceeded a value of 0.30 and were less influential: the number of species $S$, the maximum intrinsic growth rate of unenhanced species $r_{max}$, and relative fitness $f_R$.
+Therefore, in the main simulation, we fixed values of $S$ and $r_{max}$ (**Table S1**).
+In the meantime, we varied values of $K$, $r_1$, $\sigma_{\epsilon}$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**).
+Although $f_R$ had little influence on stocking effects (**Table S1**), we varied this parameter given the significant interest in relative fitness of captive-bred individuals in the wild.
+
+\newpage
+
 # Tables
 
-## Table S1 Parameter values used in the main simulation
-See Methods for model description.
+## Table S1 Simulation parameter
+Parameter values used in the main and sensitivity analysis. In the sensitivity analysis, 500 parameter values were drawn randomly from uniform distributions. See Methods for model description.
 
-```{r table_param_main_sim}
+```{r table_s1}
 
+# Table S1
 source(here::here("code/table_param_set.R"))
@@
 
-## Table S2 Parameter values used in the sensitivity analysis
-In the sensitivity analysis, parameter values were randomly drawn from uniform distributions.
-Discrete parameters (number of species, carrying capacity) were rounded to the nearest integer prior to the analysis.
-
-```{r table_param_stvy}
-
-source(here::here("code/table_param_set.R"))
-kable(df_param_stvy, format = "markdown")
-
-```
-
-\newpage
-
 ```{r data_stvy, include=FALSE}
 
+# Table S2-4
 ## load table for sensitivity analysis
@@
 
-j <- 2
+# Table S2-4
+j <- 1
 
@@
 
+## Table S5 Observed species
+Fish species found in the study watersheds.
+
+```{r table_s5}
+
+# Table S5
+source(here::here("code/table_species_list.R"))
+
+kable(df_sp_list, format = "markdown")
+
+```
+
+\newpage
+
 ```{r table_reg}
 
+# Table S6-8
 ## load regression tables
@@
 
-```{r figure_main}
+```{r figure_sim}
 
+# Figure S1-12
 ## load figures
-source(here::here("code/figure_suppl.R"))
+source(here::here("code/figure_si_theory.R"))
 
@@
                        "$r_1$ = `r df_param$r1[",i,"]`, ",
-                       "$\\sigma_{env}$ = `r df_param$sd_env[",i,"]`, ",
+                       "$\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`, ",
                        "$K$ = `r df_param$k[",i,"]`) \n",
@@
                        \n\n
-                       list_g[[",i,"]]
+                       list_g_theory[[",i,"]]
                        \n\n
@@
 Rows represent different response varaibles, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
-Other parameters used in this analysis is the following: ",
+Other parameters are: ",
                        "intrinsic growth rate of enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
-                        "environmental variability $\\sigma_{env}$ = `r df_param$sd_env[",i,"]`; ",
+                        "environmental variability $\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`; ",
                         "carrying capacity $K$ = `r df_param$k[",i,"]`.",
@@
 `r paste(knit(text = figure_sim_chunk), collapse = '\n')`
+
+```{r figure_dyns}
+
+# Figure S13-15
+## load figures
+source(here::here("code/figure_si_obs_dyns.R"))
+j <- 12
+
+c_text <- c("whole community",
+            "masu salmon",
+            "unenhanced species")
+
+figure_dyns_chunk <- knit_chunk <- NULL
+
+for(i in seq_len(length(list_g_dyns))) {
+
+  knit_chunk <- paste0("## Figure S", i + j,
+                       " Temporal dynamics of stream fish communities (`r c_text[",i,"]`) \n",
+
+                       "\n```{r figure_s", i + j,", fig.width = 11, fig.height = 8}
+                       \n\n
+                       list_g_dyns[[",i,"]]
+                       \n\n
+                       ```\n",
+                       "Temporal dynamics of stream fish communities (`r c_text[",i,"]`) in Hokkaido, Japan.
+Dots represent observed density, and solid lines are predicted values of the Bayesian state-space model.
+Panels correspond to individual watersheds, and colors distinguish samplig sites within a watershed.",
+                        "\n\\pagebreak\n")
+
+  figure_dyns_chunk <- c(figure_dyns_chunk, knit_chunk)
+
+}
+
+```
+
+`r paste(knit(text = figure_dyns_chunk), collapse = '\n')`

### 2022-01-25 code/table_param_set.R
edit: tables

@@ -5,7 +5,7 @@ rm(list = ls())
 pacman::p_load(tidyverse)
 
 
-# table for main simulation -----------------------------------------------
+# table for simulation parameters -----------------------------------------
 
 load(file = here::here("result/result_ricker.RData"))
 

### 2022-01-25 code/table_prior.R

@@ -1,0 +1,33 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+pacman::p_load(tidyverse)
+
+
+# table for simulation parameters -----------------------------------------
+
+df_prior <- tibble(Model = c("State space", rep(NA, 6),
+                             "Regression", rep(NA, 3)),
+                   Parameter = c("$ln~n_{s,1}$",
+                                 "$\\mu_{\\beta}$",
+                                 "$\\mu_r$",
+                                 "$\\sigma_r$",
+                                 "$\\sigma_{\\beta}$",
+                                 "$\\sigma_{state,s}$",
+                                 "$\\sigma_{obs,s}$",
+                                 "$\\gamma_k$",
+                                 "$\\delta_k$",
+                                 "$\\sigma_y$",
+                                 "$\\sigma_{\\gamma}$"),
+                   Prior = c("Normal(0, 10)",
+                             "Normal(0, 10)",
+                             "Normal(0, 10)",
+                             "t(0, 2.5, 3)",
+                             "t(0, 2.5, 3)",
+                             "t(0, 2.5, 3)",
+                             "t(0, 2.5, 3)",
+                             "Normal(0, 10)",
+                             "Normal(0, 10)",
+                             "t(0, 2.5, 3)",
+                             "t(0, 2.5, 3)"))

### 2022-01-25 code/table_reg.R

@@ -35,13 +35,13 @@ df_est <- lapply(filename, function(x) {
                   sd,
                   prob_positive) %>% 
     mutate(prob_negative = 1 - prob_positive,
-           Parameter = case_when(parameter == "a[1]" ~ "$\\beta_1$",
-                                 parameter == "a[2]" ~ "$\\beta_2$",
-                                 parameter == "a[3]" ~ "$\\beta_3$",
-                                 parameter == "a[4]" ~ "$\\beta_4$",
-                                 parameter == "b[1]" ~ "$\\gamma_0$",
-                                 parameter == "b[2]" ~ "$\\gamma_1$",
-                                 parameter == "b[3]" ~ "$\\gamma_2$"),
+           Parameter = case_when(parameter == "a[1]" ~ "$\\gamma_1$",
+                                 parameter == "a[2]" ~ "$\\gamma_2$",
+                                 parameter == "a[3]" ~ "$\\gamma_3$",
+                                 parameter == "a[4]" ~ "$\\gamma_4$",
+                                 parameter == "b[1]" ~ "$\\delta_0$",
+                                 parameter == "b[2]" ~ "$\\delta_1$",
+                                 parameter == "b[3]" ~ "$\\delta_2$"),
            Effect = case_when(parameter == "a[1]" ~ "Watershed area",
                               parameter == "a[2]" ~ "Air temperature",
                               parameter == "a[3]" ~ "Precipitation",

### 2022-01-25 code/table_species_list.R

@@ -9,7 +9,7 @@ pacman::p_load(tidyverse)
 
 source(here::here("code/data_fmt_fishdata.R"))
 
-df_sp_list <- d0 %>% 
+df_sp_list <- df_selected %>% 
   filter(abundance > 0) %>% 
   group_by(taxon) %>% 
   summarise(n_site = n_distinct(site_id)) %>% 

### 2022-01-25 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
   y_j &\sim Normal(\mu_j, \sigma^2)\\
-  \mu_j &= \psi_0 + \psi_1~R_j
+  \mu_j &= \xi_0 + \xi_1~R_j
 \end{aligned}
@@
 
-where $\psi_k$ ($k = 0-1$) are the intercept ($\psi_0$) and regression coefficient ($\psi_1$).
-We extracted 500 estimates of $\psi_1$, each of which represents the effect of stock enhancement $R$ on community dynamics under a given parameter combination.
-To examine influences of simulation parameters (**Table S1**) on $\psi_1$, we developed the following regression model taking $\psi_1$ as a response variable (parameter combination $n$):
+where $\xi_k$ ($k = 0-1$) are the intercept ($\xi_0$) and regression coefficient ($\xi_1$).
+We extracted 500 estimates of $\xi_1$, each of which represents the effect of stock enhancement $R$ on community dynamics under a given parameter combination.
+To examine influences of simulation parameters (**Table S1**) on $\xi_1$, we developed the following regression model taking $\xi_1$ as a response variable (parameter combination $n$):
 
@@
 \begin{aligned}
-  \psi_{n} &\sim Normal(\mu_n, \sigma^2)\\
+  \xi_{1,n} &\sim Normal(\mu_n, \sigma^2)\\
   \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 K_n + \zeta_3 r_{1,n} + \zeta_4 r_{max,n} + \zeta_5 \sigma_{\epsilon,n} + \zeta_6 f_{R, n} + \zeta_7 \bar{\alpha}_n
@@
 
+## Table S6 Priors
+Prior distributions used in the Bayesian models.
+
+```{r table_s6}
+
+# Table S6
+source(here::here("code/table_prior.R"))
+
+kable(df_prior, format = "markdown")
+
+```
+
+\newpage
+
 ```{r table_reg}
 
-# Table S6-8
+# Table S7-9
 ## load regression tables
 source(here::here("code/table_reg.R"))
-j <- 5
+j <- 6
 

### 2022-01-25 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Selective stock enhancement undermines community stability"
+title: "Stock enhancement undermines community stability"
 output:
@@
 ```{r setup, include=FALSE}
+
+# setup
 knitr::opts_chunk$set(echo = TRUE)
 pacman::p_load(tidyverse)
+op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x)
 
-# theory infomation
+# theory
 load(here::here("result/result_ricker.RData"))
@@
 param_set <- sim_result %>% 
-  filter(r_max == 2,
-         alpha != 0.3) %>% 
   distinct(n_species,
@@
            seed)
+
+# empirical data
+
+source(here::here("code/data_fmt_fishdata.R"))
+
+filename <- list.files(path = here::here("result"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "reg")) %>% 
+  filter(!str_detect(string = .$value, pattern = "reg_rich")) %>% 
+  pull()
+
+df_beta <- lapply(filename, function(x) {
+  read_csv(here::here(x)) %>% 
+    filter(parameter == "b[2]")
+})
+names(df_beta) <- str_extract(filename, "all|masu|other")
 
@@
 
-In our simulation, we used `r nrow(param_set)` simulation scenarios with varied values of the following ecological parameters: intrinsic growth of the enhanced species $r_1$, mean strength of interspecific competition $\bar{\alpha}$, carrying capacity $K$, relative fitness of captive-bred individuals $f_R$, and degree of environmental stochasticity $\sigma_{\epsilon}$.
+In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species $r_1$ (`r unique(sim_result$r1)`), mean strength of interspecific competition $\bar{\alpha}$ (`r unique(sim_result$alpha)`), carrying capacity $K$ (`r unique(sim_result$k)`), relative fitness of captive-bred individuals $f_R$ (`r unique(sim_result$phi)`), and degree of environmental stochasticity $\sigma_{\epsilon}$ (`r unique(sim_result$sd_env)`).
+We chose these parameters because our sensitivity analysis revealed that these parameters have the potential to alter the relationship between community dynamics and stock enhancement (**Supporting Information**).
 Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$).
-The last `r unique(sim_result$n_timestep)` time steps were used to obtain the number of species persist (defined as $N_i > 0.01$ at $t=1000$), the coefficient of variation (CV), the temporal mean, and the temporal SD of total community density ($\sum_i^SN_i$).
+The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the number of species persist (defined as $N_i > 0.01$ at $t=1000$), the coefficient of variation (CV), the temporal mean, and the temporal SD.
 In addition, temporal means and SDs were calculated separately for the enhanced species $N_1$ and unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie the community-level response.
 
-In general, our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (**Figure 1A**).
-This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible for this result (**Figure 1A**).
+When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (**Figure 1A**).
+This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
 For enhanced species, released individuals induced overcompensation, in which the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
@@
 Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density resulted in the increased CV.
-These patterns were qualitatively similar across most ecological scenarios, even when interspecific competition is very weak (**Figure S1-6**).
+These patterns were qualitatively similar across most ecological scenarios even when interspecific competition is very weak (**Figure S1-6**).
 
@@
 
-The only scenario where stock enhancement had a little influence on community dynamics was when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**).
-In particular, stock enhancement increased, albeit slightly, the average density of the enhanced species with low population growth rate ($r_1=0.5$; **Figures S7 and S8**).
-This result may explain why some of the best evidence for successful stock enhancement comes from endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021], which typically suffer from increased mortality.
-At the same time, our theoretical analysis illuminates limitation of stock enhancement as a primary tool of ecosystem management.
-One of the primary motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020].
-However, our results suggest that stock enhancement will not bring desired ecological outcomes unless we restore high levels of environmental capacity to support biodiversity.
+The only scenario where stock enhancement had little influence on community dynamics was when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**).
+In particular, stock enhancement increased the average density of the enhanced species with low population growth rate ($r_1=0.5$; **Figures S7 and S8**).
+This result may explain why some of the best evidence for successful stock enhancement comes from endangered species that typically suffer from increased mortality [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
+More importantly, the contrasting community response at different levels of carrying capacity provides deeper insights into ecosystem management.
+One of the core motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020].
+However, our results suggest that stock enhancement will not bring desired ecological outcomes in degraded habitats with compromised environmental capacity.
 
@@
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon on the long-term stability of stream fish communities.
-Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and XX leads extensive hatchery programs across the island.
-In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted with consistent sampling methods over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018].
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities.
+Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and extensive hatchery programs have been implemented.
+In protected watersheds where any form of exploitation is prohibited (including recreational angling) (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018].
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
-In this study, we used time-series data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).
-Using hierarchical Bayesian models, we quantified the relationship between community dynamics and the number of fish released while accounting for potential confounding effects of climates and local abiotic factors.
+In this study, we used the long-term data of stream fish communities (1999-2019) at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criterion).
+Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.
 
-As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released.
-The positive relationship between the CV and the number of fish released was strongly supported by a hierarchical linear model, in which the probability of the regression coefficient being positive was XXX.
-This pattern was associated with the reduced long-term averages of population densities of enhanced (masu salmon) and unenhanced fish groups, although statistical support for this relationship was weak to moderate (STATS).
-In the meantime, the SDs of population densities had vague relationships with the number of fish released, and neither positive or negative relationship was supported by statistical analysis.
-These results are in good agreement with previous studies.
-Negative or vague population response to stock enhancement has been widely observed in other fish and invertebrate species, implying limited effectiveness of this method as a management tool.
-Our analysis of long-term community data further illuminated the potential negative impact of stock enhancement on unenhanced species and expanded our understanding to community-level response to stock enhancement.
+As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**).
+The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])`.
+This pattern was associated with the reduced long-term average of total community density, and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2**).
+In the meantime, the SDs had vague relationships with stock enhancement, and neither positive or negative relationship was supported by statistical analysis (**Figure 1B and 2**).
+At the population level, similar responses to stock enhancement have been reported in other fish and aquatic invertebrates [@arakiHatcheryStockingHelp2010].
+However, our analysis expands our understanding by illustrating the community-level response to stock enhancement in natural systems.
 
-In our theory, the observed pattern emerges when negative density dependence operates in the recipient community, and this assumption is well supported by previous observations.
-Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that released masu salmon compete with wild individuals of masu salmon [@sahashiEvaluationContributionHatchery2015a] and other stream fishes [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018].
+In our theory, the observed pattern emerges when negative density dependence operates in the recipient community, and previous observations confirm this assumption.
+Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that released masu salmon compete with wild masu salmon [@sahashiEvaluationContributionHatchery2015a] and other stream fishes [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018].
 Hatchery-reared salmons are larger and more aggressive than wild individuals, further increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003].
-Importantly, the number of fish released is likely controlled by socioeconomic factors (e.g., budget allocation) because there was no apparent congruence between the number of fish released and the population density of masu salmon (XX).
+Importantly, the number of fish released is controlled by socioeconomic factors (e.g., budget allocation).
 As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may impose resource competition that would otherwise not exist.
@@
 Reduced fitness of captive-bred individuals may also play a role in producing the observed community response.
-As with other salmonid species, ocean-migrating adults of captive-bred masu salmon show lower return rates to the spawning river and therefore less contribute to the next generation (miyakoshi?).
+As with other salmonid species, ocean-migrating adults of captive-bred masu salmon show lower return rates to the spawning river.
 It has also been shown that hatchery-reared salmons are more susceptible to predation than wild salmons [@weberInteractionsHatcheryWild2003].
-The fitness disadvantage of captive-bred fish may interact with negative density dependence to reduce the long-term average of community density, undermining community stability in the long term.
+The fitness disadvantage of captive-bred fish may add to negative density dependence to reduce the long-term average of community density, undermining community stability in the long term.
 
@@
 As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations of enhanced species [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007a].
-Despite the significant attention to the fate of captive-bred individuals, it is rare to consider the self-regulation process of biodiversity.
+Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.
 The results of this study suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community.
@@
 
-We developed a multispecies Ricker model to simulate community dynamics with selective stock enhancement of a constituent species (species 1).
-Population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+In this study, we modified a multispecies Ricker model to include selective stock enhancement of a constituent species (species 1).
+In the basic model formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
 $$
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K})]exp(\epsilon_{i,t})
+\begin{aligned}N_{i,t+1} = N_{i,t}~exp[r_i(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t}) &\text{(1)}
+\end{aligned}
 $$
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K$ the community-level carrying capacity in the absence of niche difference, $R_t$ the number of released individuals for the stock enhancement of species 1 (set constant as $R_t = R$), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that obey an normal distribution with a mean of zero and a standard deviation of $\sigma_{\epsilon}$.
-The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that obey an normal distribution $\epsilon_{i,t} \sim Normal(0, \sigma_{\epsilon}^2)$.
+We modified this model formula to consider the effects of stock enhancement on reproduction and competition as follows:
 
 $$
+\begin{aligned}
+N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i \{1-\frac{N_{i,t}+\alpha_{i1} (N_1 + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i}\}]exp(\epsilon_{i,t}) &\text{(2)}
+\end{aligned}
+$$
+
+$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
+
+$$
+\begin{aligned}
 \phi_i = \left\{
@@
 \right.
+&\text{(3)}
+\end{aligned}
 $$
 
-$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals.
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. The equation (2) can be reorganized to:
+
+$$
+\begin{aligned}
+N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t}) &\text{(4)}
+\end{aligned}
+$$
 
@@
 
-**Time-series data.** We assembled time-series data of fish abundance across XX sites within XX protected watersheds of Hokkaido Island, Japan.
-In these watersheds, aquatic species are protected and no harvest is allowed.
+**Time-series data.** We assembled time-series data of fish abundance across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
 At these sites, the long-term monitoring program began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999.
-Data were collected in summer to fall with irregular sampling intervals (0 to 3 year intervals for most cases).
-After careful data selection (Supporting Information), we used time-series data of fish abundance at XX sites during a period of 1999-2019.
+Most data were collected in summer to fall with irregular sampling intervals (0 to 3 year intervals for most cases).
+We confined our analysis to the sites that meets the following selection criteria: (1) the observation span (from the first to the last year of observation) exceeds 10 years, (2) the number of observation years exceeds five years, and (3) masu salmon are observed at least twice during the observation period.
+As a result, we used time-series data of fish abundance at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` during a period of 1999-2019.
 
-**Fish stocking.** At the protected watersheds, masu salmon were stocked to enhance the wild populations since XXX.
+**Fish stocking.** At the protected watersheds, stocking of masu salmon began in 1950s.
 A mixture of captive-bred and wild-born individuals were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
-We examined historical records of fish stocking and obtained annual stocking data (the number of individuals released) for a period of 1999-2019 at each watershed.
+For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of individuals released) for a period of 1999-2019.
 Although fish were released at multiple locations within a watershed, we were unable to extract stocking data at the site level.
 
-**Environmental data.** At each sampling site, we collected the following data as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture, urban), local climates (annual mean air temperature [unit] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
+**Environmental data.** At each sampling site, we collected the following data as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [unit] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
 Annual data of ocean productivity (2003-2019) were extracted from OceanColor (<https://oceancolor.gsfc.nasa.gov/>) and the averaged value within the 30-km radius of each river mouth was calculated.
@@
 
-Our goal is to compare temporal dynamics of fish communities across sites.
+Our goal is to compare temporal community dynamics across sites.
 However, the data are not directly comparable because of observation errors (e.g., different observers) and missing observations.
-To confront this challenge, we developed Bayesian state space models for three species groups separately: (1) whole community, summed abundance of all species, (2) enhanced species, abundance of masu salmon, (3) unenhanced species, summed abundance of all species except masu salmon.
-Bayesian state space models is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site.
+To confront this challenge, we developed a Bayesian state space model for three species groups separately: (1) whole community, summed abundance of all species, (2) enhanced species, abundance of masu salmon, (3) unenhanced species, summed abundance of all species except masu salmon.
+A Bayesian state space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site.
 The model is composed of observation and state models as described below.
@@
 In the observation model, we model observation processes.
-Summed fish abundance of either whole community, enhanced species (masu salmon only), and unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
+Summed fish abundance of either whole community, enhanced species (masu salmon only), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
 
 $$
-N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t})
+\begin{aligned}
+N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t}) &\text{(6)}
+\end{aligned}
 $$
@@
 $$
-\lambda_{s,t} = n_{s,t}e^{\epsilon_{s,t}^{obs}} + \psi \beta_s~Fry_{w(s),t}
+\begin{aligned}
+\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t} &\text{(7)}
+\end{aligned}
 $$
@@
 $n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
-The parameter $e^{\epsilon_{s,t}^{obs}}$ is a random error variable drawn from a log-normal distribution as $\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$.
-The inclusion of this random variable allows us to account for site-specific and year-specific observation errors.
-The parameter $\psi$ equals zero when we model the unenhanced species group (otherwise $\psi = 1$).
-We included $\psi$ to exclude the term $\beta_s~Fry_{w(j),t}$ because the unenhanced species group does not include masu salmon.
+The error term $\epsilon_{s,t}^{obs}$ is drawn from a normal distribution as $\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$ to account for site- and year-specific observation errors.
+The parameter $\psi$ equals zero when we model the unenhanced species group (otherwise $\psi = 1$) so we exclude the term $\beta_s~Fry_{w(j),t}$.
 
@@
 $$
-ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
-$$where $ln~r_{s}$ is the site-specific rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
-The site-specific rate of change is random draws from a normal distribution as $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).
+\begin{aligned}
+ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state} &\text{(8)}
+\end{aligned}
+$$ where $ln~r_{s}$ is the site-specific rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
+The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).
 This hierarchical structure allows for improved estimates of $ln~r_s$ by sharing information across sites.
-We used median estimates of fish density $n_{s,t}$ to calculate temporal CV, mean ($\mu$), and SD ($\sigma$).
+We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).
 
-We developed the following linear regression models taking either log-transformed CV, mean, or SD as a response variable $ln~y_s$ with a normal error distribution.
+We developed the following linear regression models taking either CV, species richness, mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.
 
@@
 \begin{aligned}
-ln~y_s &\sim Normal(\mu_{y,s},\sigma_y^2)\\
-\mu_{y,s} &= \beta_{0,w(s)} + \sum_k \beta_kx_{k,s}
+\left\{
+\begin{array}{}
+ln~y_s &\sim Normal(\mu_y, \sigma_y^2)~&~\text{for CV, mean, and SD}\\
+y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s}))~&\text{for species richness}
+\end{array}
+\right.
+&\text{(9)}
 \end{aligned}
@@
 
-where $\beta_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\beta_k (k > 0)$ is the regression coefficient of site-level predictor $x_k$.
-The site-level predictors include upstream watershed area, air temperature, precipitation, forest land use, and local species richness (we excluded local species richness from the masu salmon model).
+where $\sigma_y$ is the SD of residual errors and $\epsilon_{y,s}$ is the normally-distributed error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$).
+The expected mean $\mu_y$ was related to linear predictors as follows:
+
+$$
+\begin{aligned}
+\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &\text{(10)}
+\end{aligned}
+$$
+
+$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictor $x_k$.
+The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use (fraction).
 The watershed-specific intercept was related to watershed-level predictors as:
@@
 \begin{aligned}
-\beta_{0,w} &\sim Normal(\mu_{\beta,w},\sigma_{\beta}^2)\\
-\mu_{\beta,w} &=\gamma_0+\sum_k\gamma_k z_{k,w}
+\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
+\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
+&&\text{(11)}
 \end{aligned}
@@
 
-The watershed-level predictors include the number of released masu salmon and ocean productivity (sea surface chlorophyll a).
+$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients.
+The watershed-level predictors $z_{k,w}$ include the number of released masu salmon and ocean productivity (sea surface chlorophyll a).
+The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that cannot be captured by the watershed-level predictors.
 
-We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R. Priors were summarized in XXX. Data manipulation and analysis were performed in R version 4.1.0.
+We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R.
+We assigned weakly informative priors for parameters, which were summarized in XXX.
+Data manipulation and analysis were performed in R version 4.1.0.
 

### 2022-01-26 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 
-In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species $r_1$ (`r unique(sim_result$r1)`), mean strength of interspecific competition $\bar{\alpha}$ (`r unique(sim_result$alpha)`), carrying capacity $K$ (`r unique(sim_result$k)`), relative fitness of captive-bred individuals $f_R$ (`r unique(sim_result$phi)`), and degree of environmental stochasticity $\sigma_{\epsilon}$ (`r unique(sim_result$sd_env)`).
-We chose these parameters because our sensitivity analysis revealed that these parameters have the potential to alter the relationship between community dynamics and stock enhancement (**Supporting Information**).
+In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species ($r_1=$ `r unique(sim_result$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(sim_result$alpha)`), carrying capacity ($K=$ `r unique(sim_result$k)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(sim_result$phi)`), and degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(sim_result$sd_env)`).
+We chose these parameters because our sensitivity analysis revealed that these parameters were influential in altering the relationship between community dynamics and stock enhancement (**Supporting Information**).
 Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$).
-The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the number of species persist (defined as $N_i > 0.01$ at $t=1000$), the coefficient of variation (CV), the temporal mean, and the temporal SD.
-In addition, temporal means and SDs were calculated separately for the enhanced species $N_1$ and unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie the community-level response.
+The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean, and the temporal SD.
+In addition, temporal means and SDs were calculated for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.
 
@@
 One of the core motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020].
-However, our results suggest that stock enhancement will not bring desired ecological outcomes in degraded habitats with compromised environmental capacity.
+However, our results suggest that stock enhancement will not bring desired ecological outcomes in degraded habitats because human influences compromised environmental capacity.
 
@@
 To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities.
-Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and extensive hatchery programs have been implemented.
-In protected watersheds where any form of exploitation is prohibited (including recreational angling) (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018].
+Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and extensive hatchery programs have been implemented [@kitadaLessonsJapanMarine2020].
+In protected watersheds where any forms of exploitation are prohibited (including recreational angling) (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018].
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
-In this study, we used the long-term data of stream fish communities (1999-2019) at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criterion).
+In this study, we used the long-term data (1999-2019) of stream fish communities at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criterion).
 Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.
@@
 As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**).
-The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])`.
-This pattern was associated with the reduced long-term average of total community density, and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2**).
+The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S7**).
+This pattern was associated with the reduced long-term average of total community density, and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Tables S7-S9** and **Figure 1B and 2**).
 In the meantime, the SDs had vague relationships with stock enhancement, and neither positive or negative relationship was supported by statistical analysis (**Figure 1B and 2**).
 At the population level, similar responses to stock enhancement have been reported in other fish and aquatic invertebrates [@arakiHatcheryStockingHelp2010].
-However, our analysis expands our understanding by illustrating the community-level response to stock enhancement in natural systems.
+Our analysis builds upon these findings by illustrating the community-level response to stock enhancement in nature.
 
@@
 Importantly, the number of fish released is controlled by socioeconomic factors (e.g., budget allocation).
-As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may impose resource competition that would otherwise not exist.
+As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may cause resource competition that would otherwise not exist.
 
@@
 However, in the protected watersheds, any exploitation of aquatic species and alteration of in-stream habitats (e.g., construction of river-crossing structure) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences played a major role in the observed relationships.
-Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables.
-Hence, we are confident in our statistical inference, and this unique study setup may have helped produce the close agreement between theory and empirical patterns.
+Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables (see **Methods** and **Tables S7-S9**).
+This unique study setup may have helped uncover the close agreement between theory and empirical patterns.
 
@@
 The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996].
-As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations of enhanced species [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007a].
+As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007a].
 Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.
@@
 We should prioritize the preservation and restoration efforts of natural habitats with a broader scope of biodiversity conservation.
-In particular, such efforts are crucial given that the undesired influence of stock enhancement is predicted to be exacerbated in degraded habitats due to the compromised capacity to support biodiversity (XX).
-It has been shown that protected areas and environmental restoration are promising tools to conserve biodiversity, and the effective spatial design is a key to achieve successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017].
+Such efforts are particularly important in the Anthropocene because the undesired influence of stock enhancement may be exacerbated in degraded habitats.
+Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieve successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017].
 For example, coordinated placement of conservation sites considering spatial biodiversity patterns is of critical importance in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013].
 Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
-These considerable potentials indicate that we have viable management options for the sustainable future of biodiversity and natural resources before blindly accepting stock enhancement programs.
+These considerable potentials indicate that we have viable management options for the sustainable future of natural resources before blindly accepting stock enhancement.
 Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.
@@
 
-In this study, we modified a multispecies Ricker model to include selective stock enhancement of a constituent species (species 1).
-In the basic model formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+We employed a multispecies Ricker model. In the basic formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
@@
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that obey an normal distribution $\epsilon_{i,t} \sim Normal(0, \sigma_{\epsilon}^2)$.
-We modified this model formula to consider the effects of stock enhancement on reproduction and competition as follows:
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
+We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
 
@@
 
-$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
+$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
 
@@
 
-We varied values of the following ecological parameters: mean strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), intrinsic growth of the enhanced species ($r_1 =$ `r unique(param_set$r1)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`), and degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).
-Other parameters were set constant or drawn randomly from a probability distribution: $S=$ `r unique(param_set$n_species)` , $K=$ `r unique(param_set$k)` , $r_i =$ $Unif$(`r unique(param_set$r_min)` , `r unique(param_set$r_max)`) ($i \ne 1$), $\alpha_{ii} = 1$, $\alpha_{ij,i \ne j} \sim Exp(\bar{\alpha})$.
+In this model, the intrinsic growth rates for unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
+We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of release $(R_t=R)$.
+
+Prior to the main simulation analysis, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement.
+We identified five influential parameters, of which multiple values were considered in the main simulation as follows: carrying capacity ($K=$ `r unique(param_set$k)`), intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`), and average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`).
+We fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`).
 This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
@@
 After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
-After the burn-in period, we continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$).
-We also calculated temporal means and standard deviations for each species group.
-Values of simulation parameters were summarized in XXX.
-We performed simulations using R version XXX.
+After the burn-in period, we continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps to obtain the coefficient of variation, temporal mean, and SD of whole community density ($\sum_i^SN_j$).
+Temporal means and SDs were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
+We summarized values of simulation parameters in **Table S1**.
 
@@
 We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).
+Raw time series data and estimated community dynamics are shown in **Figures S12-S15**.
 
-We developed the following linear regression models taking either CV, species richness, mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.
+We developed the following linear regression model taking either CV, species richness, mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.
 
@@
 \begin{array}{}
-ln~y_s &\sim Normal(\mu_y, \sigma_y^2)~&~\text{for CV, mean, and SD}\\
-y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s}))~&\text{for species richness}
+ln~y_s &\sim Normal(\mu_y, \sigma_y^2)~&&~\text{for CV, mean, and SD} &&&\text{(9a)}\\
+y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s}))~&&\text{for species richness} &&&\text{(9b)}
 \end{array}
 \right.
-&\text{(9)}
 \end{aligned}
@@
 \begin{aligned}
-\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &\text{(10)}
+\left\{
+\begin{array}{}
+\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD} &&&\text{(10a)}\\
+ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness} &&&\text{(10b)}
+\end{array}
+\right.
 \end{aligned}
@@
 \begin{aligned}
-\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
-\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
-&&\text{(11)}
+\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)  &&\text{(11a)}\\
+\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w} &&\text{(11b)}
 \end{aligned}
@@
 We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R.
-We assigned weakly informative priors for parameters, which were summarized in XXX.
+We assigned weakly informative priors for parameters, which were summarized in **Table S6**.
 Data manipulation and analysis were performed in R version 4.1.0.

### 2022-01-27 code/table_param_set.R
edit: tables

@@ -25,12 +25,12 @@ df_param <- sim_result %>%
   ungroup() %>% 
   mutate(
     id = case_when(Parameter == "n_species" ~ "a",
-                   Parameter == "k" ~ "b",
-                   Parameter == "r1" ~ "c",
-                   Parameter == "r_max" ~ "d",
-                   Parameter == "sd_env" ~ "e",
-                   Parameter == "phi" ~ "f",
-                   Parameter == "alpha" ~ "g"),
+                   Parameter == "r1" ~ "b",
+                   Parameter == "r_max" ~ "c",
+                   Parameter == "alpha" ~ "d",
+                   Parameter == "k" ~ "e",
+                   Parameter == "sd_env" ~ "f",
+                   Parameter == "phi" ~ "g"),
     Interpretation = case_when(Parameter == "n_species" ~ "Number of species",
                                Parameter == "k" ~ "Carrying capacity",
                                Parameter == "r1" ~ "Intrinsic growth rate of an enhanced species",

### 2022-01-27 code/table_prior.R

@@ -10,8 +10,8 @@ pacman::p_load(tidyverse)
 df_prior <- tibble(Model = c("State space", rep(NA, 6),
                              "Regression", rep(NA, 3)),
                    Parameter = c("$ln~n_{s,1}$",
-                                 "$\\mu_{\\beta}$",
                                  "$\\mu_r$",
+                                 "$\\mu_{\\beta}$",
                                  "$\\sigma_r$",
                                  "$\\sigma_{\\beta}$",
                                  "$\\sigma_{state,s}$",

### 2022-01-27 code/table_ssm.R

@@ -1,0 +1,57 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+pacman::p_load(tidyverse)
+op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x) 
+
+
+# data --------------------------------------------------------------------
+
+df_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
+  pull() %>% 
+  lapply(function(x) {
+    df0 <- read_csv(x) %>% 
+      filter(param %in% c("mu_b",
+                          "log_global_r",
+                          "sd_r_space",
+                          "sd_b")) %>% 
+      select(param, `50%`, `2.5%`, `97.5%`) %>% 
+      mutate(group = str_extract(x, "all|masu|other"),
+             param = factor(param, levels = c("log_global_r",
+                                              "mu_b",
+                                              "sd_r_space",
+                                              "sd_b")),
+             Parameter = case_when(param == "log_global_r" ~ "$\\mu_{r}$",
+                                   param == "mu_b" ~ "$\\mu_{\\beta}$",
+                                   param == "sd_r_space" ~ "$\\sigma_{r}$",
+                                   param == "sd_b" ~ "$\\sigma_{\\beta}$"),
+             Interpretation = case_when(param == "log_global_r" ~ "Global rate of community change",
+                                        param == "mu_b" ~ "Effect of spring stoking",
+                                        param == "sd_r_space" ~ "Variation in the site-specific rate of community change",
+                                        param == "sd_b" ~ "Variation in the site-specific effect of spring stocking"),
+             `Species group` = case_when(group == "all" & param == "log_global_r" ~ "Whole",
+                                         group == "masu" & param == "log_global_r" ~ "Enhanced (masu salmon)",
+                                         group == "other" & param == "log_global_r" ~ "Unenhanced")) %>% 
+      arrange(param)
+    
+    if(str_detect(x, "other")) {
+      df0 <- df0 %>% 
+        filter(!(param %in% c("mu_b", "sd_b")))
+    }
+    
+    df0 <- df0 %>%
+      mutate(across(.cols = `50%`:`97.5%`,
+                    .fns = op)) %>% 
+      mutate(Estimate = paste0(`50%`, " (", `2.5%`, ", ", `97.5%`, ")")) %>% 
[…]

### 2022-01-27 code/table_stvy_analysis.R

@@ -19,12 +19,12 @@ for(i in seq_len(length(text_match))) {
                                header = FALSE,
                                type = "latex",
                                covariate.labels = c("Number of species $S$",
-                                                    "Carrying capacity $K$",
                                                     "Intrinsic growth rate $r_1$",
                                                     "Maximum intrinsic growth rate $r_{max}$",
+                                                    "Competition coefficient $\\bar{\\alpha}$",
+                                                    "Carrying capacity $K$",
                                                     "Environmental variability $\\sigma_{\\epsilon}$",
                                                     "Relative fitness $f_R$",
-                                                    "Competition coefficient $\\bar{\\alpha}$",
                                                     "Intercept"),
                                single.row = FALSE,
                                digits = 3,

### 2022-01-27 rmd/figures.Rmd
Create figures.Rmd

---
output:
  pdf_document:
    latex_engine: xelatex
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
header-includes:
  \pagenumbering{gobble}
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

```

```{r figure_1, fig.width=9, fig.height=11}

source(here::here("code/figure_theory_obs.R"))

print(g)

```

**Figure 1** Theory and empirical observations agree that stock enhancement destabilizes community dynamics. Panels and colors distinguish response variables and species groups, respectively. (A) Theoretical predictions. Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`. (B) Empirical evidence. Dots represent observed values in 31 watersheds. We averaged site-level values (geometric mean) in each watershed. Lines are predicted values of regression models, and line types corresponds to posterior probabilities of regression coefficients. See Tables S8-10 for full statistics. (C) Map of sampling sites (black dots) in Hokkaido, Japan. (D) Example of an protected watershed (Okushibetsu). (E) Masu salmon *Oncorhynchus masou masou*. Photo credit: Akira Terui.

\newpage

```{r figure2, fig.width=8, fig.height=6}

source(here::here("code/figure_coef.R"))

print(g_coef)

```

**Figure 2** Posterior distributions for the standardized regression coefficients of stock enhancement. Y-axis represents different response variables grouped by colors distinguishing species groups (whole community, enhanced species [masu salmon], and unenhanced species).

### 2022-01-27 rmd/supporting_info.Rmd
edit: SI

@@
 
+## Table S7 Parameter estimates of the Bayesian state space model
+Median estimates of the Bayesian state space model. Site specific parameters were excluded due to the large number of parameters. Numbers in parenthesis indicate 95% credible intervals.
+
+```{r table_s7}
+
+# Table S7
+source(here::here("code/table_ssm.R"))
+
+kable(df_ssm, format = "markdown")
+
+```
+
+\newpage
+
 ```{r table_reg}
 
-# Table S7-9
+# Table S8-10
 ## load regression tables
 source(here::here("code/table_reg.R"))
-j <- 6
+j <- 7
 

### 2022-01-27 rmd/manuscript.Rmd
edit: rmd

@@
 
+## raw data
 source(here::here("code/data_fmt_fishdata.R"))
@@
 
+## ssm estimate
+df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
+  pull() %>% 
+  lapply(function(x) {
+    read_csv(x) %>% 
+      filter(param == "bp_value") %>% 
+      select(mean) %>% 
+      mutate(group = str_extract(x, "all|masu|other"))
+  }) %>% 
+  bind_rows()
+
 ```
@@
 
-**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Department of Ecology, Evolution and Behavior, University of Minnesota, St.
-Paul, MN 55108, USA ^3^ National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan ^4^ Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan
+**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ XXX ^3^ XXX ^4^ XXX
+
+# Abstract
+
+Although accumulating evidence suggests that stock enhancement with captive-bred organisms entails ecological risks, this method remains to be a common practice in conservation and fisheries.
+The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
+Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
+Here, we use a simple theory to show that stock enhancement undermines long-term community stability by disrupting the sensitive balance of species interactions in natural communities.
+Stock enhancement destabilized community dynamics through facilitating competitive exclusion across a wide range of simulated scenarios.
+The present study further provided empirical support for this theoretical prediction using long-term data of Japanese stream fish communities.
+As our theory predicts, stream fish communities showed greater temporal fluctuations and reduced biodiversity in watersheds with intensive stocking of hatchery masu salmon - one of the most valuable freshwater resources in the region.
+Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
 
@@
 
-where $r_i$ is the intrinsic growth rate (drawn from a uniform distribution as $r_i \sim Unif(0,2)$ except $r_1$), $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ [drawn from an exponential distribution as $\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$; intraspecific competition $\alpha_{ii}=1$], $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that follow an normal distribution with a mean of zero and a standard deviation of $\sigma_{\epsilon}$.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $Normal(0,\sigma_{\epsilon}^2)$.
+To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$), respectively.
 The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
@@
 
-In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species ($r_1=$ `r unique(sim_result$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(sim_result$alpha)`), carrying capacity ($K=$ `r unique(sim_result$k)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(sim_result$phi)`), and degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(sim_result$sd_env)`).
-We chose these parameters because our sensitivity analysis revealed that these parameters were influential in altering the relationship between community dynamics and stock enhancement (**Supporting Information**).
+In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species ($r_1=$ `r unique(sim_result$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(sim_result$alpha)`), carrying capacity ($K=$ `r unique(sim_result$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(sim_result$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(sim_result$phi)`).
+We chose these parameters because our sensitivity analysis revealed that they were influential in altering the relationship between community dynamics and stock enhancement (**Supporting Information**).
 Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$).
-The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean, and the temporal SD.
-In addition, temporal means and SDs were calculated for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.
+The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$).
+In addition, the temporal mean and SD were also calculated for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.
 
@@
 This result may explain why some of the best evidence for successful stock enhancement comes from endangered species that typically suffer from increased mortality [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
-More importantly, the contrasting community response at different levels of carrying capacity provides deeper insights into ecosystem management.
+More importantly, the contrasting community response at different levels of carrying capacity casts light on the limitation of stock enhancement.
 One of the core motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020].
-However, our results suggest that stock enhancement will not bring desired ecological outcomes in degraded habitats because human influences compromised environmental capacity.
+Ironically, however, our results suggest that stock enhancement will not bring desired ecological outcomes unless we resolve root causes that compromise environmental capacity first.
 
@@
 Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and extensive hatchery programs have been implemented [@kitadaLessonsJapanMarine2020].
-In protected watersheds where any forms of exploitation are prohibited (including recreational angling) (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018].
+In protected watersheds (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018].
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
-In this study, we used the long-term data (1999-2019) of stream fish communities at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criterion).
+In this study, we used the long-term data (1999-2019) of stream fish communities at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criteria).
 Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.
@@
 As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**).
-The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S7**).
-This pattern was associated with the reduced long-term average of total community density, and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Tables S7-S9** and **Figure 1B and 2**).
-In the meantime, the SDs had vague relationships with stock enhancement, and neither positive or negative relationship was supported by statistical analysis (**Figure 1B and 2**).
+The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
+This pattern was associated with the reduced long-term average of total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics).
+In the meantime, the SDs had vague relationships with stock enhancement, and neither positive nor negative relationship was supported by statistical analysis (**Figure 1B and 2**).
 At the population level, similar responses to stock enhancement have been reported in other fish and aquatic invertebrates [@arakiHatcheryStockingHelp2010].
-Our analysis builds upon these findings by illustrating the community-level response to stock enhancement in nature.
+Our analysis builds upon these findings by illustrating the community-level response.
 
@@
 However, in the protected watersheds, any exploitation of aquatic species and alteration of in-stream habitats (e.g., construction of river-crossing structure) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences played a major role in the observed relationships.
-Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables (see **Methods** and **Tables S7-S9**).
+Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables (see **Methods** and **Tables S8-S10**).
 This unique study setup may have helped uncover the close agreement between theory and empirical patterns.
@@
 
-We employed a multispecies Ricker model. In the basic formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012]. In the basic formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
@@
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
 We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
@@
 
-In this model, the intrinsic growth rates for unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
+In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
 We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of release $(R_t=R)$.
 
-Prior to the main simulation analysis, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement.
-We identified five influential parameters, of which multiple values were considered in the main simulation as follows: carrying capacity ($K=$ `r unique(param_set$k)`), intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`), and average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`).
-We fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`).
+Prior to the main simulation analysis, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (**Supporting Information**).
+We identified five influential parameters (**Table S2-4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`).
 This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
@@
 After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
-After the burn-in period, we continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps to obtain the coefficient of variation, temporal mean, and SD of whole community density ($\sum_i^SN_j$).
-Temporal means and SDs were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
+We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps.
+We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$).
+The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
 We summarized values of simulation parameters in **Table S1**.
@@
 We confined our analysis to the sites that meets the following selection criteria: (1) the observation span (from the first to the last year of observation) exceeds 10 years, (2) the number of observation years exceeds five years, and (3) masu salmon are observed at least twice during the observation period.
-As a result, we used time-series data of fish abundance at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` during a period of 1999-2019.
+As a result, we used time-series data of fish abundance at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds during a period of 1999-2019.
+**Table S5** summarizes observed species in these watersheds.
 
@@
 A mixture of captive-bred and wild-born individuals were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
-For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of individuals released) for a period of 1999-2019.
+For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of fish released) for a period of 1999-2019.
 Although fish were released at multiple locations within a watershed, we were unable to extract stocking data at the site level.
 
-**Environmental data.** At each sampling site, we collected the following data as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [unit] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
+We used MERIT Hydro [@yamazakiMERITHydroHighResolution2019] to delineate upstream watershed polygons for each sampling site.
+The proportion of forest land use in each watershed polygon was estimated based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+Climate data at each sampling site were extracted from CHELSA ver.
+1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
 Annual data of ocean productivity (2003-2019) were extracted from OceanColor (<https://oceancolor.gsfc.nasa.gov/>) and the averaged value within the 30-km radius of each river mouth was calculated.
+We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
 
@@
 To confront this challenge, we developed a Bayesian state space model for three species groups separately: (1) whole community, summed abundance of all species, (2) enhanced species, abundance of masu salmon, (3) unenhanced species, summed abundance of all species except masu salmon.
-A Bayesian state space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site.
+A Bayesian state space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004a; @keryBayesianPopulationAnalysis2012].
 The model is composed of observation and state models as described below.
@@
 $n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
+The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
 The error term $\epsilon_{s,t}^{obs}$ is drawn from a normal distribution as $\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$ to account for site- and year-specific observation errors.
-The parameter $\psi$ equals zero when we model the unenhanced species group (otherwise $\psi = 1$) so we exclude the term $\beta_s~Fry_{w(j),t}$.
+When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
 
@@
 We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).
-Raw time series data and estimated community dynamics are shown in **Figures S12-S15**.
+Bayesian p-values [@keryIntroductionWinBUGSEcologists2010] for the state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
+Estimated parameters and community dynamics are summarized in Supporting Information (**Table S7** and **Figures S13-S15**).
 
-We developed the following linear regression model taking either CV, species richness, mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.
+We developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.
 
@@
 
-We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R.
+We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R [@denwoodRunjagsPackageProviding2013].
 We assigned weakly informative priors for parameters, which were summarized in **Table S6**.
-Data manipulation and analysis were performed in R version 4.1.0.
+Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
 

### 2022-01-30 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
         before_body: title.tex
-bibliography: reference.bib
 knit: (function(inputFile, encoding) {
@@
   \pagenumbering{gobble}
+  \usepackage{amsmath}
+bibliography: reference.bib
+csl: science.csl
 ---
@@
 
-pacman::p_load(knitr)
+# setup
+pacman::p_load(knitr,
+               tidyverse)
 
@@
                       warning = FALSE)
+
 options(knitr.kable.NA = '')
 
+op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x)
+
+# theory
+load(here::here("result/result_ricker.RData"))
+
+n_sim <- sim_result %>% 
+  mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
+  pull(n_sim) %>% 
+  unique()
+
+param_set <- sim_result %>% 
+  distinct(n_species,
+           k,
+           r_type,
+           r1,
+           r_min,
+           r_max,
+           sd_env,
+           phi,
+           int_type,
+           alpha,
+           model,
+           seed)
+
+# empirical data
+
+## raw data
+source(here::here("code/data_fmt_fishdata.R"))
+
+filename <- list.files(path = here::here("result"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "reg")) %>% 
+  filter(!str_detect(string = .$value, pattern = "reg_rich")) %>% 
+  pull()
+
+df_beta <- lapply(filename, function(x) {
+  read_csv(here::here(x)) %>% 
+    filter(parameter == "b[2]")
+})
+names(df_beta) <- str_extract(filename, "all|masu|other")
+
+## ssm estimate
+df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
+  pull() %>% 
+  lapply(function(x) {
+    read_csv(x) %>% 
+      filter(param == "bp_value") %>% 
+      select(mean) %>% 
+      mutate(group = str_extract(x, "all|masu|other"))
+  }) %>% 
+  bind_rows()
 ```
@@
 ```
+
+# Materials and Methods
+
+## Theory
+
+We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012]. In the basic formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = N_{i,t}~exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
+\end{align}
+```
+
+ere $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
+We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_1 + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
+\end{align}
+```
+
+$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
+
+```{=tex}
+\begin{align}
+\phi_i = 
+\left\{
+\begin{array}{cc}
+f_R & (i = 1)\\
+0 & (i \ne 1)
+\end{array}
+\right.
+\end{align}
+```
+
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. The equation (2) can be reorganized to:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
+\end{align}
+```
+
+In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
+We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of release $(R_t=R)$.
+
+Prior to the main simulation analysis, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
+We identified five influential parameters (**Table S2-4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`).
+This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
+
+Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates).
+The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
+We initialized the community with populations of each species drawn from a poisson distribution with a mean of five.
+We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
+We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps.
+We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$).
+The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
+We summarized values of simulation parameters in **Table S1**.
+
+## Empirical analysis
+
+### Data
+
+**Time-series data.** We assembled time-series data of fish abundance across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
+At these sites, the long-term monitoring program began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented since 1999.
+Most data were collected in summer with irregular interannual intervals (1 to 3 year intervals for most cases).
+We confined our analysis to the sites that meets the following selection criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon are observed at least twice during the observation period.
+As a result, we used time-series data of fish abundance at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds during a period of 1999-2019.
+**Table S5** summarizes observed species in these watersheds.
+
+**Fish stocking.** At the protected watersheds, stocking of masu salmon began in 1950s.
+Hatchery fish were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
+For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of fish released) for a period of 1999-2019.
+Although fish were released at multiple locations within a watershed, we were unable to extract stocking data at the site level.
+
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
+We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.
+The proportion of forest land use in each watershed polygon was estimated based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
+Annual data of ocean productivity (2003-2019) were extracted from OceanColor ([\<https://oceancolor.gsfc.nasa.gov/\>](https://oceancolor.gsfc.nasa.gov/){.uri}) and the averaged value within the 30-km radius of each river mouth was calculated.
+We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
+
+### Statistical analysis
+
+Our goal is to compare temporal community dynamics across sites.
+However, the data are not directly comparable because of observation errors (e.g., different observers) and missing observations.
+To confront this challenge, we developed a Bayesian state space model for three species groups separately: (i) whole community, summed abundance of all species, (ii) enhanced species, abundance of masu salmon, (iii) unenhanced species, summed abundance of all species except masu salmon.
+A Bayesian state space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
+The model is composed of observation and state models as described below.
+
+In the observation model, we model observation processes.
+Summed fish abundance of either whole community, enhanced species (masu salmon only), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
+
+```{=tex}
+\begin{align}
+N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t})
+\end{align}
+```
+
+where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
+Since fish sampling was conducted after the spring stocking of masu salmon, captured fish may include individuals released in the observation year.
+To avoid biases in estimating temporal community trends, we explicitly modeled this observation process:
+
+```{=tex}
+\begin{align}
+\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
+\end{align}
+```
+
+$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
+The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
+The error term $\epsilon_{s,t}^{obs}$ is drawn from a normal distribution as $\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$ to account for site- and year-specific observation errors.
+When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
+
+In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
+
+```{=tex}
+\begin{align}
+ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
+\end{align}
+```
+
+where $ln~r_{s}$ is the site-specific rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
+The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).
+This hierarchical structure allows for improved estimates of $ln~r_s$ by sharing information across sites.
+We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).
+Bayesian p-values [@keryIntroductionWinBUGSEcologists2010] for the state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
+Estimated parameters and community dynamics are summarized in Supporting Information (**Table S7** and **Figures S13-S15**).
+
+We developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.
+
+```{=tex}
+\begin{align}
+\left\{
+\begin{aligned}
+ln~y_s &\sim Normal(\mu_y, \sigma_y^2) &&\text{for CV, mean, and SD}\\
+y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s})) &&\text{for species richness}
+\end{aligned}
+\right.
+\end{align}
+```
+
+where $\sigma_y$ is the SD of residual errors and $\epsilon_{y,s}$ is the normally-distributed error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$).
+The expected mean $\mu_y$ was related to linear predictors as follows:
+
+```{=tex}
+\begin{align}
+\left\{
+\begin{aligned}
+\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
+ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
+\end{aligned}
+\right.
+\end{align}
+```
+
+$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictor $x_k$.
+The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use (fraction).
+The watershed-specific intercept was related to watershed-level predictors as:
+
+```{=tex}
+\begin{align}
+\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
+\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
+\end{align}
+```
+
+$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients.
+The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (Chlorophyll a).
+The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that cannot be captured by the watershed-level predictors.
+
+We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
+We assigned weakly informative priors for parameters, which were summarized in **Table S6**.
+Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
+
+\newpage
 
@@
 
-```{=tex}
-\begin{equation}
+$$
 \begin{aligned}
@@
 \end{aligned}
-\end{equation}
-```
+$$
 
@@
 
-```{=tex}
-\begin{equation}
+$$
 \begin{aligned}
   \xi_{1,n} &\sim Normal(\mu_n, \sigma^2)\\
-  \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 K_n + \zeta_3 r_{1,n} + \zeta_4 r_{max,n} + \zeta_5 \sigma_{\epsilon,n} + \zeta_6 f_{R, n} + \zeta_7 \bar{\alpha}_n
+  \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 r_{1,n} + \zeta_3 r_{max,n} + \zeta_4  \bar{\alpha}_n + \zeta_5 K_n + \zeta_6 \sigma_{\epsilon,n} + \zeta_7 f_{R, n}
 \end{aligned}
-\end{equation}
-```
+$$
 
@@
 ## Table S1 Simulation parameter
+
 Parameter values used in the main and sensitivity analysis. In the sensitivity analysis, 500 parameter values were drawn randomly from uniform distributions. See Methods for model description.
@@
 ## Table S5 Observed species
+
 Fish species found in the study watersheds.
@@
 ## Table S6 Priors
+
 Prior distributions used in the Bayesian models.
@@
 ## Table S7 Parameter estimates of the Bayesian state space model
+
 Median estimates of the Bayesian state space model. Site specific parameters were excluded due to the large number of parameters. Numbers in parenthesis indicate 95% credible intervals.
@@
 `r paste(knit(text = figure_dyns_chunk), collapse = '\n')`
+
+# References

### 2022-01-30 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 ```
-
 # Materials and Methods
@@
 ```
-
-ere $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obeys an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
 We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
@@
 ```
-
 $R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
@@
 ```
-
 $f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. The equation (2) can be reorganized to:
@@
 ```
-
 In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
@@
 
-Prior to the main simulation analysis, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
+Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
 We identified five influential parameters (**Table S2-4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
@@
 The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
-We initialized the community with populations of each species drawn from a poisson distribution with a mean of five.
+We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five.
 We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period).
@@
 At these sites, the long-term monitoring program began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented since 1999.
-Most data were collected in summer with irregular interannual intervals (1 to 3 year intervals for most cases).
-We confined our analysis to the sites that meets the following selection criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon are observed at least twice during the observation period.
+Most data were collected in summer with irregular interannual intervals (1- to 3-year interval for most cases).
+We confined our analysis to the sites that meets the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon are observed at least twice during the observation period.
 As a result, we used time-series data of fish abundance at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds during a period of 1999-2019.
@@
 Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-Annual data of ocean productivity (2003-2019) were extracted from OceanColor ([\<https://oceancolor.gsfc.nasa.gov/\>](https://oceancolor.gsfc.nasa.gov/){.uri}) and the averaged value within the 30-km radius of each river mouth was calculated.
+Annual data of ocean productivity (2003-2019) were extracted from OceanColor ([\<https://oceancolor.gsfc.nasa.gov/\>](https://oceancolor.gsfc.nasa.gov/){.uri}) and the average value within the 30-km radius of each river mouth was calculated.
 We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
@@
 In the observation model, we model observation processes.
-Summed fish abundance of either whole community, enhanced species (masu salmon only), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
+Summed fish abundance of either whole community, enhanced species (masu salmon), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
 
@@
 ```
-
 where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
@@
 ```
-
 $n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
 The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The error term $\epsilon_{s,t}^{obs}$ is drawn from a normal distribution as $\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$ to account for site- and year-specific observation errors.
+The parameter $\epsilon_{s,t}^{obs}$ is the normally-distributed error term ($\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$) that accounts for site- and year-specific observation errors.
 When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
@@
 ```
-
-where $ln~r_{s}$ is the site-specific rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
+where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
 The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).
@@
 ```
-
 where $\sigma_y$ is the SD of residual errors and $\epsilon_{y,s}$ is the normally-distributed error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$).
@@
 ```
-
 $\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictor $x_k$.
@@
 ```
-
 $\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients.

### 2022-01-30 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
     reference_docx: word_format.docx
-csl: pnas.csl
+csl: science.csl
 knit: (function(inputFile, encoding) {
@@
 
-**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ XXX ^3^ XXX ^4^ XXX
+**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ XXX ^3^ Faculty of Environmental Earth Science, Hokkaido University, Sapporo, Hokkaido 060-0810, Japan ^4^ XXX
 
@@
 
-Although accumulating evidence suggests that stock enhancement with captive-bred organisms entails ecological risks, this method remains to be a common practice in conservation and fisheries.
+Although stock enhancement with captive-bred organisms entails ecological risks, this method remains to be a common practice in conservation and fisheries.
 The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
@@
 Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
-
-## Theoretical predictions
 
@@
 
-## Empirical evidence
-
 To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities.
@@
 
-## Implications
-
 The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996].
@@
 
-# Methods
-
-## Theory
-
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012]. In the basic formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
-
-$$
-\begin{aligned}N_{i,t+1} = N_{i,t}~exp[r_i(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t}) &\text{(1)}
-\end{aligned}
-$$
-
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
-We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
-
-$$
-\begin{aligned}
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i \{1-\frac{N_{i,t}+\alpha_{i1} (N_1 + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i}\}]exp(\epsilon_{i,t}) &\text{(2)}
-\end{aligned}
-$$
-
-$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
-
-$$
-\begin{aligned}
-\phi_i = \left\{
-\begin{array}{}
-f_R & (i = 1)\\
-0 & (i \ne 1)
-\end{array}
-\right.
-&\text{(3)}
-\end{aligned}
-$$
-
-$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. The equation (2) can be reorganized to:
-
-$$
-\begin{aligned}
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp[r_i(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]exp(\epsilon_{i,t}) &\text{(4)}
-\end{aligned}
-$$
-
-In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
-We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of release $(R_t=R)$.
-
-Prior to the main simulation analysis, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (**Supporting Information**).
-We identified five influential parameters (**Table S2-4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`).
-This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
-
-Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates).
-The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
-We initialized the community with populations of each species drawn from a poisson distribution with a mean of five.
-We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
-We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps.
-We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$).
-The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
-We summarized values of simulation parameters in **Table S1**.
-
-## Empirical analysis
-
-### Data
-
-**Time-series data.** We assembled time-series data of fish abundance across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-At these sites, the long-term monitoring program began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999.
-Most data were collected in summer to fall with irregular sampling intervals (0 to 3 year intervals for most cases).
-We confined our analysis to the sites that meets the following selection criteria: (1) the observation span (from the first to the last year of observation) exceeds 10 years, (2) the number of observation years exceeds five years, and (3) masu salmon are observed at least twice during the observation period.
-As a result, we used time-series data of fish abundance at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds during a period of 1999-2019.
-**Table S5** summarizes observed species in these watersheds.
-
-**Fish stocking.** At the protected watersheds, stocking of masu salmon began in 1950s.
-A mixture of captive-bred and wild-born individuals were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
-For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of fish released) for a period of 1999-2019.
-Although fish were released at multiple locations within a watershed, we were unable to extract stocking data at the site level.
-
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
-We used MERIT Hydro [@yamazakiMERITHydroHighResolution2019] to delineate upstream watershed polygons for each sampling site.
-The proportion of forest land use in each watershed polygon was estimated based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
-Climate data at each sampling site were extracted from CHELSA ver.
-1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-Annual data of ocean productivity (2003-2019) were extracted from OceanColor (<https://oceancolor.gsfc.nasa.gov/>) and the averaged value within the 30-km radius of each river mouth was calculated.
-We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
-
-### Statistical analysis
-
-Our goal is to compare temporal community dynamics across sites.
-However, the data are not directly comparable because of observation errors (e.g., different observers) and missing observations.
-To confront this challenge, we developed a Bayesian state space model for three species groups separately: (1) whole community, summed abundance of all species, (2) enhanced species, abundance of masu salmon, (3) unenhanced species, summed abundance of all species except masu salmon.
-A Bayesian state space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004a; @keryBayesianPopulationAnalysis2012].
-The model is composed of observation and state models as described below.
-
-In the observation model, we model observation processes.
-Summed fish abundance of either whole community, enhanced species (masu salmon only), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
-
-$$
-\begin{aligned}
-N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t}) &\text{(6)}
-\end{aligned}
-$$
-
-where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
-Since fish sampling was conducted after the spring stocking of masu salmon, captured fish may include individuals released in the observation year.
-To avoid biases in estimating temporal community trends, we explicitly modeled this observation process:
-
-$$
-\begin{aligned}
-\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t} &\text{(7)}
-\end{aligned}
-$$
-
-$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
-The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The error term $\epsilon_{s,t}^{obs}$ is drawn from a normal distribution as $\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$ to account for site- and year-specific observation errors.
-When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
-
-In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
-
-$$
-\begin{aligned}
-ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state} &\text{(8)}
-\end{aligned}
-$$ where $ln~r_{s}$ is the site-specific rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
-The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).
-This hierarchical structure allows for improved estimates of $ln~r_s$ by sharing information across sites.
-We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).
-Bayesian p-values [@keryIntroductionWinBUGSEcologists2010] for the state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
-Estimated parameters and community dynamics are summarized in Supporting Information (**Table S7** and **Figures S13-S15**).
-
-We developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.
-
-$$
-\begin{aligned}
-\left\{
-\begin{array}{}
-ln~y_s &\sim Normal(\mu_y, \sigma_y^2)~&&~\text{for CV, mean, and SD} &&&\text{(9a)}\\
-y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s}))~&&\text{for species richness} &&&\text{(9b)}
-\end{array}
-\right.
-\end{aligned}
-$$
-
-where $\sigma_y$ is the SD of residual errors and $\epsilon_{y,s}$ is the normally-distributed error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$).
-The expected mean $\mu_y$ was related to linear predictors as follows:
-
-$$
-\begin{aligned}
-\left\{
-\begin{array}{}
-\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD} &&&\text{(10a)}\\
-ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness} &&&\text{(10b)}
-\end{array}
-\right.
-\end{aligned}
-$$
-
-$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictor $x_k$.
-The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use (fraction).
-The watershed-specific intercept was related to watershed-level predictors as:
-
-$$
-\begin{aligned}
-\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)  &&\text{(11a)}\\
-\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w} &&\text{(11b)}
-\end{aligned}
-$$
-
-$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients.
-The watershed-level predictors $z_{k,w}$ include the number of released masu salmon and ocean productivity (sea surface chlorophyll a).
-The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that cannot be captured by the watershed-level predictors.
-
-We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R [@denwoodRunjagsPackageProviding2013].
-We assigned weakly informative priors for parameters, which were summarized in **Table S6**.
-Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
-
 # Data availability

### 2022-01-30 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 ```
-$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. The equation (2) can be reorganized to:
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation (2) can be reorganized to:
 
@@
 In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
-We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of release $(R_t=R)$.
+We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
 
@@
 We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five.
-We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period).
+We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach equilibrium without stock enhancement (initialization period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective stock enhancement (burn-in period).
 We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps.
@@
 
-**Time-series data.** We assembled time-series data of fish abundance across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-At these sites, the long-term monitoring program began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented since 1999.
-Most data were collected in summer with irregular interannual intervals (1- to 3-year interval for most cases).
-We confined our analysis to the sites that meets the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon are observed at least twice during the observation period.
-As a result, we used time-series data of fish abundance at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds during a period of 1999-2019.
+**Time-series data.** We assembled time-series fish data across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
+A long-term monitoring program began at these sites in 1971, but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999.
+Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases).
+We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
+As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019.
 **Table S5** summarizes observed species in these watersheds.
 
-**Fish stocking.** At the protected watersheds, stocking of masu salmon began in 1950s.
+**Fish stocking.** At the protected watersheds, the stocking of masu salmon began in the 1950s.
 Hatchery fish were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
-For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of fish released) for a period of 1999-2019.
-Although fish were released at multiple locations within a watershed, we were unable to extract stocking data at the site level.
+For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of fish released) from 1999 to 2019.
+Although fish were released at multiple locations within a watershed, we could not extract stocking data at the site level.
 
@@
 We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.
-The proportion of forest land use in each watershed polygon was estimated based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+We estimated the proportion of forest land use in each watershed polygon based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
 Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-Annual data of ocean productivity (2003-2019) were extracted from OceanColor ([\<https://oceancolor.gsfc.nasa.gov/\>](https://oceancolor.gsfc.nasa.gov/){.uri}) and the average value within the 30-km radius of each river mouth was calculated.
+Annual data of ocean productivity (2003-2019) were extracted from OceanColor ([\<https://oceancolor.gsfc.nasa.gov/\>](https://oceancolor.gsfc.nasa.gov/){.uri}) and we calculated the average value within the 30-km radius of each river mouth.
 We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
@@
 Our goal is to compare temporal community dynamics across sites.
-However, the data are not directly comparable because of observation errors (e.g., different observers) and missing observations.
-To confront this challenge, we developed a Bayesian state space model for three species groups separately: (i) whole community, summed abundance of all species, (ii) enhanced species, abundance of masu salmon, (iii) unenhanced species, summed abundance of all species except masu salmon.
-A Bayesian state space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
-The model is composed of observation and state models as described below.
+However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
+To confront this challenge, we developed a Bayesian state-space model for three species groups separately: (i) whole community, summed abundance of all species, (ii) enhanced species, the abundance of masu salmon, (iii) unenhanced species, summed abundance of all species except masu salmon.
+A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
+The model is composed of observation and state models, as described below.
 
@@
 The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The parameter $\epsilon_{s,t}^{obs}$ is the normally-distributed error term ($\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$) that accounts for site- and year-specific observation errors.
+The parameter $exp(\epsilon_{s,t}^{obs})$ is the error term that follows a log-normal distribution ($\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$).
+The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
 When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
@@
 The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).
-This hierarchical structure allows for improved estimates of $ln~r_s$ by sharing information across sites.
+This hierarchical structure allows for improved estimates of $ln~r_s$ by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
 We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).
-Bayesian p-values [@keryIntroductionWinBUGSEcologists2010] for the state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
-Estimated parameters and community dynamics are summarized in Supporting Information (**Table S7** and **Figures S13-S15**).
 
-We developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.
+We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data.
+Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
+**Table S7** and **Figures S13-S15** summarize estimated parameters and community dynamics.
+
+We developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
 
@@
 \begin{aligned}
-ln~y_s &\sim Normal(\mu_y, \sigma_y^2) &&\text{for CV, mean, and SD}\\
+ln~y_s &\sim Normal(\mu_{y,s}, \sigma_y^2) &&\text{for CV, mean, and SD}\\
 y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s})) &&\text{for species richness}
@@
 ```
-where $\sigma_y$ is the SD of residual errors and $\epsilon_{y,s}$ is the normally-distributed error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$).
+where $\sigma_y$ is the SD of residual errors and $exp(\epsilon_{y,s})$ is the error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$).
 The expected mean $\mu_y$ was related to linear predictors as follows:
@@
 ```
-$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictor $x_k$.
-The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use (fraction).
+$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$.
+The site-level predictors include upstream watershed area, air temperature, precipitation, and proportion of forest land use.
 The watershed-specific intercept was related to watershed-level predictors as:
@@
 The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (Chlorophyll a).
-The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that cannot be captured by the watershed-level predictors.
+The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
+All predictors were standardized (mean = 0, SD = 1) before the analysis.
 
 We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
-We assigned weakly informative priors for parameters, which were summarized in **Table S6**.
+We assigned weakly informative priors to parameters (**Table S6**).
 Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
@@
 This yields a total of 50000 simulation replicates.
-In each simulation replicate, we ran 1600 time steps of community dynamics and obtained temporal means and SDs of whole community ($\sum_i^SN_i$), enhanced species ($N_1$), and unenhanced species ($\sum_{i, i\ne1}^SN_i$) using the last 1000 time steps.
+In each simulation replicate, we ran 1600 time steps of community dynamics and obtained temporal means and SDs of the whole community ($\sum_i^SN_i$), enhanced species ($N_1$), and unenhanced species ($\sum_{i, i\ne1}^SN_i$) using the last 1000 time steps.
 The first 600 time steps were discarded as initialization and burn-in periods.
 
-For each parameter combination, we regressed mean densities and SDs of whole community, enhanced species, and unenhanced species $y_j$ on the number of release $R$ as:
+For each parameter combination, we regressed mean densities and SDs of the whole community, enhanced species, and unenhanced species $y_j$ on the number of releases $R$ as:
 
@@
 where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$).
-Both response and explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.
+Both response and explanatory variables were standardized to a mean of zero and a standard deviation of one to compare regression coefficients.
 
@@
 
-Parameter values used in the main and sensitivity analysis. In the sensitivity analysis, 500 parameter values were drawn randomly from uniform distributions. See Methods for model description.
+Parameter values used in the main and sensitivity analysis. Five hundred parameter values were drawn randomly from uniform distributions in the sensitivity analysis.
 
@@
 Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],".
-Both response and explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.")
+Both response and explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one before the analysis.")
 
@@
 
-## Table S7 Parameter estimates of the Bayesian state space model
+## Table S7 Parameter estimates of the Bayesian state-space model
 
-Median estimates of the Bayesian state space model. Site specific parameters were excluded due to the large number of parameters. Numbers in parenthesis indicate 95% credible intervals.
+Median estimates of the Bayesian state-space model. Numbers in parenthesis indicate 95% credible intervals. Site-specific parameters were excluded due to a large number of parameters.
 
@@
                        "Theoretical predictions for the stocking effect on community dynamics.
-Rows represent different response varaibles, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
+Rows represent different response variables, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
 Other parameters are: ",
@@
                        "Temporal dynamics of stream fish communities (`r c_text[",i,"]`) in Hokkaido, Japan.
-Dots represent observed density, and solid lines are predicted values of the Bayesian state-space model.
-Panels correspond to individual watersheds, and colors distinguish samplig sites within a watershed.",
+Dots represent observed density, and solid lines are the predicted values of the Bayesian state-space model.
+Panels correspond to individual watersheds, and colors distinguish sampling sites within a watershed.",
                         "\n\\pagebreak\n")

### 2022-01-31 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
+df_area <- d0 %>% 
+  group_by(site_id, year) %>% 
+  summarize(area = unique(area))
+
 filename <- list.files(path = here::here("result"), full.names = T) %>% 
@@
   bind_rows()
+
+## mcmc sample size
+df_mcmc_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
+  pull() %>% 
+  lapply(function(x) {
+    read_csv(x) %>% 
+      select(n_total_mcmc,
+             n_sample,
+             n_thin,
+             n_burn) %>% 
+      distinct()
+  }) %>% 
+  bind_rows()
+
+df_mcmc_reg <- list.files(path = here::here("result"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "reg_")) %>% 
+  filter(!str_detect(string = .$value, pattern = "rich")) %>% 
+  pull() %>% 
+  lapply(function(x) {
+    read_csv(x) %>% 
+      select(n_total_mcmc,
+             n_sample,
+             n_thin,
+             n_burn) %>% 
+      distinct()
+  }) %>% 
+  bind_rows()
+
 ```
@@
 \begin{align}
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_1 + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
+N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
 \end{align}
@@
 **Time-series data.** We assembled time-series fish data across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-A long-term monitoring program began at these sites in 1971, but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999.
-Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases).
+A long-term monitoring program began at these watersheds in 1971, but an effective sampling method (two-pass sampling with a combination of electrofishing and cast net) was implemented in 1999.
+Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
 We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
 As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019.
+Summed abundance of first and second passes was used in the following analysis.
 **Table S5** summarizes observed species in these watersheds.
@@
 However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
-To confront this challenge, we developed a Bayesian state-space model for three species groups separately: (i) whole community, summed abundance of all species, (ii) enhanced species, the abundance of masu salmon, (iii) unenhanced species, summed abundance of all species except masu salmon.
+To confront this challenge, we developed a Bayesian state-space model for three species groups separately: (i) whole community, the summed abundance of all species, (ii) enhanced species, the abundance of masu salmon, (iii) unenhanced species, the summed abundance of all species except masu salmon.
 A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
@@
 In the observation model, we model observation processes.
-Summed fish abundance of either whole community, enhanced species (masu salmon), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
+Fish abundance of either whole community, enhanced species (masu salmon), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
 
@@
 Since fish sampling was conducted after the spring stocking of masu salmon, captured fish may include individuals released in the observation year.
-To avoid biases in estimating temporal community trends, we explicitly modeled this observation process:
+We explicitly modeled this observation process to avoid biases in estimating temporal community trends:
 
@@
 We assigned weakly informative priors to parameters (**Table S6**).
+Three Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
+Total MCMC interations ranged from `r min(df_mcmc_ssm$n_total_mcmc)` to `r max(df_mcmc_ssm$n_total_mcmc)` for the state-space models and was `r unique(df_mcmc_reg$n_total_mcmc)` for the regression models.
+The first `r unique(c(df_mcmc_ssm$n_burn, df_mcmc_reg$n_burn))` iterations were discarded as burn-in, and MCMC samples were saved every `r unique(df_mcmc_ssm$n_thin)` (state-space) and `r unique(df_mcmc_reg$n_thin)` iterations (regression) to reduce autocorrelation.
+Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached \< 1.1 [@gelmanDataAnalysisUsing2007].
 Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].

### 2022-01-31 rmd/figures.Rmd
Update figures.Rmd

@@
 **Figure 1** Theory and empirical observations agree that stock enhancement destabilizes community dynamics.
-Panels and colors distinguish response variables and species groups, respectively.
+In A and B, panels and colors distinguish response variables and species groups, respectively.
 (A) Theoretical predictions.
@@
 Dots represent observed values in 31 watersheds.
-We averaged site-level values (geometric mean) in each watershed.
+Site-level values were averaged in each watershed (geometric mean).
 Lines are predicted values of regression models, and line types corresponds to posterior probabilities of regression coefficients.

### 2022-01-31 rmd/manuscript.Rmd
edit: manuscript

@@
 
-**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ XXX ^3^ Faculty of Environmental Earth Science, Hokkaido University, Sapporo, Hokkaido 060-0810, Japan ^4^ XXX
+**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Salmon and Freshwater Fisheries Research Institute, Hokkaido Research Organization, Eniwa, Hokkaido 061-1433, Japan ^3^ Faculty of Environmental Earth Science, Hokkaido University, Sapporo, Hokkaido 060-0810, Japan ^4^ XXX
 
@@
 
-Although stock enhancement with captive-bred organisms entails ecological risks, this method remains to be a common practice in conservation and fisheries.
-The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
-Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
-Here, we use a simple theory to show that stock enhancement undermines long-term community stability by disrupting the sensitive balance of species interactions in natural communities.
-Stock enhancement destabilized community dynamics through facilitating competitive exclusion across a wide range of simulated scenarios.
-The present study further provided empirical support for this theoretical prediction using long-term data of Japanese stream fish communities.
-As our theory predicts, stream fish communities showed greater temporal fluctuations and reduced biodiversity in watersheds with intensive stocking of hatchery masu salmon - one of the most valuable freshwater resources in the region.
+There is increasing awareness that stock enhancement with captive-bred organisms brings ecological risks to wild populations.
+Still, we may underestimate the negative impact of stock enhancement because current schemes rarely consider the consequences for the whole ecological community.
+Here, we use theory and long-term data of Japanese stream fish communities to show that stock enhancement undermines community stability.
+Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion.
+Consistent with this prediction, fish communities showed greater temporal fluctuations and reduced biodiversity in rivers with the intensive stocking of hatchery masu salmon - one of the most valuable freshwater resources in the region.
 Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
@@
 
-Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to the sustainable management of natural resources [@cardinaleBiodiversityLossIts2012].
-Captive breeding is a common practice to conserve or enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996].
-Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007a; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996; @griffithsCaptiveBreedingReintroduction2008; @haagNorthAmericanFreshwater2012] and fisheries [@kitadaEconomicEcologicalGenetic2018; @arakiHatcheryStockingHelp2010].
+Human demands for natural resources are ever increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@cardinaleBiodiversityLossIts2012].
+Captive breeding is a common practice to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996].
+Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996; @griffithsCaptiveBreedingReintroduction2008; @haagNorthAmericanFreshwater2012] and natural resource management [@kitadaEconomicEcologicalGenetic2018; @arakiHatcheryStockingHelp2010].
 In fisheries for example, billions of hatchery-reared individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
@@
 Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012].
-Hence, this form of species management may have significant consequences for community dynamics in the long term.
+Hence, this form of species management may undermine the ecological process that allows competing species to coexist, ultimately compromising the long-term community stability.
 Evidence for this hypothesis is lacking, however.
@@
 The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \>10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].
-Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
 
@@
 $$
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp[r_i(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i})]~exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp\left[r_i\left(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i}\right)\right]~exp(\epsilon_{i,t})
 $$
@@
 \phi_i = \left\{
-\begin{array}{}
+\begin{array}{cc}
 f_R & (i = 1)\\
@@
 The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996].
-As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007a].
+As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007].
 Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.

### 2022-01-31 rmd/manuscript.Rmd
edit: manuscript

@@
 
-## ssm estimate
-df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      filter(param == "bp_value") %>% 
-      select(mean) %>% 
-      mutate(group = str_extract(x, "all|masu|other"))
-  }) %>% 
-  bind_rows()
-
 ```
@@
 
-Human demands for natural resources are ever increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@cardinaleBiodiversityLossIts2012].
-Captive breeding is a common practice to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996].
-Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996; @griffithsCaptiveBreedingReintroduction2008; @haagNorthAmericanFreshwater2012] and natural resource management [@kitadaEconomicEcologicalGenetic2018; @arakiHatcheryStockingHelp2010].
-In fisheries for example, billions of hatchery-reared individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
+Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010].
+Captive breeding is common to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
+Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
+In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
 The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
@@
 Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
-Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
+Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
 Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012].
-Hence, this form of species management may undermine the ecological process that allows competing species to coexist, ultimately compromising the long-term community stability.
+Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability.
 Evidence for this hypothesis is lacking, however.
 
-Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a].
+Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a].
 Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences.
@@
 
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with selective stock enhancement of a constituent species (species 1).
+We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the selective stock enhancement of a constituent species (species 1).
 Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 $f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals.
-Therefore, the model accounts for fitness difference of captive-bred individuals due to genetic effects and/or plasticity [@weberInteractionsHatcheryWild2003; @snyderLimitationsCaptiveBreeding1996; @arakiHatcheryStockingHelp2010] when considering the reproductive contribution of released individuals to the next generation of the enhanced species.
+Therefore, the model accounts for the fitness difference of captive-bred individuals due to genetic effects and/or plasticity [@weberInteractionsHatcheryWild2003; @snyderLimitationsCaptiveBreeding1996; @arakiHatcheryStockingHelp2010] when considering the reproductive contribution of released individuals to the next generation.
 Without loss of generality, we assumed constant $K_i$ ($K_i = K$) and $R_t$ ($R_t = R$) across species and time, respectively.
+We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios that cover a range of ecological contexts (see **Materials and Methods**).
+The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of the total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$).
+We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.
 
-In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species ($r_1=$ `r unique(sim_result$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(sim_result$alpha)`), carrying capacity ($K=$ `r unique(sim_result$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(sim_result$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(sim_result$phi)`).
-We chose these parameters because our sensitivity analysis revealed that they were influential in altering the relationship between community dynamics and stock enhancement (**Supporting Information**).
-Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$).
-The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$).
-In addition, the temporal mean and SD were also calculated for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.
-
-When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (**Figure 1A**).
+When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (**Figure 1A**).
 This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
 For enhanced species, released individuals induced overcompensation, in which the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
-Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals, confirming previous theoretical predictions [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition caused the reduced mean density of unenhanced species and led to decreased numbers of persisting species at high levels of stock enhancement (**Figure 1A**).
+Therefore, the enhanced species reached the lower long-term average of population density with stocking, confirming previous theoretical predictions [@satakeStockingCaptivebredFish2012].
+Meanwhile, interspecific competition reduced the unenhanced species with fewer persisting species at high levels of stock enhancement (**Figure 1A**).
 Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (**Figure 1A**).
@@
 Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density resulted in the increased CV.
-These patterns were qualitatively similar across most ecological scenarios even when interspecific competition is very weak (**Figure S1-6**).
+These patterns were qualitatively similar across most ecological scenarios (**Figure S1-6**).
 
-The destabilizing effect emerges because stock enhancement undermines the balance of species interactions that underpins community stability.
-Ecological theory suggests that stable coexistence of competing species requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a].
-Under this condition, competing species can grow from small populations because numerically dominant species undergoes stronger intraspecific competition [@carrollNicheFitnessDifferences2011a].
-Such stable coexistence increases the likelihood of stabilizing temporal dynamics of species rich communities [@tilmanEcologicalConsequencesChanges1999a] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], that is, total community density of a multi-species community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$).
-However, stock enhancement is externally controlled and the number of release is not subject to density-dependent regulation.
-Therefore, excessive individuals supplemented through stock enhancement impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.
+The destabilizing effect emerges because stock enhancement affects the balance of species interactions that underpins community stability.
+In theory, the stable coexistence requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a].
+Under this condition, competing species can grow from small populations because dominant species undergo stronger intraspecific competition [@carrollNicheFitnessDifferences2011a].
+Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999a] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multispecies community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$).
+However, stock enhancement is externally controlled, and the number of releases is not subject to density-dependent regulation.
+Therefore, released individuals impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.
 
-The only scenario where stock enhancement had little influence on community dynamics was when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**).
-In particular, stock enhancement increased the average density of the enhanced species with low population growth rate ($r_1=0.5$; **Figures S7 and S8**).
-This result may explain why some of the best evidence for successful stock enhancement comes from endangered species that typically suffer from increased mortality [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
-More importantly, the contrasting community response at different levels of carrying capacity casts light on the limitation of stock enhancement.
-One of the core motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020].
-Ironically, however, our results suggest that stock enhancement will not bring desired ecological outcomes unless we resolve root causes that compromise environmental capacity first.
+Stock enhancement, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**).
+In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figures S7 and S8**).
+This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
+More importantly, the contrasting community response at different carrying capacities provides deeper insights.
+One of the core motivations for stock enhancement is to mitigate declining trends of natural resources due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020].
+Ironically, our results suggest that stock enhancement will not bring desired outcomes unless we resolve root causes that compromise environmental capacity first.
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities.
-Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and extensive hatchery programs have been implemented [@kitadaLessonsJapanMarine2020].
-In protected watersheds (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018].
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
+Masu salmon is one of Japan's most valuable freshwater resources, and over 10 million hatchery fish are released annually across the nation [@kitadaLessonsJapanMarine2020].
+In the protected watersheds (**Figure 1C and 1D**), the Hokkaido government led the standardized monitoring of fish communities over the past six decades, along with the official stocking records.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
-In this study, we used the long-term data (1999-2019) of stream fish communities at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criteria).
+In this study, we used the long-term community data (1999-2019) at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criteria).
 Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.
 
-As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**).
-The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**).
+Our analysis strongly supports the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
 This pattern was associated with the reduced long-term average of total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics).
-In the meantime, the SDs had vague relationships with stock enhancement, and neither positive nor negative relationship was supported by statistical analysis (**Figure 1B and 2**).
-At the population level, similar responses to stock enhancement have been reported in other fish and aquatic invertebrates [@arakiHatcheryStockingHelp2010].
-Our analysis builds upon these findings by illustrating the community-level response.
+In the meantime, the SDs had vague relationships with stock enhancement (**Figure 1B and 2**).
 
-In our theory, the observed pattern emerges when negative density dependence operates in the recipient community, and previous observations confirm this assumption.
-Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that released masu salmon compete with wild masu salmon [@sahashiEvaluationContributionHatchery2015a] and other stream fishes [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018].
-Hatchery-reared salmons are larger and more aggressive than wild individuals, further increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003].
-Importantly, the number of fish released is controlled by socioeconomic factors (e.g., budget allocation).
+Competition with wild masu salmon and other fish species is a likely mechanism, as our theory assumes.
+Field experiments confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018].
+Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003].
+Importantly, socioeconomic factors control the number of releases (e.g., budget allocation).
 As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may cause resource competition that would otherwise not exist.
 
-Reduced fitness of captive-bred individuals may also play a role in producing the observed community response.
-As with other salmonid species, ocean-migrating adults of captive-bred masu salmon show lower return rates to the spawning river.
-It has also been shown that hatchery-reared salmons are more susceptible to predation than wild salmons [@weberInteractionsHatcheryWild2003].
-The fitness disadvantage of captive-bred fish may add to negative density dependence to reduce the long-term average of community density, undermining community stability in the long term.
+The reduced fitness of hatchery masu salmon may also play a role in the observed response.
+Like other salmonids, ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress].
+Hatchery salmons are also more susceptible to predation than wild ones [@weberInteractionsHatcheryWild2003].
+The fitness disadvantage of captive-bred fish may add to negative density dependence to influence community stability.
 
-Like any non-experimental studies, we cannot exclude the possibility that our results were driven by spurious correlations.
-However, in the protected watersheds, any exploitation of aquatic species and alteration of in-stream habitats (e.g., construction of river-crossing structure) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences played a major role in the observed relationships.
-Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables (see **Methods** and **Tables S8-S10**).
-This unique study setup may have helped uncover the close agreement between theory and empirical patterns.
+Like any non-experimental study, we cannot exclude the possibility that spurious correlations drove our results.
+However, in the protected watersheds, human activities (e.g., exploitation, construction of river-crossing structures) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
+Further, we have statistically controlled natural variation in environmental factors, including climatic and land-use variables (see **Materials and Methods** and **Tables S8-S10**).
+This unique setup may have helped uncover the close agreement between theory and empirical patterns.
 
 The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996].
-As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007].
 Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.
-The results of this study suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community.
-While our empirical example is limited to stream fish communities, the consistent emergence of destabilizing effect across simulated ecological scenarios implies that this ecological phenomenon is pervasive across terrestrial and aquatic taxa.
+Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community.
+While our empirical example is limited to stream fish communities, the destabilizing effect emerged across diverse simulated scenarios, implying that this phenomenon is pervasive across terrestrial and aquatic taxa.
 
-We should prioritize the preservation and restoration efforts of natural habitats with a broader scope of biodiversity conservation.
-Such efforts are particularly important in the Anthropocene because the undesired influence of stock enhancement may be exacerbated in degraded habitats.
-Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieve successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017].
-For example, coordinated placement of conservation sites considering spatial biodiversity patterns is of critical importance in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013].
+We should prioritize habitat preservation and restoration with a broader scope of biodiversity conservation.
+Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement.
+Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieving successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017].
+For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020].
 Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
-These considerable potentials indicate that we have viable management options for the sustainable future of natural resources before blindly accepting stock enhancement.
-Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.
+These considerable potentials indicate that viable management options for the sustainable future exist before blindly accepting stock enhancement.
+Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.
 

### 2022-02-01 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
-The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.
+The widespread use of captive breeding is perhaps because of the "myth" that demographic benefits of released individuals may exceed the associated risks.
 
@@
 Without loss of generality, we assumed constant $K_i$ ($K_i = K$) and $R_t$ ($R_t = R$) across species and time, respectively.
-We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios that cover a range of ecological contexts (see **Materials and Methods**).
+
+We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios.
+These scenarios cover a range of ecological contexts, differing in the intrinsic growth of the enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$ (see **Materials and Methods**).
 The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of the total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$).
@@
 
-When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (**Figure 1A**).
+When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
 This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
-For enhanced species, released individuals induced overcompensation, in which the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals.
-Therefore, the enhanced species reached the lower long-term average of population density with stocking, confirming previous theoretical predictions [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition reduced the unenhanced species with fewer persisting species at high levels of stock enhancement (**Figure 1A**).
-Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (**Figure 1A**).
+The enhanced species decreased because stocking induced the negative competitive effect exceeding the demographic benefit of released individuals [@satakeStockingCaptivebredFish2012].
+Meanwhile, interspecific competition reduced the unenhanced species at high levels of stock enhancement, resulting in fewer persisting species (**Figure 1A**).
+Combined, the long-term average of the total community density decreased more sharply than individual species groups (**Figure 1A**).
 The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure 1A**).
-Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density resulted in the increased CV.
-These patterns were qualitatively similar across most ecological scenarios (**Figure S1-6**).
+Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
+These patterns were qualitatively similar in a range of ecological contexts (robust to the changes in $r_1$, $\bar{\alpha}$, $\sigma_{\epsilon}$, and $f_R$; **Figure S1-6**).
 
@@
 More importantly, the contrasting community response at different carrying capacities provides deeper insights.
-One of the core motivations for stock enhancement is to mitigate declining trends of natural resources due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020].
+One of the core motivations for stock enhancement is to mitigate declining trends of natural resources due to human impacts, such as habitat loss [@chaseEcosystemDecayExacerbates2020].
 Ironically, our results suggest that stock enhancement will not bring desired outcomes unless we resolve root causes that compromise environmental capacity first.
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
-Masu salmon is one of Japan's most valuable freshwater resources, and over 10 million hatchery fish are released annually across the nation [@kitadaLessonsJapanMarine2020].
-In the protected watersheds (**Figure 1C and 1D**), the Hokkaido government led the standardized monitoring of fish communities over the past six decades, along with the official stocking records.
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
+Masu salmon is one of Japan's most valuable freshwater resources, and over 10 million hatchery fish are released annually [@kitadaLessonsJapanMarine2020].
+In the protected watersheds (**Figure 1C and 1D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
-In this study, we used the long-term community data (1999-2019) at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criteria).
+We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see **Materials and Methods** for selection criteria).
 Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.
 
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**).
-Our analysis strongly supports the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**).
+Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
 This pattern was associated with the reduced long-term average of total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics).
@@
 
-Competition with wild masu salmon and other fish species is a likely mechanism, as our theory assumes.
+Competition is a likely mechanism, as our theory assumes.
 Field experiments confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018].
@@
 Importantly, socioeconomic factors control the number of releases (e.g., budget allocation).
-As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may cause resource competition that would otherwise not exist.
+As such, released fish are probably "excessive" given the density-dependent regulation of recipient communities and may cause resource competition that would otherwise not exist.
 
@@
 Like other salmonids, ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress].
-Hatchery salmons are also more susceptible to predation than wild ones [@weberInteractionsHatcheryWild2003].
-The fitness disadvantage of captive-bred fish may add to negative density dependence to influence community stability.
+In addition, hatchery salmons are more susceptible to predation than wild ones [@weberInteractionsHatcheryWild2003].
+The fitness disadvantage of hatchery fish may add to negative density dependence to influence community stability.
 

### 2022-02-01 code/figure_obs_stock.R
edit: figure, minor label change

@@ -128,7 +128,7 @@ g_obs <- df_plot %>%
   scale_color_hue(labels = c("Whole", "Enhanced", "Unenhanced")) +
   scale_linetype_manual(values = c("solid", "dashed", "dotted"),
                         labels = c("> 0.95", "0.90-0.95", "< 0.90")) +
-  labs(x = expression("Number of release (thousand fish year"^-1*")"),
+  labs(x = expression("Number of releases (thousand fish year"^-1*")"),
        y = "Value",
        color = "Species group",
        linetype = "Posterior prob.") +

### 2022-02-01 code/figure_theory.R

@@ -61,7 +61,7 @@ g_theory <- df0 %>%
   geom_smooth(size= 0.1,
               method = "loess") +
   scale_color_hue(labels = c("Whole", "Enhanced", "Unenhanced")) +
-  labs(x = "Number of release (individuals)",
+  labs(x = "Number of releases (individuals)",
        y = "Value",
        color = "Species group") +
   facet_wrap(facets = ~ response_name,

### 2022-02-01 rmd/manuscript.Rmd
edit: manuscript

@@
 $f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals.
-Therefore, the model accounts for the fitness difference of captive-bred individuals due to genetic effects and/or plasticity [@weberInteractionsHatcheryWild2003; @snyderLimitationsCaptiveBreeding1996; @arakiHatcheryStockingHelp2010] when considering the reproductive contribution of released individuals to the next generation.
+Therefore, the model accounts for the fitness difference of captive-bred individuals due to genetic effects and/or plasticity [@weberInteractionsHatcheryWild2003; @snyderLimitationsCaptiveBreeding1996; @arakiHatcheryStockingHelp2010] when considering the reproductive contribution to the next generation.
 Without loss of generality, we assumed constant $K_i$ ($K_i = K$) and $R_t$ ($R_t = R$) across species and time, respectively.
@@
 When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
-This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
+This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
 The enhanced species decreased because stocking induced the negative competitive effect exceeding the demographic benefit of released individuals [@satakeStockingCaptivebredFish2012].
 Meanwhile, interspecific competition reduced the unenhanced species at high levels of stock enhancement, resulting in fewer persisting species (**Figure 1A**).
-Combined, the long-term average of the total community density decreased more sharply than individual species groups (**Figure 1A**).
+Combined, the total community density decreased more sharply than individual species groups (**Figure 1A**).
 The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure 1A**).
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
-These patterns were qualitatively similar in a range of ecological contexts (robust to the changes in $r_1$, $\bar{\alpha}$, $\sigma_{\epsilon}$, and $f_R$; **Figure S1-6**).
+These patterns were qualitatively similar across most ecological contexts (robust to the changes in $r_1$, $\bar{\alpha}$, $\sigma_{\epsilon}$, and $f_R$; **Figure S1-6**).
 
@@
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
-Masu salmon is one of Japan's most valuable freshwater resources, and over 10 million hatchery fish are released annually [@kitadaLessonsJapanMarine2020].
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**), one of Japan's most valuable freshwater resources [@kitadaLessonsJapanMarine2020], on the long-term stability of stream fish communities in Hokkaido, Japan.
 In the protected watersheds (**Figure 1C and 1D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
@@
 Competition is a likely mechanism, as our theory assumes.
-Field experiments confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018].
+Field experiments confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018].
 Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003].
 Importantly, socioeconomic factors control the number of releases (e.g., budget allocation).
-As such, released fish are probably "excessive" given the density-dependent regulation of recipient communities and may cause resource competition that would otherwise not exist.
+As such, given the density-dependent regulation of recipient communities, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
 
@@
 Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement.
-Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieving successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017].
-For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020].
+Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieving successful conservation.
+For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022].
 Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
@@
 
-# Data availability
-
 # Acknowledgments
 
+We are grateful to the participants involved in the long-term monitoring program at the protected watersheds in Hokkaido.
+We thank Masato Yamamichi for helpful discussion on this manuscript.
+Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.
+
 # References

### 2022-02-01 rmd/supporting_info.Rmd
edit: manuscript

@@
 
-**Time-series data.** We assembled time-series fish data across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-A long-term monitoring program began at these watersheds in 1971, but an effective sampling method (two-pass sampling with a combination of electrofishing and cast net) was implemented in 1999.
+**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
+The Hokkaido Research Organization lead a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstituteAnnualReportMonitoring2021].
+The program began in 1963, but an effective, standardized sampling method was implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
 Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
@@
 Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-Annual data of ocean productivity (2003-2019) were extracted from OceanColor ([\<https://oceancolor.gsfc.nasa.gov/\>](https://oceancolor.gsfc.nasa.gov/){.uri}) and we calculated the average value within the 30-km radius of each river mouth.
+Annual data of ocean productivity (2003-2019) were extracted from OceanColor [@seawifsmissionpageNasaOceanBiology2019] and we calculated the average value within the 30-km radius of each river mouth.
 We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
@@
 where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
-The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$).
+The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the SD $\sigma_r$).
 This hierarchical structure allows for improved estimates of $ln~r_s$ by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
@@
 For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of stock enhancement $R$ (drawn randomly from $Unif(0, 500)$).
-This yields a total of 50000 simulation replicates.
+This yields a total of $5 \times 10^4$ simulation replicates.
 In each simulation replicate, we ran 1600 time steps of community dynamics and obtained temporal means and SDs of the whole community ($\sum_i^SN_i$), enhanced species ($N_1$), and unenhanced species ($\sum_{i, i\ne1}^SN_i$) using the last 1000 time steps.
@@
 where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$).
-Both response and explanatory variables were standardized to a mean of zero and a standard deviation of one to compare regression coefficients.
+Both response and explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.
 
@@
 Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],".
-Both response and explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one before the analysis.")
+Both response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")
 

### 2022-02-02 rmd/figures.Rmd
edit: rmd

@@
 Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
-Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`.
+Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`.
 (B) Empirical evidence.

### 2022-02-02 rmd/supporting_info.Rmd
edit: rmd

@@
 **Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-The Hokkaido Research Organization lead a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstituteAnnualReportMonitoring2021].
-The program began in 1963, but an effective, standardized sampling method was implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
+The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstituteAnnualReportMonitoring2021].
+The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
 Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
@@
 
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (chlorophyll a [mg m^-3^]).
 We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.
@@
 $\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients.
-The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (Chlorophyll a).
+The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (chlorophyll a).
 The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.

### 2022-02-02 rmd/manuscript.Rmd
edit: manuscript

@@
 These scenarios cover a range of ecological contexts, differing in the intrinsic growth of the enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$ (see **Materials and Methods**).
-The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of the total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$).
-We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.
+Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$).
+We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.
 
@@
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**), one of Japan's most valuable freshwater resources [@kitadaLessonsJapanMarine2020], on the long-term stability of stream fish communities in Hokkaido, Japan.
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
 In the protected watersheds (**Figure 1C and 1D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
@@
 As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**).
+The effect was striking in its magnitude, almost doubling the CV at the highest level of stocking (**Figure 1B**).
 Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
-This pattern was associated with the reduced long-term average of total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics).
+This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics).
 In the meantime, the SDs had vague relationships with stock enhancement (**Figure 1B and 2**).
@@
 Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003].
-Importantly, socioeconomic factors control the number of releases (e.g., budget allocation).
-As such, given the density-dependent regulation of recipient communities, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
+Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the density-dependent regulation of recipient communities.
+As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
 
@@
 Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.
-Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community.
-While our empirical example is limited to stream fish communities, the destabilizing effect emerged across diverse simulated scenarios, implying that this phenomenon is pervasive across terrestrial and aquatic taxa.
+Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning and delivery of ecosystem services [@cardinaleBiodiversityLossIts2012].
+While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive across terrestrial and aquatic taxa because the destabilizing effect emerged across diverse simulated scenarios.
 
@@
 These considerable potentials indicate that viable management options for the sustainable future exist before blindly accepting stock enhancement.
-Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.
+Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.
 

### 2022-02-02 rmd/figures.Rmd
edit: figure caption

@@
 **Figure 1** Theory and empirical observations agree that stock enhancement destabilizes community dynamics.
-In A and B, panels and colors distinguish response variables and species groups, respectively.
+In A and B, panels and colors distinguish response variables and species groups.
 (A) Theoretical predictions.
-Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
+Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and 95% confidence intervals.
 Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`.
 (B) Empirical evidence.
-Dots represent observed values in 31 watersheds.
-Site-level values were averaged in each watershed (geometric mean).
-Lines are predicted values of regression models, and line types corresponds to posterior probabilities of regression coefficients.
+Dots represent geometric means of site-level observations in 31 watersheds.
+Lines are the predicted values of the regression models, and line types correspond to the coefficient's posterior probabilities.
 See Tables S8-10 for full statistics.
 (C) Map of sampling sites (black dots) in Hokkaido, Japan.
-(D) Example of an protected watershed (Okushibetsu).
+(D) Example of a protected watershed (Okushibetsu).
 (E) Masu salmon *Oncorhynchus masou masou*.

### 2022-02-03 rmd/supporting_info.Rmd
edit: title page

@@
 **Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstituteAnnualReportMonitoring2021].
+The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
 The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).

### 2022-02-03 rmd/title.tex
edit: SI
Update title.tex
edit: title page

@@
 %\begin{titlepage}
+\begin{center}
+\LARGE{\textbf{Supplementary Materials for:}}\\[7.5mm]
+\LARGE{Stock enhancement undermines community stability}\\[7.5mm]
+\large{Akira Terui, Hirokazu Urabe, Masayuki Senzaki, Bungo Nishizawa}\\[7.5mm]
+\large{Correspondence to: hanabi0111@gmail.com}\\[15mm]
+\end{center}
 \begin{flushleft}
-\LARGE{\textbf{Supporting Information for: \newline Selective stock enhancement undermines community stability}}\\
-\vspace*{\baselineskip}
-\large{Akira Terui$^{*,1}$, Hirokazu Urabe$^2$, Masayuki Senzaki$^3$, Bungo Nishizawa$^4$}\\
-\vspace*{1\baselineskip}
-\normalsize{*Corresponding author \newline Email: hanabi0111@gmail.com}\\
-\vspace*{1\baselineskip}
-\normalsize{
-$^1$ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA \newline
-$^2$ XXX \newline
-$^3$ XXX \newline
-$^4$ XXX}\\
-\vspace*{2\baselineskip}
 \textbf{This PDF file includes:}
 \begin{itemize}
+\item Materials and Methods
 \item Supplementary text
-\item XX
-\item XX
-\item SI References
+\item Tables S1-10
+\item Figures S1-S15
+\item References
 \end{itemize}

### 2022-02-03 rmd/manuscript.Rmd
edit: manuscript

@@
 source(here::here("code/data_fmt_fishdata.R"))
+source(here::here("code/data_fmt_analysis.R"))
 
@@
 We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see **Materials and Methods** for selection criteria).
-Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.
+Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential effects of climates and local abiotic factors.
 
@@
 Competition is a likely mechanism, as our theory assumes.
-Field experiments confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018].
+Field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015].
 Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003].
-Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the density-dependent regulation of recipient communities.
+Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities.
 As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
@@
 Like other salmonids, ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress].
-In addition, hatchery salmons are more susceptible to predation than wild ones [@weberInteractionsHatcheryWild2003].
+In addition, hatchery salmons tend to be more susceptible to predation than wild ones [@weberInteractionsHatcheryWild2003].
 The fitness disadvantage of hatchery fish may add to negative density dependence to influence community stability.
 
-Like any non-experimental study, we cannot exclude the possibility that spurious correlations drove our results.
-However, in the protected watersheds, human activities (e.g., exploitation, construction of river-crossing structures) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
-Further, we have statistically controlled natural variation in environmental factors, including climatic and land-use variables (see **Materials and Methods** and **Tables S8-S10**).
+We cannot exclude the possibility that spurious correlations drove our results.
+However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(df_env$frac_forest, 2) * 100`%) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
+Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**).
 This unique setup may have helped uncover the close agreement between theory and empirical patterns.
@@
 Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.
-Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning and delivery of ecosystem services [@cardinaleBiodiversityLossIts2012].
+Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012].
 While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive across terrestrial and aquatic taxa because the destabilizing effect emerged across diverse simulated scenarios.
 
-We should prioritize habitat preservation and restoration with a broader scope of biodiversity conservation.
+We should prioritize habitat conservation with a broader scope of ecosystem management.
 Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement.
-Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieving successful conservation.
+Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation.
 For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022].
-Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
+Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
 These considerable potentials indicate that viable management options for the sustainable future exist before blindly accepting stock enhancement.
-Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.
+Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.
 

### 2022-02-03 rmd/supporting_info.Rmd
edit: manuscript

@@
 
-**Fish stocking.** At the protected watersheds, the stocking of masu salmon began in the 1950s.
-Hatchery fish were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
-For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of fish released) from 1999 to 2019.
-Although fish were released at multiple locations within a watershed, we could not extract stocking data at the site level.
+**Fish stocking.** The stocking of masu salmon began in the 1950s.
+Hatchery fish are released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
+Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level.
+We assembled annual records of stock enhancement (the total number of fish released) from 1999 to 2019 for each release stage.
 
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (chlorophyll a [mg m^-3^]).
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (chlorophyll a concentration [mg m^-3^]).
 We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.
-We estimated the proportion of forest land use in each watershed polygon based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+We estimated the proportion of forest and agricultural land use in each watershed polygon based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
 Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-Annual data of ocean productivity (2003-2019) were extracted from OceanColor [@seawifsmissionpageNasaOceanBiology2019] and we calculated the average value within the 30-km radius of each river mouth.
+We extracted annual data of chlorophyll a concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
+Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
 We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
@@
 ```
-$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
+$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released (unit: million fish) in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
 The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
@@
 Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
-**Table S7** and **Figures S13-S15** summarize estimated parameters and community dynamics.
+We summarized the estimated parameters and reconstructed community dynamics in **Table S7** and **Figures S13-S15** .
 
-We developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
+We used linear regression to quantify the impact of stock enhancement on community dynamics.
+Although our focus is stock enhancement, each model included climatic and local abiotic variables to account for important environmental differences among sites.
+Specifically, we developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
 
@@
 $\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients.
-The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (chlorophyll a).
+The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll a concentration; averaged for 2002-2019).
 The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
@@
 
-                       "\n```{r figure_s", i + j,", fig.width = 11, fig.height = 8}
+                       "\n```{r figure_s", i + j,", fig.width = 11, fig.height = 11}
                        \n\n

### 2022-02-03 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
-The widespread use of captive breeding is perhaps because of the "myth" that demographic benefits of released individuals may exceed the associated risks.
+The widespread use of captive breeding is perhaps because of the "myth" that the demographic benefits of released individuals may exceed the associated risks.
 
 Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
-Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
+Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
 Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012].
@@
 Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences.
-The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \>10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].
+The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].
 
 We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the selective stock enhancement of a constituent species (species 1).
-Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+Specifically, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
@@
 As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**).
-The effect was striking in its magnitude, almost doubling the CV at the highest level of stocking (**Figure 1B**).
+The effect was striking in its magnitude, almost doubling the CV at the highest stocking level (**Figure 1B**).
 Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
@@
 We cannot exclude the possibility that spurious correlations drove our results.
-However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(df_env$frac_forest, 2) * 100`%) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
+However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(mean(df_env$frac_forest), 2) * 100`%) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
 Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**).

### 2022-02-03 code/table_reg.R
edit: table appearance

@@ -59,7 +59,8 @@ df_est <- lapply(filename, function(x) {
              Parameter,
              Effect) %>% 
     dplyr::select(-parameter, -response) %>% 
-    mutate(across(median:prob_negative, op)) %>% 
+    mutate(across(.cols = where(is.numeric),
+                  .fns = function(x) paste0("$", op(x), "$"))) %>% 
     rename(Estimate = median,
            SE = sd,
            "Pr(> 0)" = prob_positive,
@@ -69,4 +70,5 @@ df_est <- lapply(filename, function(x) {
 })
 
 names(df_est) <- name
+
 

### 2022-02-03 code/table_ssm.R

@@ -28,12 +28,12 @@ df_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>%
                                    param == "mu_b" ~ "$\\mu_{\\beta}$",
                                    param == "sd_r_space" ~ "$\\sigma_{r}$",
                                    param == "sd_b" ~ "$\\sigma_{\\beta}$"),
-             Interpretation = case_when(param == "log_global_r" ~ "Global rate of community change",
+             Interpretation = case_when(param == "log_global_r" ~ "Rate of community change",
                                         param == "mu_b" ~ "Effect of spring stoking",
-                                        param == "sd_r_space" ~ "Variation in the site-specific rate of community change",
-                                        param == "sd_b" ~ "Variation in the site-specific effect of spring stocking"),
+                                        param == "sd_r_space" ~ "SD of the rate of community change",
+                                        param == "sd_b" ~ "SD of the effect of spring stocking"),
              `Species group` = case_when(group == "all" & param == "log_global_r" ~ "Whole",
-                                         group == "masu" & param == "log_global_r" ~ "Enhanced (masu salmon)",
+                                         group == "masu" & param == "log_global_r" ~ "Enhanced",
                                          group == "other" & param == "log_global_r" ~ "Unenhanced")) %>% 
       arrange(param)
     
@@ -43,9 +43,12 @@ df_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>%
     }
     
     df0 <- df0 %>%
-      mutate(across(.cols = `50%`:`97.5%`,
+      mutate(across(.cols = where(is.numeric),
                     .fns = op)) %>% 
-      mutate(Estimate = paste0(`50%`, " (", `2.5%`, ", ", `97.5%`, ")")) %>% 
+      mutate(Estimate = paste0("$",
+                               `50%`,
+                               "~(", `2.5%`, ",~", `97.5%`, ")",
+                               "$")) %>% 
       select(`Species group`,
              Parameter,
              Interpretation,

### 2022-02-03 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012]. In the basic formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012].
+In the basic formula without stock enhancement, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
@@
 ```
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obeys an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obeys an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
 We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
@@
 We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.
-We estimated the proportion of forest and agricultural land use in each watershed polygon based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+We estimated the proportion of forest and agricultural land use in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
 Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
@@
 The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The parameter $exp(\epsilon_{s,t}^{obs})$ is the error term that follows a log-normal distribution ($\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$).
+The parameter $\epsilon_{s,t}^{obs}$ is the error term that follows a normal distribution $Normal(0, \sigma_{obs,s}^2)$.
 The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
@@
 The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the SD $\sigma_r$).
-This hierarchical structure allows for improved estimates of $ln~r_s$ by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
+This hierarchical structure allows for improved parameter estimates by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
 We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).
@@
 We performed a sensitivity analysis of the community simulation to identify key simulation parameters that strongly affect the relationships between community dynamics (temporal mean and SD of density) and stock enhancement.
-We generated 500 sets of parameter combinations by randomly drawing values of 7 simulation parameters from uniform distributions (**Table S1**).
+We generated 500 sets of parameter combinations by randomly drawing values of seven simulation parameters from uniform distributions (**Table S1**).
 For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of stock enhancement $R$ (drawn randomly from $Unif(0, 500)$).
@@
 
-For each parameter combination, we regressed mean densities and SDs of the whole community, enhanced species, and unenhanced species $y_j$ on the number of releases $R$ as:
+For each parameter combination, we regressed the mean densities and SDs of the whole community, enhanced species, and unenhanced species $y_j$ on the number of releases $R$ as:
 
@@
 In the meantime, we varied values of $K$, $r_1$, $\sigma_{\epsilon}$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**).
-Although $f_R$ had little influence on stocking effects (**Table S1**), we varied this parameter given the significant interest in relative fitness of captive-bred individuals in the wild.
+Although $f_R$ had little influence on stocking effects (**Table S1**), we varied this parameter given the significant interest in the relative fitness of captive-bred individuals in the wild.
 
@@
 Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
-Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],".
+Response variables are the effects of stock enhancement on the temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],".
 Both response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")
@@
 
-kable(df_sp_list, format = "markdown")
+kable(df_sp_list,
+      format = "markdown")
 
@@
 
-kable(df_prior, format = "markdown")
+kable(df_prior,
+      format = "markdown")
 
@@
 
-kable(df_ssm, format = "markdown")
+kable(df_ssm,
+      align = c(rep("l", 3), "c"),
+      format = "markdown")
 
@@
 table_legend <- "Median estimates and standard errors (SEs) of regression coefficients are shown.
-Pr(> 0) and Pr(< 0) represent the proportion of positive and negative estimates (MCMC samples), respectively (i.e., posterior probability)."
+Pr(> 0) and Pr(< 0) represent the proportion of positive and negative estimates in MCMC samples, respectively (i.e., posterior probability)."
 
@@
 
-  knit_chunk <- paste0("## Table S", i + j, " Parameter estimates for the regression model of ", c_text[i], " \n",
+  knit_chunk <- paste0("## Table S", i + j, " Parameter estimates for the regression model (", c_text[i], ") \n",
                        table_legend,
@@
                        \n\n
-                       kable(df_est[[",i,"]], format = 'markdown')
+                       kable(df_est[[",i,"]],
+                             align = c(rep('l', 3), rep('c', 4)),
+                             format = 'markdown')
                        \n\n

### 2022-02-03 code/table_prior.R
edit: table

@@ -23,11 +23,11 @@ df_prior <- tibble(Model = c("State space", rep(NA, 6),
                    Prior = c("Normal(0, 10)",
                              "Normal(0, 10)",
                              "Normal(0, 10)",
-                             "t(0, 2.5, 3)",
-                             "t(0, 2.5, 3)",
-                             "t(0, 2.5, 3)",
-                             "t(0, 2.5, 3)",
+                             "half-Student's t(0, 2.5, 3)",
+                             "half-Student's t(0, 2.5, 3)",
+                             "half-Student's t(0, 2.5, 3)",
+                             "half-Student's t(0, 2.5, 3)",
                              "Normal(0, 10)",
                              "Normal(0, 10)",
-                             "t(0, 2.5, 3)",
-                             "t(0, 2.5, 3)"))
+                             "half-Student's t(0, 2.5, 3)",
+                             "half-Student's t(0, 2.5, 3)"))

### 2022-02-03 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
-We identified five influential parameters (**Table S2-4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+We identified five influential parameters (**Table S2-S4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
 Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`).
@@
 Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
-We summarized the estimated parameters and reconstructed community dynamics in **Table S7** and **Figures S13-S15** .
+We summarized the reconstructed community dynamics in **Figures S7-S9**.
 
@@
 $\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$.
-The site-level predictors include upstream watershed area, air temperature, precipitation, and proportion of forest land use.
+The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use.
+Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**).
 The watershed-specific intercept was related to watershed-level predictors as:
@@
 Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
+Parameter estimates were summarized in **Table S7-S10**.
 
@@
 
-For each parameter combination, we regressed the mean densities and SDs of the whole community, enhanced species, and unenhanced species $y_j$ on the number of releases $R$ as:
+For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community statistics (the mean densities and SDs of the whole community, enhanced species, and unhenaced species).
+To examine influences of simulation parameters on $\xi$ (**Table S1**), we developed the following regression model taking $\xi$ as a response variable (parameter combination $n$):
 
@@
 \begin{aligned}
-  y_j &\sim Normal(\mu_j, \sigma^2)\\
-  \mu_j &= \xi_0 + \xi_1~R_j
-\end{aligned}
-$$
-
-where $\xi_k$ ($k = 0-1$) are the intercept ($\xi_0$) and regression coefficient ($\xi_1$).
-We extracted 500 estimates of $\xi_1$, each of which represents the effect of stock enhancement $R$ on community dynamics under a given parameter combination.
-To examine influences of simulation parameters (**Table S1**) on $\xi_1$, we developed the following regression model taking $\xi_1$ as a response variable (parameter combination $n$):
-
-$$
-\begin{aligned}
-  \xi_{1,n} &\sim Normal(\mu_n, \sigma^2)\\
+  \xi_{n} &\sim Normal(\mu_n, \sigma^2)\\
   \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 r_{1,n} + \zeta_3 r_{max,n} + \zeta_4  \bar{\alpha}_n + \zeta_5 K_n + \zeta_6 \sigma_{\epsilon,n} + \zeta_7 f_{R, n}
@@
 
-where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$).
-Both response and explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.
+where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$). Explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.
 
-We found that regression coefficients of the following parameters ($\zeta$) never exceeded a value of 0.30 and were less influential: the number of species $S$, the maximum intrinsic growth rate of unenhanced species $r_{max}$, and relative fitness $f_R$.
-Therefore, in the main simulation, we fixed values of $S$ and $r_{max}$ (**Table S1**).
-In the meantime, we varied values of $K$, $r_1$, $\sigma_{\epsilon}$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**).
+We found that regression coefficients of the following parameters ($\zeta$) never exceeded a value of 0.10: the number of species $S$, maximum intrinsic growth rate of unenhanced species $r_{max}$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$.
+Therefore, these parameters have little influence on the qualitative relationship between the number of releases and community dynamics.
+In the main simulation, we fixed values of $S$, $r_{max}$, and $\sigma_{\epsilon}$ (**Table S1**).
+In the meantime, we varied values of $K$, $r_1$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**).
 Although $f_R$ had little influence on stocking effects (**Table S1**), we varied this parameter given the significant interest in the relative fitness of captive-bred individuals in the wild.
@@
 
-# Figure S1-12
+# Figure S1-6
 ## load figures
@@
                        "$r_1$ = `r df_param$r1[",i,"]`, ",
-                       "$\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`, ",
                        "$K$ = `r df_param$k[",i,"]`) \n",
@@
 Other parameters are: ",
-                       "intrinsic growth rate of enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
-                        "environmental variability $\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`; ",
+                       "number of species $S$ = `r df_param$n_species[",i,"]`; ",
+                       "intrinsic growth rate of an enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
+                       "maximum intrinsic growth rate of unenhanced species $r_{max}$ = `r df_param$r_max[",i,"]`; ",
+                        "environmental stochasticity $\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`; ",
                         "carrying capacity $K$ = `r df_param$k[",i,"]`.",
@@
 
-# Figure S13-15
+# Figure S7-9
 ## load figures
 source(here::here("code/figure_si_obs_dyns.R"))
-j <- 12
+j <- 6
 
@@
 
+\newpage
+
+## Figure S10 Environmental variables
+
+```{r figure_s10, fig.width=11, fig.height=8}
+
+source(here::here("code/figure_si_env.R"))
+
+print(g_env)
+```
+
+Distribution of environmental variables in the protected watershed.
+Note that the number of fish released and ocean productivity (chlorophyll a) are measured at the watershed level while others are measured at the site level.
+
+\newpage
+
+## Figure S11 Correlation plot
+
+```{r figure_s11, fig.width=11, fig.height=11}
+
+source(here::here("code/figure_si_cor.R"))
+```
+
+Correlation plot among environmental variables in the protected watersheds. Numbers indicate Spearman's rank correlations.
+
+\newpage
+
 # References

### 2022-02-04 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
-We identified five influential parameters (**Table S2-S4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`).
+We identified five influential parameters (**Table S2-S4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).
 This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
@@
 Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level.
-We assembled annual records of stock enhancement (the total number of fish released) from 1999 to 2019 for each release stage.
+We assembled annual records of stock enhancement (the number of fish released) from 1999 to 2019 for each release stage.
 
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (chlorophyll a concentration [mg m^-3^]).
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll a concentration [mg m^-3^]).
 We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.
-We estimated the proportion of forest and agricultural land use in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
 Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
@@
 Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
-Response variables are the effects of stock enhancement on the temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],".
-Both response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")
+Response variables are Spearman's correlation between stock enhancement and either temporal mean density ($\\mu$) or SD ($\\sigma$) of ", c_text[i],".
+Explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")
 

### 2022-02-04 rmd/manuscript.Rmd
edit: manuscript

@@
 This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
-The enhanced species decreased because stocking induced the negative competitive effect exceeding the demographic benefit of released individuals [@satakeStockingCaptivebredFish2012].
+The enhanced species decreased because stocking induced the negative competitive effect exceeding the reproductive contribution of released individuals [@satakeStockingCaptivebredFish2012].
 Meanwhile, interspecific competition reduced the unenhanced species at high levels of stock enhancement, resulting in fewer persisting species (**Figure 1A**).
@@
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
-These patterns were qualitatively similar across most ecological contexts (robust to the changes in $r_1$, $\bar{\alpha}$, $\sigma_{\epsilon}$, and $f_R$; **Figure S1-6**).
+These patterns were qualitatively similar across most ecological contexts (robust to the changes in $r_1$, $\bar{\alpha}$, $\sigma_{\epsilon}$, and $f_R$; **Figures S1-S3**).
 
@@
 
-Stock enhancement, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**).
-In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figures S7 and S8**).
+Stock enhancement, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S4-S6**).
+In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figures S4 and S5**).
 This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
@@
 To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
-In the protected watersheds (**Figure 1C and 1D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
+In the protected watersheds (**Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
@@
 Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
-This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics).
-In the meantime, the SDs had vague relationships with stock enhancement (**Figure 1B and 2**).
+This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S8-S10** for full statistics).
+In the meantime, the SDs had vague relationships with stock enhancement (**Figures 1B and 2**).
 

### 2022-02-04 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll a concentration [mg m^-3^]).
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [$^\circ C$]and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll a concentration [mg m^-3^]).
 We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.

### 2022-02-04 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [$^\circ C$]and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll a concentration [mg m^-3^]).
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]).
 We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.
@@
 Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-We extracted annual data of chlorophyll a concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
+We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
 Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
@@
 $\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients.
-The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll a concentration; averaged for 2002-2019).
+The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019).
 The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
@@
 Distribution of environmental variables in the protected watershed.
-Note that the number of fish released and ocean productivity (chlorophyll a) are measured at the watershed level while others are measured at the site level.
+Note that the number of fish released and ocean productivity (chlorophyll *a*) are measured at the watershed level while others are measured at the site level.
 

### 2022-02-04 rmd/manuscript.Rmd
edit: manuscript

@@
 
-There is increasing awareness that stock enhancement with captive-bred organisms brings ecological risks to wild populations.
-Still, we may underestimate the negative impact of stock enhancement because current schemes rarely consider the consequences for the whole ecological community.
+The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals into the wild (stock enhancement).
+Still, we may underestimate the negative impact because current schemes rarely consider the consequences of stock enhancement for the whole ecological community.
 Here, we use theory and long-term data of Japanese stream fish communities to show that stock enhancement undermines community stability.
 Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion.
-Consistent with this prediction, fish communities showed greater temporal fluctuations and reduced biodiversity in rivers with the intensive stocking of hatchery masu salmon - one of the most valuable freshwater resources in the region.
+Consistent with this prediction, fish communities showed greater temporal fluctuations and reduced biodiversity in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in the region.
 Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
@@
 Captive breeding is common to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
+Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
 In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
@@
 Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
-Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
+Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
 Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012].
@@
 
-Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a].
+Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999].
 Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences.
@@
 We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios.
-These scenarios cover a range of ecological contexts, differing in the intrinsic growth of the enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$ (see **Materials and Methods**).
+These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Materials and Methods**).
 Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$).
@@
 Under this condition, competing species can grow from small populations because dominant species undergo stronger intraspecific competition [@carrollNicheFitnessDifferences2011a].
-Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999a] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multispecies community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$).
+Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multispecies community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$).
 However, stock enhancement is externally controlled, and the number of releases is not subject to density-dependent regulation.
@@
 In the protected watersheds (**Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
+The majority of stocking occurs in spring, after which salmon fry stay in freshwater for \~1 year and compete with wild individuals during growing seasons.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
@@
 
-The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996].
-Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.
+There is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996].
+However, despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.
 Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012].

### 2022-02-04 rmd/supporting_info.Rmd
edit: manuscript

@@
 
+## stocking data
+source(here::here("code/data_fmt_stock.R"))
+
+df_stock_stage <- df_stock %>% 
+  group_by(release_stage) %>% 
+  summarize(stock = sum(abundance)) %>% 
+  mutate(ratio = stock / max(stock),
+         prop = stock / sum(stock))
+
 ```
@@
 ```
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obeys an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
 We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
@@
 **Fish stocking.** The stocking of masu salmon began in the 1950s.
-Hatchery fish are released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]).
+Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage).
 Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level.
-We assembled annual records of stock enhancement (the number of fish released) from 1999 to 2019 for each release stage.
+For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by Hokkaido National Research Institute and Salmon and Freshwater Fisheries Research Institute.
+During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
 
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]).
-We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site.
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]).
+We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site.
 We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
@@
 We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
-Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
 We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
@@
 This hierarchical structure allows for improved parameter estimates by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
-We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).
+We used median estimates of fish density $n_{s,t}$ to calculate the temporal CV, mean ($\mu$), and SD ($\sigma$) for each site.
+We summarized the reconstructed community dynamics in **Figures S7-S9**.
 
@@
 Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
-We summarized the reconstructed community dynamics in **Figures S7-S9**.
 
@@
 Although our focus is stock enhancement, each model included climatic and local abiotic variables to account for important environmental differences among sites.
-Specifically, we developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
+Specifically, we developed the following linear regression model taking either the CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
 
@@
 $\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$.
-The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use.
+The site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
 Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**).
@@
 ```
-$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients.
+$\delta_{0}$ is the global intercept and $\delta_k (k > 0)$ are the regression coefficients.
 The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019).
+Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
 The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
@@
 
-For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community statistics (the mean densities and SDs of the whole community, enhanced species, and unhenaced species).
-To examine influences of simulation parameters on $\xi$ (**Table S1**), we developed the following regression model taking $\xi$ as a response variable (parameter combination $n$):
+For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community dynamics, which indicate the effect of stock enhancement under a given ecological context.
+To examine influences of simulation parameters on $\xi$ (**Table S1**), we developed the following regression model taking $\xi$ as a response variable:
 
@@
 
-where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$). Explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.
+where $\xi_n$ is Spearman's rank correlation for parameter combination $n$, and $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$).
+Explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.
 
@@
 Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
-Response variables are Spearman's correlation between stock enhancement and either temporal mean density ($\\mu$) or SD ($\\sigma$) of ", c_text[i],".
+Response variables are Spearman's rank correlation between stock enhancement and either temporal mean density ($\\mu$) or SD ($\\sigma$) of ", c_text[i],".
 Explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")

### 2022-02-04 rmd/figures.Rmd
edit: manuscript

@@
 Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and 95% confidence intervals.
-Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`.
+Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`.
 (B) Empirical evidence.

### 2022-02-04 rmd/manuscript.Rmd
edit: manuscript

@@
 
-**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Salmon and Freshwater Fisheries Research Institute, Hokkaido Research Organization, Eniwa, Hokkaido 061-1433, Japan ^3^ Faculty of Environmental Earth Science, Hokkaido University, Sapporo, Hokkaido 060-0810, Japan ^4^ XXX
+**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Salmon and Freshwater Fisheries Research Institute, Hokkaido Research Organization, Eniwa, Hokkaido, 061-1433, Japan ^3^ Faculty of Environmental Earth Science, Hokkaido University, Sapporo, Hokkaido, 060-0810, Japan ^4^ National Institute of Polar Research, Tachikawa, Tokyo, 190-8518, Japan
 
@@
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
-These patterns were qualitatively similar across most ecological contexts (robust to the changes in $r_1$, $\bar{\alpha}$, $\sigma_{\epsilon}$, and $f_R$; **Figures S1-S3**).
+These patterns were qualitatively similar across most ecological contexts (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S1-S3**).
 
@@
 Like other salmonids, ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress].
-In addition, hatchery salmons tend to be more susceptible to predation than wild ones [@weberInteractionsHatcheryWild2003].
+In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003].
 The fitness disadvantage of hatchery fish may add to negative density dependence to influence community stability.
@@
 We cannot exclude the possibility that spurious correlations drove our results.
-However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(mean(df_env$frac_forest), 2) * 100`%) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
+However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(mean(df_env$frac_forest), 2) * 100`%; see also **Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
 Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**).
@@
 
-There is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996].
-However, despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity.
+Despite the significant attention to the fate of captive-bred individuals [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996], current schemes rarely consider the self-regulation process of biodiversity.
 Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012].

### 2022-02-07 rmd/manuscript.Rmd
edit: manuscript

@@
 
-The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals into the wild (stock enhancement).
+The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals (stock enhancement).
 Still, we may underestimate the negative impact because current schemes rarely consider the consequences of stock enhancement for the whole ecological community.
@@
 Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010].
-Captive breeding is common to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
+Captive breeding is a form of the efforts to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
+Although releases of captive-bred organisms ("stock enhancement") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
 In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
@@
 Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
-Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012].
+Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@careyNativeInvadersChallenges2012].
 Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability.
@@
 In the protected watersheds (**Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
-The majority of stocking occurs in spring, after which salmon fry stay in freshwater for \~1 year and compete with wild individuals during growing seasons.
+The majority of stocking occurs in spring, after which salmon fry stay in freshwater for growing seasons.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
@@
 Field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015].
-Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003].
+Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@weberInteractionsHatcheryWild2003].
 Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities.
@@
 We cannot exclude the possibility that spurious correlations drove our results.
-However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(mean(df_env$frac_forest), 2) * 100`%; see also **Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
+However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(mean(df_env$frac_forest), 2) * 100`%; see **Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
 Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**).
@@
 Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation.
-For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022].
+For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022].
 Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
@@
 
-We are grateful to the participants involved in the long-term monitoring program at the protected watersheds in Hokkaido.
+We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido.
 We thank Masato Yamamichi for helpful discussion on this manuscript.

### 2022-02-08 rmd/manuscript.Rmd
edit: manuscript

@@
 where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $Normal(0,\sigma_{\epsilon}^2)$.
-To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$), respectively.
+To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$).
 The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
@@
 In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003].
-The fitness disadvantage of hatchery fish may add to negative density dependence to influence community stability.
+The fitness disadvantage may add to negative density dependence to influence community stability.
 
@@
 Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
-These considerable potentials indicate that viable management options for the sustainable future exist before blindly accepting stock enhancement.
+These considerable potentials indicate that viable management options exist before blindly accepting stock enhancement.
 Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.

### 2022-02-08 rmd/supporting_info.Rmd
edit: support info

@@
 **Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
+The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterfisheriesresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
 The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
@@
 Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level.
-For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by Hokkaido National Research Institute and Salmon and Freshwater Fisheries Research Institute.
+For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
 During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)

### 2022-02-18 rmd/manuscript.Rmd
edit: manuscript

@@
 
-Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999].
-Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences.
+Here, we show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999].
+Our theory illuminates that stock enhancement compromises the stabilizing mechanism emerging from species niche differences.
 The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].
@@
 These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Materials and Methods**).
-Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$).
+Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: coefficient of variation (CV), number of species persist (defined as $N_i > 0.01$ at $t=1600$), temporal mean ($\mu$), and temporal SD ($\sigma$).
 We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.
@@
 Competition is a likely mechanism, as our theory assumes.
-Field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015].
 Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@weberInteractionsHatcheryWild2003].
+Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015].
 Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities.
@@
 We cannot exclude the possibility that spurious correlations drove our results.
-However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(mean(df_env$frac_forest), 2) * 100`%; see **Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
+However, the protected watersheds preserve nearly intact landscapes (**Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
 Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**).
-This unique setup may have helped uncover the close agreement between theory and empirical patterns.
+This unique setup may have helped uncover the qualitative agreement between theory and empirical patterns.
 
@@
 Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012].
-While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive across terrestrial and aquatic taxa because the destabilizing effect emerged across diverse simulated scenarios.
+While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive in nature because the destabilizing effect emerged across diverse simulated scenarios.
 

### 2022-02-20 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Stock enhancement undermines community stability"
+title: "Stock enhancement undermines ecological community stability"
 output:

### 2022-02-20 code/data_fmt_fishdata.R
Update data_fmt_fishdata.R

@@ -13,14 +13,16 @@ pacman::p_load(tidyverse, foreach)
 ## remove sites with no coordinates - "usubetsu4", "atsuta6", "kokamotsu4"
 
 d0 <- read_csv(here::here("data_fmt/data_hkd_prtwsd_fmt.csv")) %>% 
-  mutate(taxon = case_when(genus == "Cottus" ~ "Cottus_spp",
-                           genus == "Pungitius" ~ "Pungitius_spp",
-                           genus == "Tribolodon" ~ "Tribolodon_spp",
+  mutate(taxon = case_when(genus == "Tribolodon" ~ "Pseudaspius_spp",
                            genus == "Gymnogobius" ~ "Gymnogobius_spp",
                            genus == "Lethenteron" ~ "Lethenteron_spp",
                            genus == "Rhinogobius" ~ "Rhinogobius_spp",
+                           # update latin name
                            latin == "Gasterosteus_aculeatus" ~ "Gasterosteus_spp",
-                           latin == "Salvelinus_malma" ~ "Salvelinus_malma_krascheninnikovi",
+                           latin == "Hucho_perryi" ~ "Parahucho_perryi",
+                           latin == "Noemacheilus_barbatulus" ~ "Barbatula_oreas",
+                           latin == "Phoxinus_lagowskii_steindachneri" ~ "Rhynchocypris_lagowskii_steindachneri",
+                           latin == "Phoxinus_percnurus_sachalinensis" ~ "Rhynchocypris_percnura_sachalinensis",
                            TRUE ~ as.character(latin)),
          site_id = paste0(river, site)) %>% 
   group_by(year, river, site, site_id, taxon) %>% 

### 2022-02-20 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Captive breeding is a form of the efforts to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-Although releases of captive-bred organisms ("stock enhancement") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
+Although releases of captive-bred organisms (stock enhancement) entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
 In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].

### 2022-02-21 rmd/supporting_info.Rmd
edit: minor error

@@
 Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
-We identified five influential parameters (**Table S2-S4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+We identified five influential parameters (**Table S2-S4**), of which different values were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
 Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).

### 2022-02-21 code/data_fmt_fishdata.R

@@ -13,16 +13,19 @@ pacman::p_load(tidyverse, foreach)
 ## remove sites with no coordinates - "usubetsu4", "atsuta6", "kokamotsu4"
 
 d0 <- read_csv(here::here("data_fmt/data_hkd_prtwsd_fmt.csv")) %>% 
-  mutate(taxon = case_when(genus == "Tribolodon" ~ "Pseudaspius_spp",
+  mutate(taxon = case_when(genus == "Cottus" ~ "Cottus_spp",
                            genus == "Gymnogobius" ~ "Gymnogobius_spp",
                            genus == "Lethenteron" ~ "Lethenteron_spp",
+                           genus == "Pungitius" ~ "Pungitius_spp",
                            genus == "Rhinogobius" ~ "Rhinogobius_spp",
+                           genus == "Tribolodon" ~ "Pseudaspius_spp",
                            # update latin name
                            latin == "Gasterosteus_aculeatus" ~ "Gasterosteus_spp",
                            latin == "Hucho_perryi" ~ "Parahucho_perryi",
                            latin == "Noemacheilus_barbatulus" ~ "Barbatula_oreas",
                            latin == "Phoxinus_lagowskii_steindachneri" ~ "Rhynchocypris_lagowskii_steindachneri",
                            latin == "Phoxinus_percnurus_sachalinensis" ~ "Rhynchocypris_percnura_sachalinensis",
+                           latin == "Salvelinus_malma" ~ "Salvelinus_malma_krascheninnikovi",
                            TRUE ~ as.character(latin)),
          site_id = paste0(river, site)) %>% 
   group_by(year, river, site, site_id, taxon) %>% 

### 2022-02-21 rmd/manuscript.Rmd
edit: title

@@
 ---
-title: "Stock enhancement undermines ecological community stability"
+title: "Stock enhancement undermines ecological stability"
 output:

### 2022-02-21 rmd/manuscript.Rmd
edit: reference

@@
 In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figures S4 and S5**).
-This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021].
+This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [e.g., @jonesRestorationMauritiusKestrel1995].
 More importantly, the contrasting community response at different carrying capacities provides deeper insights.

### 2022-02-23 rmd/manuscript.Rmd
edit: manuscript

@@
 output:
-  word_document:
-    reference_docx: word_format.docx
+  pdf_document:
+    latex_engine: xelatex
+#  word_document:
+#    reference_docx: word_format.docx
 csl: science.csl
@@
 bibliography: reference.bib
+fontsize: 11pt
 ---
@@
 Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion.
-Consistent with this prediction, fish communities showed greater temporal fluctuations and reduced biodiversity in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in the region.
+Consistent with this prediction, fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in the region.
 Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
@@
 where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $Normal(0,\sigma_{\epsilon}^2)$.
-To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$).
+To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0.5,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$).
 The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
@@
 We thank Masato Yamamichi for helpful discussion on this manuscript.
-Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.
+Data and codes will be made available upon the acceptance of the manuscript.
 

### 2022-02-23 rmd/manuscript.Rmd
edit: manuscript

@@
 Stock enhancement, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S4-S6**).
-In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figures S4 and S5**).
+In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figure S4**).
 This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [e.g., @jonesRestorationMauritiusKestrel1995].
@@
 To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
-In the protected watersheds (**Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
+In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
 The majority of stocking occurs in spring, after which salmon fry stay in freshwater for growing seasons.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
-We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see **Materials and Methods** for selection criteria).
+We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Materials and Methods** for selection criteria).
 Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential effects of climates and local abiotic factors.
@@
 As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**).
-The effect was striking in its magnitude, almost doubling the CV at the highest stocking level (**Figure 1B**).
+The effect was striking in its magnitude, almost doubling the CV at the highest stocking level.
 Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
-This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S8-S10** for full statistics).
+This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S8-S10** for full statistics).
 In the meantime, the SDs had vague relationships with stock enhancement (**Figures 1B and 2**).
@@
 We thank Masato Yamamichi for helpful discussion on this manuscript.
-Data and codes will be made available upon the acceptance of the manuscript.
+Data and codes will be made available upon acceptance.
 

### 2022-02-23 rmd/supporting_info.Rmd
edit: manuscript

@@
 where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
-We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
+We modified this formula to include the effects of stock enhancement (species 1) on reproduction and competition as follows:
 
@@
 ```
-In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
+In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0.5,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
 We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
@@
 ln~y_s &\sim Normal(\mu_{y,s}, \sigma_y^2) &&\text{for CV, mean, and SD}\\
-y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s})) &&\text{for species richness}
+y_s &\sim Poisson(\lambda_{y,s} exp(\epsilon_{\lambda,s})) &&\text{for species richness}
 \end{aligned}
@@
 ```
-where $\sigma_y$ is the SD of residual errors and $exp(\epsilon_{y,s})$ is the error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$).
-The expected mean $\mu_y$ was related to linear predictors as follows:
+where $\sigma_y$ is the SD of residual errors and $exp(\epsilon_{\lambda,s})$ is the error term that accounts for overdispersion ($\epsilon_{\lambda,s} \sim Normal(0, \sigma_{\lambda}^2)$).
+The expected means were related to linear predictors as follows:
 
@@
 \mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
-ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
+ln~\lambda_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
 \end{aligned}

### 2022-02-23 rmd/manuscript.Rmd
edit: manuscript

@@
 fontsize: 11pt
+header-includes:
+  - \usepackage{lineno}
+  - \linenumbers
 ---
@@
 We thank Masato Yamamichi for helpful discussion on this manuscript.
-Data and codes will be made available upon acceptance.
+Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.
 

### 2022-02-24 rmd/manuscript.Rmd
edit: manuscript
edit: title

@@
 ---
-title: "Stock enhancement undermines ecological stability"
+title: "Intentional stocking undermines ecological stability"
 output:
@@
 
+**One Sentence Summary:** Large-scale releases of captive-bred organisms undermine the long-term persistence of ecological communities by disrupting the stable coexistence of competing species.
+
 **Authors:** Akira Terui^1,\*^, Hirokazu Urabe^2^, Masayuki Senzaki^3^, Bungo Nishizawa^4^
@@
 
-The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals (stock enhancement).
+The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement").
 Still, we may underestimate the negative impact because current schemes rarely consider the consequences of stock enhancement for the whole ecological community.
@@
 Captive breeding is a form of the efforts to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-Although releases of captive-bred organisms (stock enhancement) entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
+Although releases of captive-bred organisms ("stock enhancement") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
 In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].

### 2022-02-25 rmd/manuscript.Rmd
edit: manuscript

@@
 Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@weberInteractionsHatcheryWild2003].
-Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015].
+Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
 Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities.
@@
 We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido.
-We thank Masato Yamamichi for helpful discussion on this manuscript.
+We thank Genki Sahashi and Masato Yamamichi for helpful discussion on this manuscript.
 Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.

### 2022-03-02 rmd/manuscript.Rmd
edit: manuscript
edit: minor change

@@
 Consistent with this prediction, fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in the region.
-Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.
+Our findings alarm that the current overreliance on stock enhancement may accelerate global biodiversity loss.
 
@@
 
-When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
+When carrying capacity was small ($K=100$), our model predicted a destabilizing effect of stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
 This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
@@
 
-We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido.
-We thank Genki Sahashi and Masato Yamamichi for helpful discussion on this manuscript.
+We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Genki Sahashi and Masato Yamamichi for helpful discussion on this manuscript.
+
+# Funding
+
+No funding.
+
+# Author contributions
+
+AT conceived the project.
+AT, HU and BN assembled data for empirical analysis.
+AT analyzed data with inputs from HU, MS, and BN.
+AT wrote the first draft and HU, MS, and BN significantly contributed to the final version of the manuscript.
+
+# Competing interests
+
+None declared.
+
+# **Data and materials availability**
+
 Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.

### 2022-03-03 rmd/manuscript.Rmd
edit: manuscript
move methods section

@@
 #    reference_docx: word_format.docx
-csl: science.csl
+csl: nature.csl
 knit: (function(inputFile, encoding) {
@@
 
+## ssm estimate
+df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
+  pull() %>% 
+  lapply(function(x) {
+    read_csv(x) %>% 
+      filter(param == "bp_value") %>% 
+      select(mean) %>% 
+      mutate(group = str_extract(x, "all|masu|other"))
+  }) %>% 
+  bind_rows()
+
+## mcmc sample size
+df_mcmc_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
+  pull() %>% 
+  lapply(function(x) {
+    read_csv(x) %>% 
+      select(n_total_mcmc,
+             n_sample,
+             n_thin,
+             n_burn) %>% 
+      distinct()
+  }) %>% 
+  bind_rows()
+
+df_mcmc_reg <- list.files(path = here::here("result"), full.names = T) %>% 
+  as_tibble() %>% 
+  filter(str_detect(string = .$value, pattern = "reg_")) %>% 
+  filter(!str_detect(string = .$value, pattern = "rich")) %>% 
+  pull() %>% 
+  lapply(function(x) {
+    read_csv(x) %>% 
+      select(n_total_mcmc,
+             n_sample,
+             n_thin,
+             n_burn) %>% 
+      distinct()
+  }) %>% 
+  bind_rows()
+
+## stocking data
+source(here::here("code/data_fmt_stock.R"))
+
+df_stock_stage <- df_stock %>% 
+  group_by(release_stage) %>% 
+  summarize(stock = sum(abundance)) %>% 
+  mutate(ratio = stock / max(stock),
+         prop = stock / sum(stock))
+
 ```
-
-**One Sentence Summary:** Large-scale releases of captive-bred organisms undermine the long-term persistence of ecological communities by disrupting the stable coexistence of competing species.
 
@@
 
-The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement").
-Still, we may underestimate the negative impact because current schemes rarely consider the consequences of stock enhancement for the whole ecological community.
-Here, we use theory and long-term data of Japanese stream fish communities to show that stock enhancement undermines community stability.
-Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion.
-Consistent with this prediction, fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in the region.
-Our findings alarm that the current overreliance on stock enhancement may accelerate global biodiversity loss.
+The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement") [@arakiHatcheryStockingHelp2010; @krkosekDecliningWildSalmon2007].
+Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks [@kitadaEconomicEcologicalGenetic2018; @laikreCompromisingGeneticDiversity2010].
+Here, contrary to this intuition, we show that stock enhancement undermines community stability with no demographic benefit to the enhanced species.
+Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species via intensified competition.
+Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan [@kitadaLessonsJapanMarine2020].
+The current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.
+A radical change in management strategies is therefore required to achieve the sustainability of natural resources.
 
@@
 We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios.
-These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Materials and Methods**).
+These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Methods**).
 Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: coefficient of variation (CV), number of species persist (defined as $N_i > 0.01$ at $t=1600$), temporal mean ($\mu$), and temporal SD ($\sigma$).
@@
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
-We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Materials and Methods** for selection criteria).
+We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria).
 Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential effects of climates and local abiotic factors.
@@
 However, the protected watersheds preserve nearly intact landscapes (**Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
-Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**).
+Further, we have statistically controlled natural variation in environmental factors (see **Methods** and **Tables S8-S10**).
 This unique setup may have helped uncover the qualitative agreement between theory and empirical patterns.
@@
 Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.
+
+# Methods
+
+## Theory
+
+We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012].
+In the basic formula without stock enhancement, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = N_{i,t}~exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
+\end{align}
+```
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
+We modified this formula to include the effects of stock enhancement (species 1) on reproduction and competition as follows:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
+\end{align}
+```
+$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
+
+```{=tex}
+\begin{align}
+\phi_i = 
+\left\{
+\begin{array}{cc}
+f_R & (i = 1)\\
+0 & (i \ne 1)
+\end{array}
+\right.
+\end{align}
+```
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation (2) can be reorganized to:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
+\end{align}
+```
+In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0.5,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
+We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
+
+Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
+We identified five influential parameters (**Table S2-S4**), of which different values were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).
+This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
+
+Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates).
+The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
+We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five.
+We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach equilibrium without stock enhancement (initialization period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective stock enhancement (burn-in period).
+We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps.
+We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$).
+The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
+We summarized values of simulation parameters in **Table S1**.
+
+## Empirical analysis
+
+### Data
+
+**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
+The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterfisheriesresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
+The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
+Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
+We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
+As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019.
+Summed abundance of first and second passes was used in the following analysis.
+**Table S5** summarizes observed species in these watersheds.
+
+**Fish stocking.** The stocking of masu salmon began in the 1950s.
+Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage).
+Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level.
+For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
+During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
+
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]).
+We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site.
+We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
+We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
+We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
+
+### Statistical analysis
+
+Our goal is to compare temporal community dynamics across sites.
+However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
+To confront this challenge, we developed a Bayesian state-space model for three species groups separately: (i) whole community, the summed abundance of all species, (ii) enhanced species, the abundance of masu salmon, (iii) unenhanced species, the summed abundance of all species except masu salmon.
+A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
+The model is composed of observation and state models, as described below.
+
+In the observation model, we model observation processes.
+Fish abundance of either whole community, enhanced species (masu salmon), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
+
+```{=tex}
+\begin{align}
+N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t})
+\end{align}
+```
+where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
+Since fish sampling was conducted after the spring stocking of masu salmon, captured fish may include individuals released in the observation year.
+We explicitly modeled this observation process to avoid biases in estimating temporal community trends:
+
+```{=tex}
+\begin{align}
+\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
+\end{align}
+```
+$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released (unit: million fish) in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
+The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
+The parameter $\epsilon_{s,t}^{obs}$ is the error term that follows a normal distribution $Normal(0, \sigma_{obs,s}^2)$.
+The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
+When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
+
+In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
+
+```{=tex}
+\begin{align}
+ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
+\end{align}
+```
+where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
+The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the SD $\sigma_r$).
+This hierarchical structure allows for improved parameter estimates by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
+We used median estimates of fish density $n_{s,t}$ to calculate the temporal CV, mean ($\mu$), and SD ($\sigma$) for each site.
+We summarized the reconstructed community dynamics in **Figures S7-S9**.
+
+We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data.
+Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
+
+We used linear regression to quantify the impact of stock enhancement on community dynamics.
+Although our focus is stock enhancement, each model included climatic and local abiotic variables to account for important environmental differences among sites.
+Specifically, we developed the following linear regression model taking either the CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
+
+```{=tex}
+\begin{align}
+\left\{
+\begin{aligned}
+ln~y_s &\sim Normal(\mu_{y,s}, \sigma_y^2) &&\text{for CV, mean, and SD}\\
+y_s &\sim Poisson(\lambda_{y,s} exp(\epsilon_{\lambda,s})) &&\text{for species richness}
+\end{aligned}
+\right.
+\end{align}
+```
+where $\sigma_y$ is the SD of residual errors and $exp(\epsilon_{\lambda,s})$ is the error term that accounts for overdispersion ($\epsilon_{\lambda,s} \sim Normal(0, \sigma_{\lambda}^2)$).
+The expected means were related to linear predictors as follows:
+
+```{=tex}
+\begin{align}
+\left\{
+\begin{aligned}
+\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
+ln~\lambda_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
+\end{aligned}
+\right.
+\end{align}
+```
+$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$.
+The site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
+Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**).
+The watershed-specific intercept was related to watershed-level predictors as:
+
+```{=tex}
+\begin{align}
+\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
+\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
+\end{align}
+```
+$\delta_{0}$ is the global intercept and $\delta_k (k > 0)$ are the regression coefficients.
+The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019).
+Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
+The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
+All predictors were standardized (mean = 0, SD = 1) before the analysis.
+
+We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
+We assigned weakly informative priors to parameters (**Table S6**).
+Three Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
+Total MCMC interations ranged from `r min(df_mcmc_ssm$n_total_mcmc)` to `r max(df_mcmc_ssm$n_total_mcmc)` for the state-space models and was `r unique(df_mcmc_reg$n_total_mcmc)` for the regression models.
+The first `r unique(c(df_mcmc_ssm$n_burn, df_mcmc_reg$n_burn))` iterations were discarded as burn-in, and MCMC samples were saved every `r unique(df_mcmc_ssm$n_thin)` (state-space) and `r unique(df_mcmc_reg$n_thin)` iterations (regression) to reduce autocorrelation.
+Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached \< 1.1 [@gelmanDataAnalysisUsing2007].
+Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
+Parameter estimates were summarized in **Table S7-S10**.
 

### 2022-03-03 rmd/supporting_info.Rmd
Update supporting_info.Rmd
edit: minor change
edit: manuscript
move methods section

--- 2022-02-21 rmd/supporting_info.Rmd
@@
 
-df_area <- d0 %>% 
-  group_by(site_id, year) %>% 
-  summarize(area = unique(area))
-
-filename <- list.files(path = here::here("result"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "reg")) %>% 
-  filter(!str_detect(string = .$value, pattern = "reg_rich")) %>% 
-  pull()
-
-df_beta <- lapply(filename, function(x) {
-  read_csv(here::here(x)) %>% 
-    filter(parameter == "b[2]")
-})
-names(df_beta) <- str_extract(filename, "all|masu|other")
-
-## ssm estimate
-df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      filter(param == "bp_value") %>% 
-      select(mean) %>% 
-      mutate(group = str_extract(x, "all|masu|other"))
-  }) %>% 
-  bind_rows()
-
-## mcmc sample size
-df_mcmc_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      select(n_total_mcmc,
-             n_sample,
-             n_thin,
-             n_burn) %>% 
-      distinct()
-  }) %>% 
-  bind_rows()
-
-df_mcmc_reg <- list.files(path = here::here("result"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "reg_")) %>% 
-  filter(!str_detect(string = .$value, pattern = "rich")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      select(n_total_mcmc,
-             n_sample,
-             n_thin,
-             n_burn) %>% 
-      distinct()
-  }) %>% 
-  bind_rows()
-
-## stocking data
-source(here::here("code/data_fmt_stock.R"))
-
-df_stock_stage <- df_stock %>% 
-  group_by(release_stage) %>% 
-  summarize(stock = sum(abundance)) %>% 
-  mutate(ratio = stock / max(stock),
-         prop = stock / sum(stock))
-
 ```
@@
 ```
-# Materials and Methods
-
-## Theory
-
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012].
-In the basic formula without stock enhancement, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = N_{i,t}~exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
-\end{align}
-```
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
-We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
-\end{align}
-```
-$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
-
-```{=tex}
-\begin{align}
-\phi_i = 
-\left\{
-\begin{array}{cc}
-f_R & (i = 1)\\
-0 & (i \ne 1)
-\end{array}
-\right.
-\end{align}
-```
-$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation (2) can be reorganized to:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
-\end{align}
-```
-In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
-We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
-
-Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
-We identified five influential parameters (**Table S2-S4**), of which different values were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).
-This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
-
-Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates).
-The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
-We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five.
-We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach equilibrium without stock enhancement (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective stock enhancement (burn-in period).
-We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps.
-We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$).
-The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
-We summarized values of simulation parameters in **Table S1**.
-
-## Empirical analysis
-
-### Data
-
-**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterfisheriesresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
-The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
-Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
-We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
-As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019.
-Summed abundance of first and second passes was used in the following analysis.
-**Table S5** summarizes observed species in these watersheds.
-
-**Fish stocking.** The stocking of masu salmon began in the 1950s.
-Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage).
-Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level.
-For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
-During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
-
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]).
-We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site.
-We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
-Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
-We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
-
-### Statistical analysis
-
-Our goal is to compare temporal community dynamics across sites.
-However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
-To confront this challenge, we developed a Bayesian state-space model for three species groups separately: (i) whole community, the summed abundance of all species, (ii) enhanced species, the abundance of masu salmon, (iii) unenhanced species, the summed abundance of all species except masu salmon.
-A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
-The model is composed of observation and state models, as described below.
-
-In the observation model, we model observation processes.
-Fish abundance of either whole community, enhanced species (masu salmon), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
-
-```{=tex}
-\begin{align}
-N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t})
-\end{align}
-```
-where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
-Since fish sampling was conducted after the spring stocking of masu salmon, captured fish may include individuals released in the observation year.
-We explicitly modeled this observation process to avoid biases in estimating temporal community trends:
-
-```{=tex}
-\begin{align}
-\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
-\end{align}
-```
-$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released (unit: million fish) in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
-The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The parameter $\epsilon_{s,t}^{obs}$ is the error term that follows a normal distribution $Normal(0, \sigma_{obs,s}^2)$.
-The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
-When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
-
-In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
-
-```{=tex}
-\begin{align}
-ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
-\end{align}
-```
-where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
-The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the SD $\sigma_r$).
-This hierarchical structure allows for improved parameter estimates by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
-We used median estimates of fish density $n_{s,t}$ to calculate the temporal CV, mean ($\mu$), and SD ($\sigma$) for each site.
-We summarized the reconstructed community dynamics in **Figures S7-S9**.
-
-We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data.
-Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
-
-We used linear regression to quantify the impact of stock enhancement on community dynamics.
-Although our focus is stock enhancement, each model included climatic and local abiotic variables to account for important environmental differences among sites.
-Specifically, we developed the following linear regression model taking either the CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
-
-```{=tex}
-\begin{align}
-\left\{
-\begin{aligned}
-ln~y_s &\sim Normal(\mu_{y,s}, \sigma_y^2) &&\text{for CV, mean, and SD}\\
-y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s})) &&\text{for species richness}
-\end{aligned}
-\right.
-\end{align}
-```
-where $\sigma_y$ is the SD of residual errors and $exp(\epsilon_{y,s})$ is the error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$).
-The expected mean $\mu_y$ was related to linear predictors as follows:
-
-```{=tex}
-\begin{align}
-\left\{
-\begin{aligned}
-\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
-ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
-\end{aligned}
-\right.
-\end{align}
-```
-$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$.
-The site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
-Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**).
-The watershed-specific intercept was related to watershed-level predictors as:
-
-```{=tex}
-\begin{align}
-\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
-\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
-\end{align}
-```
-$\delta_{0}$ is the global intercept and $\delta_k (k > 0)$ are the regression coefficients.
-The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019).
-Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
-The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
-All predictors were standardized (mean = 0, SD = 1) before the analysis.
-
-We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
-We assigned weakly informative priors to parameters (**Table S6**).
-Three Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
-Total MCMC interations ranged from `r min(df_mcmc_ssm$n_total_mcmc)` to `r max(df_mcmc_ssm$n_total_mcmc)` for the state-space models and was `r unique(df_mcmc_reg$n_total_mcmc)` for the regression models.
-The first `r unique(c(df_mcmc_ssm$n_burn, df_mcmc_reg$n_burn))` iterations were discarded as burn-in, and MCMC samples were saved every `r unique(df_mcmc_ssm$n_thin)` (state-space) and `r unique(df_mcmc_reg$n_thin)` iterations (regression) to reduce autocorrelation.
-Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached \< 1.1 [@gelmanDataAnalysisUsing2007].
-Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
-Parameter estimates were summarized in **Table S7-S10**.
-
-\newpage
-
 # Supplementary text

### 2022-03-03 rmd/supporting_info.Rmd
edit: suppl info

@@
 op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x)
-
-# theory
-load(here::here("result/result_ricker.RData"))
-
-n_sim <- sim_result %>% 
-  mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
-  pull(n_sim) %>% 
-  unique()
-
-param_set <- sim_result %>% 
-  distinct(n_species,
-           k,
-           r_type,
-           r1,
-           r_min,
-           r_max,
-           sd_env,
-           phi,
-           int_type,
-           alpha,
-           model,
-           seed)
-
-# empirical data
-
-## raw data
-source(here::here("code/data_fmt_fishdata.R"))
 

### 2022-03-03 rmd/presubmission_enquiry.Rmd
Create presubmission_enquiry.Rmd

---
date: "3/2/2022"
output:
  word_document:
    reference_docx: word_format.docx
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

Dear Editor

We are interested in your opinion regarding the suitability of our manuscript entitled "*Intentional stocking undermines ecological stability*" for publication in *Nature* as *Article*. We can submit it formally in a week if we receive a positive feedback from you. Our manuscript content is summarized below.

Every year, humans release billions of captive-bred organisms into the wild to restore depleting natural resources across the globe (hereafter, "stock enhancement"). Scientists have discovered significant risks associated with stock enhancement, such as the accumulation of deleterious genes in wild populations. Yet, this form of species management is prevalent in fisheries, forestry, and wildlife management because the demographic benefits seem to exceed the associated risks.

**We argue that this "myth" is a misunderstanding with serious consequences for global biodiversity conservation - current assessments rarely consider the impact of stock enhancement on whole ecological communities.** Stock enhancement introduces unnaturally high numbers of individuals into the wild. Hence, it should disrupt the sensitive balance of species interactions that allows the stable coexistence of competing species, ultimately undermining the long-term persistence of ecological communities. We are unaware of any research addressing this critical hypothesis.

In this study, we used theory and long-term data of stream fish communities to show that stock enhancement undermines the stability of ecological communities. Our theory and empirical results agreed that stock enhancement inhibits the stable coexistence of competing species, thereby increasing the risk of community collapse. Importantly, stock enhancement tended to have a negative - rather than positive - effect on the stocked species due to intensified within-species competition. While our empirical evidence comes from stream ecosystems, this pattern appeared in most simulated ecological scenarios, implying that this phenomenon is pervasive across aquatic and terrestrial ecosystems.

Our study distinguishes itself from previous studies in three important ways:

1.  This study is the first to show the community-level impact of stock enhancement ***in the long term***. Although numerous studies paid close attention to the fate of captive-bred organisms in the wild, none has assessed its demographic impact on the long-term persistence of whole ecological communities.

2.  Our empirical analysis exploited \> 20 years of fish community data at 97 sites collected by consistent sampling methods. Furthermore, while these sites greatly varied in stocking intensity, they preserved intact landscapes with strict regulations of human activities. Hence, our study system set the stage for a "natural experiment" to test our hypothesis.

3.  Our findings will trigger radical changes to the current management of natural resources. Despite the widespread recognition that stock enhancement entails ecological risks, trillions of dollars are invested into stock enhancement to manage natural resources globally. The results of this study alarm that the continued use of this method will accelerate biodiversity loss with no obvious benefit to the stocked species.

In addition to the significance described above, the connection between natural resource management and ecology has a broad implication for a truly interdisciplinary audience, including policy-decision makers, stakeholders, conservation biologists, and basic ecologists. Therefore, we believe *Nature* is an ideal outlet for this manuscript.

We are looking forward to hearing from you.

### 2022-03-03 rmd/manuscript.Rmd
edit: manuscript

@@
 output:
-  pdf_document:
-    latex_engine: xelatex
-#  word_document:
-#    reference_docx: word_format.docx
+#  pdf_document:
+#    latex_engine: xelatex
+  word_document:
+    reference_docx: word_format.docx
 csl: nature.csl
@@
 Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks [@kitadaEconomicEcologicalGenetic2018; @laikreCompromisingGeneticDiversity2010].
-Here, contrary to this intuition, we show that stock enhancement undermines community stability with no demographic benefit to the enhanced species.
+Here, contrary to this intuition, we show that stock enhancement undermines community stability with little demographic benefit to the enhanced species.
 Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species via intensified competition.
@@
 
-We should prioritize habitat conservation with a broader scope of ecosystem management.
+We should prioritize habitat conservation with a broader scope of ecosystem management to achieve the sustainability of natural resources.
 Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement.

### 2022-03-04 rmd/manuscript.Rmd
Update manuscript.Rmd

--- 2022-03-03 rmd/manuscript.Rmd
@@
 Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks [@kitadaEconomicEcologicalGenetic2018; @laikreCompromisingGeneticDiversity2010].
-Here, contrary to this intuition, we show that stock enhancement undermines community stability with no demographic benefit to the enhanced species.
-Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species via intensified competition.
+Here, contrary to this intuition, we show that stock enhancement triggers community collapse with little demographic benefit to the enhanced species.
+Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion.
+In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition.
 Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan [@kitadaLessonsJapanMarine2020].
 The current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.
-A radical change in management strategies is therefore required to achieve the sustainability of natural resources.
+A radical change in management strategies is therefore required for the sustainability of natural resources.
 
@@
 
-We should prioritize habitat conservation with a broader scope of ecosystem management.
+We should prioritize habitat conservation with a broader scope of ecosystem management for the sustainability of natural resources.
 Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement.

### 2022-03-04 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan [@kitadaLessonsJapanMarine2020].
-The current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.
+Our findings alarm that the current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.
 A radical change in management strategies is therefore required for the sustainability of natural resources.

### 2022-03-08 rmd/manuscript.Rmd
edit: manuscript

@@
 #    reference_docx: word_format.docx
-csl: nature.csl
+csl: science.csl
 knit: (function(inputFile, encoding) {
@@
 
-The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement") [@arakiHatcheryStockingHelp2010; @krkosekDecliningWildSalmon2007].
-Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks [@kitadaEconomicEcologicalGenetic2018; @laikreCompromisingGeneticDiversity2010].
+The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement").
+Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks.
 Here, contrary to this intuition, we show that stock enhancement triggers community collapse with little demographic benefit to the enhanced species.
@@
 In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition.
-Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan [@kitadaLessonsJapanMarine2020].
+Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan.
 Our findings alarm that the current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.

### 2022-03-08 rmd/manuscript.Rmd
edit: manuscript

@@
 output:
-  pdf_document:
-    latex_engine: xelatex
-#  word_document:
-#    reference_docx: word_format.docx
+  #pdf_document:
+  #  latex_engine: xelatex
+  word_document:
+    reference_docx: word_format.docx
 csl: science.csl
@@
 
-# theory
+# theory ####
 load(here::here("result/result_ricker.RData"))
@@
 
-# empirical data
-
-## raw data
+# empirical data ####
 source(here::here("code/data_fmt_fishdata.R"))
@@
 
-# Methods
-
-## Theory
-
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012].
-In the basic formula without stock enhancement, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = N_{i,t}~exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
-\end{align}
-```
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
-We modified this formula to include the effects of stock enhancement (species 1) on reproduction and competition as follows:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
-\end{align}
-```
-$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
-
-```{=tex}
-\begin{align}
-\phi_i = 
-\left\{
-\begin{array}{cc}
-f_R & (i = 1)\\
-0 & (i \ne 1)
-\end{array}
-\right.
-\end{align}
-```
-$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation (2) can be reorganized to:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
-\end{align}
-```
-In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0.5,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
-We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
-
-Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
-We identified five influential parameters (**Table S2-S4**), of which different values were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).
-This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
-
-Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates).
-The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
-We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five.
-We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach equilibrium without stock enhancement (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective stock enhancement (burn-in period).
-We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps.
-We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$).
-The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
-We summarized values of simulation parameters in **Table S1**.
-
-## Empirical analysis
-
-### Data
-
-**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterfisheriesresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
-The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
-Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
-We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
-As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019.
-Summed abundance of first and second passes was used in the following analysis.
-**Table S5** summarizes observed species in these watersheds.
-
-**Fish stocking.** The stocking of masu salmon began in the 1950s.
-Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage).
-Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level.
-For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
-During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
-
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]).
-We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site.
-We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
-Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
-We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
-
-### Statistical analysis
-
-Our goal is to compare temporal community dynamics across sites.
-However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
-To confront this challenge, we developed a Bayesian state-space model for three species groups separately: (i) whole community, the summed abundance of all species, (ii) enhanced species, the abundance of masu salmon, (iii) unenhanced species, the summed abundance of all species except masu salmon.
-A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
-The model is composed of observation and state models, as described below.
-
-In the observation model, we model observation processes.
-Fish abundance of either whole community, enhanced species (masu salmon), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
-
-```{=tex}
-\begin{align}
-N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t})
-\end{align}
-```
-where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
-Since fish sampling was conducted after the spring stocking of masu salmon, captured fish may include individuals released in the observation year.
-We explicitly modeled this observation process to avoid biases in estimating temporal community trends:
-
-```{=tex}
-\begin{align}
-\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
-\end{align}
-```
-$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released (unit: million fish) in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
-The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The parameter $\epsilon_{s,t}^{obs}$ is the error term that follows a normal distribution $Normal(0, \sigma_{obs,s}^2)$.
-The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
-When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
-
-In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
-
-```{=tex}
-\begin{align}
-ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
-\end{align}
-```
-where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
-The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the SD $\sigma_r$).
-This hierarchical structure allows for improved parameter estimates by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
-We used median estimates of fish density $n_{s,t}$ to calculate the temporal CV, mean ($\mu$), and SD ($\sigma$) for each site.
-We summarized the reconstructed community dynamics in **Figures S7-S9**.
-
-We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data.
-Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
-
-We used linear regression to quantify the impact of stock enhancement on community dynamics.
-Although our focus is stock enhancement, each model included climatic and local abiotic variables to account for important environmental differences among sites.
-Specifically, we developed the following linear regression model taking either the CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
-
-```{=tex}
-\begin{align}
-\left\{
-\begin{aligned}
-ln~y_s &\sim Normal(\mu_{y,s}, \sigma_y^2) &&\text{for CV, mean, and SD}\\
-y_s &\sim Poisson(\lambda_{y,s} exp(\epsilon_{\lambda,s})) &&\text{for species richness}
-\end{aligned}
-\right.
-\end{align}
-```
-where $\sigma_y$ is the SD of residual errors and $exp(\epsilon_{\lambda,s})$ is the error term that accounts for overdispersion ($\epsilon_{\lambda,s} \sim Normal(0, \sigma_{\lambda}^2)$).
-The expected means were related to linear predictors as follows:
-
-```{=tex}
-\begin{align}
-\left\{
-\begin{aligned}
-\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
-ln~\lambda_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
-\end{aligned}
-\right.
-\end{align}
-```
-$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$.
-The site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
-Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**).
-The watershed-specific intercept was related to watershed-level predictors as:
-
-```{=tex}
-\begin{align}
-\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
-\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
-\end{align}
-```
-$\delta_{0}$ is the global intercept and $\delta_k (k > 0)$ are the regression coefficients.
-The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019).
-Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
-The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
-All predictors were standardized (mean = 0, SD = 1) before the analysis.
-
-We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
-We assigned weakly informative priors to parameters (**Table S6**).
-Three Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
-Total MCMC interations ranged from `r min(df_mcmc_ssm$n_total_mcmc)` to `r max(df_mcmc_ssm$n_total_mcmc)` for the state-space models and was `r unique(df_mcmc_reg$n_total_mcmc)` for the regression models.
-The first `r unique(c(df_mcmc_ssm$n_burn, df_mcmc_reg$n_burn))` iterations were discarded as burn-in, and MCMC samples were saved every `r unique(df_mcmc_ssm$n_thin)` (state-space) and `r unique(df_mcmc_reg$n_thin)` iterations (regression) to reduce autocorrelation.
-Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached \< 1.1 [@gelmanDataAnalysisUsing2007].
-Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
-Parameter estimates were summarized in **Table S7-S10**.
-
 # Acknowledgments
@@
 
+\newpage
+
 # References

### 2022-03-12 rmd/figures.Rmd
Squashed commit of the following:
commit 42b7838e55c1587f6a744b0a978c367eac453d43
Author: AkiraTerui <hanabi0111@gmail.com>
Date:   Sat Mar 12 11:50:40 2022 -0500

    edit: affiliation

commit 1933aaca4b7cc7f4d29771b59b45cf512e403b48
Author: aterui <hanabi0111@gmail.com>
Date:   Thu Mar 10 22:06:24 2022 -0500

    edit:  manuscript

commit 0884ad16cc1eb71df364fe1aaf0e7cec0dadd794
Author: aterui <hanabi0111@gmail.com>
Date:   Thu Mar 10 21:32:32 2022 -0500

    edit: manuscript

commit db4e8b6bab9c85a4ba5ba4767ac5442fcf493553
Author: AkiraTerui <hanabi0111@gmail.com>
Date:   Thu Mar 10 19:04:2

@@
 
-**Figure 1** Theory and empirical observations agree that stock enhancement destabilizes community dynamics.
+**Figure 1** Theory and empirical observations agree that intentional release destabilizes community dynamics.
 In A and B, panels and colors distinguish response variables and species groups.
@@
 
-**Figure 2** Posterior distributions for the standardized regression coefficients of stock enhancement.
+**Figure 2** Posterior distributions for the standardized regression coefficients of intentional release.
 Y-axis represents different response variables grouped by colors distinguishing species groups (whole community, enhanced species [masu salmon], and unenhanced species).

### 2022-03-12 rmd/manuscript.Rmd
Squashed commit of the following:
commit 42b7838e55c1587f6a744b0a978c367eac453d43
Author: AkiraTerui <hanabi0111@gmail.com>
Date:   Sat Mar 12 11:50:40 2022 -0500

    edit: affiliation

commit 1933aaca4b7cc7f4d29771b59b45cf512e403b48
Author: aterui <hanabi0111@gmail.com>
Date:   Thu Mar 10 22:06:24 2022 -0500

    edit:  manuscript

commit 0884ad16cc1eb71df364fe1aaf0e7cec0dadd794
Author: aterui <hanabi0111@gmail.com>
Date:   Thu Mar 10 21:32:32 2022 -0500

    edit: manuscript

commit db4e8b6bab9c85a4ba5ba4767ac5442fcf493553
Author: AkiraTerui <hanabi0111@gmail.com>
Date:   Thu Mar 10 19:04:2

@@
 ---
-title: "Intentional stocking undermines ecological stability"
+title: "Intentional release of native species undermines ecological stability"
 output:
-  #pdf_document:
-  #  latex_engine: xelatex
-  word_document:
-    reference_docx: word_format.docx
-csl: science.csl
+  pdf_document:
+    latex_engine: xelatex
+  #word_document:
+  # reference_docx: word_format.docx
+csl: nature.csl
 knit: (function(inputFile, encoding) {
@@
 
-## stocking data
+## release data
 source(here::here("code/data_fmt_stock.R"))
@@
 
-**Authors:** Akira Terui^1,\*^, Hirokazu Urabe^2^, Masayuki Senzaki^3^, Bungo Nishizawa^4^
-
-\*Corresponding author: hanabi0111\@gmail.com
-
-**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Salmon and Freshwater Fisheries Research Institute, Hokkaido Research Organization, Eniwa, Hokkaido, 061-1433, Japan ^3^ Faculty of Environmental Earth Science, Hokkaido University, Sapporo, Hokkaido, 060-0810, Japan ^4^ National Institute of Polar Research, Tachikawa, Tokyo, 190-8518, Japan
-
 # Abstract
 
-The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement").
+The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred native species ("intentional release").
 Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks.
-Here, contrary to this intuition, we show that stock enhancement triggers community collapse with little demographic benefit to the enhanced species.
-Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion.
+Here, contrary to this intuition, we show that intentional release triggers community collapse with little demographic benefit to the enhanced species.
+Our theory predicted that intentional release destabilizes community dynamics by facilitating competitive exclusion.
 In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition.
-Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan.
-Our findings alarm that the current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.
-A radical change in management strategies is therefore required for the sustainability of natural resources.
+Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery masu salmon - a major freshwater resource in Japan.
+Our findings alarm that the current overreliance on intentional release may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.
 
@@
 Captive breeding is a form of the efforts to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-Although releases of captive-bred organisms ("stock enhancement") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
+Although releases of captive-bred native species ("intentional release") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
 In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
@@
 
-Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement.
+Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of intentional release.
 Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
-Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@careyNativeInvadersChallenges2012].
+Intentional release may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@careyNativeInvadersChallenges2012].
 Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability.
@@
 
-Here, we show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999].
-Our theory illuminates that stock enhancement compromises the stabilizing mechanism emerging from species niche differences.
+Here, we show that intentional release undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999].
+Our theory illuminates that intentional release compromises the stabilizing mechanism emerging from species niche differences.
 The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].
 
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the selective stock enhancement of a constituent species (species 1).
+We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the selective intentional release of a constituent species (species 1).
 Specifically, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Methods**).
-Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: coefficient of variation (CV), number of species persist (defined as $N_i > 0.01$ at $t=1600$), temporal mean ($\mu$), and temporal SD ($\sigma$).
+Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to intentional release: coefficient of variation (CV), number of species persist (defined as $N_i > 0.01$ at $t=1600$), temporal mean ($\mu$), and temporal SD ($\sigma$).
 We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.
 
-When carrying capacity was small ($K=100$), our model predicted a destabilizing effect of stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
+When carrying capacity was small ($K=100$), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
 This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
-The enhanced species decreased because stocking induced the negative competitive effect exceeding the reproductive contribution of released individuals [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition reduced the unenhanced species at high levels of stock enhancement, resulting in fewer persisting species (**Figure 1A**).
+The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals [@satakeStockingCaptivebredFish2012].
+Meanwhile, interspecific competition reduced the unenhanced species at high levels of intentional release, resulting in fewer persisting species (**Figure 1A**).
 Combined, the total community density decreased more sharply than individual species groups (**Figure 1A**).
@@
 
-The destabilizing effect emerges because stock enhancement affects the balance of species interactions that underpins community stability.
+The destabilizing effect emerges because intentional release affects the balance of species interactions that underpins community stability.
 In theory, the stable coexistence requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a].
@@
 Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multispecies community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$).
-However, stock enhancement is externally controlled, and the number of releases is not subject to density-dependent regulation.
+However, intentional release is externally controlled, and the number of releases is not subject to density-dependent regulation.
 Therefore, released individuals impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.
 
-Stock enhancement, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S4-S6**).
-In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figure S4**).
-This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [e.g., @jonesRestorationMauritiusKestrel1995].
+Intentional release, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S4-S6**).
+In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figure S4**).
+This result may explain why some of the best evidence for successful intentional release comes from long-lived endangered species [e.g., @jonesRestorationMauritiusKestrel1995].
 More importantly, the contrasting community response at different carrying capacities provides deeper insights.
-One of the core motivations for stock enhancement is to mitigate declining trends of natural resources due to human impacts, such as habitat loss [@chaseEcosystemDecayExacerbates2020].
-Ironically, our results suggest that stock enhancement will not bring desired outcomes unless we resolve root causes that compromise environmental capacity first.
+One of the core motivations for intentional release is to mitigate declining trends of natural resources due to human impacts, such as habitat loss [@chaseEcosystemDecayExacerbates2020].
+Ironically, our results suggest that intentional release will not bring desired outcomes unless we resolve root causes that compromise environmental capacity first.
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
-In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official stocking records.
-The majority of stocking occurs in spring, after which salmon fry stay in freshwater for growing seasons.
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
+In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records.
+The majority of release occurs in spring, after which salmon fry stay in freshwater for growing seasons.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
 We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria).
-Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential effects of climates and local abiotic factors.
+Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for potential effects of climates and local abiotic factors.
 
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**).
-The effect was striking in its magnitude, almost doubling the CV at the highest stocking level.
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive release (**Figure 1B**).
+The effect was striking in its magnitude, almost doubling the CV at the highest release level.
 Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
 This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S8-S10** for full statistics).
-In the meantime, the SDs had vague relationships with stock enhancement (**Figures 1B and 2**).
+In the meantime, the SDs had vague relationships with intentional release (**Figures 1B and 2**).
 
@@
 We should prioritize habitat conservation with a broader scope of ecosystem management for the sustainability of natural resources.
-Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement.
+Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of intentional release.
 Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation.
@@
 Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].
-These considerable potentials indicate that viable management options exist before blindly accepting stock enhancement.
-Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.
+These considerable potentials indicate that viable management options exist before blindly accepting intentional release.
+Without a comprehensive framework that appreciates the ecological integrity of natural communities, the intentional release will never be effective but impairs biodiversity.
 

### 2022-03-12 rmd/supporting_info.Rmd
edit: manuscript
Squashed commit of the following:
commit 42b7838e55c1587f6a744b0a978c367eac453d43
Author: AkiraTerui <hanabi0111@gmail.com>
Date:   Sat Mar 12 11:50:40 2022 -0500

    edit: affiliation

commit 1933aaca4b7cc7f4d29771b59b45cf512e403b48
Author: aterui <hanabi0111@gmail.com>
Date:   Thu Mar 10 22:06:24 2022 -0500

    edit:  manuscript

commit 0884ad16cc1eb71df364fe1aaf0e7cec0dadd794
Author: aterui <hanabi0111@gmail.com>
Date:   Thu Mar 10 21:32:32 2022 -0500

    edit: manuscript

commit db4e8b6bab9c85a4ba5ba4767ac5442fcf493553
Author: AkiraTerui <hanabi0111@gmail.com>
Date:   T

--- 2022-02-23 rmd/supporting_info.Rmd
@@
 bibliography: reference.bib
-csl: science.csl
+csl: nature.csl
 ---
@@
 
-# empirical data
+# empirical data ####
 
@@
 ```
-# Materials and Methods
+# Methods
 
@@
 We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012].
-In the basic formula without stock enhancement, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+In the basic formula without intentional release, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
 
@@
 where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
-We modified this formula to include the effects of stock enhancement (species 1) on reproduction and competition as follows:
+We modified this formula to include the effects of intentional release (species 1) on reproduction and competition as follows:
 
@@
 \begin{align}
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
 \end{align}
@@
 \begin{align}
-N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
 \end{align}
@@
 
-Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**).
+Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and intentional release (see **Supplementary text**).
 We identified five influential parameters (**Table S2-S4**), of which different values were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
@@
 We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five.
-We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach equilibrium without stock enhancement (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective stock enhancement (burn-in period).
-We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps.
+We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach equilibrium without intentional release (initialization period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective intentional release (burn-in period).
+We continued the simulation run with intentional release and saved the last `r unique(sim_result$n_timestep)` time steps.
 We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$).
@@
 
-**Fish stocking.** The stocking of masu salmon began in the 1950s.
+**Fish release.** The release of masu salmon began in the 1950s.
 Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage).
-Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level.
-For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
-During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
+Although the fish release occurs at multiple locations within a watershed, the release information is available only at the watershed level.
+For each release stage, we assembled annual records of intentional release (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
+During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
 
@@
 where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
-Since fish sampling was conducted after the spring stocking of masu salmon, captured fish may include individuals released in the observation year.
+Since fish sampling was conducted after the spring release of masu salmon, captured fish may include individuals released in the observation year.
 We explicitly modeled this observation process to avoid biases in estimating temporal community trends:
@@
 
-We used linear regression to quantify the impact of stock enhancement on community dynamics.
-Although our focus is stock enhancement, each model included climatic and local abiotic variables to account for important environmental differences among sites.
+We used linear regression to quantify the impact of intentional release on community dynamics.
+Although our focus is intentional release, each model included climatic and local abiotic variables to account for important environmental differences among sites.
 Specifically, we developed the following linear regression model taking either the CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
@@
 $\delta_{0}$ is the global intercept and $\delta_k (k > 0)$ are the regression coefficients.
-The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019).
+The watershed-level predictors $z_{k,w}$ include the yearly release of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019).
 Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
@@
 
-We performed a sensitivity analysis of the community simulation to identify key simulation parameters that strongly affect the relationships between community dynamics (temporal mean and SD of density) and stock enhancement.
+We performed a sensitivity analysis of the community simulation to identify key simulation parameters that strongly affect the relationships between community dynamics (temporal mean and SD of density) and intentional release.
 We generated 500 sets of parameter combinations by randomly drawing values of seven simulation parameters from uniform distributions (**Table S1**).
-For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of stock enhancement $R$ (drawn randomly from $Unif(0, 500)$).
+For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of intentional release $R$ (drawn randomly from $Unif(0, 500)$).
 This yields a total of $5 \times 10^4$ simulation replicates.
@@
 
-For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community dynamics, which indicate the effect of stock enhancement under a given ecological context.
+For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community dynamics, which indicate the effect of intentional release under a given ecological context.
 To examine influences of simulation parameters on $\xi$ (**Table S1**), we developed the following regression model taking $\xi$ as a response variable:
@@
 In the meantime, we varied values of $K$, $r_1$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**).
-Although $f_R$ had little influence on stocking effects (**Table S1**), we varied this parameter given the significant interest in the relative fitness of captive-bred individuals in the wild.
+Although $f_R$ had little influence on release effects (**Table S1**), we varied this parameter given the significant interest in the relative fitness of captive-bred individuals in the wild.
 
@@
 Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
-Response variables are Spearman's rank correlation between stock enhancement and either temporal mean density ($\\mu$) or SD ($\\sigma$) of ", c_text[i],".
+Response variables are Spearman's rank correlation between intentional release and either temporal mean density ($\\mu$) or SD ($\\sigma$) of ", c_text[i],".
 Explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")
@@
 
-                       "Theoretical predictions for the stocking effect on community dynamics.
+                       "Theoretical predictions for the release effect on community dynamics.
 Rows represent different response variables, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).

### 2022-03-12 code/figure_coef.R

@@ -69,7 +69,7 @@ g_coef <- df_mcmc %>%
              linetype = "dashed") +
   geom_density_ridges(alpha = 0.5) +
   labs(y = "Response",
-       x = "Stocking effect",
+       x = "Release effect",
        fill = "Species group") +
   guides(color = "none") +
   theme_ridges()

### 2022-03-12 code/table_reg.R

@@ -48,7 +48,7 @@ df_est <- lapply(filename, function(x) {
                               parameter == "a[4]" ~ "Forest fraction",
                               parameter == "a[5]" ~ "Forest fraction",
                               parameter == "b[1]" ~ "Intercept",
-                              parameter == "b[2]" ~ "Stock enhancement",
+                              parameter == "b[2]" ~ "Intentional release",
                               parameter == "b[3]" ~ "Ocean productivity"),
            Response = ifelse(parameter == "b[1]", response, NA),
            Response = case_when(Response == "richness" ~ "Species richness",

### 2022-03-12 code/table_ssm.R

@@ -29,9 +29,9 @@ df_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>%
                                    param == "sd_r_space" ~ "$\\sigma_{r}$",
                                    param == "sd_b" ~ "$\\sigma_{\\beta}$"),
              Interpretation = case_when(param == "log_global_r" ~ "Rate of community change",
-                                        param == "mu_b" ~ "Effect of spring stoking",
+                                        param == "mu_b" ~ "Effect of spring release",
                                         param == "sd_r_space" ~ "SD of the rate of community change",
-                                        param == "sd_b" ~ "SD of the effect of spring stocking"),
+                                        param == "sd_b" ~ "SD of the effect of spring release"),
              `Species group` = case_when(group == "all" & param == "log_global_r" ~ "Whole",
                                          group == "masu" & param == "log_global_r" ~ "Enhanced",
                                          group == "other" & param == "log_global_r" ~ "Unenhanced")) %>% 

### 2022-03-14 rmd/manuscript.Rmd
edit: double-blind

@@
 
-We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Genki Sahashi and Masato Yamamichi for helpful discussion on this manuscript.
+Blinded for double-blind review
 
@@
 
-AT conceived the project.
-AT, HU and BN assembled data for empirical analysis.
-AT analyzed data with inputs from HU, MS, and BN.
-AT wrote the first draft and HU, MS, and BN significantly contributed to the final version of the manuscript.
+Blinded for double-blind review
 
@@
 
-Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.
+Data and codes will be made available upon the acceptance of the manuscript.
 

### 2022-03-14 rmd/manuscript.Rmd
edit: minor

--- 2022-03-12 rmd/manuscript.Rmd
@@
 ```
+
+**Authors:** Akira Terui^1\*^, Hirokazu Urabe^2^, Masayuki Senzaki^3^, Bungo Nishizawa^4^
+
+**\*Corresponding author:** hanabi0111\@gmail.com
+
+**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Salmon and Freshwater Fisheries Research Institute, Hokkaido Research Organization, Eniwa, Hokkaido, 061-1433, Japan ^3^ Faculty of Environmental Earth Science, Hokkaido University, Sapporo, Hokkaido, 060-0810, Japan ^4^ National Institute of Polar Research, Tachikawa, Tokyo, 190-8518, Japan
 
@@
 
-# Acknowledgments
+# Acknowledgements
 
@@
 
-# Competing interests
+# Competing interest
 
-None declared.
+None declared
 
-# **Data and materials availability**
+# Data availability
 
@@
 
-\newpage
-
 # References

### 2022-03-30 code/figure_coef.R
edit: figure

@@ -70,8 +70,8 @@ g_coef <- df_mcmc %>%
   geom_density_ridges(alpha = 0.5) +
   labs(y = "Response",
        x = "Release effect",
-       fill = "Species group") +
-  guides(color = "none") +
+       fill = "Species group",
+       color = "Species group") +
   theme_ridges()
 
 ggsave(g_coef,

### 2022-03-30 rmd/manuscript.Rmd
edit: manuscript

@@
   # reference_docx: word_format.docx
-csl: nature.csl
+csl: pnas.csl
 knit: (function(inputFile, encoding) {
@@
 Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks.
-Here, contrary to this intuition, we show that intentional release triggers community collapse with little demographic benefit to the enhanced species.
-Our theory predicted that intentional release destabilizes community dynamics by facilitating competitive exclusion.
+However, such external inputs may disrupt the sensitive balance of species interactions that allows competing species to coexist, potentially compromising the long-term community stability.
+Here, we use theory and long-term data of stream fish communities to show that intentional release triggers community collapse with little demographic benefit to the enhanced species.
+Our theory predicted that intentional release intensifies interspecific competition, facilitating competitive exclusion of unenhanced species that otherwise stablely coexist.
 In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition.
-Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery masu salmon - a major freshwater resource in Japan.
+Consequently, the ecological community with intentional release is predicted to show reduced community density with unstable temporal dynamics.
+Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery salmon - a major fishery resource worldwide.
 Our findings alarm that the current overreliance on intentional release may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.
 
-# Maintext
+# Significance
+
+Intentional release of captive-bred individuals is a common practice for conservation and natural resource management.
+However, we know little about its potential consequences for the whole ecological community.
+Here, we show that intentional release undermines community stability with little demographic benefit to the enhanced species.
+Theory and data agreed that intentional release destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species.
+The effect size of intentional release was striking in its magnitude, doubling temporal fluctuations of enhanced communities compared to those with no intentional release.
+Our findings point to major limitations of intentional release as a primary tool for biodiversity conservation and sustainability.
+
+**Key words:** coexistence theory, competition, resilience, ecological modeling, fishery
+
+# Introduction
 
@@
 The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].
+
+# Results and Discussion
 

### 2022-07-12 rmd/ppt_test.Rmd
add: deterministic model

---
date: "`r Sys.Date()`"
author: "Your Name"
title: "Untitled"
output: 
  officedown::rpptx_document:
    reference_doc: alison-template.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.cap = TRUE)
library(officedown)
library(ggplot2)
library(rvg)
```

## Table

```{r layout='Two Content', ph=officer::ph_location_left()}
head(cars)
```

```{r layout='Two Content', ph=officer::ph_location_right()}
head(iris)
```

## Slide with Plot

```{r plot1}
dml(plot(pressure))
```

## Slide with ggplot

```{r layout='Title and Content', ph=officer::ph_location_type(type="body")}
mygg <- ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_point()
dml(ggobj = mygg)
```

## Slide with ggplot

```{r ph=officer::ph_location_fullsize()}
mygg <- ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_point()
dml(ggobj = mygg)
```

## ggplot in left column

```{r ph=officer::ph_location_left()}
mygg <- ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_point()
dml(ggobj = mygg)
```

## ggplot in right column

- Some
- Bullets

```{r ph=officer::ph_location_right()}
mygg <- ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_point()
dml(ggobj = mygg)
```

## ggplot in both columns

```{r ph=officer::ph_location_left()}
dml(ggobj = mygg)
```

```{r ph=officer::ph_location_right()}
dml(ggobj = mygg)
```

## custom plot locations

```{r ph=officer::ph_location(width = 2, height = 2, left = 2, top = 2)}
dml(plot(pressure))
```

```{r ph=officer::ph_location(width = 3, height = 3, left = 4, top = 4)}
dml(plot(pressure))
```

## Non-editable plot

```{r}
dml(plot(pressure), editable = FALSE)
```

### 2022-07-12 code/figure_theory_2sp.R

@@ -1,0 +1,54 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+
+pacman::p_load(here,
+               cdyns,
+               tidyverse,
+               foreach)
+
+df_sim <- readRDS(here::here("result/result_ricker_2sp.rds"))
+
+# plot --------------------------------------------------------------------
+
+df_sim %>% 
+  mutate(cv = sd_density / mean_density) %>% 
+  pivot_longer(cols = c(mean_density, sd_density),
+               names_to = "metric",
+               values_to = "value") %>% 
+  filter(r1 %in% unique(r1)[c(5, 15)],
+         k %in% unique(k)[c(5, 15)],
+         alpha == 0.5,
+         phi == 0.5,
+         sd_env == 0,
+         status == "all") %>% 
+  ggplot(aes(x = stock,
+             y = value,
+             color = metric)) +
+  geom_line(alpha = 0.8) +
+  facet_wrap(facets = ~r1 + k,
+             scales = "free_y")
+  
+
+df_sim %>% 
+  mutate(cv = sd_density / mean_density) %>% 
+  pivot_longer(cols = c(mean_density,
+                        sd_density,
+                        cv),
+               names_to = "metric",
+               values_to = "value") %>%
+  filter(status == "all",
+         sd_env == 0) %>% 
+  group_by(r1, k, alpha, phi, metric) %>% 
+  mutate(rho = cor(x = value,
+                   y = stock,
+                   method = "spearman")) %>% 
+  ggplot(aes(x = r1,
+             y = k,
+             fill = rho)) +
+  geom_raster(alpha = 0.8) +
+  facet_grid(rows = vars(alpha, phi),
+             cols = vars(metric)) +
+  MetBrewer::scale_fill_met_c("Hiroshige",
+                              direction = -1)

### 2022-07-12 code/run_simulation_analytical.R

@@ -1,0 +1,100 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls(all.names = TRUE))
+
+pacman::p_load(here,
+               cdyns,
+               tidyverse,
+               foreach,
+               doParallel,
+               doSNOW)
+
+n_core <- detectCores() - 1
+cl <- makeCluster(n_core)
+registerDoSNOW(cl)
+
+# set parameters ----------------------------------------------------------
+
+df_param <- expand.grid(n_timestep = 1000,
+                        n_warmup = 0,
+                        n_burnin = 100,
+                        n_species = 2,
+                        k = seq(50, 500, length = 20),
+                        r_type = "constant",
+                        r1 = seq(0.5, 3.5, length = 20),
+                        sd_env = c(0, 0.5),
+                        phi = c(0.5, 1),
+                        int_type = "constant",
+                        alpha = c(0.1, 0.5),
+                        model = "ricker",
+                        seed = 50,
+                        seed_interval = 0) %>% 
+  mutate(param_id = seq_len(nrow(.)))
+
+n_rep <- 100
+stock <- seq(0, 500, length = n_rep)
+
+# run simulation ----------------------------------------------------------
+
+pb <- txtProgressBar(max = nrow(df_param), style = 3)
+fun_progress <- function(n) setTxtProgressBar(pb, n)
+opts <- list(progress = fun_progress)
+
+result <- foreach(x = iter(df_param, by = 'row'),
+                  .combine = "bind_rows",
+                  .packages = c("foreach",
+                                "dplyr",
+                                "cdyns"),
+                  .options.snow = opts) %dopar% {
+                    
+                    df_set <- foreach(j = seq_len(n_rep),
+                                      .combine = "bind_rows") %do% {
+                                        
+                                        dyn <- cdynsim(n_timestep = x$n_timestep,
+                                                       n_warmup = x$n_warmup,
+                                                       n_burnin = x$n_burnin,
+                                                       n_species = x$n_species,
+                                                       k = x$k,
+                                                       r_type = x$r_type,
+                                                       r = x$r1,
+                                                       sd_env = x$sd_env,
+                                                       stock = stock[j],
+                                                       phi = x$phi,
+                                                       int_type = x$int_type,
+                                                       alpha = x$alpha,
+                                                       model = x$model,
+                                                       seed = x$seed)
+                                        
+                                        dyn_summary <- dyn$df_dyn %>% 
[…]

### 2022-09-14 code/data_fmt_analysis.R
Squashed commit of the following:
commit c274913bbbf475b2379bfd5ff5714134b1c4d743
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Sep 14 12:52:06 2022 -0400

    edit: rmd misc

commit b83fa58b0ac121cf4f89fff102048b2ff07a3b1e
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:49 2022 -0400

    Update mcmc_trace_reg.pdf

commit 184921982330ea83d449b2fe44159659f9c52210
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:45 2022 -0400

    edit: misc

commit aaac7131a165551933b99ae948f54d710a673206
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:32 2022 -0

@@ -16,41 +16,30 @@ df_sp <- df_selected %>%
   group_by(river, site, site_id) %>% 
   summarize(n_species = n_distinct(taxon),
             n_species_unstock = n_distinct(taxon[.data$taxon != "Oncorhynchus_masou_masou"])) %>% 
-  ungroup() %>% 
-  mutate(scl_n_species = c(scale(n_species)),
-         scl_n_species_unstock = c(scale(n_species_unstock)))
+  ungroup()
 
 ## df for environmental covariates
 df_env <- read_csv(here::here("data_fmt/data_env_fmt.csv")) %>% 
   rename(wsd_area = area) %>% 
   mutate(site_id = paste0(river, site)) %>% 
-  filter(site_id %in% site_selected) %>% 
-  mutate(scl_wsd_area = c(scale(wsd_area)),
-         scl_ppt = c(scale(ppt)),
-         scl_temp = c(scale(temp)),
-         scl_forest = c(scale(frac_forest)))
+  filter(site_id %in% site_selected)
 
 ## df for ocean environments
 df_ocean <- read_csv(here::here("data_fmt/data_ocean_fmt.csv")) %>% 
-  filter(river %in% river_id) %>% 
-  mutate(scl_chr_a = c(scale(chr_a)),
-         scl_sst = c(scale(sst)))
+  filter(river %in% river_id)
 
 ## df for stock data
 source(here::here("code/data_fmt_stock.R"))
 
-## group name
-group <- c("all", "masu", "other")
 
 # ssm data ----------------------------------------------------------------
 
 df_ssm <- readRDS(file = here::here("data_fmt/data_joint3.rds")) %>% 
-  bind_rows() %>% 
   rename(median = '50%',
          high = '97.5%',
          low = '2.5%') %>% 
   filter(str_detect(param_name, "log_d")) %>% 
-  group_by(river, site, site_id, group) %>%
+  group_by(river, site, site_id, site_id_numeric, group) %>%
   summarize(mu = mean(exp(median)),
             sigma = sd(exp(median)),
             cv = sigma / mu) %>% 

### 2022-09-14 code/figure_obs_stock.R

@@ -7,60 +7,107 @@ source(here::here("code/library.R"))
 # data --------------------------------------------------------------------
 
 ## raw data for cv, mean, sd
-source(here::here("code/data_fmt_analysis.R"))
+suppressMessages(source(here::here("code/data_fmt_analysis.R")))
 
 df_m <- df_ssm %>%
   filter(!(group != "all" & response == "cv")) %>%
   filter(!(group != "all" & response == "n_species")) %>%
-  mutate(response = case_when(response == "n_species" ~ "Species~richness",
-                              response == "cv" ~ "CV~sigma/mu",
-                              response == "mu" ~ "Mean~mu~(ind.~m^-2)",
-                              response == "sigma" ~ "SD~sigma~(ind.~m^-2)"),
-         group_id = case_when(group == "all" ~ "a",
-                              group == "masu" ~ "b",
-                              group == "other" ~ "c")) %>% 
-  mutate(response = factor(response,
-                           levels = c("CV~sigma/mu",
-                                      "Species~richness",
-                                      "Mean~mu~(ind.~m^-2)",
-                                      "SD~sigma~(ind.~m^-2)")))
+  mutate(group = factor(group),
+         response = ifelse(response == "n_species",
+                           "species_richness",
+                           response),
+         response = fct_relevel(response, "cv", "species_richness"))
 
-## parameter estimates
-file_name <- list.files(path = here::here("result"),
-                        full.names = TRUE,
-                        pattern = "reg_all|reg_masu|reg_other")
+## regression data
+df_reg <- list.files(path = here::here("result"),
+                     full.names = TRUE,
+                     pattern = "summary_reg") %>% 
+  readRDS() %>% 
+  mutate(y = response)
 
-df_beta <- lapply(file_name, 
-                  FUN = function(x) {
-                    mutate(readRDS(x),
-                           group = str_extract(x, "all|masu|other"))
-                  }) %>%
-  bind_rows() %>%
-  filter(!(group != "all" & response == "cv")) %>%
-  mutate(response = case_when(response == "richness" ~ "Species~richness",
-                              response == "cv" ~ "CV~sigma/mu",
-                              response == "mu" ~ "Mean~mu~(ind.~m^-2)",
[…]

### 2022-09-14 code/figure_set_theme.R

@@ -22,3 +22,10 @@ plt_theme <- theme_bw() + theme(
 )
 
 theme_set(plt_theme)
+
+# color setup
+lum <- 85
+con <- 50
+hs <- c(30, 140, 250)
+pt_size <- 0.8
+

### 2022-09-14 code/figure_test.R

@@ -1,0 +1,31 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+source(here::here("code/library.R"))
+
+# data --------------------------------------------------------------------
+
+## raw data for cv, mean, sd
+source(here::here("code/data_fmt_analysis.R"))
+
+df_m <- df_ssm %>%
+  mutate(river_id = as.numeric(factor(river))) %>% 
+  group_by(river) %>% 
+  mutate(site0 = as.numeric(factor(site)),
+         p_id = as.numeric(factor(response, levels = c("sigma", "mu")))) %>% 
+  ungroup() %>% 
+  relocate(river, river_id, site, site0, site_id)
+
+# plot --------------------------------------------------------------------
+
+df_m %>% 
+  ggplot(aes(x = mean_stock,
+             y = value,
+             color = river)) +
+  geom_point(alpha = 0.5) +
+  facet_grid(cols = vars(group),
+             rows = vars(response),
+             scales = "free_y") +
+  scale_y_continuous(trans = "log10") +
+  theme_bw()

### 2022-09-14 code/figure_theory.R

@@ -51,23 +51,23 @@ g_theory <- df0 %>%
              x = stock,
              color = group_id,
              fill = group_id)) +
-  geom_point(data = filter(df0, status == "enhanced"),
-             size = 0.75,
-             color = hue_pal(h.start = 140, l = 85, c = 30)(1)) +
-  geom_point(data = filter(df0, status == "unenhanced"),
-             size = 0.75,
-             color = hue_pal(h.start = 250, l = 85, c = 50)(1)) +
-  geom_point(data = filter(df0, status == "all"),
-             size = 0.75,
-             color = hue_pal(h.start = 30, l = 85, c = 50)(1)) +
+  geom_point(data = . %>% filter(status == "enhanced"),
+             size = pt_size,
+             color = hue_pal(h.start = hs[2], l = lum, c = con)(1)) +
+  geom_point(data = . %>% filter(status == "unenhanced"),
+             size = pt_size,
+             color = hue_pal(h.start = hs[3], l = lum, c = con)(1)) +
+  geom_point(data = . %>% filter(status == "all"),
+             size = pt_size,
+             color = hue_pal(h.start = hs[1], l = lum, c = con)(1)) +
   geom_point(data = filter(df0, status == "dummy"),
              color = NA) +
   geom_smooth(size= 0.5,
               method = "loess") +
-  scale_color_hue(h = c(30, 250),
+  scale_color_hue(h = c(hs[1], hs[3]),
                   l = 70,
                   labels = c("Whole", "Enhanced", "Unenhanced")) +
-  scale_fill_hue(h = c(30, 250),
+  scale_fill_hue(h = c(hs[1], hs[3]),
                  l = 70) +
   labs(x = "Number of releases (individuals)",
        y = "Value") +

### 2022-09-14 code/figure_theory_obs.R

@@ -7,9 +7,9 @@ pacman::p_load(tidyverse,
 
 # data --------------------------------------------------------------------
 
-source(here::here("code/figure_theory.R"))
-source(here::here("code/figure_obs_stock.R"))
-source(here::here("code/figure_map.R"))
+suppressMessages(source(here::here("code/figure_theory.R")))
+suppressMessages(source(here::here("code/figure_obs_stock.R")))
+suppressMessages(source(here::here("code/figure_map.R")))
 
 layout <- "
 ABC

### 2022-09-14 code/model_joint.R

@@ -63,7 +63,7 @@ model {
   tau0 <- 1 / 50
   tau100 <- 100
   scale0 <- 2.5
-  df0 <- 3
+  df0 <- 6
   v_scale0 <- rep(scale0, 2)
   
   ## local parameters ####
@@ -83,10 +83,8 @@ model {
   for (i in 1:Nsite) {
     for (g in 1:Ng) {
       for(t in St_year[i]:(St_year[i] + Q - 1)) {
-        log_d[i, t, g] ~ dt(log_d1[i, g], tau_t1[i, g], 5)
+        log_d[i, t, g] ~ dt(-2, 0.5, df0)
       }
-      
-      tau_t1[i, g] <- pow(log_max_d[i, g] - log_d1[i, g], -2)
     }
   }
   
@@ -121,12 +119,6 @@ data {
   ## stock data conversion
   for (n in 1:Nsample_stock) {
     stock[Site_stock[n], Year_stock[n]] <- Stock[n]
-  }
-  
-  ## initial population size
-  for (n in 1:N_t1) {
-    log_d1[Site_t1[n], Group_t1[n]] <- Log_d1[n]
-    log_max_d[Site_t1[n], Group_t1[n]] <- Log_max_d[n]
   }
   
 }

### 2022-09-14 code/model_reg.R

@@ -1,0 +1,143 @@
+model {
+  
+  # likelihood --------------------------------------------------------------
+  
+  for (i in 1:Nsite) {
+    ## regression for sigma (p = 1) and mu (p = 2)
+    for (g in 1:Ngroup) {
+      ## site-level
+      log_y[i, g, 1:(Np - 1)] ~ dmnorm(mu[i, g, ], TAU[g, , ])
+      
+      for (p in 1:(Np - 1)) {
+        mu[i, g, p] <-
+          (a[1, g, p] + r[River[i], g, p]) +
+          a[2, g, p] * scl_ef_stock[i] +
+          a[3, g, p] * scl_log_wsd_area[i] +
+          a[4, g, p] * scl_temp[i] +
+          a[5, g, p] * scl_ppt[i] +
+          a[6, g, p] * scl_forest[i]
+      }
+    }
+    
+    ## regression for species richness (p = 3)
+    ## group for "all" (g = 1)
+    y[i, 1, 3] ~ dpois(lambda[i])
+    log(lambda[i]) <- 
+      (a[1, 1, 3] + r[River[i], 1, 3]) +
+      a[2, 1, 3] * scl_ef_stock[i] +
+      a[3, 1, 3] * scl_log_wsd_area[i] +
+      a[4, 1, 3] * scl_temp[i] +
+      a[5, 1, 3] * scl_ppt[i] +
+      a[6, 1, 3] * scl_forest[i] +
+      eps[i]
+    
+    eps[i] ~ dnorm(0, tau_eps)
+        
+    ## effective release    
+    scl_ef_stock[i] <- (ef_stock[i] - mean(ef_stock[])) / sd(ef_stock[])
+    ef_stock[i] <- w[River[i], Reach[i]] * Stock[River[i]]
+  }
+    
+  for (j in 1:Nriver) {
+    ## weight factor
+    w[j, 1:(Ngs[j] + 1)] ~ ddirch(alpha[1:(Ngs[j] + 1)])
+    
+    for (g in 1:Ngroup) {
+      for (p in 1:Np) {
+        ## watershed-level random effect
+        r[j, g, p] ~ dnorm(theta[j, g, p], tau_r[g, p])
+        theta[j, g, p] <- b[1, g, p] * scl_chr_a[j]
+      }
+    }
+  }
+  
+  for (g in 1:Ngroup) {
[…]

### 2022-09-14 code/model_reg_cv.R

@@ -1,77 +1,0 @@
-model {
-  
-  scale <- 2.5
-  df <- 3
-  ninfo <- 0.1
-  
-  # prior -------------------------------------------------------------------
-  
-  tau ~ dscaled.gamma(scale, df)
-  sigma <- sqrt(1 / tau)
-  
-  tau_r ~ dscaled.gamma(scale, df)
-  sigma_r <- sqrt(1 / tau_r)
-  
-  for(i in 1:4) {
-    a[i] ~ dnorm(0, ninfo)
-  }
-  
-  for(i in 1:3) {
-    b[i] ~ dnorm(0, ninfo)
-  }
-  
-  
-  # likelihood --------------------------------------------------------------
-  
-  ## site-level
-  for(i in 1:Nsite) {
-    
-    log_y[i] ~ dnorm(mu[i], tau)
-    
-    mu[i] <-
-      a0[River[i]] + 
-      a[1] * scl_log_wsd_area[i] +
-      a[2] * scl_temp[i] +
-      a[3] * scl_ppt[i] +
-      a[4] * scl_forest[i]
-    
-  }
-  
-  ## watershed-level
-  for(j in 1:Nriver) {
-    
-    a0[j] ~ dnorm(theta[j], tau_r)
-    
-    theta[j] <- 
-      b[1] +
-      b[2] * scl_stock[j] +
-      b[3] * scl_chr_a[j]
-    
-  }
-  
-  b_raw[1] <- b[1] - b_raw[2] * mean(Stock[])
-  b_raw[2] <- b[2] / sd(Stock[])
-  
-}
-
-data {
-  
-  # standardization ---------------------------------------------------------
-  
-  for(i in 1:Nsite) {
-    log_y[i] <- log(Y[i])
-    log_wsd_area[i] <- log(Wsd_area[i])
-    
-    scl_log_wsd_area[i] <- (log_wsd_area[i] - mean(log_wsd_area[])) / sd(log_wsd_area[])
-    scl_temp[i] <- (Temp[i] - mean(Temp[])) / sd(Temp[])
-    scl_ppt[i] <- (Ppt[i] - mean(Ppt[])) / sd(Ppt[])
-    scl_forest[i] <- (Forest[i] - mean(Forest[])) / sd(Forest[])
-  }
-  
-  for(j in 1:Nriver) {
[…]

### 2022-09-14 code/model_reg_rich.R

@@ -1,79 +1,0 @@
-model {
-  
-  scale <- 2.5
-  df <- 3
-  ninfo <- 0.1
-  
-  # prior -------------------------------------------------------------------
-  
-  tau ~ dscaled.gamma(scale, df)
-  sigma <- sqrt(1 / tau)
-  
-  tau_r ~ dscaled.gamma(scale, df)
-  sigma_r <- sqrt(1 / tau_r)
-  
-  for(i in 1:4) {
-    a[i] ~ dnorm(0, ninfo)
-  }
-  
-  for(i in 1:3) {
-    b[i] ~ dnorm(0, ninfo)
-  }
-  
-  
-  # likelihood --------------------------------------------------------------
-  
-  ## site-level
-  for(i in 1:Nsite) {
-    
-    Y[i] ~ dpois(lambda[i])
-    
-    log(lambda[i]) <-
-      a0[River[i]] + 
-      a[1] * scl_log_wsd_area[i] +
-      a[2] * scl_temp[i] +
-      a[3] * scl_ppt[i] +
-      a[4] * scl_forest[i] +
-      eps[i]
-    
-    eps[i] ~ dnorm(0, tau)
-    
-  }
-  
-  ## watershed-level
-  for(j in 1:Nriver) {
-    
-    a0[j] ~ dnorm(theta[j], tau_r)
-    
-    theta[j] <- 
-      b[1] +
-      b[2] * scl_stock[j] +
-      b[3] * scl_chr_a[j]
-    
-  }
-  
-  b_raw[1] <- b[1] - b_raw[2] * mean(Stock[])
-  b_raw[2] <- b[2] / sd(Stock[])
-  
-}
-
-data {
-  
-  # standardization ---------------------------------------------------------
-  
-  for(i in 1:Nsite) {
-    log_wsd_area[i] <- log(Wsd_area[i])
-    
-    scl_log_wsd_area[i] <- (log_wsd_area[i] - mean(log_wsd_area[])) / sd(log_wsd_area[])
-    scl_temp[i] <- (Temp[i] - mean(Temp[])) / sd(Temp[])
-    scl_ppt[i] <- (Ppt[i] - mean(Ppt[])) / sd(Ppt[])
-    scl_forest[i] <- (Forest[i] - mean(Forest[])) / sd(Forest[])
-  }
-  
-  for(j in 1:Nriver) {
[…]

### 2022-09-14 code/run_model_joint.R

@@ -10,7 +10,7 @@ source(here::here("code/function_set.R"))
 
 ## fish data ####
 ## "data_fmt_stock.R" calls `df_fish` through "data_fmt_fishdata.R"
-source("code/data_fmt_stock.R")
+suppressMessages(source("code/data_fmt_stock.R"))
 Order <- 3
 model <- "joint"
 
@@ -58,7 +58,8 @@ df_subset <- df_fish %>%
 df_t1 <- df_subset %>%
   group_by(site_id_numeric, group_numeric) %>%
   summarize(log_mu_d = log(mean(density)),
-            log_max_d = log(max(density))) %>%
+            log_max_d = log(max(density)),
+            log_range = log_max_d - log_mu_d) %>%
   ungroup()
 
 d_jags <- list(N = df_subset$abundance,
@@ -80,14 +81,7 @@ d_jags <- list(N = df_subset$abundance,
                Nsample_stock = nrow(df_fry),
                
                # order of auto-regressive process
-               Q = Order,
-
-               # max for initial densities
-               N_t1 = nrow(df_t1),
-               Log_d1 = df_t1$log_mu_d,
-               Log_max_d = df_t1$log_max_d,
-               Site_t1 = df_t1$site_id_numeric,
-               Group_t1 = df_t1$group_numeric)
+               Q = Order)
 
 ## run jags ####
 post <- run.jags(m$model,

### 2022-09-14 code/run_model_reg.R

@@ -1,0 +1,181 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+source(here::here("code/library.R"))
+
+
+# data --------------------------------------------------------------------
+
+source("code/data_fmt_analysis.R")
+
+df_m <- df_ssm %>%
+  filter(response %in% c("mu", "sigma", "n_species"),
+         !(response == "n_species" & group != "all")) %>% 
+  mutate(river_id = as.numeric(factor(river))) %>% 
+  group_by(river) %>% 
+  mutate(site0 = as.numeric(factor(site)),
+         p_id = as.numeric(factor(response,
+                                  levels = c("sigma", "mu", "n_species"))),
+         group_id = as.numeric(factor(group))) %>% 
+  ungroup() %>% 
+  relocate(river, river_id, site, site0, site_id, group, group_id)
+
+df_site <- df_m %>%
+  distinct(site_id_numeric,
+           river,
+           river_id,
+           site0,
+           wsd_area,
+           temp,
+           ppt,
+           frac_forest) %>% 
+  relocate(site_id_numeric, river, river_id) %>% 
+  arrange(site_id_numeric)
+
+df_river <- df_m %>% 
+  group_by(river, river_id) %>% 
+  summarize(stock = unique(mean_stock),
+            chr_a = unique(chr_a),
+            n_site = n_distinct(site_id))
+
+
+# jags setup --------------------------------------------------------------
+
+## parameters ####
+para <- c("a",
+          "b",
+          "sigma",
+          "sigma_r",
+          "beta_raw",
+          "RHO",
+          "w",
+          "ef_stock")
+
+## model file ####
+m <- runjags::read.jagsfile("code/model_reg.R")
+
+## mcmc setup ####
+n_ad <- 1000
+n_iter <- 1.0E+4
+n_thin <- max(3, ceiling(n_iter / 500))
+n_burn <- ceiling(max(10, n_iter/2))
+n_sample <- ceiling(n_iter / n_thin)
+n_chain <- 4
+
+inits <- replicate(n_chain,
+                   list(.RNG.name = "base::Mersenne-Twister",
+                        .RNG.seed = NA),
+                   simplify = FALSE)
+
+for (j in 1:n_chain) inits[[j]]$.RNG.seed <- (j - 1) * 10 + 1
+
+
+# jags --------------------------------------------------------------------
+
+d_jags <- list(Y = df_m$value,
+               P = df_m$p_id,
[…]

### 2022-09-14 code/run_model_reg01_rich.R

@@ -1,116 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-rm(list = ls())
-source(here::here("code/library.R"))
-
-
-# jags setup --------------------------------------------------------------
-
-source("code/data_fmt_analysis.R")
-df_m <- df_ssm %>% 
-  filter(group == "all",
-         response == "n_species")
-
-## parameters ####
-para <- c("b",
-          "a",
-          "sigma",
-          "sigma_r",
-          "b_raw")
-
-## model file ####
-m <- runjags::read.jagsfile("code/model_reg_rich.R")
-
-## mcmc setup ####
-n_ad <- 100
-n_iter <- 1.0E+4
-n_thin <- max(3, ceiling(n_iter / 500))
-n_burn <- ceiling(max(10, n_iter/2))
-n_sample <- ceiling(n_iter / n_thin)
-
-inits <- replicate(3,
-                   list(.RNG.name = "base::Mersenne-Twister",
-                        .RNG.seed = NA),
-                   simplify = FALSE)
-
-for (j in 1:3) inits[[j]]$.RNG.seed <- (j - 1) * 10 + 1
-
-
-# jags --------------------------------------------------------------------
-
-df_site <- df_m %>%
-  mutate(river_id = as.numeric(factor(river)))
-
-df_river <- df_m %>% 
-  mutate(river_id = as.numeric(factor(river))) %>% 
-  group_by(river, river_id) %>% 
-  summarize(stock = unique(mean_stock),
-            chr_a = unique(chr_a))
-
-d_jags <- list(Y = df_site$value,
-               Wsd_area = df_site$wsd_area,
-               Temp = df_site$temp,
-               Ppt = df_site$ppt,
-               Forest = df_site$frac_forest,
-               River = df_site$river_id,
-               
-               Stock = df_river$stock,
-               Chr_a = df_river$chr_a,
-               
-               Nsite = nrow(df_site),
-               Nriver = nrow(df_river))
-
-
-## run jags ####
-post <- runjags::run.jags(m$model,
-                          monitor = para,
-                          data = d_jags,
-                          n.chains = 3,
-                          inits = inits,
-                          method = "parallel",
-                          burnin = n_burn,
-                          sample = n_sample,
-                          adapt = n_ad,
-                          thin = n_thin,
-                          n.sims = 3,
-                          module = "glm")
-
[…]

### 2022-09-14 code/run_model_reg02_all.R

@@ -1,132 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-rm(list = ls())
-source(here::here("code/library.R"))
-
-
-# jags setup --------------------------------------------------------------
-
-source("code/data_fmt_analysis.R")
-df_m <- df_ssm %>% 
-  filter(group == "all")
-
-## parameters ####
-para <- c("b",
-          "a",
-          "sigma",
-          "sigma_r",
-          "b_raw")
-
-## model file ####
-m <- runjags::read.jagsfile("code/model_reg_cv.R")
-
-## mcmc setup ####
-n_ad <- 100
-n_iter <- 1.0E+4
-n_thin <- max(3, ceiling(n_iter / 500))
-n_burn <- ceiling(max(10, n_iter/2))
-n_sample <- ceiling(n_iter / n_thin)
-
-inits <- replicate(3,
-                   list(.RNG.name = "base::Mersenne-Twister",
-                        .RNG.seed = NA),
-                   simplify = FALSE)
-
-for (j in 1:3) inits[[j]]$.RNG.seed <- (j - 1) * 10 + 1
-
-
-# jags --------------------------------------------------------------------
-
-variable <- c("cv", "mu", "sigma")
-mcmc_file <- paste0("mcmc_all_", variable) %>%
-  paste0("result/", ., ".rds")
-
-out <- foreach(i = seq_len(length(variable)),
-               .combine = bind_rows) %do% {
-  
-  ## data format ####
-  df_site <- df_m %>%
-    dplyr::filter(response == variable[i]) %>% 
-    mutate(river_id = as.numeric(factor(river)))
-                 
-  df_river <- df_m %>% 
-    mutate(river_id = as.numeric(factor(river))) %>% 
-    group_by(river, river_id) %>% 
-    summarize(stock = unique(mean_stock),
-              chr_a = unique(chr_a))
-                 
-  d_jags <- list(Y = df_site$value,
-                 Wsd_area = df_site$wsd_area,
-                 Temp = df_site$temp,
-                 Ppt = df_site$ppt,
-                 Forest = df_site$frac_forest,
-                 River = df_site$river_id,
-                 
-                 Stock = df_river$stock,
-                 Chr_a = df_river$chr_a,
-                 
-                 Nsite = nrow(df_site),
-                 Nriver = nrow(df_river))
-                 
-  ## run jags ####
-  post <- runjags::run.jags(m$model,
-                            monitor = para,
-                            data = d_jags,
-                            n.chains = 3,
[…]

### 2022-09-14 code/run_model_reg03_masu.R

@@ -1,127 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-rm(list = ls())
-source(here::here("code/library.R"))
-
-
-# jags setup --------------------------------------------------------------
-
-source("code/data_fmt_analysis.R")
-df_m <- df_ssm %>% 
-  filter(group == "masu_salmon")
-
-## parameters ####
-para <- c("b",
-          "a",
-          "sigma",
-          "sigma_r",
-          "b_raw")
-
-## model file ####
-m <- runjags::read.jagsfile("code/model_reg_cv.R")
-
-## mcmc setup ####
-n_ad <- 100
-n_iter <- 1.0E+4
-n_thin <- max(3, ceiling(n_iter / 500))
-n_burn <- ceiling(max(10, n_iter/2))
-n_sample <- ceiling(n_iter / n_thin)
-
-inits <- replicate(3,
-                   list(.RNG.name = "base::Mersenne-Twister",
-                        .RNG.seed = NA),
-                   simplify = FALSE)
-
-for (j in 1:3) inits[[j]]$.RNG.seed <- (j - 1) * 10 + 1
-
-
-# jags --------------------------------------------------------------------
-
-variable <- c("cv", "mu", "sigma")
-mcmc_file <- paste0("mcmc_masu_", variable) %>%
-  paste0("result/", ., ".rds")
-
-
-out <- foreach(i = seq_len(length(variable)),
-               .combine = bind_rows) %do% {
-
-  ## data format ####
-  df_site <- df_m %>%
-    dplyr::filter(response == variable[i]) %>% 
-    mutate(river_id = as.numeric(factor(river)))
-  
-  df_river <- df_m %>% 
-    mutate(river_id = as.numeric(factor(river))) %>% 
-    group_by(river, river_id) %>% 
-    summarize(stock = unique(mean_stock),
-              chr_a = unique(chr_a))
-  
-  d_jags <- list(Y = df_site$value,
-                 Wsd_area = df_site$wsd_area,
-                 Temp = df_site$temp,
-                 Ppt = df_site$ppt,
-                 Forest = df_site$frac_forest,
-                 River = df_site$river_id,
-                 
-                 Stock = df_river$stock,
-                 Chr_a = df_river$chr_a,
-                 
-                 Nsite = nrow(df_site),
-                 Nriver = nrow(df_river))
-                 
-  ## run jags ####
-  post <- runjags::run.jags(m$model,
-                            monitor = para,
-                            data = d_jags,
-                            n.chains = 3,
[…]

### 2022-09-14 code/run_model_reg04_other.R

@@ -1,127 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-rm(list = ls())
-source(here::here("code/library.R"))
-
-
-# jags setup --------------------------------------------------------------
-
-source("code/data_fmt_analysis.R")
-df_m <- df_ssm %>% 
-  filter(group == "other")
-
-## parameters ####
-para <- c("b",
-          "a",
-          "sigma",
-          "sigma_r",
-          "b_raw")
-
-## model file ####
-m <- runjags::read.jagsfile("code/model_reg_cv.R")
-
-## mcmc setup ####
-n_ad <- 100
-n_iter <- 1.0E+4
-n_thin <- max(3, ceiling(n_iter / 500))
-n_burn <- ceiling(max(10, n_iter/2))
-n_sample <- ceiling(n_iter / n_thin)
-
-inits <- replicate(3,
-                   list(.RNG.name = "base::Mersenne-Twister",
-                        .RNG.seed = NA),
-                   simplify = FALSE)
-
-for (j in 1:3) inits[[j]]$.RNG.seed <- (j - 1) * 10 + 1
-
-
-# jags --------------------------------------------------------------------
-
-variable <- c("cv", "mu", "sigma")
-mcmc_file <- paste0("mcmc_other_", variable) %>%
-  paste0("result/", ., ".rds")
-
-out <- foreach(i = seq_len(length(variable)),
-               .combine = bind_rows) %do% {
-                 
-  ## data format ####
-  df_site <- df_m %>%
-    dplyr::filter(response == variable[i]) %>% 
-    mutate(river_id = as.numeric(factor(river)))
-  
-  df_river <- df_m %>% 
-    mutate(river_id = as.numeric(factor(river))) %>% 
-    group_by(river, river_id) %>% 
-    summarize(stock = unique(mean_stock),
-              chr_a = unique(chr_a))
-  
-  d_jags <- list(Y = df_site$value,
-                 Wsd_area = df_site$wsd_area,
-                 Temp = df_site$temp,
-                 Ppt = df_site$ppt,
-                 Forest = df_site$frac_forest,
-                 River = df_site$river_id,
-                 
-                 Stock = df_river$stock,
-                 Chr_a = df_river$chr_a,
-                 
-                 Nsite = nrow(df_site),
-                 Nriver = nrow(df_river))
-                 
-                 
-  ## run jags ####
-  post <- runjags::run.jags(m$model,
-                            monitor = para,
-                            data = d_jags,
-                            n.chains = 3,
[…]

### 2022-09-14 code/run_regression.R

@@ -1,14 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-rm(list = ls())
-source(here::here("code/library.R"))
-
-
-# run models --------------------------------------------------------------
-
-(run_model <- list.files(path = here::here("code"),
-                        full.names = TRUE,
-                        pattern = "run_model_reg"))
-
-lapply(run_model, source)

### 2022-09-21 rmd/supporting_info.Rmd
edit: manuscript
Squashed commit of the following:
commit c274913bbbf475b2379bfd5ff5714134b1c4d743
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Sep 14 12:52:06 2022 -0400

    edit: rmd misc

commit b83fa58b0ac121cf4f89fff102048b2ff07a3b1e
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:49 2022 -0400

    Update mcmc_trace_reg.pdf

commit 184921982330ea83d449b2fe44159659f9c52210
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:45 2022 -0400

    edit: misc

commit aaac7131a165551933b99ae948f54d710a673206
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17

@@
 knit: (function(inputFile, encoding) {
-        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
+        rmarkdown::render(inputFile,
+                          encoding = encoding, 
+                          output_dir = "document_output")
       })
 header-includes:
-  \pagenumbering{gobble}
-  \usepackage{amsmath}
+  - \pagenumbering{gobble}
+  - \usepackage{amsmath}
 bibliography: reference.bib
-csl: nature.csl
+csl: https://www.zotero.org/styles/pnas
 ---
@@
 
-# setup
-pacman::p_load(knitr,
-               tidyverse)
+# setup ####
+source(here::here("code/library.R"))
+source(here::here("code/set_functions.R"))
 
@@
 
-op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x)
+# theory ####
+cols <- c(
+  "n_species",
+  "k",
+  "r_type",
+  "r1",
+  "r_min",
+  "r_max",
+  "sd_env",
+  "phi",
+  "int_type",
+  "alpha",
+  "model",
+  "seed")
 
-# theory ####
-load(here::here("result/result_ricker.RData"))
-
-n_sim <- sim_result %>% 
+sim_result <- list(readRDS(here::here("output/result_ricker_2sp.rds")),
+                   readRDS(here::here("output/result_ricker.rds"))) %>% 
+  lapply(FUN = function(x) {
+      n_sim <- x %>% 
         mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
@@
 
-param_set <- sim_result %>% 
-  distinct(n_species,
-           k,
-           r_type,
-           r1,
-           r_min,
-           r_max,
-           sd_env,
-           phi,
-           int_type,
-           alpha,
-           model,
-           seed)
+      param_set <- x %>% 
+        dplyr::select(which(colnames(x) %in% cols)) %>% 
+        distinct()
+
+      attr(param_set, "n_sim") <- n_sim
+      return(param_set)
+  })
 
@@
 source(here::here("code/data_fmt_fishdata.R"))
-source(here::here("code/data_fmt_analysis.R"))
+source(here::here("code/data_fmt_reg.R"))
 
@@
 
-filename <- list.files(path = here::here("result"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "reg")) %>% 
-  filter(!str_detect(string = .$value, pattern = "reg_rich")) %>% 
-  pull()
-
-df_beta <- lapply(filename, function(x) {
-  read_csv(here::here(x)) %>% 
-    filter(parameter == "b[2]")
-})
-names(df_beta) <- str_extract(filename, "all|masu|other")
-
 ## ssm estimate
-df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
+df_bp <- list.files(path = here::here("data_fmt"),
+                    full.names = T,
+                    pattern = "joint") %>% 
+  readRDS() %>% 
   filter(param == "bp_value") %>% 
-      select(mean) %>% 
-      mutate(group = str_extract(x, "all|masu|other"))
-  }) %>% 
-  bind_rows()
+  dplyr::select(mean)
 
 ## mcmc sample size
-df_mcmc_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      select(n_total_mcmc,
+df_mcmc_ssm <- list.files(path = here::here("data_fmt"),
+                    full.names = T,
+                    pattern = "joint") %>% 
+  readRDS() %>% 
+  ungroup() %>% 
+  dplyr::select(n_total_mcmc,
                 n_sample,
@@
   distinct()
-  }) %>% 
-  bind_rows()
 
-df_mcmc_reg <- list.files(path = here::here("result"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "reg_")) %>% 
-  filter(!str_detect(string = .$value, pattern = "rich")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      select(n_total_mcmc,
+df_mcmc_reg <- list.files(path = here::here("output"),
+                          full.names = T,
+                          pattern = "summary_reg") %>% 
+  readRDS() %>% 
+  dplyr::select(n_total_mcmc,
                 n_sample,
@@
   distinct()
-  }) %>% 
-  bind_rows()
 
@@
 
+### Model
+
 We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012].
@@
 \begin{align}
-N_{i,t+1} = N_{i,t}~exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
+N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\epsilon_{i,t})
 \end{align}
@@
 \begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\epsilon_{i,t})
 \end{align}
@@
 \begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\epsilon_{i,t})
 \end{align}
@@
 
-Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and intentional release (see **Supplementary text**).
-We identified five influential parameters (**Table S2-S4**), of which different values were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+### Model analysis
+
+First, we analyzed a two-species community to gain insights into the model behavior and to guide the N-species analysis.
+Specifically, we examined the release effect with $20$ parameter values of intrinsic population growth rate $r_i$ ($0.5$ to $3.5$ with an equal interval) and carrying capacity $K$ ($50$ to $500$ with an equal interval), resulting in $400$ parameter combinations.
+In an ordinary Ricker model, the chosen range of $r_i$ can generate stable equilibrium, damped oscillations, limit cycle, and chaos (XXX).
+For simplicity, we assumed $r_1 = r_2$.
+We crossed this parameter setup with environmental stochasticity ($\sigma = \{0, 0.75\}$) and competition strength ($\alpha = \{0.1, 0.5\}$) and generated $1600$ simulation scenarios ($400 \times 2 \times 2$).
+
+Under each simulation scenario, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` with $100$ values of release level $R$ ($0$ to $500$ with an equal interval).
+We initialized the community with populations of each species drawn from a Poisson distribution with a mean of $50$.
+We let species grow with no release for the first `r unique(sim_result$n_warmup)` time steps to allow them reach equilibrium without intentional release (initialization period).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective intentional release (burn-in period).
+We continued the simulation run with intentional release and saved the last `r unique(sim_result$n_timestep)` time steps, which were used to obtain the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
+
+We subsequently analyzed a whole community model with $10$ species using important parameter combinations identified in the two-species model: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+We confirmed that these parameters are influential in the ten-species community model via sensitivity analysis (**Table S2-S4**).
 Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).
-This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
+This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations.
 
-Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates).
-The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$.
-We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five.
-We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach equilibrium without intentional release (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective intentional release (burn-in period).
-We continued the simulation run with intentional release and saved the last `r unique(sim_result$n_timestep)` time steps.
-We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$).
-The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately.
+As with the two-species model, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` with $100$ values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
+Initial seed inidividuals of each species were drawn from a Poisson distribution with a mean of five.
+In this simulation, we repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to account for possible complex dynamics within a ten-species community (initialization period).
+The rest of simulation procedures is identical to the two-species model.
 We summarized values of simulation parameters in **Table S1**.

### 2022-09-21 code/table_stvy_analysis.R
Update table_stvy_analysis.R

@@ -2,13 +2,12 @@
 # setup -------------------------------------------------------------------
 
 rm(list = ls())
-pacman::p_load(tidyverse,
-               stargazer)
-
-load(here::here("output/result_stvy_analysis.RData"))
+source("code/library.R")
 
 
 # table -------------------------------------------------------------------
+
+fit_sense <- readRDS(here::here("output/result_stvy_analysis.rds"))
 
 table_stvy <- list(NULL)
 text_match <- c("_all", "_enhanced", "_unenhanced")

### 2022-09-21 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-Our goal is to compare temporal community dynamics across sites.
+**Community dynamics comparison.** Our goal is to compare temporal community dynamics across sites.
 However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
@@
 
-We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
+**Species interaction.** XXX
+
+**Model fitting.** We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
 We assigned weakly informative priors to parameters (**Table S6**).
@@
 source(here::here("code/table_param_set.R"))
-kable(df_param, format = "markdown")
+knitr::kable(df_param, format = "markdown")
 
@@
 
-kable(df_sp_list,
+knitr::kable(df_sp_list,
              format = "markdown")
-
 ```
@@
 
-kable(df_prior,
+knitr::kable(df_prior,
              format = "markdown")
@@
 
-kable(df_ssm,
+knitr::kable(df_ssm,
              align = c(rep("l", 3), "c"),
@@
 ## load figures
-source(here::here("code/figure_si_theory.R"))
+source(here::here("code/si_figure_theory.R"))
 
@@
 ## load figures
-source(here::here("code/figure_si_obs_dyns.R"))
+source(here::here("code/si_figure_obs_dyns.R"))
 j <- 6
@@
 
-source(here::here("code/figure_si_env.R"))
+source(here::here("code/si_figure_env.R"))
 
@@
 
-source(here::here("code/figure_si_cor.R"))
+source(here::here("code/si_figure_cor.R"))
 ```

### 2022-09-22 rmd/supporting_info.Rmd
edit: tables

@@
 
-sim_result <- list(readRDS(here::here("output/result_ricker_2sp.rds")),
-                   readRDS(here::here("output/result_ricker.rds"))) %>% 
+list_sim <- list(readRDS(here::here("output/result_ricker_2sp.rds")),
+                   readRDS(here::here("output/result_ricker.rds")))
+
+list_param <- list_sim %>% 
   lapply(FUN = function(x) {
@@
 For simplicity, we assumed $r_1 = r_2$.
-We crossed this parameter setup with environmental stochasticity ($\sigma = \{0, 0.75\}$) and competition strength ($\alpha = \{0.1, 0.5\}$) and generated $1600$ simulation scenarios ($400 \times 2 \times 2$).
+We crossed this parameter setup with environmental stochasticity ($\sigma =$ `r unique(list_param[[1]]$sd_env)`) and competition strength ($\alpha =$ `r unique(list_param[[1]]$alpha)`) and generated `r nrow(list_param[[1]])` simulation scenarios ($400 \times 2 \times 2$).
 
-Under each simulation scenario, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` with $100$ values of release level $R$ ($0$ to $500$ with an equal interval).
-We initialized the community with populations of each species drawn from a Poisson distribution with a mean of $50$.
-We let species grow with no release for the first `r unique(sim_result$n_warmup)` time steps to allow them reach equilibrium without intentional release (initialization period).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective intentional release (burn-in period).
-We continued the simulation run with intentional release and saved the last `r unique(sim_result$n_timestep)` time steps, which were used to obtain the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
+Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` time steps of community dynamics for $100$ values of release level $R$ ($0$ to $500$ with an equal interval).
+We initialized populations of each species drawn from a Poisson distribution with a mean of $50$ and let species grow with no release for the first `r unique(list_sim[[1]]$n_warmup)` time steps.
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(list_sim[[1]]$n_burnin)` time steps to reach new equilibrium with selective intentional release (burn-in period).
+We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` time steps, which were used to obtain the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
 
-We subsequently analyzed a whole community model with $10$ species using important parameter combinations identified in the two-species model: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`).
+We subsequently analyzed a whole community model with $10$ species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[1]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[1]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[1]]$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[1]]$phi)`).
 We confirmed that these parameters are influential in the ten-species community model via sensitivity analysis (**Table S2-S4**).
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`).
-This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations.
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[1]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[1]]$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(list_param[[1]]$sd_env)`).
+This simulation setup resulted in `r nrow(list_param[[1]])` sets of parameter combinations.
 
-As with the two-species model, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` with $100$ values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
+As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` time steps of `r max(list_sim[[2]]$n_rep)` with $100$ values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
 Initial seed inidividuals of each species were drawn from a Poisson distribution with a mean of five.
-In this simulation, we repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to account for possible complex dynamics within a ten-species community (initialization period).
+In this simulation, we repeated the seeding procedure every 10 time steps over the first `r unique(list_sim[[2]]$n_warmup)` time steps to account for possible complex dynamics within a ten-species community (initialization period).
 The rest of simulation procedures is identical to the two-species model.
@@
 
-`r paste(knit(text = table_stvy_chunk), collapse = '\n')`
+`r paste(knitr::knit(text = table_stvy_chunk), collapse = '\n')`
 
@@
 
-`r paste(knit(text = table_reg_chunk), collapse = '\n')`
+`r paste(knitr::knit(text = table_reg_chunk), collapse = '\n')`
 
@@
 
-`r paste(knit(text = figure_sim_chunk), collapse = '\n')`
+`r paste(knitr::knit(text = figure_sim_chunk), collapse = '\n')`
 
@@
 
-`r paste(knit(text = figure_dyns_chunk), collapse = '\n')`
+`r paste(knitr::knit(text = figure_dyns_chunk), collapse = '\n')`
 

### 2022-09-22 code/table_ssm.R

@@ -3,7 +3,7 @@
 
 rm(list = ls())
 paste0("code/", c("library.R", "set_functions.R")) %>% 
-  lapply(source)
+  lapply(FUN = function(x) source(here::here(x)))
 
 
 # data --------------------------------------------------------------------

### 2022-09-22 code/table_stvy_analysis.R

@@ -2,7 +2,7 @@
 # setup -------------------------------------------------------------------
 
 rm(list = ls())
-source("code/library.R")
+source(here::here("code/library.R"))
 
 
 # table -------------------------------------------------------------------

### 2022-09-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-We subsequently analyzed a whole community model with $10$ species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[1]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[1]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[1]]$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[1]]$phi)`).
+We subsequently analyzed a whole community model with $10$ species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`).
 We confirmed that these parameters are influential in the ten-species community model via sensitivity analysis (**Table S2-S4**).
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[1]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[1]]$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(list_param[[1]]$sd_env)`).
-This simulation setup resulted in `r nrow(list_param[[1]])` sets of parameter combinations.
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(list_param[[2]]$sd_env)`).
+This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.
 
@@
 ## conditional text
-c_text <- case_when(name == "all" ~ "whole community",
-                    name == "masu" ~ "masu salmon",
-                    name == "other" ~ "unenhanced species")
+c_text <- case_when(group == "all" ~ "whole community",
+                    group == "masu_salmon" ~ "masu salmon",
+                    group == "other" ~ "unenhanced species")
 
@@
 
-for(i in seq_len(length(df_est))) {
+for(i in seq_len(length(list_reg))) {
 
@@
                        \n\n
-                       kable(df_est[[",i,"]],
+                       kable(list_reg[[",i,"]],
                              align = c(rep('l', 3), rep('c', 4)),

### 2022-09-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 output:
-  pdf_document:
+  bookdown::pdf_document2:
     latex_engine: xelatex
@@
         before_body: title.tex
+mainfont: "Times New Roman"
+fontsize: 11pt
 knit: (function(inputFile, encoding) {
@@
 \begin{align}
-N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\epsilon_{i,t})
+N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
 \end{align}
 ```
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $\text{Normal}(0, \sigma_{\varepsilon}^2)$.
 We modified this formula to include the effects of intentional release (species 1) on reproduction and competition as follows:
@@
 \begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\varepsilon_{i,t})
 \end{align}
@@
 \begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t) ~ \exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
 \end{align}
 ```
-In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0.5,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively.
+In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim \text{Exp}(1/\bar{\alpha})$), respectively.
 We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
@@
 Specifically, we examined the release effect with $20$ parameter values of intrinsic population growth rate $r_i$ ($0.5$ to $3.5$ with an equal interval) and carrying capacity $K$ ($50$ to $500$ with an equal interval), resulting in $400$ parameter combinations.
-In an ordinary Ricker model, the chosen range of $r_i$ can generate stable equilibrium, damped oscillations, limit cycle, and chaos (XXX).
+In a single-species Ricker model, the chosen range of $r_i$ can generate stable equilibrium, damped oscillations, limit cycle, and chaos (XXX).
 For simplicity, we assumed $r_1 = r_2$.
-We crossed this parameter setup with environmental stochasticity ($\sigma =$ `r unique(list_param[[1]]$sd_env)`) and competition strength ($\alpha =$ `r unique(list_param[[1]]$alpha)`) and generated `r nrow(list_param[[1]])` simulation scenarios ($400 \times 2 \times 2$).
+We crossed this parameter setup with environmental stochasticity ($\sigma_{\varepsilon} =$ `r unique(list_param[[1]]$sd_env)`) and competition strength ($\alpha_{ij} =$ `r unique(list_param[[1]]$alpha)`) and generated `r nrow(list_param[[1]])` simulation scenarios ($400 \times 2 \times 2$).
 
-Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` time steps of community dynamics for $100$ values of release level $R$ ($0$ to $500$ with an equal interval).
-We initialized populations of each species drawn from a Poisson distribution with a mean of $50$ and let species grow with no release for the first `r unique(list_sim[[1]]$n_warmup)` time steps.
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(list_sim[[1]]$n_burnin)` time steps to reach new equilibrium with selective intentional release (burn-in period).
-We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` time steps, which were used to obtain the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
+Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` time steps of community dynamics for $100$ values of release level $R$ (0 to 500 with an equal interval).
+We introduced 50 individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` time steps (initialization).
+After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(list_sim[[1]]$n_burnin)` time steps to reach new equilibrium with intentional release (burn-in period).
+We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` time steps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$: the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
 
-We subsequently analyzed a whole community model with $10$ species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`).
-We confirmed that these parameters are influential in the ten-species community model via sensitivity analysis (**Table S2-S4**).
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(list_param[[2]]$sd_env)`).
+We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`).
+We confirmed that these parameters were influential in the ten-species community model via sensitivity analysis (**Table S2 -- S4**).
+We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs.
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`).
 This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.
 
-As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` time steps of `r max(list_sim[[2]]$n_rep)` with $100$ values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
-Initial seed inidividuals of each species were drawn from a Poisson distribution with a mean of five.
-In this simulation, we repeated the seeding procedure every 10 time steps over the first `r unique(list_sim[[2]]$n_warmup)` time steps to account for possible complex dynamics within a ten-species community (initialization period).
-The rest of simulation procedures is identical to the two-species model.
+As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` time steps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
+In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every 10 time steps to account for possible complex dynamics of a ten-species community.
+The rest of the simulation procedure is identical to the two-species model.
 We summarized values of simulation parameters in **Table S1**.
@@
 However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
-To confront this challenge, we developed a Bayesian state-space model for three species groups separately: (i) whole community, the summed abundance of all species, (ii) enhanced species, the abundance of masu salmon, (iii) unenhanced species, the summed abundance of all species except masu salmon.
+To confront this challenge, we developed a Bayesian state-space model for two species groups separately: (i) enhanced species, the abundance of masu salmon, and (ii) unenhanced species, the summed abundance of all species except masu salmon.
 A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
@@
 
-In the observation model, we model observation processes.
-Fish abundance of either whole community, enhanced species (masu salmon), or unenhanced species at site $s$ in year $t$, $N_{s,t}$, was assumed to follow a Poisson distribution:
+In the observation model, we model observation processes. Fish abundance at site $s$ in year $t$ (either enhanced or unenhanced species), $N_{s,t}$, was assumed to follow a Poisson distribution:
 
@@
 \begin{align}
-N_{s,t} \sim Poisson(\lambda_{s,t} A_{s,t})
+N_{s,t} \sim \text{Poisson}(\lambda_{s,t} A_{s,t})
 \end{align}
@@
 \begin{align}
-\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
+\lambda_{s,t} = n_{s,t}\exp(\varepsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
 \end{align}
@@
 The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The parameter $\epsilon_{s,t}^{obs}$ is the error term that follows a normal distribution $Normal(0, \sigma_{obs,s}^2)$.
+The parameter $\varepsilon_{s,t}^{obs}$ is the error term that follows a normal distribution $Normal(0, \sigma_{obs,s}^2)$.
 The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
@@
 
-In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
+In the state model, we model temporal dynamics of fish density $n_{s,t,g}$ as follows:
 
@@
 \begin{align}
-ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
+\begin{split}
+&\ln n_{s,t} = \nu_{1,s} + \nu_{2,s} \ln n'_{s,t-1} + \varepsilon_{s,t}^{state}\\
+&\ln n'_{s,t-1} = \frac{\sum_{q=1}^Q (\tau^{q} \ln n_{s,t-q})}{\sum_{q=1}^Q \tau^{q}}
+\end{split}
+(\#eq:state)
 \end{align}
 ```
-where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$.
-The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the SD $\sigma_r$).
-This hierarchical structure allows for improved parameter estimates by partially sharing information across sites [@gelmanDataAnalysisUsing2007].
+where $\nu_{1,s}$ is the site-specific growth rate at site $s$, $\nu_{2,s}$ the parameter charactering density-dependence, and $\varepsilon_{s,t}^{state}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{state} \sim \text{Normal}(0, \sigma_{state,s}^2)$.
+Equation \@ref(eq:state) is strucutrally equivalent to a $Q$-order autoregressive (AR) model; however, our model has only one AR parameter $\tau$ (range: 0 -- 1) unlike ordinary AR models that require $Q$ AR parameters.
+This reduction of parameter numbers is possible because we express the AR parameters as a geometric-series $\tau^q$.
+Thus, the parameter $\tau$ controls how fast the density influence attenuates towards the past.
+In this study, we set $Q=3$ given the life span of the study species (typically 1 -- 3 years).
 We used median estimates of fish density $n_{s,t}$ to calculate the temporal CV, mean ($\mu$), and SD ($\sigma$) for each site.
-We summarized the reconstructed community dynamics in **Figures S7-S9**.
+For a whole community, we summed the densities of enhanced and unenhanced species.
+We summarized the reconstructed community dynamics in **Figures S7 -- S9**.
 
-We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data.
-Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.
+We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0 --1 and indicates over- (\~0.00), under- (\~1.00), or suitable-fitting (\~0.50) to the data.
+A Bayesian p-value for our state-space models was `r op(min(df_bp$mean))`, indicating that our model specification is appropriate.
 
@@
 Although our focus is intentional release, each model included climatic and local abiotic variables to account for important environmental differences among sites.
-Specifically, we developed the following linear regression model taking either the CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.
+Specifically, we developed the following linear regression model taking either species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$.
 
@@
 \begin{aligned}
-ln~y_s &\sim Normal(\mu_{y,s}, \sigma_y^2) &&\text{for CV, mean, and SD}\\
-y_s &\sim Poisson(\lambda_{y,s} exp(\epsilon_{\lambda,s})) &&\text{for species richness}
+y_s &\sim \text{Poisson}(\lambda_{y,s} \exp(\varepsilon_{\lambda,s})) &&\text{for species richness}\\
+\ln \pmb{y_s} &\sim \text{MN}(\pmb{\mu_{y,s}}, \pmb{\Omega_y}) &&\text{for mean and SD}
 \end{aligned}
 \right.
+ (\#eq:reg)
 \end{align}
 ```
-where $\sigma_y$ is the SD of residual errors and $exp(\epsilon_{\lambda,s})$ is the error term that accounts for overdispersion ($\epsilon_{\lambda,s} \sim Normal(0, \sigma_{\lambda}^2)$).
-The expected means were related to linear predictors as follows:
+In the poisson model for species richness, $\exp(\varepsilon_{\lambda,s})$ is the error term accounting for overdispersion ($\varepsilon_{\lambda,s} \sim \text{Normal}(0, \sigma_{\lambda}^2)$).
+In the multi-variate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multi-variate normal distribution with a variance-covariance matrix $\pmb{\Omega_y}$.
+The expected means $\lambda_{y,s}$ and $\pmb{\mu_s}$ were related to linear predictors as follows:
 
@@
 \begin{aligned}
-\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
-ln~\lambda_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
+\ln \lambda_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}\\
+\mu_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_k x_{k,s} &&\text{for mean and SD}
 \end{aligned}
@@
 ```
-$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$.
-The site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
+$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of effective release of masu salmon $R'_s$ and other site-level predictors $x_k$.
+$R'_s$ is the product of the average yearly release at watershed $w$ ($R_w$; fry + juvenile + smolt, averaged for 1999 -- 2019) and the site-specific weight factor $\eta_{w,s'}$ ($s'=1,...,S_w + 1$, where $S_w$ is the number of sites within watershed $w$):
+
+```{=tex}
+\begin{align}
+\begin{split}
+R'_s &= \eta_{w,s'} R_w\\
+\sum_{s'}^{S_w + 1} \eta_{w,s'} &= 1
+(\#eq:effr)
+\end{split}
+\end{align}
+```
+In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$.
+The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be a unity because non-negligible portion of release may escape into unsurveyed areas.
+Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data (see **Model fitting**).
+Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
 Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**).
@@
 \begin{align}
-\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
-\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
+\begin{split}
+\gamma_{0,w} &\sim \text{Normal}(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
+\mu_{\gamma,w} &= \delta_0 + \delta_1 z_{w}
+\end{split}
 \end{align}
 ```
-$\delta_{0}$ is the global intercept and $\delta_k (k > 0)$ are the regression coefficients.
-The watershed-level predictors $z_{k,w}$ include the yearly release of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019).
+$\delta_{0}$ is the global intercept and $\delta_1$ is the regression coefficient of ocean productivity $z_{w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019).
 Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
@@
 Three Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
-Total MCMC interations ranged from `r min(df_mcmc_ssm$n_total_mcmc)` to `r max(df_mcmc_ssm$n_total_mcmc)` for the state-space models and was `r unique(df_mcmc_reg$n_total_mcmc)` for the regression models.
-The first `r unique(c(df_mcmc_ssm$n_burn, df_mcmc_reg$n_burn))` iterations were discarded as burn-in, and MCMC samples were saved every `r unique(df_mcmc_ssm$n_thin)` (state-space) and `r unique(df_mcmc_reg$n_thin)` iterations (regression) to reduce autocorrelation.
+The total MCMC iteration was XXX.
 Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached \< 1.1 [@gelmanDataAnalysisUsing2007].
-Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
-Parameter estimates were summarized in **Table S7-S10**.
+Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021].
+Parameter estimates were summarized in **Table S7 -- S10**.
 
@@
 We generated 500 sets of parameter combinations by randomly drawing values of seven simulation parameters from uniform distributions (**Table S1**).
-For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of intentional release $R$ (drawn randomly from $Unif(0, 500)$).
+For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of intentional release $R$ (drawn randomly from $\text{Unif}(0, 500)$).
 This yields a total of $5 \times 10^4$ simulation replicates.
@@
 
-For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community dynamics, which indicate the effect of intentional release under a given ecological context.
-To examine influences of simulation parameters on $\xi$ (**Table S1**), we developed the following regression model taking $\xi$ as a response variable:
+For each parameter combination, we estimated Spearman's rank correlation $\rho$ between the number of releases $R$ and community dynamics, which indicate the effect of intentional release under a given ecological context.
+To examine influences of simulation parameters on $\rho$ (**Table S1**), we developed the following regression model taking $\rho$ as a response variable:
 
@@
 \begin{aligned}
-  \xi_{n} &\sim Normal(\mu_n, \sigma^2)\\
-  \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 r_{1,n} + \zeta_3 r_{max,n} + \zeta_4  \bar{\alpha}_n + \zeta_5 K_n + \zeta_6 \sigma_{\epsilon,n} + \zeta_7 f_{R, n}
+  \rho_{n} &\sim \text{Normal}(\mu_{\rho, n}, \sigma_{\rho}^2)\\
+  \mu_{\rho,n} &= \zeta_0 + \zeta_1 S_n + \zeta_2 r_{1,n} + \zeta_3 r_{max,n} + \zeta_4  \bar{\alpha}_n + \zeta_5 K_n + \zeta_6 \sigma_{\varepsilon,n} + \zeta_7 f_{R, n}
 \end{aligned}
@@
 
-where $\xi_n$ is Spearman's rank correlation for parameter combination $n$, and $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$).
+where $\rho_n$ is Spearman's rank correlation for parameter combination $n$, and $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$).
 Explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.
 
-We found that regression coefficients of the following parameters ($\zeta$) never exceeded a value of 0.10: the number of species $S$, maximum intrinsic growth rate of unenhanced species $r_{max}$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$.
+We found that regression coefficients of the following parameters ($\zeta$) never exceeded a value of 0.10: the number of species $S$, maximum intrinsic growth rate of unenhanced species $r_{max}$, environmental stochasticity $\sigma_{\varepsilon}$, and relative fitness $f_R$.
 Therefore, these parameters have little influence on the qualitative relationship between the number of releases and community dynamics.
-In the main simulation, we fixed values of $S$, $r_{max}$, and $\sigma_{\epsilon}$ (**Table S1**).
+In the main simulation, we fixed values of $S$, $r_{max}$, and $\sigma_{\varepsilon}$ (**Table S1**).
 In the meantime, we varied values of $K$, $r_1$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**).
@@
                        "maximum intrinsic growth rate of unenhanced species $r_{max}$ = `r df_param$r_max[",i,"]`; ",
-                        "environmental stochasticity $\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`; ",
+                        "environmental stochasticity $\\sigma_{\\varepsilon}$ = `r df_param$sd_env[",i,"]`; ",
                         "carrying capacity $K$ = `r df_param$k[",i,"]`.",

### 2022-09-26 code/analysis_stvy.R
edit: stvy

@@ -25,14 +25,26 @@ df_psi <- sim_stvy_result %>%
               values_from = c(mean_density,
                               sd_density)) %>% 
   group_by(group_id) %>% 
-  summarize(slope_mean_enhanced = cor(mean_density_enhanced, stock, method = "spearman"),
-            slope_mean_unenhanced = cor(mean_density_unenhanced, stock, method = "spearman"),
-            slope_mean_all = cor(mean_density_all, stock, method = "spearman"),
-            slope_sd_enhanced = cor(sd_density_enhanced, stock, method = "spearman"),
-            slope_sd_unenhanced = cor(sd_density_unenhanced, stock, method = "spearman"),
-            slope_sd_all = cor(sd_density_all, stock, method = "spearman")) %>% 
-  mutate(across(.fns = as.numeric)) %>% 
-  ungroup()
+  summarize(slope_mean_enhanced = cor(mean_density_enhanced,
+                                      stock,
+                                      method = "spearman"),
+            slope_mean_unenhanced = cor(mean_density_unenhanced,
+                                        stock,
+                                        method = "spearman"),
+            slope_mean_all = cor(mean_density_all, 
+                                 stock,
+                                 method = "spearman"),
+            slope_sd_enhanced = cor(sd_density_enhanced,
+                                    stock,
+                                    method = "spearman"),
+            slope_sd_unenhanced = cor(sd_density_unenhanced,
+                                      stock, 
+                                      method = "spearman"),
+            slope_sd_all = cor(sd_density_all, 
+                               stock, 
+                               method = "spearman")) %>% 
+   mutate(across(.fns = replace_na, replace = 0)) %>% 
+   ungroup()
 
 ## combine
 df_m <- df_psi %>% 

### 2022-09-26 code/run_simulation_stvy.R

@@ -18,7 +18,7 @@ df_param <- tibble(n_timestep = 1000,
                    r_type = "constant",
                    r1 = runif(n_para, 0.5, 3.5),
                    r_min = 0.5,
-                   r_max = runif(n_para, 0.5, 2.5),
+                   r_max = runif(n_para, 0.5, 3.5),
                    sd_env = runif(n_para, 0.01, 1.5),
                    phi = runif(n_para, 0.5, 1),
                    int_type = "random",

### 2022-09-26 code/table_param_set.R

@@ -40,8 +40,8 @@ df_param <- sim_result %>%
                                Parameter == "alpha" ~ "Average strength of interspecific competition"),
     Sensitivity = case_when(Parameter == "n_species" ~ "Unif(5, 20)",
                             Parameter == "k" ~ "Unif(100, 1000)",
-                            Parameter == "r1" ~ "Unif(0.5, 2.5)",
-                            Parameter == "r_max" ~ "Unif(0.5, 2.5)",
+                            Parameter == "r1" ~ "Unif(0.5, 3.5)",
+                            Parameter == "r_max" ~ "Unif(0.5, 3.5)",
                             Parameter == "sd_env" ~ "Unif(0.05, 1.5)",
                             Parameter == "phi" ~ "Unif(0.5, 1)",
                             Parameter == "alpha" ~ "Unif(0.05, 0.5)"),

### 2022-09-26 rmd/supporting_info.Rmd
text

@@
 y_s &\sim \text{Poisson}(\lambda_{y,s} \exp(\varepsilon_{\lambda,s})) &&\text{for species richness}\\
-\ln \pmb{y_s} &\sim \text{MN}(\pmb{\mu_{y,s}}, \pmb{\Omega_y}) &&\text{for mean and SD}
+\ln \pmb{y_s} &\sim \text{MN}(\pmb{\theta_{y,s}}, \pmb{\Omega_y}) &&\text{for mean and SD}
 \end{aligned}
@@
 In the multi-variate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multi-variate normal distribution with a variance-covariance matrix $\pmb{\Omega_y}$.
-The expected means $\lambda_{y,s}$ and $\pmb{\mu_s}$ were related to linear predictors as follows:
+The expected means $\lambda_{y,s}$ and $\pmb{\theta_s}$ were related to linear predictors as follows:
 
@@
 \ln \lambda_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}\\
-\mu_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_k x_{k,s} &&\text{for mean and SD}
+\theta_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_k x_{k,s} &&\text{for mean and SD}
 \end{aligned}
 \right.
+(\#eq:model)
 \end{align}
@@
 The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
+
+As for the effects of environmental variables on the CV, we did not explicitly develop a regression model.
+Instead, we derived their effects from the multi-variate normal model of mean and SD since the CV is a additive function of mean and SD in a log scale:
+
+```{=tex}
+\begin{align}
+\text{E}(\ln CV_s) = \text{E}(\ln y_s^{(\sigma)}) - \text{E}(\ln y_s^{(\mu)})
+\end{align}
+```
+Considering that $\text{E}(\ln y_s^{(\sigma)}) = \theta_{y,s}^{(\sigma)}$ and $\text{E}(\ln y_s^{(\mu)}) = \theta_{y,s}^{(\mu)}$,
+
+```{=tex}
+\begin{align}
+\text{E}(\ln CV_s) = (\gamma_{0,w(s)}^{(\sigma)} - \gamma_{0,w(s)}^{(\mu)}) + (\gamma_{1}^{(\sigma)} - \gamma_{1}^{(\mu)})R'_s + \sum_k (\gamma_{k}^{(\sigma)} - \gamma_{k}^{(\mu)})x_{k,s}
+\end{align}
+```
 All predictors were standardized (mean = 0, SD = 1) before the analysis.

### 2022-09-26 rmd/supporting_info.Rmd
rmd

@@
 \begin{align}
-N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
+N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{\sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
 \end{align}
@@
 \begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{N_{i,t}+\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\varepsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\varepsilon_{i,t})
+(\#eq:ricker)
 \end{align}
@@
 ```
-$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation (2) can be reorganized to:
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation \@ref(eq:ricker) can be reorganized to:
 
@@
 \begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t) ~ \exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t) ~ \exp \left[r_i \left(1-\frac{\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
 \end{align}
@@
 Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
+We extracted annual data of chlorophyll *a* concentration (2002 -- 2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
 We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
@@
 \begin{align}
-\lambda_{s,t} = n_{s,t}\exp(\varepsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
+\lambda_{s,t} = n_{s,t}\exp(\varepsilon_{s,t}^{\text{obs}}) + \psi \beta_s~Fry_{w(s),t}
 \end{align}
@@
 The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The parameter $\varepsilon_{s,t}^{obs}$ is the error term that follows a normal distribution $Normal(0, \sigma_{obs,s}^2)$.
+The parameter $\varepsilon_{s,t}^{\text{obs}}$ is the error term that follows a normal distribution $\text{Normal}(0, \sigma_{\text{obs},s}^2)$.
 The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
@@
 \begin{split}
-&\ln n_{s,t} = \nu_{1,s} + \nu_{2,s} \ln n'_{s,t-1} + \varepsilon_{s,t}^{state}\\
+&\ln n_{s,t} = \nu_{1,s} + \nu_{2,s} \ln n'_{s,t-1} + \varepsilon_{s,t}^{\text{state}}\\
 &\ln n'_{s,t-1} = \frac{\sum_{q=1}^Q (\tau^{q} \ln n_{s,t-q})}{\sum_{q=1}^Q \tau^{q}}
@@
 ```
-where $\nu_{1,s}$ is the site-specific growth rate at site $s$, $\nu_{2,s}$ the parameter charactering density-dependence, and $\varepsilon_{s,t}^{state}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{state} \sim \text{Normal}(0, \sigma_{state,s}^2)$.
-Equation \@ref(eq:state) is strucutrally equivalent to a $Q$-order autoregressive (AR) model; however, our model has only one AR parameter $\tau$ (range: 0 -- 1) unlike ordinary AR models that require $Q$ AR parameters.
+where $\nu_{1,s}$ is the site-specific growth rate at site $s$, $\nu_{2,s}$ the parameter characterizing density-dependence, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
+The parameters $\nu_{1,s}$ and $\nu_{2,s}$ were drawn from a multi-variate normal distribution as $\pmb{\nu} \sim \text{MVN}(\pmb{\theta_{\nu}}, \pmb{\Omega_{\nu}})$, where $\pmb{\nu}$ is the matrix of $\nu_{1,s}$ and $\nu_{2,s}$.
+Equation \@ref(eq:state) is structurally equivalent to a $Q$-order autoregressive (AR) model; however, our model has only one AR parameter $\tau$ (range: 0 -- 1) unlike ordinary AR models that require $Q$ AR parameters.
 This reduction of parameter numbers is possible because we express the AR parameters as a geometric-series $\tau^q$.
@@
 y_s &\sim \text{Poisson}(\lambda_{y,s} \exp(\varepsilon_{\lambda,s})) &&\text{for species richness}\\
-\ln \pmb{y_s} &\sim \text{MN}(\pmb{\theta_{y,s}}, \pmb{\Omega_y}) &&\text{for mean and SD}
+\ln \pmb{y_s} &\sim \text{MVN}(\pmb{\theta_{y,s}}, \pmb{\Omega_y}) &&\text{for mean and SD}
 \end{aligned}
@@
 In the poisson model for species richness, $\exp(\varepsilon_{\lambda,s})$ is the error term accounting for overdispersion ($\varepsilon_{\lambda,s} \sim \text{Normal}(0, \sigma_{\lambda}^2)$).
-In the multi-variate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multi-variate normal distribution with a variance-covariance matrix $\pmb{\Omega_y}$.
+In the multi-variate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multi-variate normal distribution with the variance-covariance matrix $\pmb{\Omega_y}$.
 The expected means $\lambda_{y,s}$ and $\pmb{\theta_s}$ were related to linear predictors as follows:
@@
 ```
-$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of effective release of masu salmon $R'_s$ and other site-level predictors $x_k$.
+$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ is the $k^\text{th}$ regression coefficient [effective release of masu salmon $R'_s$ ($k = 1$) and other site-level predictors $x_k$ ($k \ge 2$)].
 $R'_s$ is the product of the average yearly release at watershed $w$ ($R_w$; fry + juvenile + smolt, averaged for 1999 -- 2019) and the site-specific weight factor $\eta_{w,s'}$ ($s'=1,...,S_w + 1$, where $S_w$ is the number of sites within watershed $w$):
@@
 The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be a unity because non-negligible portion of release may escape into unsurveyed areas.
-Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data (see **Model fitting**).
+Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **Model fitting**).
 Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
@@
 
-As for the effects of environmental variables on the CV, we did not explicitly develop a regression model.
-Instead, we derived their effects from the multi-variate normal model of mean and SD since the CV is a additive function of mean and SD in a log scale:
+Since the CV is a additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation \@ref(eq:model):
 
@@
 
-**Species interaction.** XXX
+**Species interaction.** We analyzed a subset of our data to estimate the strength of interspecific interactions among stream fishes.
+In this analysis, we focused on `r n_distinct(df_complete$site_id)` sites with (1) \> 16 years of observations and (2) no intentional release of masu salmon.
+These additional constraints were necessary to estimate parameters in a complex multi-species model within a state-space modeling framework.
+
+We fitted the following state-space model to the data for each site separately. In the observation model, we modeled fish abundance $N_{i,t}$ for species $i$ at year $t$ as:
+
+```{=tex}
+\begin{align}
+\begin{split}
+N_{i,t} \sim \text{Poisson}(\lambda_{i,t} A_{t})\\
+\lambda_{s,t} = n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})
+\end{split}
+\end{align}
+```
+In the state model, we described a multi-species Ricker model for fish density $n_{i,t}$:
+
+```{=tex}
+\begin{align}
+\ln n_{i,t} = \ln n_{i,t-1} + r_{i} - \sum_{j=1}^S\alpha'_{ij} n_{i,t-1} + \varepsilon_{i,t}^{\text{state}}
+(\#eq:ricker-ssm)
+\end{align}
+```
+Equation \@ref(eq:ricker-ssm) is equivalent to Equation \@ref(eq:ricker) except the scale of competition coefficients $\alpha'_{ij}$ ($\frac{\alpha'_{ij}}{\alpha'_{ii}}=\alpha_{ij}$, where $\alpha'_{ii}=\frac{r_i}{K_i}$).
+We used sparse priors for $\alpha'_{ij}$ to reduce the risk of over-fitting [@mutshindaWhatDrivesCommunity2009]:
+
+```{=tex}
+\begin{align}
+\begin{split}
+\alpha'_{ij} \sim \text{half-Normal}(0, \sigma^2_{\alpha, ij})\\
+\sigma_{\alpha,ij}^2 = z_{ij}c_1 + (1-z_{ij})c_0
+\end{split}
+(\#eq:sparse)
+\end{align}
+```
+In Equation \@ref(eq:sparse), the latent variable $z_{ij}$ is drawn from a Bernoulli distribution and controls the prior for $\alpha'_{ij}$.
+We used $c_1 = 1$ and $c_0 = 0.01$ so that $\alpha'_{ij}$ is freely estimated when $z_{ij}=1$ ($\sigma^2_{\alpha} = 1$).
+Otherwise, the probability density of $\alpha'_{ij}$ would be concentrated around zero ($\sigma^2_{\alpha} = 0.01$), effectively omitting the parameter from the model [@mutshindaWhatDrivesCommunity2009].
+We assigned different "inclusion" probabilities to diagonal (intraspecific competition) and off-diagonal elements (interspecific competition) as $z_{ii} \sim \text{Bernoulli}(p_{\alpha}^{\text{intra}})$ and $z_{ij,i \ne j} \sim \text{Bernoulli}(p_{\alpha}^{\text{inter}})$.
+
+We assumed that environmental noise $\varepsilon_{i,t}^{\text{state}}$ is correlated among species by introducing the variance-covariance matrix $\pmb{\Omega_{\varepsilon}}$.
+The matrix $\pmb{\Omega_{\varepsilon}}$ was modeled with the aid of latent factors $\zeta_{t,d}$ and factor loadings $\delta_{d,i}$:
+
+```{=tex}
+\begin{align}
+\varepsilon_{i,t}^{\text{state}}=\sum_{d}^{D}\zeta_{t,d}\delta_{d,i} + I_{ij}\epsilon_{i,t}
+\end{align}
+```
+where $D$ is the number of latent factors, $\epsilon_{i,t} \sim \text{Normal}(0, \sigma_{\epsilon,i}^2)$, and $I_{ij}$ is the identity matrix ($I_{ii}=1$ and $I_{ij, i \ne j} = 0$).
+With this formulation, the matrix $\pmb{\Omega_{\varepsilon}}$ can be described as $\pmb{\Omega_{\varepsilon}}=\pmb{\Delta}^T\pmb{\Delta} + \text{diag}(\sigma_{\epsilon,i}^2)$, where $\pmb{\Delta}$ is the matrix of factor loadings $\delta_{d,i}$.
+This model structure has a merit of reduced number of parameters while capturing the correlated nature of environmental noises [@ovaskainenHowAreSpecies2017].
+We set $D=2$ when the number of species in a community is greater than four, otherwise $D=1$.
+We reported the estimates of $\alpha_{ij}$ so the values are comparable to those used in the theoretical analysis.
 
@@
 We assigned weakly informative priors to parameters (**Table S6**).
-Three Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
+Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
 The total MCMC iteration was XXX.
@@
 
-# Supplementary text
-
-## Sensitivity analysis
-
-We performed a sensitivity analysis of the community simulation to identify key simulation parameters that strongly affect the relationships between community dynamics (temporal mean and SD of density) and intentional release.
-We generated 500 sets of parameter combinations by randomly drawing values of seven simulation parameters from uniform distributions (**Table S1**).
-For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of intentional release $R$ (drawn randomly from $\text{Unif}(0, 500)$).
-This yields a total of $5 \times 10^4$ simulation replicates.
-In each simulation replicate, we ran 1600 time steps of community dynamics and obtained temporal means and SDs of the whole community ($\sum_i^SN_i$), enhanced species ($N_1$), and unenhanced species ($\sum_{i, i\ne1}^SN_i$) using the last 1000 time steps.
-The first 600 time steps were discarded as initialization and burn-in periods.
-
-For each parameter combination, we estimated Spearman's rank correlation $\rho$ between the number of releases $R$ and community dynamics, which indicate the effect of intentional release under a given ecological context.
-To examine influences of simulation parameters on $\rho$ (**Table S1**), we developed the following regression model taking $\rho$ as a response variable:
-
-$$
-\begin{aligned}
-  \rho_{n} &\sim \text{Normal}(\mu_{\rho, n}, \sigma_{\rho}^2)\\
-  \mu_{\rho,n} &= \zeta_0 + \zeta_1 S_n + \zeta_2 r_{1,n} + \zeta_3 r_{max,n} + \zeta_4  \bar{\alpha}_n + \zeta_5 K_n + \zeta_6 \sigma_{\varepsilon,n} + \zeta_7 f_{R, n}
-\end{aligned}
-$$
-
-where $\rho_n$ is Spearman's rank correlation for parameter combination $n$, and $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$).
-Explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.
-
-We found that regression coefficients of the following parameters ($\zeta$) never exceeded a value of 0.10: the number of species $S$, maximum intrinsic growth rate of unenhanced species $r_{max}$, environmental stochasticity $\sigma_{\varepsilon}$, and relative fitness $f_R$.
-Therefore, these parameters have little influence on the qualitative relationship between the number of releases and community dynamics.
-In the main simulation, we fixed values of $S$, $r_{max}$, and $\sigma_{\varepsilon}$ (**Table S1**).
-In the meantime, we varied values of $K$, $r_1$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**).
-Although $f_R$ had little influence on release effects (**Table S1**), we varied this parameter given the significant interest in the relative fitness of captive-bred individuals in the wild.
-
-\newpage
-
-# Tables
+# Supplementary Tables
 
@@
 
-```{r data_stvy, include=FALSE}
-
-# Table S2-4
-## load table for sensitivity analysis
-source(here::here("code/table_stvy_analysis.R"))
-
-```
-
-```{r table_sensitivity, results="asis"}
-
-# Table S2-4
-j <- 1
-
-## conditional text
-c_text <- c("whole community",
-            "enhanced species",
-            "unenhanced species")
-
-table_stvy_chunk <- knit_chunk <- NULL
-
-for(i in 1:length(table_stvy)) {
-
-  table_legend <- paste0("Sensitivity analysis of the community simulation.
-Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
-Response variables are Spearman's rank correlation between intentional release and either temporal mean density ($\\mu$) or SD ($\\sigma$) of ", c_text[i],".
-Explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")
-
-  knit_chunk <- paste0("## Table S", i + j, " Sensitivity analysis (", c_text[i],") \n",
-                       table_legend,
-                       "\n```{r table_s", i + j,", results='asis'}
-                       \n\n
-                       cat(table_stvy[[", i,"]], sep = '\n')
-                       \n\n
-                       ```\n",
-                       "\n\\pagebreak\n")
-
-  table_stvy_chunk <- c(table_stvy_chunk, knit_chunk)
-
-}
-
-```
-
-`r paste(knitr::knit(text = table_stvy_chunk), collapse = '\n')`
-
-## Table S5 Observed species
+## Table S2 Observed species
 
@@
 
-## Table S6 Priors
+## Table S3 Priors
 
@@
 
-## Table S7 Parameter estimates of the Bayesian state-space model
+## Table S4 Parameter estimates of the Bayesian state-space model
 
@@
 
-# Figures
+# Supplementary Figures
 

### 2022-09-27 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
+df_mcmc_ssm <- list.files(path = here::here("data_fmt"),
+                    full.names = T,
+                    pattern = "joint") %>% 
+  readRDS() %>% 
+  ungroup() %>% 
+  dplyr::select(n_total_mcmc,
+                n_sample,
+                n_thin,
+                n_burn) %>% 
+  distinct()
+
+df_mcmc_ricker <- list.files(path = here::here("output"),
+                             full.names = T,
+                             pattern = "summary_multi_ricker") %>% 
+  readRDS() %>% 
+  dplyr::select(n_total_mcmc,
+                n_sample,
+                n_thin,
+                n_burn) %>% 
+  distinct()
+
 ## release data
@@
 ```
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $\text{Normal}(0, \sigma_{\varepsilon}^2)$.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey a normal distribution $\text{Normal}(0, \sigma_{\varepsilon}^2)$.
 We modified this formula to include the effects of intentional release (species 1) on reproduction and competition as follows:
@@
 $n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released (unit: million fish) in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
-The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
+The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\theta_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
 The parameter $\varepsilon_{s,t}^{\text{obs}}$ is the error term that follows a normal distribution $\text{Normal}(0, \sigma_{\text{obs},s}^2)$.
@@
 
-In the state model, we model temporal dynamics of fish density $n_{s,t,g}$ as follows:
+In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
 
@@
 \begin{split}
-&\ln n_{s,t} = \nu_{1,s} + \nu_{2,s} \ln n'_{s,t-1} + \varepsilon_{s,t}^{\text{state}}\\
+&\ln n_{s,t} = \xi_{1,s} + \xi_{2,s} \ln n'_{s,t-1} + \varepsilon_{s,t}^{\text{state}}\\
 &\ln n'_{s,t-1} = \frac{\sum_{q=1}^Q (\tau^{q} \ln n_{s,t-q})}{\sum_{q=1}^Q \tau^{q}}
@@
 ```
-where $\nu_{1,s}$ is the site-specific growth rate at site $s$, $\nu_{2,s}$ the parameter characterizing density-dependence, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
-The parameters $\nu_{1,s}$ and $\nu_{2,s}$ were drawn from a multi-variate normal distribution as $\pmb{\nu} \sim \text{MVN}(\pmb{\theta_{\nu}}, \pmb{\Omega_{\nu}})$, where $\pmb{\nu}$ is the matrix of $\nu_{1,s}$ and $\nu_{2,s}$.
+where $\xi_{1,s}$ is the site-specific growth rate at site $s$, $\xi_{2,s}$ the parameter characterizing density-dependence, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
+The parameters $\xi_{1,s}$ and $\xi_{2,s}$ were drawn from a multi-variate normal distribution as $\pmb{\xi} \sim \text{MVN}(\pmb{\theta_{\xi}}, \pmb{\Omega_{\xi}})$, where $\pmb{\xi}$ is the matrix of $\xi_{1,s}$ and $\xi_{2,s}$.
 Equation \@ref(eq:state) is structurally equivalent to a $Q$-order autoregressive (AR) model; however, our model has only one AR parameter $\tau$ (range: 0 -- 1) unlike ordinary AR models that require $Q$ AR parameters.
@@
 ```
-$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ is the $k^\text{th}$ regression coefficient [effective release of masu salmon $R'_s$ ($k = 1$) and other site-level predictors $x_k$ ($k \ge 2$)].
+$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k = 1,2,...)$ is the $k^\text{th}$ regression coefficient [effective release of masu salmon $R'_s$ ($k = 1$) and other site-level predictors $x_k$ ($k \ge 2$)].
 $R'_s$ is the product of the average yearly release at watershed $w$ ($R_w$; fry + juvenile + smolt, averaged for 1999 -- 2019) and the site-specific weight factor $\eta_{w,s'}$ ($s'=1,...,S_w + 1$, where $S_w$ is the number of sites within watershed $w$):
@@
 \begin{split}
-\gamma_{0,w} &\sim \text{Normal}(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
-\mu_{\gamma,w} &= \delta_0 + \delta_1 z_{w}
+\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\
+\theta_{\gamma,w} &= \gamma'_0 + \gamma'_1 x'_{w}
 \end{split}
@@
 ```
-$\delta_{0}$ is the global intercept and $\delta_1$ is the regression coefficient of ocean productivity $z_{w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019).
+$\gamma'_{0}$ is the global intercept and $\gamma'_1$ is the regression coefficient of ocean productivity $\gamma'_{w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019).
 Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
@@
 ```
-In the state model, we described a multi-species Ricker model for fish density $n_{i,t}$:
+where $\varepsilon_{i,t}^{\text{obs}} \sim \text{Normal}(0, \sigma_{\text{obs},i})$. In the state model, we described a multi-species Ricker model for fish density $n_{i,t}$:
 
@@
 \begin{split}
-\alpha'_{ij} \sim \text{half-Normal}(0, \sigma^2_{\alpha, ij})\\
+\alpha'_{ij} \sim \text{Half-normal}(0, \sigma^2_{\alpha, ij})\\
 \sigma_{\alpha,ij}^2 = z_{ij}c_1 + (1-z_{ij})c_0
@@
 In Equation \@ref(eq:sparse), the latent variable $z_{ij}$ is drawn from a Bernoulli distribution and controls the prior for $\alpha'_{ij}$.
-We used $c_1 = 1$ and $c_0 = 0.01$ so that $\alpha'_{ij}$ is freely estimated when $z_{ij}=1$ ($\sigma^2_{\alpha} = 1$).
+We used $c_1 = 1$ and $c_0 = 0.01$ so that $\alpha'_{ij}$ is freely estimated when $z_{ij}$ equals one ($\sigma^2_{\alpha} = 1$).
 Otherwise, the probability density of $\alpha'_{ij}$ would be concentrated around zero ($\sigma^2_{\alpha} = 0.01$), effectively omitting the parameter from the model [@mutshindaWhatDrivesCommunity2009].
@@
 We reported the estimates of $\alpha_{ij}$ so the values are comparable to those used in the theoretical analysis.
+
+**Priors.** Vague priors were assigned to most parameters: $\text{Normal(0, 10)}$ for regression coefficients ($\gamma$ and $\gamma'$) and means ($\theta_{\beta}$ and $\pmb{\theta_{\xi}}$), $\text{Half-student's}~t(0, 2.5, 6)$ for SDs ($\sigma_{\beta}$, $\sigma_{\text{obs},s}$, $\sigma_{\text{state},s}$, $\sigma_{\text{obs},i}$, $\sigma_{\text{state},i}$ $\sigma_{\lambda}$, $\sigma_{\gamma}$, and $\sigma_{\epsilon,i}$), $\text{scaled-Inv-Wishart}(\pmb{\phi})$ ($\pmb{\phi}$ is a vector of prior scales $\pmb{\phi}=\{2.5,...,2.5\}$) with the degrees of freedom = 2 for variance-covariance matrices ($\pmb{\Omega_{\xi}}$, $\pmb{\Omega_y}$, and $\pmb{\Omega_{\varepsilon}}$), and $\text{Normal}(0, 1)$ for latent factors ($\zeta_{t,d}$).
+We used multiplicative gamma priors with parameters $\nu = 3$, $a_1=2$, and $a_2=3$ (see Durante [@duranteNoteMultiplicativeGamma2017] for interpretation) for latent factors ($\delta_{d,i}$) following Ovaskainen *et al.* [@ovaskainenHowAreSpecies2017].
+We assigned a weakly informative priors to initial fish densities $\text{ln}~n_{i,t}$ ($t = 1, 2, 3$) using $\text{Student's}~t(-2, 2, 6)$ to enhance model convergence.
 
@@
 
-```{r table_s5}
+```{r table_s2}
 
-# Table S5
+# Table S2
 source(here::here("code/table_species_list.R"))
@@
 
-```{r table_s6}
+```{r table_s3}
 

### 2022-09-27 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 ## mcmc sample size
-df_mcmc_ssm <- list.files(path = here::here("data_fmt"),
+
+df_mcmc <- lapply(c("summary_joint", "summary_reg", "summary_multi_ricker"),
+       function(x) {
+         list.files(path = here::here("output"),
                     full.names = T,
-                    pattern = "joint") %>% 
+                    pattern = x) %>% 
            readRDS() %>% 
@@
                          n_burn) %>% 
-  distinct()
-
-df_mcmc_reg <- list.files(path = here::here("output"),
-                          full.names = T,
-                          pattern = "summary_reg") %>% 
-  readRDS() %>% 
-  dplyr::select(n_total_mcmc,
-                n_sample,
-                n_thin,
-                n_burn) %>% 
-  distinct()
-
-df_mcmc_ssm <- list.files(path = here::here("data_fmt"),
-                    full.names = T,
-                    pattern = "joint") %>% 
-  readRDS() %>% 
-  ungroup() %>% 
-  dplyr::select(n_total_mcmc,
-                n_sample,
-                n_thin,
-                n_burn) %>% 
-  distinct()
-
-df_mcmc_ricker <- list.files(path = here::here("output"),
-                             full.names = T,
-                             pattern = "summary_multi_ricker") %>% 
-  readRDS() %>% 
-  dplyr::select(n_total_mcmc,
-                n_sample,
-                n_thin,
-                n_burn) %>% 
-  distinct()
+           distinct() %>% 
+           mutate(model = str_extract(x, "joint|reg|ricker"))
+       }) %>% 
+  bind_rows()
 

### 2022-09-27 code/si_figure_theory.R
Update si_figure_theory.R

@@ -46,13 +46,12 @@ list_g_theory <- foreach(i = seq_len(nrow(df_param))) %do% {
   df_set <- df0 %>% 
     filter(r1 == df_param$r1[i],
            k == df_param$k[i]) %>% 
-    mutate(alpha_label = case_when(alpha == min(df0$alpha) ~ sprintf('bar(alpha)=="%.1f")',
+    mutate(alpha_label = case_when(alpha == min(df0$alpha) ~ sprintf('bar(alpha)=="%.2f"',
                                                                      alpha),
-                                   alpha == max(df0$alpha) ~ sprintf('bar(alpha)=="%.1f")',
+                                   alpha == max(df0$alpha) ~ sprintf('bar(alpha)=="%.2f"',
                                                                      alpha)),
-           phi_label = case_when(phi == min(df0$phi) ~ sprintf('f[R]=="%1f"', phi),
-                                 phi == max(df0$phi) ~ sprintf('f[R]=="%1f"', phi)
-                                 )
+           phi_label = case_when(phi == min(df0$phi) ~ sprintf('f[R]=="%.1f"', phi),
+                                 phi == max(df0$phi) ~ sprintf('f[R]=="%.1f"', phi))
            )
   
   g <- df_set %>% 
@@ -60,7 +59,7 @@ list_g_theory <- foreach(i = seq_len(nrow(df_param))) %do% {
                x = stock,
                color = group_id,
                fill = group_id)) +
-    geom_smooth(size= 0.1,
+    geom_smooth(size= 1,
                 method = "loess") +
     scale_color_hue(labels = c("Whole", "Enhanced", "Unenhanced")) +
     labs(x = "Number of releases (individuals)",
@@ -68,10 +67,12 @@ list_g_theory <- foreach(i = seq_len(nrow(df_param))) %do% {
     facet_grid(cols = vars(alpha_label, phi_label),
                rows = vars(response_name),
                scales = "free_y",
-               labeller = label_parsed) +
+               labeller = label_parsed, 
+               switch = "y") +
     guides(color = guide_legend(override.aes = list(fill = NA)),
            fill = "none") +
-    theme(axis.title.y = element_blank())
+    theme(axis.title.y = element_blank(),
+          strip.placement = "outside")
   
   return(g)
 }

### 2022-09-27 code/table_param_set.R
Update table_param_set.R

@@ -19,9 +19,9 @@ df_param <- sim_result %>%
                 alpha) %>% 
   pivot_longer(cols = everything(),
                names_to = "Parameter",
-               values_to = "Main") %>% 
+               values_to = "Value") %>% 
   group_by(Parameter) %>% 
-  summarize(Main = list(unique(Main))) %>% 
+  summarize(Value = list(unique(Value))) %>% 
   ungroup() %>% 
   mutate(
     id = case_when(Parameter == "n_species" ~ "a",
@@ -38,13 +38,6 @@ df_param <- sim_result %>%
                                Parameter == "sd_env" ~ "Environmental variability",
                                Parameter == "phi" ~ "Relative fitness of captive-bred individuals",
                                Parameter == "alpha" ~ "Average strength of interspecific competition"),
-    Sensitivity = case_when(Parameter == "n_species" ~ "Unif(5, 20)",
-                            Parameter == "k" ~ "Unif(100, 1000)",
-                            Parameter == "r1" ~ "Unif(0.5, 3.5)",
-                            Parameter == "r_max" ~ "Unif(0.5, 3.5)",
-                            Parameter == "sd_env" ~ "Unif(0.05, 1.5)",
-                            Parameter == "phi" ~ "Unif(0.5, 1)",
-                            Parameter == "alpha" ~ "Unif(0.05, 0.5)"),
     Parameter = case_when(Parameter == "n_species" ~ "$S$",
                           Parameter == "k" ~ "$K$",
                           Parameter == "r1" ~ "$r_1$",

### 2022-09-27 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 ## ssm estimate
-df_bp <- list.files(path = here::here("data_fmt"),
+df_bp <- list.files(path = here::here("output"),
                     full.names = T,
-                    pattern = "joint") %>% 
+                    pattern = "summary_ssm_ar") %>% 
   readRDS() %>% 
@@
 
-df_mcmc <- lapply(c("summary_joint", "summary_reg", "summary_multi_ricker"),
+df_mcmc <- lapply(c("summary_ssm_ar", "summary_reg", "summary_multi_ricker"),
        function(x) {
@@
            distinct() %>% 
-           mutate(model = str_extract(x, "joint|reg|ricker"))
+           mutate(model = str_extract(x, "ssm|reg|ricker"))
        }) %>% 
@@
 We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`).
-We confirmed that these parameters were influential in the ten-species community model via sensitivity analysis (**Table S2 -- S4**).
 We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs.
@@
 ```
-where $\xi_{1,s}$ is the site-specific growth rate at site $s$, $\xi_{2,s}$ the parameter characterizing density-dependence, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
+where $\xi_{1,s}$ is the site-specific constant at site $s$, $\xi_{2,s}$ the parameter characterizing an autoregressive (AR) process, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
 The parameters $\xi_{1,s}$ and $\xi_{2,s}$ were drawn from a multi-variate normal distribution as $\pmb{\xi} \sim \text{MVN}(\pmb{\theta_{\xi}}, \pmb{\Omega_{\xi}})$, where $\pmb{\xi}$ is the matrix of $\xi_{1,s}$ and $\xi_{2,s}$.
-Equation \@ref(eq:state) is structurally equivalent to a $Q$-order autoregressive (AR) model; however, our model has only one AR parameter $\tau$ (range: 0 -- 1) unlike ordinary AR models that require $Q$ AR parameters.
-This reduction of parameter numbers is possible because we express the AR parameters as a geometric-series $\tau^q$.
-Thus, the parameter $\tau$ controls how fast the density influence attenuates towards the past.
+Equation \@ref(eq:state) is structurally equivalent to a $Q$-order AR model; however, we expressed the part of AR parameters as a geometric-series $\tau^q$ to reduce the number of parameters (our model has two AR parameters $\xi_{2,s}$ and $\tau$ regardless of order $Q$).
+The parameter $\tau$ controls how fast the density influence attenuates towards the past [@takagiTimescaleDependencyHost2015].
 In this study, we set $Q=3$ given the life span of the study species (typically 1 -- 3 years).
@@
 We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0 --1 and indicates over- (\~0.00), under- (\~1.00), or suitable-fitting (\~0.50) to the data.
-A Bayesian p-value for our state-space models was `r op(min(df_bp$mean))`, indicating that our model specification is appropriate.
+A Bayesian p-value for our state-space models was `r op(round(df_bp$mean, 2))`, indicating that our model specification is appropriate.
 
@@
 
-**Priors.** Vague priors were assigned to most parameters: $\text{Normal(0, 10)}$ for regression coefficients ($\gamma$ and $\gamma'$) and means ($\theta_{\beta}$ and $\pmb{\theta_{\xi}}$), $\text{Half-student's}~t(0, 2.5, 6)$ for SDs ($\sigma_{\beta}$, $\sigma_{\text{obs},s}$, $\sigma_{\text{state},s}$, $\sigma_{\text{obs},i}$, $\sigma_{\text{state},i}$ $\sigma_{\lambda}$, $\sigma_{\gamma}$, and $\sigma_{\epsilon,i}$), $\text{scaled-Inv-Wishart}(\pmb{\phi})$ ($\pmb{\phi}$ is a vector of prior scales $\pmb{\phi}=\{2.5,...,2.5\}$) with the degrees of freedom = 2 for variance-covariance matrices ($\pmb{\Omega_{\xi}}$, $\pmb{\Omega_y}$, and $\pmb{\Omega_{\varepsilon}}$), and $\text{Normal}(0, 1)$ for latent factors ($\zeta_{t,d}$).
-We used multiplicative gamma priors with parameters $\nu = 3$, $a_1=2$, and $a_2=3$ (see Durante [@duranteNoteMultiplicativeGamma2017] for interpretation) for latent factors ($\delta_{d,i}$) following Ovaskainen *et al.* [@ovaskainenHowAreSpecies2017].
-We assigned a weakly informative priors to initial fish densities $\text{ln}~n_{i,t}$ ($t = 1, 2, 3$) using $\text{Student's}~t(-2, 2, 6)$ to enhance model convergence.
-
 **Model fitting.** We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
-We assigned weakly informative priors to parameters (**Table S6**).
+We assigned vague or weakly informative priors to parameters (**Table S3**).
 Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
-The total MCMC iteration was XXX.
-Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached \< 1.1 [@gelmanDataAnalysisUsing2007].
+The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc)` to `r max(df_mcmc$n_total_mcmc)`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period.
+Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached $<1.1$ [@gelmanDataAnalysisUsing2007].
 Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021].
@@
 
-# Figure S1-6
+# Figure S1-8
 ## load figures
@@
 
-# Figure S7-9
+# Figure S9-11
 ## load figures
 source(here::here("code/si_figure_obs_dyns.R"))
-j <- 6
+j <- 8
 
@@
 
-## Figure S10 Environmental variables
+## Figure S12 Environmental variables
 
-```{r figure_s10, fig.width=11, fig.height=8}
+```{r figure_s12, fig.width=11, fig.height=8}
 
@@
 
-## Figure S11 Correlation plot
+## Figure S13 Correlation plot
 
-```{r figure_s11, fig.width=11, fig.height=11}
+```{r figure_s13, fig.width=11, fig.height=11}
 

### 2022-09-27 code/si_figure_obs_dyns.R
Update si_figure_obs_dyns.R

@@ -17,6 +17,9 @@ df0 <- readRDS(file = here::here("output/summary_ssm_ar3.rds")) %>%
   mutate(est_density = exp(median),
          river = str_to_sentence(river))
 
+Group <- unique(df0$group) %>% 
+  sort()
+
 ## plot
 source(here::here("code/set_figure_theme.R"))
 theme_set(plt_theme)
@@ -24,7 +27,7 @@ theme_set(plt_theme)
 list_g_dyns <- foreach(i = seq_len(length(unique(df0$group)))) %do% {
   
   g <- df0 %>% 
-    filter(group == unique(df0$group)[i]) %>% 
+    filter(group == Group[i]) %>% 
     ggplot() + 
     geom_line(aes(x = year_id_numeric + 1998,
                   y = est_density,
@@ -39,7 +42,8 @@ list_g_dyns <- foreach(i = seq_len(length(unique(df0$group)))) %do% {
     ylab(expression("Density (ind."~m^-2*")")) +
     xlab("Year") +
     labs(color = "Site") +
-    theme_bw()
+    theme_bw() +
+    theme(strip.background = element_blank())
   
   ggsave(g,
          filename = here::here(paste0("output/figure_obs_dyn_",

### 2022-09-27 code/table_prior.R
edit: tables

@@ -18,7 +18,7 @@ df_prior <- tibble(Model = c(rep("State space (AR model)", 8),
                      "$\\sigma_{\\text{obs},s}$",
                      "$\\sigma_{\\text{state},s}$",
                      "$\\Omega_{\\xi}$",
-                     "$\\ln*n_{s,1-3}$",
+                     "$\\ln n_{s,1-3}$",
                      
                      "$\\sigma_{\\text{obs},i}$",
                      "$\\sigma_{\\text{state},i}$",
@@ -30,7 +30,7 @@ df_prior <- tibble(Model = c(rep("State space (AR model)", 8),
                      "$p_{\\alpha}^{\\text{inter}}$",
                      "$\\zeta_{t,d}$",
                      "$\\delta_{d,i}$",
-                     "$\\ln*n_{i,1}$",
+                     "$\\ln n_{i,1}$",
                      
                      "$\\gamma$",
                      "$\\gamma'$",

### 2022-09-27 code/table_ssm.R

@@ -39,11 +39,14 @@ df_ssm <- list.files(path = here::here("output"),
                                param_name == "sd_b" ~ "$\\sigma_{\\beta}$"),
          parameter = factor(parameter,
                             levels = p_level),
-         estimate = paste0(op(median),
-                           " [", op(lower),
-                           " to ",
-                           op(upper), "]")) %>%
-  dplyr::select(group, parameter, estimate) %>% 
+         estimate = paste0("$",
+                           op(median),
+                           "$"),
+         "95% CI" = paste0("$",
+                          op(lower), "~\\text{to}~", op(upper),
+                          "$")) %>%
+  dplyr::select(group, parameter, estimate, "95% CI") %>% 
   arrange(group, parameter) %>% 
   mutate(group = replace(group, duplicated(group), values = NA)) %>% 
-  rename_with(.fn = str_to_sentence)
+  rename_with(.cols = -"95% CI",
+              .fn = str_to_sentence)

### 2022-09-27 code/figure_theory.R
Update figure_theory.R

@@ -14,7 +14,7 @@ df0 <- sim_result %>%
   pivot_longer(cols = mean_density:cv,
                names_to = "response",
                values_to = "value") %>% 
-  filter(r1 == min(sim_result$r1),
+  filter(r1 == 1.5,
          sd_env == max(sim_result$sd_env), # sd_env = 0.75
          alpha == min(sim_result$alpha), # alpha = 0.25
          phi == min(sim_result$phi), # phi = 0.5

### 2022-09-27 rmd/supporting_info.Rmd
Update supporting_info.Rmd
rmd

@@
 
-Parameter values used in the main and sensitivity analysis. Five hundred parameter values were drawn randomly from uniform distributions in the sensitivity analysis.
+Parameter values used in the whole community simulation.
 
@@
 
-Median estimates of the Bayesian state-space model. Numbers in parenthesis indicate 95% credible intervals. Site-specific parameters were excluded due to a large number of parameters.
+Median estimates of the Bayesian state-space model. Site-specific parameters were excluded due to a large number of parameters.
 
@@
 knitr::kable(df_ssm,
-             align = c(rep("l", 3), "c"),
+             align = c(rep("l", 2), rep("c", 2)),
              format = "markdown")
@@
 
-                       "\n```{r figure_s", i + j,", fig.width = 9.5, fig.height = 8}
+                       "\n```{r figure_s", i + j,", fig.width = 10, fig.height = 7}
                        \n\n
@@
 
-c_text <- c("whole community",
-            "masu salmon",
-            "unenhanced species")
+c_text <- tibble(Group) %>% 
+  mutate(text = case_when(Group == "all" ~ "whole community",
+                          Group == "masu_salmon" ~ "masu salmon",
+                          Group == "other" ~ "unenhanced species")) %>% 
+  pull(text)
 

### 2022-09-28 code/table_prior.R
Update table_prior.R

@@ -54,12 +54,12 @@ df_prior <- tibble(Model = c(rep("State space (AR model)", 8),
                              "Beta(1, 1)",
                              "Beta(1, 1)",
                              "Normal(0, 1)",
-                             "Multiplicative gamma prior",
+                             "Multiplicative gamma prior ($\\nu = 3$, $a_1 = 2$, $a_2 = 3$)",
                              "Half-t(-2, 2, 6)",
                              
                              "Normal(0, 10)",
                              "Normal(0, 10)",
-                             "Dirichlet(1,...,$S_w$)",
+                             "Dirichlet(1,...,1) for $s' = 1,...,S_w$)",
                              "Scaled Inv-Wishart($\\pmb{\\phi}$)"),
                    ) %>% 
   mutate(Model = replace(Model, duplicated(Model), NA))

### 2022-09-28 code/set_rmd.R
Create set_rmd.R

@@ -1,0 +1,94 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+
+source(here::here("code/library.R"))
+source(here::here("code/set_functions.R"))
+
+knitr::opts_chunk$set(echo = FALSE,
+                      message = FALSE,
+                      warning = FALSE)
+
+options(knitr.kable.NA = '')
+
+
+# theory ------------------------------------------------------------------
+
+cols <- c(
+  "n_species",
+  "k",
+  "r_type",
+  "r1",
+  "r_min",
+  "r_max",
+  "sd_env",
+  "phi",
+  "int_type",
+  "alpha",
+  "model",
+  "seed")
+
+list_sim <- list(readRDS(here::here("output/result_ricker_2sp.rds")),
+                 readRDS(here::here("output/result_ricker.rds")))
+
+list_param <- list_sim %>% 
+  lapply(FUN = function(x) {
+    n_sim <- x %>% 
+      mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
+      pull(n_sim) %>% 
+      unique()
+    
+    param_set <- x %>% 
+      dplyr::select(which(colnames(x) %in% cols)) %>% 
+      distinct()
+    
+    attr(param_set, "n_sim") <- n_sim
+    return(param_set)
+  })
+
+
+# empirical ---------------------------------------------------------------
+
+## raw data
+source(here::here("code/data_fmt_fishdata.R"))
+source(here::here("code/data_fmt_reg.R"))
+
+df_area <- d0 %>% 
+  group_by(site_id, year) %>% 
+  summarize(area = unique(area))
+
+## ssm estimate
+df_bp <- list.files(path = here::here("output"),
+                    full.names = T,
+                    pattern = "summary_ssm_ar") %>% 
+  readRDS() %>% 
+  filter(param == "bp_value") %>% 
+  dplyr::select(mean)
+
+## mcmc sample size
+
+df_mcmc <- lapply(c("summary_ssm_ar", "summary_reg", "summary_multi_ricker"),
+                  function(x) {
+                    list.files(path = here::here("output"),
+                               full.names = T,
+                               pattern = x) %>% 
+                      readRDS() %>% 
+                      ungroup() %>% 
+                      dplyr::select(n_total_mcmc,
+                                    n_sample,
+                                    n_thin,
+                                    n_burn) %>% 
+                      distinct() %>% 
[…]

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-# setup ####
-source(here::here("code/library.R"))
-source(here::here("code/set_functions.R"))
-
-knitr::opts_chunk$set(echo = FALSE,
-                      message = FALSE,
-                      warning = FALSE)
-
-options(knitr.kable.NA = '')
-
-# theory ####
-cols <- c(
-  "n_species",
-  "k",
-  "r_type",
-  "r1",
-  "r_min",
-  "r_max",
-  "sd_env",
-  "phi",
-  "int_type",
-  "alpha",
-  "model",
-  "seed")
-
-list_sim <- list(readRDS(here::here("output/result_ricker_2sp.rds")),
-                   readRDS(here::here("output/result_ricker.rds")))
-
-list_param <- list_sim %>% 
-  lapply(FUN = function(x) {
-      n_sim <- x %>% 
-        mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
-        pull(n_sim) %>% 
-        unique()
-
-      param_set <- x %>% 
-        dplyr::select(which(colnames(x) %in% cols)) %>% 
-        distinct()
-
-      attr(param_set, "n_sim") <- n_sim
-      return(param_set)
-  })
-
-# empirical data ####
-
-## raw data
-source(here::here("code/data_fmt_fishdata.R"))
-source(here::here("code/data_fmt_reg.R"))
-
-df_area <- d0 %>% 
-  group_by(site_id, year) %>% 
-  summarize(area = unique(area))
-
-## ssm estimate
-df_bp <- list.files(path = here::here("output"),
-                    full.names = T,
-                    pattern = "summary_ssm_ar") %>% 
-  readRDS() %>% 
-  filter(param == "bp_value") %>% 
-  dplyr::select(mean)
-
-## mcmc sample size
-
-df_mcmc <- lapply(c("summary_ssm_ar", "summary_reg", "summary_multi_ricker"),
-       function(x) {
-         list.files(path = here::here("output"),
-                    full.names = T,
-                    pattern = x) %>% 
-           readRDS() %>% 
-           ungroup() %>% 
-           dplyr::select(n_total_mcmc,
-                         n_sample,
-                         n_thin,
-                         n_burn) %>% 
-           distinct() %>% 
-           mutate(model = str_extract(x, "ssm|reg|ricker"))
-       }) %>% 
-  bind_rows()
-
-## release data
-source(here::here("code/data_fmt_stock.R"))
-
-df_stock_stage <- df_stock %>% 
-  group_by(release_stage) %>% 
-  summarize(stock = sum(abundance)) %>% 
-  mutate(ratio = stock / max(stock),
-         prop = stock / sum(stock))
-
+suppressMessages(source(here::here("code/set_rmd.R")))
 ```
@@
 **Species interaction.** We analyzed a subset of our data to estimate the strength of interspecific interactions among stream fishes.
-In this analysis, we focused on `r n_distinct(df_complete$site_id)` sites with (1) \> 16 years of observations and (2) no intentional release of masu salmon.
+In this analysis, we focused on `r n_distinct(df_complete$site_id)` sites with $>16$ years of observations and no intentional release of masu salmon.
 These additional constraints were necessary to estimate parameters in a complex multi-species model within a state-space modeling framework.
@@
 This model structure has a merit of reduced number of parameters while capturing the correlated nature of environmental noises [@ovaskainenHowAreSpecies2017].
-We set $D=2$ when the number of species in a community is greater than four, otherwise $D=1$.
+We set $D=2$ in our model.
 We reported the estimates of $\alpha_{ij}$ so the values are comparable to those used in the theoretical analysis.
@@
 # Table S1
-source(here::here("code/table_param_set.R"))
+suppressMessages(source(here::here("code/table_param_set.R")))
 knitr::kable(df_param, format = "markdown")
@@
 # Table S2
-source(here::here("code/table_species_list.R"))
+suppressMessages(source(here::here("code/table_species_list.R")))
 
@@
 # Table S6
-source(here::here("code/table_prior.R"))
+suppressMessages(source(here::here("code/table_prior.R")))
 
@@
 
-Median estimates of the Bayesian state-space model. Site-specific parameters were excluded due to a large number of parameters.
+Median estimates of the Bayesian state-space model.
+See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
+The parameter $\pmb{\phi}$ is a vector of prior scales ($\pmb{\phi}=2.5,...,2.5$).
+Site-specific parameters were excluded due to a large number of parameters.
 
@@
 # Table S7
-source(here::here("code/table_ssm.R"))
+suppressMessages(source(here::here("code/table_ssm.R")))
 
@@
 ## load regression tables
-source(here::here("code/table_reg.R"))
+suppressMessages(source(here::here("code/table_reg.R")))
 j <- 7
@@
 ## load figures
-source(here::here("code/si_figure_theory.R"))
+suppressMessages(source(here::here("code/si_figure_theory.R")))
 
@@
 ## load figures
-source(here::here("code/si_figure_obs_dyns.R"))
+suppressMessages(source(here::here("code/si_figure_obs_dyns.R")))
 j <- 8
@@
 
-source(here::here("code/si_figure_env.R"))
+suppressMessages(source(here::here("code/si_figure_env.R")))
 
@@
 
-source(here::here("code/si_figure_cor.R"))
+suppressMessages(source(here::here("code/si_figure_cor.R")))
 ```

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
   bookdown::pdf_document2:
+    number_sections: false
     latex_engine: xelatex
@@
   - \pagenumbering{gobble}
-  - \usepackage{amsmath}
+  - \usepackage{amsmath,fancyhdr, caption}
+  - \captionsetup{width=1.3\linewidth, labelfont={bf}}
+  - \pagestyle{fancy}
 bibliography: reference.bib
@@
 \pagenumbering{arabic}
+\def\figurename{Figure S\hspace{-.6ex}}
+\def\tablename{Table S\hspace{-.6ex}}
 ```
@@
 
-## Table S3 Priors
-
-Prior distributions used in the Bayesian models.
+## Priors
 
@@
 knitr::kable(df_prior,
-             format = "markdown")
+             format = "markdown",
+             caption = "Prior distributions used in the Bayesian models.
+See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
+The parameter $\\pmb{\\phi}$ is a vector of prior scales ($\\pmb{\\phi}=2.5,...,2.5$).")
 
@@
 
-## Table S4 Parameter estimates of the Bayesian state-space model
-
-Median estimates of the Bayesian state-space model.
-See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
-The parameter $\pmb{\phi}$ is a vector of prior scales ($\pmb{\phi}=2.5,...,2.5$).
-Site-specific parameters were excluded due to a large number of parameters.
+## Parameter estimates of the Bayesian state-space model
 
@@
              align = c(rep("l", 2), rep("c", 2)),
-             format = "markdown")
+             format = "markdown",
+             caption = "Median estimates of the Bayesian state-space model. Site-specific parameters were excluded due to a large number of parameters.")
 

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
   bookdown::pdf_document2:
+    fig_caption: true
     number_sections: false
@@
   - \pagestyle{fancy}
+  - \fancyhead[L]{}
+  - \fancyhead[C]{}
+  - \setlength{\headheight}{13.7pt}
 bibliography: reference.bib
@@
 With this formulation, the matrix $\pmb{\Omega_{\varepsilon}}$ can be described as $\pmb{\Omega_{\varepsilon}}=\pmb{\Delta}^T\pmb{\Delta} + \text{diag}(\sigma_{\epsilon,i}^2)$, where $\pmb{\Delta}$ is the matrix of factor loadings $\delta_{d,i}$.
-This model structure has a merit of reduced number of parameters while capturing the correlated nature of environmental noises [@ovaskainenHowAreSpecies2017].
+This model structure has a merit of reduced number of parameters while capturing the correlated nature of species responses to environmental fluctuations [@ovaskainenHowAreSpecies2017].
 We set $D=2$ in our model.
@@
 
-## Table S1 Simulation parameter
+## Simulation parameter
 
-Parameter values used in the whole community simulation.
+```{r tab_para}
 
-```{r table_s1}
-
-# Table S1
 suppressMessages(source(here::here("code/table_param_set.R")))
-knitr::kable(df_param, format = "markdown")
+knitr::kable(df_param,
+             format = "markdown",
+             caption = "Parameter values used in the whole community simulation.")
 
@@
 
-## Table S2 Observed species
+## Observed species
 
-Fish species found in the study watersheds.
+```{r tab_splist}
 
-```{r table_s2}
-
-# Table S2
 suppressMessages(source(here::here("code/table_species_list.R")))
@@
 knitr::kable(df_sp_list,
-             format = "markdown")
+             format = "markdown",
+             caption = "Fish species found in the study watersheds.")
 ```
@@
 
-```{r table_s3}
+```{r tab_prior}
 
-# Table S6
 suppressMessages(source(here::here("code/table_prior.R")))
@@
 
-## Parameter estimates of the Bayesian state-space model
+## Parameter estimates for the Bayesian state-space model
 
-```{r table_s7}
+```{r tab_ssm}
 
-# Table S7
 suppressMessages(source(here::here("code/table_ssm.R")))
@@
 
-# Table S8-10
 ## load regression tables
@@
 
-## common text
-table_legend <- "Median estimates and standard errors (SEs) of regression coefficients are shown.
-Pr(> 0) and Pr(< 0) represent the proportion of positive and negative estimates in MCMC samples, respectively (i.e., posterior probability)."
-
-table_reg_chunk <- knit_chunk <- NULL
+table_reg_chunk <- knit_chunk <- table_legend <- NULL
 
@@
 
-  knit_chunk <- paste0("## Table S", i + j, " Parameter estimates for the regression model (", c_text[i], ") \n",
-                       table_legend,
-                       "\n```{r table_s", i + j,"}
+  table_legend[i] <- paste0("Parameter estimates for the regression model (", c_text[i], ").
+Median estimates and standard errors (SEs) of regression coefficients are shown.
+Pr(> 0) and Pr(< 0) represent the proportion of positive and negative estimates in MCMC samples, respectively (i.e., posterior probability).")
+
+  knit_chunk <- paste0("## Parameter estimates for the regression model (", c_text[i], ")",
+                       "\n```{r tab_reg", i, "}
                        \n\n
                        kable(list_reg[[",i,"]],
-                             align = c(rep('l', 3), rep('c', 4)),
-                             format = 'markdown')
+                             align = c(rep('l', 2), 'r', rep('c', 3)),
+                             format = 'markdown',
+                             caption = table_legend[",i,"])
                        \n\n
@@
 
-j <- 0
-figure_sim_chunk <- knit_chunk <- NULL
+figure_sim_chunk <- knit_chunk <- cap <- NULL
 
@@
 
-  knit_chunk <- paste0("## Figure S", i + j,
-                       " Theoretical prediction (",
+  cap[i] <- paste0("Theoretical predictions for the release effect on community dynamics.
+Rows represent different response variables, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
+Other parameters are: ",
+                       "number of species $S$ = ", df_param$n_species[i], "; intrinsic growth rate of an enhanced species $r_1$ = ", df_param$r1[i], "; maximum intrinsic growth rate of unenhanced species $r_{max}$ = ", df_param$r_max[i], "; environmental stochasticity $\\sigma_{\\varepsilon}$ = ", df_param$sd_env[i], "; carrying capacity $K$ = ", df_param$k[i], ".")
+
+  knit_chunk <- paste0("## Theoretical prediction (",
                        "$r_1$ = `r df_param$r1[",i,"]`, ",
                        "$K$ = `r df_param$k[",i,"]`) \n",
-
-                       "\n```{r figure_s", i + j,", fig.width = 10, fig.height = 7}
+                       "\n```{r fig_sim", i,", fig.width = 10, fig.height = 7, fig.cap = cap[", i, "]}
                        \n\n
@@
                        ```\n",
-
-                       "Theoretical predictions for the release effect on community dynamics.
-Rows represent different response variables, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
-Other parameters are: ",
-                       "number of species $S$ = `r df_param$n_species[",i,"]`; ",
-                       "intrinsic growth rate of an enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
-                       "maximum intrinsic growth rate of unenhanced species $r_{max}$ = `r df_param$r_max[",i,"]`; ",
-                        "environmental stochasticity $\\sigma_{\\varepsilon}$ = `r df_param$sd_env[",i,"]`; ",
-                        "carrying capacity $K$ = `r df_param$k[",i,"]`.",
                         "\n\\pagebreak\n")
@@
 
-```{r figure_dyns}
+```{r fig_dyns}
 
@@
 suppressMessages(source(here::here("code/si_figure_obs_dyns.R")))
-j <- 8
 
@@
 
-figure_dyns_chunk <- knit_chunk <- NULL
+figure_dyns_chunk <- knit_chunk <- cap <- NULL
 
@@
 
-  knit_chunk <- paste0("## Figure S", i + j,
-                       " Temporal dynamics of stream fish communities (`r c_text[",i,"]`) \n",
+  cap[i] <- paste0("Temporal dynamics of stream fish communities (", c_text[i], ") in Hokkaido, Japan.
+Dots represent observed density, and solid lines are the predicted values of the Bayesian state-space model.
+Panels correspond to individual watersheds, and colors distinguish sampling sites within a watershed.")
 
-                       "\n```{r figure_s", i + j,", fig.width = 11, fig.height = 11}
+  knit_chunk <- paste0(
+    "## Temporal dynamics of stream fish communities (`r c_text[",i,"]`)\n",
+    "\n```{r fig_d", i,", fig.width = 10, fig.height = 7, fig.cap=cap[", i ,"]}
     \n\n
@@
     ```\n",
-                       "Temporal dynamics of stream fish communities (`r c_text[",i,"]`) in Hokkaido, Japan.
-Dots represent observed density, and solid lines are the predicted values of the Bayesian state-space model.
-Panels correspond to individual watersheds, and colors distinguish sampling sites within a watershed.",
     "\n\\pagebreak\n")
@@
 
-## Figure S12 Environmental variables
+## Environmental variables
 
-```{r figure_s12, fig.width=11, fig.height=8}
+```{r fig_env, fig.width=11, fig.height=8, fig.cap="Distribution of environmental variables in the protected watershed.
+Note that the number of fish released and ocean productivity (chlorophyll a) are measured at the watershed level while others are measured at the site level."}
 
@@
 
-Distribution of environmental variables in the protected watershed.
-Note that the number of fish released and ocean productivity (chlorophyll *a*) are measured at the watershed level while others are measured at the site level.
-
 \newpage
 
-## Figure S13 Correlation plot
+## Correlation plot
 
-```{r figure_s13, fig.width=11, fig.height=11}
+```{r fig_cor, fig.width=11, fig.height=11, fig.cap="Correlation plot among environmental variables in the protected watersheds. Numbers indicate Spearman's rank correlations."}
 
@@
 
-Correlation plot among environmental variables in the protected watersheds. Numbers indicate Spearman's rank correlations.
-
 \newpage

### 2022-09-28 code/set_rmd.R
Update set_rmd.R

@@ -8,7 +8,8 @@ source(here::here("code/set_functions.R"))
 
 knitr::opts_chunk$set(echo = FALSE,
                       message = FALSE,
-                      warning = FALSE)
+                      warning = FALSE,
+                      eval.after = "fig.cap") # to embed codes in fig.cap
 
 options(knitr.kable.NA = '')
 

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
+<!--# Figure S1 -->
+
+```{r fig_2sp}
+
+cap <- paste0("(A) Spearman's rank correlations between intentional release and community dynamics in a strong cometition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").
+Rows distinguish different summary statistics of community dynamics (top: CV, middle: mean, bottom: SD) while columns distinguish deterministic ($\\sigma_{\\varepsilon}=$ ", min(list_param[[1]]$sd_env) ,") and stochastic simulations ($\\sigma_{\\varepsilon}=$ ", max(list_param[[1]]$sd_env) ,").
+Cells indicate 400 combinations of carrying capacity and intrinsic growth rate (20 values each).
+Colors are proportional to Spearman's rank correlations.
+Dots indicate parameter combinations that are used in the whole community simulation.
+(B) Examples of community dynamics with and without intentional release.
+Community dynamics diverge at the broken vertical lines, the time step at which intentional release begins.
+Rows distinguish intrinsic growth rates while columns distinguish deterministic and stochastic simulations.
+Colors indicate release levels, and line types differ in carrying capacities.")
+
+source(here::here("code/figure_theory_2sp.R"))
+
+figure_sim2sp <- paste0("## Theoretical prediction (2-species community)",
+                        "\n```{r fig_sim2sp, fig.width = 10, fig.height = 8, fig.cap = cap}
+                       \n\n
+                       print(list_g_c[[2]])
+                       \n\n
+                       ```\n",
+                        "\n\\pagebreak\n")
+```
+
+`r paste(knitr::knit(text = figure_sim2sp), collapse = '\n')`
+
+<!--# Figure S2-S9 -->
+
 ```{r figure_sim}
 
-# Figure S1-8
 ## load figures
@@
 
+<!--# Figure S10-12 -->
+
 ```{r fig_dyns}
 
-# Figure S9-11
 ## load figures
@@
 
+## Empirical estimates of competition coefficients
+
+```{r fig_int, fig.width=11, fig.height=11, fig.cap="Estimates of competition coefficients $\\alpha_{ij}$ in a multi-species Ricker model.
+Panels distinguish sites, and values in each cell indicate median estimates of $\\alpha_{ij}$ for a given pair of species.
+Cells are colored in proportion to $\\alpha_{ij}$."}
+
+source(here::here("code/si_figure_species_int.R"))
+print(g_alpha_site)
+```
+
+\newpage
+
 # References

### 2022-09-28 code/figure_theory_2sp.R
minor

@@ -1,7 +1,6 @@
 
 # setup -------------------------------------------------------------------
 
-rm(list = ls())
 source(here::here("code/library.R"))
 source(here::here("code/set_figure_theme.R"))
 

### 2022-09-28 code/table_prior.R

@@ -1,7 +1,6 @@
 
 # setup -------------------------------------------------------------------
 
-rm(list = ls())
 pacman::p_load(tidyverse)
 
 

### 2022-09-28 code/table_ssm.R

@@ -1,7 +1,6 @@
 
 # setup -------------------------------------------------------------------
 
-rm(list = ls())
 lapply(paste0("code/", c("library.R", "set_functions.R")),
        FUN = function(x) source(here::here(x)))
 

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-```{r tab_para}
+```{r tab-para}
 
@@
 
-```{r tab_splist}
+```{r tab-splist}
 
@@
 
-```{r tab_prior}
+```{r tab-prior}
 
@@
 
-```{r tab_ssm}
+```{r tab-ssm}
 
@@
   knit_chunk <- paste0("## Parameter estimates for the regression model (", c_text[i], ")",
-                       "\n```{r tab_reg", i, "}
+                       "\n```{r tab-reg", i, "}
                        \n\n
@@
 
-<!--# Figure S1 -->
+## Theoretical prediction (2-species community)
 
-```{r fig_2sp}
-
-cap <- paste0("(A) Spearman's rank correlations between intentional release and community dynamics in a strong cometition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").
+```{r fig-2sp, fig.width=11, fig.height=8, fig.cap = paste0("(A) Spearman's rank correlations between intentional release and community dynamics in a strong cometition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").
 Rows distinguish different summary statistics of community dynamics (top: CV, middle: mean, bottom: SD) while columns distinguish deterministic ($\\sigma_{\\varepsilon}=$ ", min(list_param[[1]]$sd_env) ,") and stochastic simulations ($\\sigma_{\\varepsilon}=$ ", max(list_param[[1]]$sd_env) ,").
@@
 Rows distinguish intrinsic growth rates while columns distinguish deterministic and stochastic simulations.
-Colors indicate release levels, and line types differ in carrying capacities.")
+Colors indicate release levels, and line types differ in carrying capacities.")}
 
 source(here::here("code/figure_theory_2sp.R"))
-
-figure_sim2sp <- paste0("## Theoretical prediction (2-species community)",
-                        "\n```{r fig_sim2sp, fig.width = 10, fig.height = 8, fig.cap = cap}
-                       \n\n
 print(list_g_c[[2]])
-                       \n\n
-                       ```\n",
-                        "\n\\pagebreak\n")
 ```
 
-`r paste(knitr::knit(text = figure_sim2sp), collapse = '\n')`
+\newpage
 
@@
 
-```{r figure_sim}
+```{r figure-sim}
 
@@
                        "$K$ = `r df_param$k[",i,"]`) \n",
-                       "\n```{r fig_sim", i,", fig.width = 10, fig.height = 7, fig.cap = cap[", i, "]}
+                       "\n```{r fig-sim", i,", fig.width = 10, fig.height = 7, fig.cap = cap[", i, "]}
                        \n\n
@@
 
-```{r fig_dyns}
+```{r fig-dyns}
 
@@
     "## Temporal dynamics of stream fish communities (`r c_text[",i,"]`)\n",
-    "\n```{r fig_d", i,", fig.width = 10, fig.height = 7, fig.cap=cap[", i ,"]}
+    "\n```{r fig-d", i,", fig.width = 10, fig.height = 7, fig.cap=cap[", i ,"]}
     \n\n
@@
 
-```{r fig_env, fig.width=11, fig.height=8, fig.cap="Distribution of environmental variables in the protected watershed.
+```{r fig-env, fig.width=11, fig.height=8, fig.cap="Distribution of environmental variables in the protected watershed.
 Note that the number of fish released and ocean productivity (chlorophyll a) are measured at the watershed level while others are measured at the site level."}
@@
 
-```{r fig_cor, fig.width=11, fig.height=11, fig.cap="Correlation plot among environmental variables in the protected watersheds. Numbers indicate Spearman's rank correlations."}
+```{r fig-cor, fig.width=11, fig.height=11, fig.cap="Correlation plot among environmental variables in the protected watersheds. Numbers indicate Spearman's rank correlations."}
 
@@
 
-```{r fig_int, fig.width=11, fig.height=11, fig.cap="Estimates of competition coefficients $\\alpha_{ij}$ in a multi-species Ricker model.
+```{r fig-int, fig.width=11, fig.height=11, fig.cap="Estimates of competition coefficients $\\alpha_{ij}$ in a multi-species Ricker model.
 Panels distinguish sites, and values in each cell indicate median estimates of $\\alpha_{ij}$ for a given pair of species.

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 knitr::kable(df_ssm,
-             align = c(rep("l", 2), rep("c", 2)),
+             align = c(rep("l", 2), rep("r", 2)),
              format = "markdown",
@@
                        kable(list_reg[[",i,"]],
-                             align = c(rep('l', 2), 'r', rep('c', 3)),
+                             align = c(rep('l', 2), rep('r', 4)),
                              format = 'markdown',
@@
 
-```{r fig-2sp, fig.width=11, fig.height=8, fig.cap = paste0("(A) Spearman's rank correlations between intentional release and community dynamics in a strong cometition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").
+```{r fig-2sp, fig.width=11, fig.height=8, fig.cap = paste0("Theoretical predictions in a 2-species community.
+**(A)** Spearman's rank correlations between intentional release and community dynamics in a strong competition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").
 Rows distinguish different summary statistics of community dynamics (top: CV, middle: mean, bottom: SD) while columns distinguish deterministic ($\\sigma_{\\varepsilon}=$ ", min(list_param[[1]]$sd_env) ,") and stochastic simulations ($\\sigma_{\\varepsilon}=$ ", max(list_param[[1]]$sd_env) ,").
@@
 Dots indicate parameter combinations that are used in the whole community simulation.
-(B) Examples of community dynamics with and without intentional release.
+**(B)** Examples of community dynamics with and without intentional release.
 Community dynamics diverge at the broken vertical lines, the time step at which intentional release begins.

### 2022-09-28 rmd/README.Rmd
readme

---
title: README
output: github_document
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = here::here())
      })
---

```{r, include=F}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

## Article Information

Title: Intentional release of native species undermines ecological stability
Authors: Akira Terui, Hirokazu Urabe, Masayuki Senzaki, Bungo Nishizawa

## Contents

```{r}
source(here::here("code/set_readme.R"))
knitr::kable(tbl_readme)
```

## Session Information

```{r}
sessionInfo()
```

### 2022-09-28 code/table_prior.R
tables

@@ -43,7 +43,7 @@ df_prior <- tibble(Model = c(rep("AR model", 9),
                              "Half-t(0, 2.5, 6)",
                              "Half-t(0, 2.5, 6)",
                              "Half-t(0, 2.5, 6)",
-                             "Scaled Inv-Wishart_2($\\pmb{\\phi}$)",
+                             "Scaled Inv-Wishart$_2$($\\pmb{\\phi}$)",
                              "Half-t(0, 2.5, 6)",
                              
                              "Half-t(0, 2.5, 6)",
@@ -51,7 +51,7 @@ df_prior <- tibble(Model = c(rep("AR model", 9),
                              "Half-t(0, 2.5, 6)",
                              "Half-t(0, 2.5, 6)",
                              "Half-t(0, 2.5, 6)",
-                             "Scaled Inv-Wishart_2($\\pmb{\\phi}$)",
+                             "Scaled Inv-Wishart$_2$($\\pmb{\\phi}$)",
                              "Beta(1, 1)",
                              "Beta(1, 1)",
                              "Normal(0, 1)",
@@ -61,6 +61,6 @@ df_prior <- tibble(Model = c(rep("AR model", 9),
                              "Normal(0, 10)",
                              "Normal(0, 10)",
                              "Dirichlet(1,...,1)",
-                             "Scaled Inv-Wishart_2($\\pmb{\\phi}$)"),
+                             "Scaled Inv-Wishart$_2$($\\pmb{\\phi}$)"),
                    ) %>% 
   mutate(Model = replace(Model, duplicated(Model), NA))

### 2022-09-28 code/table_ricker.R

@@ -13,39 +13,18 @@ p_level <- c("$\\theta_{\\beta}$",
              "$\\theta_{\\xi2}$",
              "$\\tau$")
 
-df_ssm <- list.files(path = here::here("output"),
-                     full.names = T,
-                     pattern = "summary_ssm_ar") %>% 
+df_ricker <- list.files(path = here::here("output"),
+                        full.names = T,
+                        pattern = "summary_multi_ricker") %>% 
   readRDS() %>%
-  ungroup() %>% 
-  filter(param_name %in% c("nu0",
-                           "mu_xi",
-                           "mu_b",
-                           "sd_b")) %>% 
-  dplyr::select(param_name,
-                param,
-                group,
-                median = `50%`,
-                lower = `2.5%`,
-                upper = `97.5%`) %>% 
-  mutate(group = replace_na(group, "masu_salmon"),
-         group= case_when(group == "masu_salmon" ~ "Enhanced (masu salmon)",
-                          group == "other" ~ "Unenhanced"),
-         parameter = case_when(param_name == "nu0" ~ "$\\tau$",
-                               str_detect(param, "mu_xi\\[1,.\\]") ~ "$\\theta_{\\xi1}$",
-                               str_detect(param, "mu_xi\\[2,.\\]") ~ "$\\theta_{\\xi2}$",
-                               param_name == "mu_b" ~ "$\\theta_{\\beta}$",
-                               param_name == "sd_b" ~ "$\\sigma_{\\beta}$"),
-         parameter = factor(parameter,
-                            levels = p_level),
-         estimate = paste0("$",
-                           op(median),
-                           "$"),
-         "95% CI" = paste0("$",
-                           op(lower), "~\\text{to}~", op(upper),
-                           "$")) %>%
-  dplyr::select(group, parameter, estimate, "95% CI") %>% 
-  arrange(group, parameter) %>% 
-  mutate(group = replace(group, duplicated(group), values = NA)) %>% 
-  rename_with(.cols = -"95% CI",
-              .fn = str_to_sentence)
+  filter(param_name %in% c("p0")) %>% 
+  arrange(param) %>% 
+  transmute(Parameter = case_when(param == "p0[1]" ~ "$p_{\\alpha}^{\\text{Intra}}$",
+                                  param == "p0[2]" ~ "$p_{\\alpha}^{\\text{Inter}}$"),
+            Site = str_to_sentence(site),
+            Estimate = paste0("$", op(median), "$"),
[…]

### 2022-09-28 code/table_ssm_ar.R

@@ -13,9 +13,9 @@ p_level <- c("$\\theta_{\\beta}$",
              "$\\theta_{\\xi2}$",
              "$\\tau$")
 
-df_ssm <- list.files(path = here::here("output"),
-                     full.names = T,
-                     pattern = "summary_ssm_ar") %>% 
+df_ssm_ar <- list.files(path = here::here("output"),
+                        full.names = T,
+                        pattern = "summary_ssm_ar") %>% 
   readRDS() %>%
   ungroup() %>% 
   filter(param_name %in% c("nu0",
@@ -42,8 +42,8 @@ df_ssm <- list.files(path = here::here("output"),
                            op(median),
                            "$"),
          "95% CI" = paste0("$",
-                          op(lower), "~\\text{to}~", op(upper),
-                          "$")) %>%
+                           op(lower), "~\\text{to}~", op(upper),
+                           "$")) %>%
   dplyr::select(group, parameter, estimate, "95% CI") %>% 
   arrange(group, parameter) %>% 
   mutate(group = replace(group, duplicated(group), values = NA)) %>% 

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 \pagenumbering{arabic}
-\def\figurename{Figure S\hspace{-.6ex}}
-\def\tablename{Table S\hspace{-.6ex}}
+\def\figurename{Figure S\hspace{-.4ex}}
+\def\tablename{Table S\hspace{-.4ex}}
 ```
@@
 The rest of the simulation procedure is identical to the two-species model.
-We summarized values of simulation parameters in **Table S1**.
+We summarized values of simulation parameters in **Table S**\@ref(tab:tab-para).
 
@@
 Summed abundance of first and second passes was used in the following analysis.
-**Table S5** summarizes observed species in these watersheds.
+**Table S**\@ref(tab:tab-splist) summarizes observed species in these watersheds.
 
@@
 For a whole community, we summed the densities of enhanced and unenhanced species.
-We summarized the reconstructed community dynamics in **Figures S7 -- S9**.
+We summarized the reconstructed community dynamics in **Figures S**\@ref(fig:fig-d1) -- **S**\@ref(fig:fig-d3).
 
@@
 Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
-Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**).
+Urban and agricultural land use were omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)).
 The watershed-specific intercept was related to watershed-level predictors as:
@@
 **Model fitting.** We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
-We assigned vague or weakly informative priors to parameters (**Table S3**).
+We assigned vague or weakly informative priors to parameters (**Table S**\@ref(tab:tab-prior)).
 Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
@@
 Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021].
-Parameter estimates were summarized in **Table S7 -- S10**.
+Parameter estimates were summarized in **Tables S**\@ref(tab:tab-reg1) -- S\@ref(tab:tab-reg3).
 
@@
 
-## Parameter estimates for the Bayesian state-space model
+## Parameter estimates for the state-space autoregressive model
 
-```{r tab-ssm}
+```{r tab-ssm-ar}
 
-suppressMessages(source(here::here("code/table_ssm.R")))
+suppressMessages(source(here::here("code/table_ssm_ar.R")))
 
-knitr::kable(df_ssm,
+knitr::kable(df_ssm_ar,
              align = c(rep("l", 2), rep("r", 2)),
              format = "markdown",
-             caption = "Median estimates of the Bayesian state-space model. Site-specific parameters were excluded due to a large number of parameters.")
+             caption = "Median estimates for key parameters of the state-space autoregressive model. Site-specific parameters were excluded due to a large number of parameters.")
+
+```
+
+\newpage
+
+## Parameter estimates for the state-space Ricker model
+
+```{r tab-ricker}
+
+suppressMessages(source(here::here("code/table_ricker.R")))
+
+knitr::kable(df_ricker,
+             align = c(rep("l", 2), rep("r", 2)),
+             format = "markdown",
+             caption = "Median estimates for key parameters of the state-space Ricker model. Site-specific parameters were excluded due to a large number of parameters.")
 

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012].
+We employed a multi-species Ricker model [@fowlerSpeciesDynamicsAlter2012].
 In the basic formula without intentional release, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 
-Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` time steps of community dynamics for $100$ values of release level $R$ (0 to 500 with an equal interval).
-We introduced 50 individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` time steps (initialization).
-After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(list_sim[[1]]$n_burnin)` time steps to reach new equilibrium with intentional release (burn-in period).
-We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` time steps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$: the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
+Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` timesteps of community dynamics for $100$ values of release level $R$ (0 to 500 with an equal interval).
+We introduced 50 individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` timesteps (initialization).
+After the initialization period, we released $R$ individuals of the enhanced species every timestep over the next `r unique(list_sim[[1]]$n_burnin)` timesteps to reach a new equilibrium with the intentional release (burn-in period).
+We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` timesteps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$: the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
 
@@
 
-As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` time steps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
-In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every 10 time steps to account for possible complex dynamics of a ten-species community.
+As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` timesteps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
+In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community.
 The rest of the simulation procedure is identical to the two-species model.
@@
 Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
-We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
+We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds ten years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
 As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019.
-Summed abundance of first and second passes was used in the following analysis.
+The summed abundance of first and second passes was used in the following analysis.
 **Table S**\@ref(tab:tab-splist) summarizes observed species in these watersheds.
@@
 where $\xi_{1,s}$ is the site-specific constant at site $s$, $\xi_{2,s}$ the parameter characterizing an autoregressive (AR) process, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
-The parameters $\xi_{1,s}$ and $\xi_{2,s}$ were drawn from a multi-variate normal distribution as $\pmb{\xi} \sim \text{MVN}(\pmb{\theta_{\xi}}, \pmb{\Omega_{\xi}})$, where $\pmb{\xi}$ is the matrix of $\xi_{1,s}$ and $\xi_{2,s}$.
+The parameters $\xi_{1,s}$ and $\xi_{2,s}$ were drawn from a multivariate normal distribution as $\pmb{\xi} \sim \text{MVN}(\pmb{\theta_{\xi}}, \pmb{\Omega_{\xi}})$, where $\pmb{\xi}$ is the matrix of $\xi_{1,s}$ and $\xi_{2,s}$.
 Equation \@ref(eq:state) is structurally equivalent to a $Q$-order AR model; however, we expressed the part of AR parameters as a geometric-series $\tau^q$ to reduce the number of parameters (our model has two AR parameters $\xi_{2,s}$ and $\tau$ regardless of order $Q$).
@@
 
-We used linear regression to quantify the impact of intentional release on community dynamics.
+We used linear regression to quantify the impact of the intentional release on community dynamics.
 Although our focus is intentional release, each model included climatic and local abiotic variables to account for important environmental differences among sites.
@@
 In the poisson model for species richness, $\exp(\varepsilon_{\lambda,s})$ is the error term accounting for overdispersion ($\varepsilon_{\lambda,s} \sim \text{Normal}(0, \sigma_{\lambda}^2)$).
-In the multi-variate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multi-variate normal distribution with the variance-covariance matrix $\pmb{\Omega_y}$.
+In the multivariate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multivariate normal distribution with the variance-covariance matrix $\pmb{\Omega_y}$.
 The expected means $\lambda_{y,s}$ and $\pmb{\theta_s}$ were related to linear predictors as follows:
@@
 In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$.
-The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be a unity because non-negligible portion of release may escape into unsurveyed areas.
-Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **Model fitting**).
+The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas.
+Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **model fitting**).
 Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
-Urban and agricultural land use were omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)).
+Urban and agricultural land use was omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)).
 The watershed-specific intercept was related to watershed-level predictors as:
@@
 
-Since the CV is a additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation \@ref(eq:model):
+Since the CV is an additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation \@ref(eq: model):
 
@@
 With this formulation, the matrix $\pmb{\Omega_{\varepsilon}}$ can be described as $\pmb{\Omega_{\varepsilon}}=\pmb{\Delta}^T\pmb{\Delta} + \text{diag}(\sigma_{\epsilon,i}^2)$, where $\pmb{\Delta}$ is the matrix of factor loadings $\delta_{d,i}$.
-This model structure has a merit of reduced number of parameters while capturing the correlated nature of species responses to environmental fluctuations [@ovaskainenHowAreSpecies2017].
+This model structure has the merit of the reduced number of parameters while capturing the correlated nature of species responses to environmental fluctuations [@ovaskainenHowAreSpecies2017].
 We set $D=2$ in our model.
-We reported the estimates of $\alpha_{ij}$ so the values are comparable to those used in the theoretical analysis.
+We reported the estimates of $\alpha_{ij}$, so the values are comparable to those used in the theoretical analysis.
 
@@
 **(B)** Examples of community dynamics with and without intentional release.
-Community dynamics diverge at the broken vertical lines, the time step at which intentional release begins.
-Rows distinguish intrinsic growth rates while columns distinguish deterministic and stochastic simulations.
+Community dynamics diverge at the broken vertical lines, the timestep at which intentional release begins.
+Rows distinguish intrinsic growth rates, while columns distinguish deterministic and stochastic simulations.
 Colors indicate release levels, and line types differ in carrying capacities.")}
@@
   cap[i] <- paste0("Theoretical predictions for the release effect on community dynamics.
-Rows represent different response variables, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
+Rows represent different response variables, and columns show distinct simulation scenarios with different strengths of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
 Other parameters are: ",

### 2022-09-28 rmd/supporting_info.Rmd
edit: misc

@@
   - \captionsetup{width=1.3\linewidth, labelfont={bf}}
-  - \pagestyle{fancy}
-  - \fancyhead[L]{}
-  - \fancyhead[C]{}
-  - \setlength{\headheight}{13.7pt}
 bibliography: reference.bib
@@
 \newpage
+\pagestyle{fancy}
+\fancyhead[L]{Terui et al.}
+\fancyhead[C]{}
+\setlength{\headheight}{13.7pt}
 \pagenumbering{arabic}
@@
 Specifically, we examined the release effect with $20$ parameter values of intrinsic population growth rate $r_i$ ($0.5$ to $3.5$ with an equal interval) and carrying capacity $K$ ($50$ to $500$ with an equal interval), resulting in $400$ parameter combinations.
-In a single-species Ricker model, the chosen range of $r_i$ can generate stable equilibrium, damped oscillations, limit cycle, and chaos (XXX).
+In a single-species Ricker model, the chosen range of $r_i$ can generate stable equilibrium, damped oscillations, limit cycle, and chaos [@sunDynamicBehaviorsRicker2000].
 For simplicity, we assumed $r_1 = r_2$.
@@
 Urban and agricultural land use was omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)).
-The watershed-specific intercept was related to watershed-level predictors as:
+The watershed-specific intercept was related to a watershed-level predictor as:
 
@@
 Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
-The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
+The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictor cannot capture.
 
-Since the CV is an additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation \@ref(eq: model):
+Since the CV is an additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation \@ref(eq:model):
 
@@
 Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021].
-Parameter estimates were summarized in **Tables S**\@ref(tab:tab-reg1) -- S\@ref(tab:tab-reg3).
+Parameter estimates were summarized in **Tables S**\@ref(tab:tab-ssm-ar) -- **S**\@ref(tab:tab-reg3).
 
@@
 See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
-The parameter $\\pmb{\\phi}$ is a vector of prior scales ($\\pmb{\\phi}=2.5,...,2.5$).")
+The parameter $\\pmb{\\omicron}$ is a vector of prior scales ($\\pmb{\\omicron}=2.5,...,2.5$).")
 
@@
 
-## Theoretical prediction (2-species community)
+## Theoretical prediction (two-species community)
 
-```{r fig-2sp, fig.width=11, fig.height=8, fig.cap = paste0("Theoretical predictions in a 2-species community.
+```{r fig-2sp, fig.width=12, fig.height=8, fig.cap = paste0("Theoretical predictions in a two-species community.
 **(A)** Spearman's rank correlations between intentional release and community dynamics in a strong competition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").
@@
 
-  cap[i] <- paste0("Theoretical predictions for the release effect on community dynamics.
+  cap[i] <- paste0("Theoretical predictions for the release effect in a ten-species community.
 Rows represent different response variables, and columns show distinct simulation scenarios with different strengths of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
@@
                        "$K$ = `r df_param$k[",i,"]`) \n",
-                       "\n```{r fig-sim", i,", fig.width = 10, fig.height = 7, fig.cap = cap[", i, "]}
+                       "\n```{r fig-sim", i,", fig.width = 10, fig.height = 8.5, fig.cap = cap[", i, "]}
                        \n\n
@@
 
-```{r fig-int, fig.width=11, fig.height=11, fig.cap="Estimates of competition coefficients $\\alpha_{ij}$ in a multi-species Ricker model.
+```{r fig-int, fig.width=7, fig.height=7, fig.cap="Estimates of competition coefficients $\\alpha_{ij}$ in a multi-species Ricker model.
 Panels distinguish sites, and values in each cell indicate median estimates of $\\alpha_{ij}$ for a given pair of species.
@@
 source(here::here("code/si_figure_species_int.R"))
-print(g_alpha_site)
+knitr::include_graphics(here::here("output/figure_alpha_site.pdf"))
 ```

### 2022-09-28 code/si_figure_theory.R

@@ -15,10 +15,10 @@ df0 <- sim_result %>%
   pivot_longer(cols = mean_density:cv,
                names_to = "response",
                values_to = "value") %>% 
-  filter(response %in% c("n_sp_persist", "cv", "mean_density", "sd_density")) %>% 
+  filter(response %in% c("n_sp_last", "cv", "mean_density", "sd_density")) %>% 
   filter(!(response == "cv" & status != "all")) %>%
-  filter(!(response == "n_sp_persist" & status != "all")) %>%
-  mutate(response_name = case_when(response == "n_sp_persist" ~ "Number~of~species~persist",
+  filter(!(response == "n_sp_last" & status != "all")) %>%
+  mutate(response_name = case_when(response == "n_sp_last" ~ "Number~of~species~persist",
                                    response == "cv" ~ "CV~sigma/mu",
                                    response == "mean_density" ~ "Mean~mu~(ind.)",
                                    response == "sd_density" ~ "SD~sigma~(ind.)"),

### 2022-09-28 code/table_prior.R

@@ -43,7 +43,7 @@ df_prior <- tibble(Model = c(rep("AR model", 9),
                              "Half-t(0, 2.5, 6)",
                              "Half-t(0, 2.5, 6)",
                              "Half-t(0, 2.5, 6)",
-                             "Scaled Inv-Wishart$_2$($\\pmb{\\phi}$)",
+                             "Scaled Inv-Wishart$_2$($\\pmb{\\omicron}$)",
                              "Half-t(0, 2.5, 6)",
                              
                              "Half-t(0, 2.5, 6)",
@@ -51,7 +51,7 @@ df_prior <- tibble(Model = c(rep("AR model", 9),
                              "Half-t(0, 2.5, 6)",
                              "Half-t(0, 2.5, 6)",
                              "Half-t(0, 2.5, 6)",
-                             "Scaled Inv-Wishart$_2$($\\pmb{\\phi}$)",
+                             "Scaled Inv-Wishart$_2$($\\pmb{\\omicron}$)",
                              "Beta(1, 1)",
                              "Beta(1, 1)",
                              "Normal(0, 1)",
@@ -61,6 +61,6 @@ df_prior <- tibble(Model = c(rep("AR model", 9),
                              "Normal(0, 10)",
                              "Normal(0, 10)",
                              "Dirichlet(1,...,1)",
-                             "Scaled Inv-Wishart$_2$($\\pmb{\\phi}$)"),
+                             "Scaled Inv-Wishart$_2$($\\pmb{\\omicron}$)"),
                    ) %>% 
   mutate(Model = replace(Model, duplicated(Model), NA))

### 2022-09-28 code/table_ricker.R

@@ -7,20 +7,14 @@ lapply(paste0("code/", c("library.R", "set_functions.R")),
 
 # data --------------------------------------------------------------------
 
-p_level <- c("$\\theta_{\\beta}$",
-             "$\\sigma_{\\beta}$",
-             "$\\theta_{\\xi1}$",
-             "$\\theta_{\\xi2}$",
-             "$\\tau$")
-
 df_ricker <- list.files(path = here::here("output"),
                         full.names = T,
                         pattern = "summary_multi_ricker") %>% 
   readRDS() %>%
   filter(param_name %in% c("p0")) %>% 
   arrange(param) %>% 
-  transmute(Parameter = case_when(param == "p0[1]" ~ "$p_{\\alpha}^{\\text{Intra}}$",
-                                  param == "p0[2]" ~ "$p_{\\alpha}^{\\text{Inter}}$"),
+  transmute(Parameter = case_when(param == "p0[1]" ~ "$p_{\\alpha}^{\\text{intra}}$",
+                                  param == "p0[2]" ~ "$p_{\\alpha}^{\\text{inter}}$"),
             Site = str_to_sentence(site),
             Estimate = paste0("$", op(median), "$"),
             "95% CI" = paste0("$", 

### 2022-09-28 rmd/supporting_info.Rmd
edit: misc

@@
     fig_caption: true
-    number_sections: false
+    number_sections: true
     latex_engine: xelatex
@@
 With this formulation, the matrix $\pmb{\Omega_{\varepsilon}}$ can be described as $\pmb{\Omega_{\varepsilon}}=\pmb{\Delta}^T\pmb{\Delta} + \text{diag}(\sigma_{\epsilon,i}^2)$, where $\pmb{\Delta}$ is the matrix of factor loadings $\delta_{d,i}$.
-This model structure has the merit of the reduced number of parameters while capturing the correlated nature of species responses to environmental fluctuations [@ovaskainenHowAreSpecies2017].
+This model structure with multiplicative gamma priors on factor loadings [@duranteNoteMultiplicativeGamma2017] has the merit of the reduced number of parameters while capturing the correlated nature of species responses to environmental fluctuations [@ovaskainenHowAreSpecies2017].
 We set $D=2$ in our model.

### 2022-09-28 code/si_figure_theory.R
misc

@@ -59,7 +59,7 @@ list_g_theory <- foreach(i = seq_len(nrow(df_param))) %do% {
                x = stock,
                color = group_id,
                fill = group_id)) +
-    geom_smooth(size= 1,
+    geom_smooth(size= 0.6,
                 method = "loess") +
     scale_color_hue(labels = c("Whole", "Enhanced", "Unenhanced")) +
     labs(x = "Number of releases (individuals)",

### 2022-09-29 code/data_fmt_trait.R
edit: trait data

@@ -12,39 +12,12 @@ source(here::here("code/set_functions.R"))
 ## trophic guild - herbivore = 1; detritivore = 2; omnivore = 3; invertivore = 4; invertivore-piscivore = 5
 ## spawning substrate - vegetation = 1; mineral substrate = 2; various = 3
 
-### fish shape, species-level average
-df_fs_sp <- read_csv(here::here("data_raw/data_fish_shapes.csv")) %>% 
-  rename_with(.fn = str_to_lower) %>% 
-  group_by(tree_name) %>% 
-  summarize(across(.fns = function(x) mean(x, na.rm = T),
-                   .cols = where(is.numeric))) %>% 
-  pivot_longer(cols = where(is.numeric),
-               names_to = "trait",
-               values_to = "value")
-
-### fish shape, genus-level average
-df_fs_genus <- read_csv(here::here("data_raw/data_fish_shapes.csv")) %>% 
-  rename_with(.fn = str_to_lower) %>% 
-  separate(tree_name,
-           into = c("genus", "species"),
-           sep = "_",
-           remove = FALSE) %>% 
-  group_by(genus) %>% 
-  summarize(across(.fns = function(x) mean(x, na.rm = T),
-                   .cols = where(is.numeric))) %>% 
-  pivot_longer(cols = where(is.numeric),
-               names_to = "trait",
-               values_to = "genus_value")
-
 df_trait <- read_csv(here::here("data_raw/data_trait_full.csv"))
-
 skimr::skim(df_trait)
 
 
 # summarize trait ---------------------------------------------------------
 
-## -  substitute FishShape values with genus mean only if no species-level value
-##    available within the genus
 ## -  Pseudorasbora spp; data from Pseudorasbora parva were used
 
 ## long format
@@ -53,14 +26,6 @@ df_trait_l <- df_trait %>%
            into = c("genus", "species"),
            sep = "_",
            remove = FALSE) %>% 
-  left_join(df_fs_genus,
-            by = c("genus", "trait")) %>%
-  group_by(genus) %>% 
-  mutate(fishshape = ifelse(trait %in% unique(df_fs_sp$trait), 1, 0),
-         value = ifelse(str_detect(taxon, "spp|Rhynchocypris") & fishshape == 1,
-                        genus_value,
-                        value)) %>% 
-  ungroup() %>% 
   group_by(taxon, trait) %>% 
   summarize(value = f_num(value),
             source = source,
[…]

### 2022-09-29 code/table_species_list.R

@@ -7,11 +7,14 @@ pacman::p_load(tidyverse)
 # data --------------------------------------------------------------------
 
 source(here::here("code/data_fmt_fishdata.R"))
+df_trait <- readRDS(here::here("data_fmt/data_trait.rds"))
 
 df_sp_list <- df_selected %>% 
   filter(abundance > 0) %>% 
   group_by(taxon) %>% 
   summarise(n_site = n_distinct(site_id)) %>% 
+  ungroup() %>% 
+  left_join(df_trait, by = "taxon") %>% 
   mutate(taxon = str_replace_all(taxon,
                                  pattern = "_",
                                  replacement = " "),
@@ -22,5 +25,10 @@ df_sp_list <- df_selected %>%
          taxon = str_replace(taxon,
                              pattern = "\\sspp.*",
                              replacement = "* spp.")) %>% 
-  rename(Taxon = taxon,
-         'Number of sites observed' = n_site)
+  rename('Number of sites observed' = n_site) %>%
+  mutate(across(.fns = str_replace_all,
+                pattern = "_",
+                replace = " ")) %>% 
+  rename_with(.fn = function(x) str_to_sentence(x) %>%
+                str_replace_all(pattern = "_",
+                                replace = " ")) %>% view

### 2022-09-29 code/table_species_list.R
Update table_species_list.R

@@ -11,9 +11,7 @@ df_trait <- readRDS(here::here("data_fmt/data_trait.rds"))
 
 df_sp_list <- df_selected %>% 
   filter(abundance > 0) %>% 
-  group_by(taxon) %>% 
-  summarise(n_site = n_distinct(site_id)) %>% 
-  ungroup() %>% 
+  distinct(taxon) %>% 
   left_join(df_trait, by = "taxon") %>% 
   mutate(taxon = str_replace_all(taxon,
                                  pattern = "_",
@@ -25,10 +23,13 @@ df_sp_list <- df_selected %>%
          taxon = str_replace(taxon,
                              pattern = "\\sspp.*",
                              replacement = "* spp.")) %>% 
-  rename('Number of sites observed' = n_site) %>%
   mutate(across(.fns = str_replace_all,
                 pattern = "_",
                 replace = " ")) %>% 
   rename_with(.fn = function(x) str_to_sentence(x) %>%
                 str_replace_all(pattern = "_",
-                                replace = " ")) %>% view
+                                replace = " ")) %>% 
+  rename("Current preference" = Current,
+         "Max total length (mm)" = "Max total length")
+
+  

### 2022-09-29 rmd/supporting_info.Rmd
misc
Update supporting_info.Rmd
rmd

@@
 In this analysis, we focused on `r n_distinct(df_complete$site_id)` sites with $>16$ years of observations and no intentional release of masu salmon.
+Further, at each site, we confined our analysis to species that occurred more than four times.
 These additional constraints were necessary to estimate parameters in a complex multi-species model within a state-space modeling framework.
@@
              format = "markdown",
-             caption = "Fish species found in the study watersheds.")
+             caption = "Fish species found in the study watersheds.
+Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge.")
 ```
@@
 Rows represent different response variables, and columns show distinct simulation scenarios with different strengths of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$).
+Lines are loess curves (mean) with shades indicating associated 95% confidence intervals.
 Other parameters are: ",

### 2022-09-29 code/table_species_list.R
Update table_species_list.R

@@ -7,7 +7,11 @@ pacman::p_load(tidyverse)
 # data --------------------------------------------------------------------
 
 source(here::here("code/data_fmt_fishdata.R"))
-df_trait <- readRDS(here::here("data_fmt/data_trait.rds"))
+df_trait <- readRDS(here::here("data_fmt/data_trait.rds")) %>% 
+  mutate(body_size = case_when(max_total_length < 100 ~ "small",
+                               between(max_total_length, 100, 200) ~ "medium",
+                               max_total_length > 200 ~ "large")) %>% 
+  dplyr::select(-max_total_length)
 
 df_sp_list <- df_selected %>% 
   filter(abundance > 0) %>% 
@@ -29,7 +33,6 @@ df_sp_list <- df_selected %>%
   rename_with(.fn = function(x) str_to_sentence(x) %>%
                 str_replace_all(pattern = "_",
                                 replace = " ")) %>% 
-  rename("Current preference" = Current,
-         "Max total length (mm)" = "Max total length")
+  rename("Current preference" = Current)
 
   

### 2022-09-29 rmd/supporting_info.Rmd
rmd

@@
              caption = "Fish species found in the study watersheds.
-Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge.")
+Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge.
+Body size is categoraized as follows: total length (TL) $< 100$ mm (small), $100\\le$  TL $\\le 200$ (medium), and TL $> 200$ (large).")
 ```

### 2022-09-29 rmd/supporting_info.Rmd
rmd

@@
 Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge.
-Body size is categoraized as follows: total length (TL) $< 100$ mm (small), $100\\le$  TL $\\le 200$ (medium), and TL $> 200$ (large).")
+Body size is coded as follows: maximum total length (TL) $< 100$ mm (S), $100\\le$  TL $\\le 200$ (M), and TL $> 200$ (L).")
 ```
@@
 source(here::here("code/figure_theory_2sp.R"))
-print(list_g_c[[2]])
+knitr::include_graphics(here::here("output/figure_2sp_model_strong.pdf"))
 ```
@@
 
-<!--# Figure S2-S9 -->
+<!--# Figure for the whole community simulation -->
 

### 2022-09-29 code/figure_theory_2sp.R
edit: figure

@@ -146,8 +146,8 @@ list_g_c <- foreach(x = 1:length(v_alpha)) %do% {
   
   ggsave(g_c,
          filename = here::here(paste0("output/figure_2sp_model_", lbs[x], ".pdf")),
-         height = 8.5,
-         width = 15)
+         height = 10,
+         width = 13)
   
   return(g_c)  
 }

### 2022-09-29 code/si_figure_species_int.R

@@ -124,7 +124,7 @@ g_alpha_site <- df_plot %>%
              fill = value,
              label = sprintf("%.2f", value))) +
   geom_tile() +
-  geom_text(size = 3) +
+  geom_text(size = 2) +
   facet_wrap(facets = ~site_id,
              scales = "free",
              nrow = 3,
@@ -148,8 +148,8 @@ g_alpha_site <- df_plot %>%
 
 ggsave(g_alpha_site,
        filename = here::here("output/figure_alpha_site.pdf"),
-       height = 10,
-       width = 11)
+       height = 9,
+       width = 10)
 
 ggsave(g_alpha,
        filename = here::here("output/figure_alpha_dist.pdf"),

### 2022-09-29 code/set_functions.R
Update set_functions.R

@@ -91,7 +91,7 @@ spabb <- function(x, sep = "\\s") {
     
     if (length(q) > 1) {
       ## length > 1
-      if (any(str_detect(q, "spp|sp"))) {
+      if (any(str_detect(q, "(spp$)|(sp$)"))) {
         ## sp or spp
         z <- paste(str_to_sentence(q[1]),
                    paste0(na.omit(str_extract(q, "(^sp{1,2})$")),

### 2022-09-29 code/si_figure_co.R
Create si_figure_co.R

@@ -1,0 +1,87 @@
+
+# setup -------------------------------------------------------------------
+
+source(here::here("code/library.R"))
+source(here::here("code/set_functions.R"))
+
+
+# data --------------------------------------------------------------------
+
+source(here::here("code/data_fmt_fishdata.R"))
+
+m_co <- df_selected %>% 
+  group_by(taxon, site_id) %>% 
+  summarize(count = sum(abundance)) %>% 
+  ungroup() %>% 
+  mutate(psi = ifelse(count > 0, 1, 0)) %>% 
+  dplyr::select(-count) %>% 
+  pivot_wider(names_from = taxon,
+              values_from = psi,
+              names_prefix = "sp_") %>% 
+  dplyr::select(starts_with("sp_")) %>% 
+  data.matrix() %>% 
+  crossprod()
+
+m_co[upper.tri(m_co)] <- NA
+m_cop <- m_co / n_distinct(df_selected$site_id)
+
+df_cop <- m_cop %>% 
+  as_tibble() %>% 
+  mutate(species_1 = colnames(.)) %>% 
+  pivot_longer(cols = !starts_with("species"),
+               names_to = "species_2",
+               values_to = "p") %>% 
+  drop_na(p) %>% 
+  mutate(across(.col = where(is.character),
+                .fns = function(x) str_remove(x, "sp_") %>% 
+                  spabb(sep = "_"))) %>% 
+  mutate(lbs1 = ifelse(test = str_detect(species_1, "\\sspp\\."),
+                       yes = paste0('italic("',
+                                    str_remove(species_1, "\\sspp\\."),
+                                    '")~spp.'),
+                       no = paste0('italic("', species_1, '")')),
+         lbs2 = ifelse(test = str_detect(species_2, "\\sspp\\."),
+                       yes = paste0('italic("',
+                                    str_remove(species_2, "\\sspp\\."),
+                                    '")~spp.'),
+                       no = paste0('italic("', species_2, '")')))
+
+lbs1_level <- df_cop %>% 
+  group_by(lbs1) %>% 
+  tally() %>% 
+  arrange(n) %>% 
+  pull(lbs1)
+
+lbs2_level <- df_cop %>% 
+  group_by(lbs2) %>% 
+  tally() %>% 
+  arrange(desc(n)) %>% 
+  pull(lbs2)
+
+g_co <- df_cop %>% 
+  ggplot(aes(y = factor(lbs1, levels = rev(lbs1_level)),
[…]

### 2022-09-29 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-```{r fig-2sp, fig.width=12, fig.height=8, fig.cap = paste0("Theoretical predictions in a two-species community.
+```{r fig-2sp, fig.width=9, fig.height=9, fig.cap = paste0("Theoretical predictions in a two-species community.
 **(A)** Spearman's rank correlations between intentional release and community dynamics in a strong competition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").
@@
 
+## Co-occurrence matrix
+
+```{r fig-co, fig.cap="Co-occurrence matrix of stream fishes at 97 sites.
+Values in each cell indicate the proportion of co-occurrence for a given pair of species (off-diagonal) or the propotion of sites occurred for a given species (diagonal).
+Colors are proportional to the values."}
+
+source(here::here("code/si_figure_co.R"))
+knitr::include_graphics(here::here("output/figure_co.pdf"))
+```
+
+\newpage
+
 ## Empirical estimates of competition coefficients

### 2022-09-29 rmd/manuscript.Rmd
Squashed commit of the following:
commit c274913bbbf475b2379bfd5ff5714134b1c4d743
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Sep 14 12:52:06 2022 -0400

    edit: rmd misc

commit b83fa58b0ac121cf4f89fff102048b2ff07a3b1e
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:49 2022 -0400

    Update mcmc_trace_reg.pdf

commit 184921982330ea83d449b2fe44159659f9c52210
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:45 2022 -0400

    edit: misc

commit aaac7131a165551933b99ae948f54d710a673206
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:32 2022 -0

@@
 output:
-  pdf_document:
-    latex_engine: xelatex
-  #word_document:
-  # reference_docx: word_format.docx
+  #bookdown::pdf_document2:
+  #  latex_engine: xelatex
+  bookdown::word_document2:
+   reference_docx: word_format.docx
 csl: pnas.csl
 knit: (function(inputFile, encoding) {
-        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
+        rmarkdown::render(inputFile,
+                          encoding = encoding, 
+                          output_dir = "document_output")
       })
@@
 
-# setup
-knitr::opts_chunk$set(echo = TRUE)
-pacman::p_load(tidyverse)
-op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x)
-
-# theory ####
-load(here::here("result/result_ricker.RData"))
-
-n_sim <- sim_result %>% 
-  mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
-  pull(n_sim) %>% 
-  unique()
-
-param_set <- sim_result %>% 
-  distinct(n_species,
-           k,
-           r_type,
-           r1,
-           r_min,
-           r_max,
-           sd_env,
-           phi,
-           int_type,
-           alpha,
-           model,
-           seed)
-
-# empirical data ####
-source(here::here("code/data_fmt_fishdata.R"))
-source(here::here("code/data_fmt_analysis.R"))
-
-df_area <- d0 %>% 
-  group_by(site_id, year) %>% 
-  summarize(area = unique(area))
-
-filename <- list.files(path = here::here("result"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "reg")) %>% 
-  filter(!str_detect(string = .$value, pattern = "reg_rich")) %>% 
-  pull()
-
-df_beta <- lapply(filename, function(x) {
-  read_csv(here::here(x)) %>% 
-    filter(parameter == "b[2]")
-})
-names(df_beta) <- str_extract(filename, "all|masu|other")
-
-## ssm estimate
-df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      filter(param == "bp_value") %>% 
-      select(mean) %>% 
-      mutate(group = str_extract(x, "all|masu|other"))
-  }) %>% 
-  bind_rows()
-
-## mcmc sample size
-df_mcmc_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      select(n_total_mcmc,
-             n_sample,
-             n_thin,
-             n_burn) %>% 
-      distinct()
-  }) %>% 
-  bind_rows()
-
-df_mcmc_reg <- list.files(path = here::here("result"), full.names = T) %>% 
-  as_tibble() %>% 
-  filter(str_detect(string = .$value, pattern = "reg_")) %>% 
-  filter(!str_detect(string = .$value, pattern = "rich")) %>% 
-  pull() %>% 
-  lapply(function(x) {
-    read_csv(x) %>% 
-      select(n_total_mcmc,
-             n_sample,
-             n_thin,
-             n_burn) %>% 
-      distinct()
-  }) %>% 
-  bind_rows()
-
-## release data
-source(here::here("code/data_fmt_stock.R"))
-
-df_stock_stage <- df_stock %>% 
-  group_by(release_stage) %>% 
-  summarize(stock = sum(abundance)) %>% 
-  mutate(ratio = stock / max(stock),
-         prop = stock / sum(stock))
+suppressMessages(source(here::here("code/set_rmd.R")))
 
@@
 $$
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp\left[r_i\left(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i}\right)\right]~exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp\left[r_i\left(1-\frac{\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i}\right)\right]~exp(\epsilon_{i,t})
 $$

### 2022-10-01 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010].
-Captive breeding is a form of the efforts to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-Although releases of captive-bred native species ("intentional release") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010].
-In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018].
-The widespread use of captive breeding is perhaps because of the "myth" that the demographic benefits of released individuals may exceed the associated risks.
+Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
+The magnitude of intentional release for commercial and recreational species is massive; typically, a single program releases tens of thousands to millions of plant, invertebrate (bivalves @haagNorthAmericanFreshwater2012, insects), and vertebrate individuals (fish, birds) into the wild annually (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]).
+There is growing awareness that intentional release entails ecological risks, including the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007], the spread of diseases and parasites in wild populations [@krkosekDecliningWildSalmon2007], and the intensification of intraspecific competition within the enhanced species.
+Yet, this method is still pervasive in natural resource management likely because of the apparent economic benefit of release programs.
+For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed economic performance of release programs for 12 major fishery resources -- the gross monetary yield exceeded the per-seed cost in nine species, suggesting that release programs are economically profitable in general.
 
@@
 Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability.
+In particular, the community-wide impact must be serious in release programs for fishery resouces as many of them release millions of hatchery individuals into a single water body (e.g., a watershed) every year, which is likely far beyond the environmental capacity of the recipient ecosystem.
 Evidence for this hypothesis is lacking, however.
@@
 
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the selective intentional release of a constituent species (species 1).
+We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the intentional release of a constituent species (species 1).
 Specifically, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 $$
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp\left[r_i\left(1-\frac{\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i}\right)\right]~exp(\epsilon_{i,t})
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)\exp\left[r_i\left(1-\frac{\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i}\right)\right]\exp(\varepsilon_{i,t})
 $$
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $Normal(0,\sigma_{\epsilon}^2)$.
-To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0.5,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$).
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $\text{Normal}(0,\sigma_{\varepsilon}^2)$.
+To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,2.5)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim \text{Exp}(1/\bar{\alpha})$).
 The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:

### 2022-10-02 rmd/supporting_info.Rmd
edit: si

@@
 
-Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` timesteps of community dynamics for $100$ values of release level $R$ (0 to 500 with an equal interval).
-We introduced 50 individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` timesteps (initialization).
+Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` timesteps of community dynamics for $100$ values of release level $R$ ($0$ to $500$ with an equal interval).
+We introduced $50$ individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` timesteps (initialization).
 After the initialization period, we released $R$ individuals of the enhanced species every timestep over the next `r unique(list_sim[[1]]$n_burnin)` timesteps to reach a new equilibrium with the intentional release (burn-in period).
@@
 
+# Supplementary text
+
+## Two-species model
+
+The analysis of a two-species community revealed the distinct parameter space predicting a stabilizing, neutral, or destabilizing effect of intentional release.
+The left column in **Figure S**\@ref(fig:fig-2sp-w)A) shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`).
+For lower values of intrinsic growth rate $r_i$ ($<1.5$), intentional release had neutral (with higher $K$) to destabilizing effects (with lower $K$) on community dynamics.
+In the meantime, stabilization with intentional release occurred for higher values of $r_i$ ($\ge 1.5$) by dampening limit cycles or chaos (**Figure S**\@ref(fig:fig-2sp-s)), which is reflected in decreased SD $\sigma$ (**Figure S**\@ref(fig:fig-2sp-w)).
+However, the long-term mean of community density $\mu$ consistently decreased with intentional release in almost all cases except for only a few combinations of $r_i$ and $K$ (**Figure S**\@ref(fig:fig-2sp-w)).
+Environmental stochasticity did not change the qualitative patterns of deterministic simulations but greatly expanded the parameter space with destabilizing effects of intentional release (the right columns in **Figure S**\@ref(fig:fig-2sp-w)**A and B**).
+Increasing the competition coefficient $\bar{\alpha}$ shifted the region with the destabilizing effects to higher carrying capacities ($\bar{\alpha}=$ `r max(list_param[[1]]$alpha)`, **Figure S**\@ref(fig:fig-2sp-s)); otherwise, general patterns were similar to the weak competition scenario.
+
+\newpage
+
 # Supplementary Tables
@@
 
-## Theoretical prediction (two-species community)
+## Theoretical prediction (two-species community with weak competition)
 
-```{r fig-2sp, fig.width=9, fig.height=9, fig.cap = paste0("Theoretical predictions in a two-species community.
+```{r fig-2sp-w, fig.width=9, fig.height=9, fig.cap = paste0("Theoretical predictions in a two-species community.
+**(A)** Spearman's rank correlations between intentional release and community dynamics in a weak competition scenario ($\\bar{\\alpha}=$ ", min(list_param[[1]]$alpha) ,").
+Rows distinguish different summary statistics of community dynamics (top: CV, middle: mean, bottom: SD) while columns distinguish deterministic ($\\sigma_{\\varepsilon}=$ ", min(list_param[[1]]$sd_env) ,") and stochastic simulations ($\\sigma_{\\varepsilon}=$ ", max(list_param[[1]]$sd_env) ,").
+Cells indicate 400 combinations of carrying capacity and intrinsic growth rate (20 values each).
+Colors are proportional to Spearman's rank correlations.
+Dots indicate parameter combinations that are used in the whole community simulation.
+**(B)** Examples of community dynamics with and without intentional release.
+Community dynamics diverge at the broken vertical lines, the timestep at which intentional release begins.
+Rows distinguish intrinsic growth rates, while columns distinguish deterministic and stochastic simulations.
+Colors indicate release levels, and line types differ in carrying capacities.")}
+
+source(here::here("code/figure_theory_2sp.R"))
+knitr::include_graphics(here::here("output/figure_2sp_model_weak.pdf"))
+```
+
+\newpage
+
+## Theoretical prediction (two-species community with strong competition)
+
+```{r fig-2sp-s, fig.width=9, fig.height=9, fig.cap = paste0("Theoretical predictions in a two-species community.
 **(A)** Spearman's rank correlations between intentional release and community dynamics in a strong competition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").

### 2022-10-02 code/table_species_list.R

@@ -27,6 +27,7 @@ df_sp_list <- df_selected %>%
          taxon = str_replace(taxon,
                              pattern = "\\sspp.*",
                              replacement = "* spp.")) %>% 
+  arrange(taxon) %>% 
   mutate(across(.fns = str_replace_all,
                 pattern = "_",
                 replace = " ")) %>% 
@@ -34,5 +35,5 @@ df_sp_list <- df_selected %>%
                 str_replace_all(pattern = "_",
                                 replace = " ")) %>% 
   rename("Current preference" = Current)
-
+  
   

### 2022-10-03 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 After the initialization period, we released $R$ individuals of the enhanced species every timestep over the next `r unique(list_sim[[1]]$n_burnin)` timesteps to reach a new equilibrium with the intentional release (burn-in period).
-We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` timesteps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$: the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
+We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` timesteps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$ ($S$: the number of species): the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
+The results of the two-species system were reported in [Supplementary Text].
 
@@
 
-# Supplementary text
+# Supplementary Text
 
@@
 However, the long-term mean of community density $\mu$ consistently decreased with intentional release in almost all cases except for only a few combinations of $r_i$ and $K$ (**Figure S**\@ref(fig:fig-2sp-w)).
-Environmental stochasticity did not change the qualitative patterns of deterministic simulations but greatly expanded the parameter space with destabilizing effects of intentional release (the right columns in **Figure S**\@ref(fig:fig-2sp-w)**A and B**).
+
+Environmental stochasticity did not change the qualitative patterns of deterministic simulations; however, it greatly expanded the parameter space with destabilizing effects of intentional release (the right columns in **Figure S**\@ref(fig:fig-2sp-w)**A and B**).
+In particular, destabilizing effects were more broadly observed when intrinsic growth rates were low.
+
 Increasing the competition coefficient $\bar{\alpha}$ shifted the region with the destabilizing effects to higher carrying capacities ($\bar{\alpha}=$ `r max(list_param[[1]]$alpha)`, **Figure S**\@ref(fig:fig-2sp-s)); otherwise, general patterns were similar to the weak competition scenario.

### 2022-10-03 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community.
+In addition, we defined a threshold density ($N_i = 0.01$) below which species are removed from the simulation (i.e., an absorbing condition) and are recorded as "extinct".
 The rest of the simulation procedure is identical to the two-species model.
@@
 The analysis of a two-species community revealed the distinct parameter space predicting a stabilizing, neutral, or destabilizing effect of intentional release.
-The left column in **Figure S**\@ref(fig:fig-2sp-w)A) shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`).
+The left column in **Figure S**\@ref(fig:fig-2sp-w)**A**) shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`).
 For lower values of intrinsic growth rate $r_i$ ($<1.5$), intentional release had neutral (with higher $K$) to destabilizing effects (with lower $K$) on community dynamics.

### 2022-10-03 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
    reference_docx: word_format.docx
-csl: pnas.csl
+csl: https://www.zotero.org/styles/pnas
 knit: (function(inputFile, encoding) {
@@
 
+## Theoretical prediction
+
 We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the intentional release of a constituent species (species 1).
@@
 
-We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios.
-These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Methods**).
-Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to intentional release: coefficient of variation (CV), number of species persist (defined as $N_i > 0.01$ at $t=1600$), temporal mean ($\mu$), and temporal SD ($\sigma$).
+Prior to our full-community analysis, we analyzed a two species community to understand the model behavior.
+The prior analysis revealed distinct parameter spaces predicting destabilizing, neutral, and stabilizing effects of intentional release on community dynamics.
+In general, intentional release had a neutral to destabilizing effect in a community with slow-growing species ($r_i < 1.5$).
+Meanwhile, for higher values of $r_i$ ($\ge 1.5$), intentional release stabilized community dynamics by dampening limit cycles or chaos.
+Carrying capacity and competition also played an important role in shaping the parameter spaces with different effects of intentional release.
+According to this result, we chose `r nrow(list_param[[2]])` simulation scenarios, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Methods**).
+Under each parameter scenario, we ran `r attr(list_param[[2]], "n_sim")` time steps of `r max(list_sim[[2]]$n_rep)` independent communities (i.e., simulation replicates).
+Using the last `r unique(list_sim[[2]]$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to intentional release: coefficient of variation (CV), number of species persist (defined as $N_i > 0.01$ for the entire simulation), temporal mean ($\mu$), and temporal SD ($\sigma$).
 We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.
 
-When carrying capacity was small ($K=100$), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
+When carrying capacity was small ($K=$ `r min(list_param[[2]]$k`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
 This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
@@
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
-These patterns were qualitatively similar across most ecological contexts (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S1-S3**).
+These patterns were qualitatively similar across most ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S1-S3**).
 
@@
 
-Intentional release, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S4-S6**).
-In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figure S4**).
-This result may explain why some of the best evidence for successful intentional release comes from long-lived endangered species [e.g., @jonesRestorationMauritiusKestrel1995].
-More importantly, the contrasting community response at different carrying capacities provides deeper insights.
-One of the core motivations for intentional release is to mitigate declining trends of natural resources due to human impacts, such as habitat loss [@chaseEcosystemDecayExacerbates2020].
-Ironically, our results suggest that intentional release will not bring desired outcomes unless we resolve root causes that compromise environmental capacity first.
+Intentional release, however, had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k`); **Figures S4-S6**).
+In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S4**).
+This pattern suggests that intentional release may be effective for species or in environments with limited intraspecific competition (= $r_1 K^{-1}$) and is consistent with the fact that some of the best evidence for successful intentional release comes from re-introduction/translocation programs of extirpated species or population enhancement of long-lived endangered species.
+In the Sado island (Japan), for example, the endangered Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008.
+Similarly, translocations of Humpback chub, a federally-listed fish species, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River.
+It is important to note that there are two common features in these successful examples.
+First, the receiving ecosystem remains nearly-intact (i.e., high carrying capacity).
+Second, the number of releases is rather small unlike release programs for commercial and recreational species.
+These conditions meet the theoretical assumptions with which intentional release led to increased abundance of the enhanced species with negligible impacts on other species.
+However, the preponderance of unsuccessful reintroduction programs implies that these conditions are not always sufficed.
+Our analysis suggests that pre-release examination and restoration of environmental capacity may be a key to successful release programs with minimal impacts on other community members.
+
+## Empirical evidence
 
@@
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**).
+Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was XXX (**Table S8**).
 This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S8-S10** for full statistics).

### 2022-10-03 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Yet, this method is still pervasive in natural resource management likely because of the apparent economic benefit of release programs.
-For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed economic performance of release programs for 12 major fishery resources -- the gross monetary yield exceeded the per-seed cost in nine species, suggesting that release programs are economically profitable in general.
+For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed economic performance of release programs for 12 major fishery resources -- the gross monetary yield exceeded the seed-production cost in nine species, suggesting that release programs are economically profitable in general.
 
@@
 Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
-Intentional release may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@careyNativeInvadersChallenges2012].
+Intentional release may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@laikreCompromisingGeneticDiversity2010; @careyNativeInvadersChallenges2012; @kitadaEconomicEcologicalGenetic2018].
 Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability.
-In particular, the community-wide impact must be serious in release programs for fishery resouces as many of them release millions of hatchery individuals into a single water body (e.g., a watershed) every year, which is likely far beyond the environmental capacity of the recipient ecosystem.
+The community-wide impact must be particularly serious in release programs for fishery resources as many of them release millions of hatchery individuals into a single water body (e.g., a watershed) every year, which is likely far beyond the environmental capacity of the recipient ecosystem.
 Evidence for this hypothesis is lacking, however.
@@
 Meanwhile, for higher values of $r_i$ ($\ge 1.5$), intentional release stabilized community dynamics by dampening limit cycles or chaos.
-Carrying capacity and competition also played an important role in shaping the parameter spaces with different effects of intentional release.
+Carrying capacity and competition also played an important role in shifting the parameter spaces.
 According to this result, we chose `r nrow(list_param[[2]])` simulation scenarios, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Methods**).
@@
 
-When carrying capacity was small ($K=$ `r min(list_param[[2]]$k`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
+When carrying capacity was small ($K=$ `r min(list_param[[2]]$k)`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
 This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
@@
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
-These patterns were qualitatively similar across most ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S1-S3**).
+These patterns were qualitatively similar across ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S1-S3**).
 
@@
 
-Intentional release, however, had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k`); **Figures S4-S6**).
-In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S4**).
-This pattern suggests that intentional release may be effective for species or in environments with limited intraspecific competition (= $r_1 K^{-1}$) and is consistent with the fact that some of the best evidence for successful intentional release comes from re-introduction/translocation programs of extirpated species or population enhancement of long-lived endangered species.
+Intentional release, however, had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S4-S6**).
+In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S4**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective.
+Our result is reasonable because some of the best evidence for successful intentional release comes from re-introduction/translocation programs of extirpated species or population enhancement of long-lived endangered species.
 In the Sado island (Japan), for example, the endangered Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008.
 Similarly, translocations of Humpback chub, a federally-listed fish species, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River.
-It is important to note that there are two common features in these successful examples.
+Two common features exist in these successful examples.
 First, the receiving ecosystem remains nearly-intact (i.e., high carrying capacity).
-Second, the number of releases is rather small unlike release programs for commercial and recreational species.
+Second, the number of releases in these conservation-oriented programs is rather small (several tens to hundreds) unlike release programs for commercial and recreational species (up to several tens of millions).
 These conditions meet the theoretical assumptions with which intentional release led to increased abundance of the enhanced species with negligible impacts on other species.
 However, the preponderance of unsuccessful reintroduction programs implies that these conditions are not always sufficed.
+In several examples, excessive numbers of individuals are released into degraded ecosystems with absolute failures of population enhancement or establishment.
 Our analysis suggests that pre-release examination and restoration of environmental capacity may be a key to successful release programs with minimal impacts on other community members.

### 2022-10-03 rmd/manuscript.Rmd
rmd

@@
 Similarly, translocations of Humpback chub, a federally-listed fish species, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River.
-Two common features exist in these successful examples.
+Two common features exist in these successful cases.
 First, the receiving ecosystem remains nearly-intact (i.e., high carrying capacity).
 Second, the number of releases in these conservation-oriented programs is rather small (several tens to hundreds) unlike release programs for commercial and recreational species (up to several tens of millions).
-These conditions meet the theoretical assumptions with which intentional release led to increased abundance of the enhanced species with negligible impacts on other species.
+These conditions meet the theoretical assumptions with which intentional release led to increased abundance of the enhanced species.
 However, the preponderance of unsuccessful reintroduction programs implies that these conditions are not always sufficed.
@@
 In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records.
-The majority of release occurs in spring, after which salmon fry stay in freshwater for growing seasons.
+The release of masu salmon began in 1950s, with the annual average ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019.
+The majority of release occurs in spring at fish survey locations, after which salmon fry stay in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
@@
 
-Competition is a likely mechanism, as our theory assumes.
-Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@weberInteractionsHatcheryWild2003].
-Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
-Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities.
-As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
+To gain better insights into the driving mechanisms, we fitted a multi-species Ricker model to a subset of our time-series data at nine sites with few missing observations and no intentional release (**Methods**); thus, the parameter estimates of this model is directly comparable to those used in the theoretical Ricker model.
+The estimated competition coefficients $\alpha_{ij}$ ranged `r round(min(df_pd$alpha_prime), 2)` -- `r round(max(df_pd$alpha_prime), 2)` with the median of `r round(median(df_pd$alpha_prime), 2)` (Figure 3), suggesting that competition is a likely mechanism as our theory assumes.
+Our statistical inference is supported by previous observational studies.
+For example, interference competition between masu salmon and white-spotted charr is well studied.
+Their diets are innately overlapped (e.g., drift terrestrial insects), but they choose different prey items when they co-occur [@miyasakaFoodHabitDivergence2003].
+Exploitative competition between masu salmon and benthic fish (e.g., sculpins) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014], which are dominant prey items for benthic fish species.
+Importantly, hatchery masu salmon may intensify intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
+Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition [@weberInteractionsHatcheryWild2003].
+Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
 
@@
 The fitness disadvantage may add to negative density dependence to influence community stability.
+
+Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities.
+As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
 

### 2022-10-03 code/set_rmd.R
Update set_rmd.R

@@ -54,6 +54,14 @@ list_param <- list_sim %>%
 ## raw data
 source(here::here("code/data_fmt_fishdata.R"))
 source(here::here("code/data_fmt_reg.R"))
+source(here::here("code/data_fmt_stock.R")) # call `df_stock_mu`
+source(here::here("code/si_figure_species_int.R")) # call `df_pd`
+
+df_stock_stage <- df_stock %>% 
+  group_by(release_stage) %>% 
+  summarize(stock = sum(abundance)) %>% 
+  mutate(ratio = stock / max(stock),
+         prop = stock / sum(stock))
 
 df_area <- d0 %>% 
   group_by(site_id, year) %>% 
@@ -66,6 +74,7 @@ df_bp <- list.files(path = here::here("output"),
   readRDS() %>% 
   filter(param == "bp_value") %>% 
   dplyr::select(mean)
+
 
 ## mcmc sample size
 
@@ -84,12 +93,3 @@ df_mcmc <- lapply(c("summary_ssm_ar", "summary_reg", "summary_multi_ricker"),
                       mutate(model = str_extract(x, "ssm|reg|ricker"))
                   }) %>% 
   bind_rows()
-
-## release data
-source(here::here("code/data_fmt_stock.R"))
-
-df_stock_stage <- df_stock %>% 
-  group_by(release_stage) %>% 
-  summarize(stock = sum(abundance)) %>% 
-  mutate(ratio = stock / max(stock),
-         prop = stock / sum(stock))

### 2022-10-05 code/figure_layout.R
edit: figure codes

@@ -1,7 +1,6 @@
 
 # setup -------------------------------------------------------------------
 
-rm(list = ls(all.names = TRUE))
 source(here::here("code/library.R"))
 
 

### 2022-10-05 code/figure_obs_coef.R

@@ -1,7 +1,6 @@
 
 # setup -------------------------------------------------------------------
 
-rm(list = ls())
 pacman::p_load(foreach,
                tidyverse,
                ggridges)

### 2022-10-05 code/figure_obs_stock.R

@@ -125,7 +125,7 @@ theme_set(plt_theme)
 
 ## plot
 ylab <- c(`cv` = "CV~sigma/mu",
-          `species_richness` = "Species~richness",
+          `species_richness` = "Taxonomic~richness",
           `mu` = "Mean~mu~(ind.~m^-2)",
           `sigma` = "SD~sigma~(ind.~m^-2)")
 

### 2022-10-05 code/set_rmd.R

@@ -55,6 +55,7 @@ list_param <- list_sim %>%
 source(here::here("code/data_fmt_fishdata.R"))
 source(here::here("code/data_fmt_reg.R"))
 source(here::here("code/data_fmt_stock.R")) # call `df_stock_mu`
+source(here::here("code/figure_obs_stock.R")) # call `df_beta`
 source(here::here("code/si_figure_species_int.R")) # call `df_pd`
 
 df_stock_stage <- df_stock %>% 

### 2022-10-05 rmd/figures.Rmd
Squashed commit of the following:
commit c274913bbbf475b2379bfd5ff5714134b1c4d743
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Sep 14 12:52:06 2022 -0400

    edit: rmd misc

commit b83fa58b0ac121cf4f89fff102048b2ff07a3b1e
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:49 2022 -0400

    Update mcmc_trace_reg.pdf

commit 184921982330ea83d449b2fe44159659f9c52210
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:45 2022 -0400

    edit: misc

commit aaac7131a165551933b99ae948f54d710a673206
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:32 2022 -0

@@
 knit: (function(inputFile, encoding) {
-        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
+        rmarkdown::render(inputFile,
+                          encoding = encoding, 
+                          output_dir = "document_output")
       })
@@
 
+source(here::here("code/set_functions.R"))
+
 ```
 
-```{r figure_1, fig.width=9, fig.height=11}
+```{r figure1, fig.width=9, fig.height=11}
 
-source(here::here("code/figure_theory_obs.R"))
+source(here::here("code/figure_layout.R"))
 
-print(g)
-
+knitr::include_graphics(here::here("output/figure_theory_obs.pdf"))
 ```
@@
 (A) Theoretical predictions.
-Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and 95% confidence intervals.
-Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`.
+Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and 50% prediction intervals (light shade).
+Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ `r round(na.omit(unique(df0$r1)), 2)`, average interspecific competition $\bar{\alpha}=$ `r round(na.omit(unique(df0$alpha)), 2)`, carrying capacity $K=$ `r round(na.omit(unique(df0$k)), 2)`, environmental stochasticity $\sigma_{\epsilon}=$ `r round(na.omit(unique(df0$sd_env)), 2)`, relative fitness of captive-bred individuals $f_R=$ `r round(na.omit(unique(df0$phi)), 2)`.
+These parameter values are comparable to the estimates of the multi-species Ricker model.
 (B) Empirical evidence.
-Dots represent geometric means of site-level observations in 31 watersheds.
-Lines are the predicted values of the regression models, and line types correspond to the coefficient's posterior probabilities.
-See Tables S8-10 for full statistics.
+Dots represent observations at 97 sites within 31 watersheds.
+Lines and shades are the predicted values and their 95% credible intervals of the regression models, and line types correspond to the coefficient's posterior probabilities.
+Effective release is a latent explanatory variable estimated in our hierarchical Baysian model.
+See Methods for details.
+Full statistics were reported in Tables S6-8.
 (C) Map of sampling sites (black dots) in Hokkaido, Japan.
@@
 
-source(here::here("code/figure_coef.R"))
+source(here::here("code/figure_obs_coef.R"))
 
-print(g_coef)
+knitr::include_graphics(here::here("output/figure_coef.pdf"))
 
@@
 Y-axis represents different response variables grouped by colors distinguishing species groups (whole community, enhanced species [masu salmon], and unenhanced species).
+Triangles indicate median estimates.
+
+\newpage
+
+```{r figure3, fig.width=9, fig.height=11}
+
+source(here::here("code/si_figure_species_int.R"))
+
+knitr::include_graphics(here::here("output/figure_alpha_dist.pdf"))
+```
+
+**Figure 3** Estimated competition coefficients of the multi-species Ricker model.
+Dots represent a given pair of taxa, and box plots show median (thick vertical lines) and quantile (hinges).
+Whiskers show smallest (largest) observation less (greater) than or equal to upper hinge - 1.5 \* quantile (+ 1.5 \* quantile).
+The vertical line denotes the median.
+The density plot on the top shows the overall distribution of the competition coefficient.
+Colors distinguish taxa.

### 2022-10-05 rmd/manuscript.Rmd
edit: text

@@
 
-The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred native species ("intentional release").
-Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks.
+Massive releases of captive-bred native species ("intentional release") is a pervasive method to enhance wild populations of commercial and recreational species.
 However, such external inputs may disrupt the sensitive balance of species interactions that allows competing species to coexist, potentially compromising the long-term community stability.
@@
 Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-The magnitude of intentional release for commercial and recreational species is massive; typically, a single program releases tens of thousands to millions of plant, invertebrate (bivalves @haagNorthAmericanFreshwater2012, insects), and vertebrate individuals (fish, birds) into the wild annually (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]).
-There is growing awareness that intentional release entails ecological risks, including the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007], the spread of diseases and parasites in wild populations [@krkosekDecliningWildSalmon2007], and the intensification of intraspecific competition within the enhanced species.
+The magnitude of intentional release for commercial and recreational species is massive; a single program releases tens of thousands to millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@villanuaSanitaryRisksRedlegged2008; @kitadaEconomicEcologicalGenetic2018] into the wild annually (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]).
+There is growing awareness that intentional release entails ecological risks, including the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007], the spread of diseases and parasites in wild populations [@krkosekDecliningWildSalmon2007], and the intensification of intraspecific competition within the enhanced species [@kitadaLessonsLearnedJapanese2006].
 Yet, this method is still pervasive in natural resource management likely because of the apparent economic benefit of release programs.
@@
 Prior to our full-community analysis, we analyzed a two species community to understand the model behavior.
-The prior analysis revealed distinct parameter spaces predicting destabilizing, neutral, and stabilizing effects of intentional release on community dynamics.
+The prior analysis revealed distinct parameter spaces predicting destabilizing, neutral, and stabilizing effects of intentional release on community dynamics (**Figures S1 and S2**).
 In general, intentional release had a neutral to destabilizing effect in a community with slow-growing species ($r_i < 1.5$).
@@
 The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition reduced the unenhanced species at high levels of intentional release, resulting in fewer persisting species (**Figure 1A**).
+Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure 1A**).
 Combined, the total community density decreased more sharply than individual species groups (**Figure 1A**).
@@
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
-These patterns were qualitatively similar across ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S1-S3**).
+These patterns were qualitatively similar across ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S3-S6**).
 
@@
 
-Intentional release, however, had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S4-S6**).
-In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S4**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective.
-Our result is reasonable because some of the best evidence for successful intentional release comes from re-introduction/translocation programs of extirpated species or population enhancement of long-lived endangered species.
-In the Sado island (Japan), for example, the endangered Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008.
-Similarly, translocations of Humpback chub, a federally-listed fish species, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River.
+Intentional release, however, had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S7-S10**).
+In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S7**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective.
+Our result is reasonable because some of the best evidence for successful intentional release comes from re-introduction/translocation programs of extirpated species or population enhancement of long-lived endangered species [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021].
+In the Sado island (Japan), for example, the endangered Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008 [@okahisaEvaluationOngoingCrested2022].
+Similarly, translocations of Humpback chub, a federally-listed fish species in the US, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River [@yackulicAssessingPopulationImpacts2021].
 Two common features exist in these successful cases.
-First, the receiving ecosystem remains nearly-intact (i.e., high carrying capacity).
-Second, the number of releases in these conservation-oriented programs is rather small (several tens to hundreds) unlike release programs for commercial and recreational species (up to several tens of millions).
+First, the receiving ecosystem supports suitable habitats (i.e., high carrying capacity).
+Second, the number of releases in these conservation-oriented programs is rather small (several tens to hundreds) [@fischerAssessmentPublishedResults2000] in comparison to release programs for commercial and recreational species (up to several tens of millions).
 These conditions meet the theoretical assumptions with which intentional release led to increased abundance of the enhanced species.
-However, the preponderance of unsuccessful reintroduction programs implies that these conditions are not always sufficed.
-In several examples, excessive numbers of individuals are released into degraded ecosystems with absolute failures of population enhancement or establishment.
+However, the preponderance of unsuccessful reintroduction programs implies that these conditions are not always sufficed [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019].
+Indeed, non-negligible numbers of projects seem to release captive-bred individuals into the wild without knowing whether the release habitat is suitable for the focal species [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012].
 Our analysis suggests that pre-release examination and restoration of environmental capacity may be a key to successful release programs with minimal impacts on other community members.
@@
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was XXX (**Table S8**).
-This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S8-S10** for full statistics).
+Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S8**).
+This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6-S8** for full statistics).
 In the meantime, the SDs had vague relationships with intentional release (**Figures 1B and 2**).
 
-To gain better insights into the driving mechanisms, we fitted a multi-species Ricker model to a subset of our time-series data at nine sites with few missing observations and no intentional release (**Methods**); thus, the parameter estimates of this model is directly comparable to those used in the theoretical Ricker model.
-The estimated competition coefficients $\alpha_{ij}$ ranged `r round(min(df_pd$alpha_prime), 2)` -- `r round(max(df_pd$alpha_prime), 2)` with the median of `r round(median(df_pd$alpha_prime), 2)` (Figure 3), suggesting that competition is a likely mechanism as our theory assumes.
-Our statistical inference is supported by previous observational studies.
-For example, interference competition between masu salmon and white-spotted charr is well studied.
-Their diets are innately overlapped (e.g., drift terrestrial insects), but they choose different prey items when they co-occur [@miyasakaFoodHabitDivergence2003].
-Exploitative competition between masu salmon and benthic fish (e.g., sculpins) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014], which are dominant prey items for benthic fish species.
+To gain better insights into the driving mechanisms, we fitted a multi-species Ricker model to a subset of our time-series data at nine sites with few missing observations and no intentional release (**Methods**).
+The parameter estimates of this model are thus directly comparable to those used in the theoretical Ricker model.
+The estimated competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure 3**), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
+Our statistical inference is supported by previous studies.
+For example, interference competition between masu salmon and other salmonid species is well documented [@miyasakaFoodHabitDivergence2003; @hasegawaComparisonCompetitiveAbility2004a].
+Diets of salmonid species are innately overlapped (e.g., drift terrestrial insects), such that they interfere with each other for preferable foraging microhabitats [@hasegawaComparisonCompetitiveAbility2004a].
+Exploitative competition between masu salmon and benthic fish (e.g., sculpins and stone loaches in our study system) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014], which are dominant prey items for many benthic fish species [@natsumedaEvaluationEcologicalFeatures2010; @natsumedaDietFoodSelectivity2012].
 Importantly, hatchery masu salmon may intensify intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
-Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition [@weberInteractionsHatcheryWild2003].
+Hatchery salmons are larger and more aggressive than wild individuals at a comparable life stage, increasing the likelihood of intense intra- and interspecific competition [@weberInteractionsHatcheryWild2003].
 Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
@@
 The reduced fitness of hatchery masu salmon may also play a role in the observed response.
-Like other salmonids, ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress].
+Like other salmonids, masu salmon exhibits a life history of partial migration [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013].
+In our study region, almost all females and the majority of males migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @moritaTemperaturedependentVariationAlternative2014].
+It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress].
 In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003].
@@
 As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
+XXX -
 
-We cannot exclude the possibility that spurious correlations drove our results.
-However, the protected watersheds preserve nearly intact landscapes (**Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships.
-Further, we have statistically controlled natural variation in environmental factors (see **Methods** and **Tables S8-S10**).
-This unique setup may have helped uncover the qualitative agreement between theory and empirical patterns.
+It is noteworthy that the magnitude of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is comparable or even smaller when compared with those for other commercial and recreational species [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018].
+For example, 0.5 -- 1.2 million juveniles of Black sea bream are released annually in the Kagoshima bay, Japan, where substantial declines of genetic diversity and wild individuals have been reported [@kitadaRigorousMonitoringLargescale2019].
+Importantly, a meta-analysis focusing on fishery resources revealed that only a few of these massive release programs led to increased abundance of the enhanced species [@arakiHatcheryStockingHelp2010].
+Hence, the patterns observed in the protected watersheds are likely to be general, although none of those studies quantified the community-level impact of massive releases.
+Future studies addressing this knowledge gap is therefore highly valuable.
+
+The near-intact environment of the protected watersheds with strict regulations of human activities (**Figure S10**) may have helped uncover the qualitative agreement between theory and empirical patterns.
+For example, any form of exploitation, including angling, is strictly prohibited for any fish species in the protected watersheds.
+In addition, an exclusive permission is required to physically alter in-stream and riparian habitats (e.g., construction of river-crossing structures).
+Therefore, unmeasured human influences should have minimal influences on the observed relationships.
+Further, we have statistically controlled natural variation in environmental factors (see **Methods**).
+Nevertheless, our results must be viewed with caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research.
+Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics if sufficient time-series data are available.
 
 Despite the significant attention to the fate of captive-bred individuals [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996], current schemes rarely consider the self-regulation process of biodiversity.
-Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012].
-While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive in nature because the destabilizing effect emerged across diverse simulated scenarios.
-
-We should prioritize habitat conservation with a broader scope of ecosystem management for the sustainability of natural resources.
-Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of intentional release.
+Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the stable delivery of ecosystem services [@cardinaleBiodiversityLossIts2012].
+While more sophisticated analysis is required to provide detailed guidance on how to improve release programs, it is clear from our analysis that habitat conservation should be prioritized with a broader scope of ecosystem management for the sustainability of natural resources.
+Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of intentional release by compromising the environmental capacity.
 Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation.

### 2022-10-05 rmd/supporting_info.Rmd
si

@@
 csl: https://www.zotero.org/styles/pnas
+nocite: |
+  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
 ---
@@
 Dots indicate parameter combinations that are used in the whole community simulation.
+Vertical line is the average value of $r_i$ (1.43) for salmonid species [@myersMaximumReproductiveRate1999].
 **(B)** Examples of community dynamics with and without intentional release.

### 2022-10-05 code/si_figure_theory_2sp.R
rename

@@ -146,8 +146,8 @@ list_g_c <- foreach(x = 1:length(v_alpha)) %do% {
   
   ggsave(g_c,
          filename = here::here(paste0("output/figure_2sp_model_", lbs[x], ".pdf")),
-         height = 10,
-         width = 13)
+         height = 9,
+         width = 12)
   
   return(g_c)  
 }

### 2022-10-05 rmd/supporting_info.Rmd
si

--- 2022-10-03 rmd/supporting_info.Rmd
@@
 csl: https://www.zotero.org/styles/pnas
+nocite: |
+  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
 ---
@@
 
+\newpage
+
 ## Simulation parameter
@@
 
-```{r fig-2sp-w, fig.width=9, fig.height=9, fig.cap = paste0("Theoretical predictions in a two-species community.
+```{r fig-2sp-w, fig.cap = paste0("Theoretical predictions in a two-species community.
 **(A)** Spearman's rank correlations between intentional release and community dynamics in a weak competition scenario ($\\bar{\\alpha}=$ ", min(list_param[[1]]$alpha) ,").
@@
 Dots indicate parameter combinations that are used in the whole community simulation.
+Broken vertical lines denote the average value of $r_i$ (1.43) for salmonid species [@myersMaximumReproductiveRate1999].
 **(B)** Examples of community dynamics with and without intentional release.
@@
 
-source(here::here("code/figure_theory_2sp.R"))
+source(here::here("code/si_figure_theory_2sp.R"))
 knitr::include_graphics(here::here("output/figure_2sp_model_weak.pdf"))
@@
 
-```{r fig-2sp-s, fig.width=9, fig.height=9, fig.cap = paste0("Theoretical predictions in a two-species community.
+```{r fig-2sp-s, fig.cap = paste0("Theoretical predictions in a two-species community.
 **(A)** Spearman's rank correlations between intentional release and community dynamics in a strong competition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,").
@@
 
-source(here::here("code/figure_theory_2sp.R"))
+source(here::here("code/si_figure_theory_2sp.R"))
 knitr::include_graphics(here::here("output/figure_2sp_model_strong.pdf"))

### 2022-10-05 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 
-\newpage
-
 ## Simulation parameter
@@
 Colors are proportional to Spearman's rank correlations.
-Dots indicate parameter combinations that are used in the whole community simulation.
+Dots indicate parameter combinations that are used in the whole community simulation and Panel B.
 Broken vertical lines denote the average value of $r_i$ (1.43) for salmonid species [@myersMaximumReproductiveRate1999].
 **(B)** Examples of community dynamics with and without intentional release.
-Community dynamics diverge at the broken vertical lines, the timestep at which intentional release begins.
+Community dynamics diverge at broken vertical lines, the timestep at which intentional release begins.
 Rows distinguish intrinsic growth rates, while columns distinguish deterministic and stochastic simulations.
@@
 Colors are proportional to Spearman's rank correlations.
-Dots indicate parameter combinations that are used in the whole community simulation.
+Dots indicate parameter combinations that are used in the whole community simulation  and Panel B.
 Broken vertical lines denote the average value of $r_i$ (1.43) for salmonid species [@myersMaximumReproductiveRate1999].
 **(B)** Examples of community dynamics with and without intentional release.
-Community dynamics diverge at the broken vertical lines, the timestep at which intentional release begins.
+Community dynamics diverge at broken vertical lines, the timestep at which intentional release begins.
 Rows distinguish intrinsic growth rates, while columns distinguish deterministic and stochastic simulations.

### 2022-10-05 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S8**).
+Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
 This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6-S8** for full statistics).

### 2022-10-14 rmd/manuscript.Rmd
rmd

@@
 output:
-  #bookdown::pdf_document2:
-  #  latex_engine: xelatex
-  bookdown::word_document2:
-   reference_docx: word_format.docx
+  bookdown::pdf_document2:
+   latex_engine: xelatex
+   toc: false
+  #bookdown::word_document2:
+  # reference_docx: word_format.docx
 csl: https://www.zotero.org/styles/pnas
@@
 fontsize: 11pt
+mainfont: "Times New Roman"
 header-includes:
@@
 Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-The magnitude of intentional release for commercial and recreational species is massive; a single program releases tens of thousands to millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@villanuaSanitaryRisksRedlegged2008; @kitadaEconomicEcologicalGenetic2018] into the wild annually (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]).
-There is growing awareness that intentional release entails ecological risks, including the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007], the spread of diseases and parasites in wild populations [@krkosekDecliningWildSalmon2007], and the intensification of intraspecific competition within the enhanced species [@kitadaLessonsLearnedJapanese2006].
-Yet, this method is still pervasive in natural resource management likely because of the apparent economic benefit of release programs.
-For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed economic performance of release programs for 12 major fishery resources -- the gross monetary yield exceeded the seed-production cost in nine species, suggesting that release programs are economically profitable in general.
+In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@villanuaSanitaryRisksRedlegged2008; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
+There is growing awareness that intentional release entails ecological risks, including the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007], the spread of diseases in wild populations [@krkosekDecliningWildSalmon2007], and the intensification of intraspecific competition within the enhanced species [@kitadaLessonsLearnedJapanese2006].
+Yet, this method is still pervasive in natural resource management owing to the significant economic benefit [@malkamakiSystematicReviewSocioeconomic2018; @davidEconomicFeasibilityIntensification2018; @rutledgeCostBenefitHatcheryreared1990; @kitadaEconomicEcologicalGenetic2018].
+For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed economic performance of release programs for 12 major fishery resources across the globe.
+The gross monetary yield exceeded the seed-production cost in nine species, suggesting that release programs are economically profitable in general.
 
@@
 Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability.
-The community-wide impact must be particularly serious in release programs for fishery resources as many of them release millions of hatchery individuals into a single water body (e.g., a watershed) every year, which is likely far beyond the environmental capacity of the recipient ecosystem.
+The community-wide impact may be particularly serious in release programs for fishery resources as many of them release millions of hatchery individuals into a single water body (e.g., a watershed) every year.
 Evidence for this hypothesis is lacking, however.
@@
 Our theory illuminates that intentional release compromises the stabilizing mechanism emerging from species niche differences.
-The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].
+The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes across the nation [@kitadaLessonsJapanMarine2020].
+Once released as fry, masu salmon stay in freshwater for at least one year before sea migration and compete for resources with other stream-dwelling species.
+Therefore, this system serves as an excellent model to study the community-wide impact of intentional release.
+Our integrative approach provides strong evidence for the destabilizing effect of intentional release on ecological communities.
 

### 2022-10-14 rmd/supporting_info.Rmd
rmd

@@
 The analysis of a two-species community revealed the distinct parameter space predicting a stabilizing, neutral, or destabilizing effect of intentional release.
-The left column in **Figure S**\@ref(fig:fig-2sp-w)**A**) shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`).
+The left column in **Figure S**\@ref(fig:fig-2sp-w)**A** shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`).
 For lower values of intrinsic growth rate $r_i$ ($<1.5$), intentional release had neutral (with higher $K$) to destabilizing effects (with lower $K$) on community dynamics.

### 2022-10-17 rmd/manuscript.Rmd
rmd

@@
 where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $\text{Normal}(0,\sigma_{\varepsilon}^2)$.
-To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,2.5)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim \text{Exp}(1/\bar{\alpha})$).
 The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
@@
 Carrying capacity and competition also played an important role in shifting the parameter spaces.
-According to this result, we chose `r nrow(list_param[[2]])` simulation scenarios, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Methods**).
+According to this result, we chose `r nrow(list_param[[2]])` simulation scenarios, differing in the intrinsic growth of an enhanced species $r_1$, average competition strength $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Methods**).
+To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,2.5)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim \text{Exp}(1/\bar{\alpha})$).
 Under each parameter scenario, we ran `r attr(list_param[[2]], "n_sim")` time steps of `r max(list_sim[[2]]$n_rep)` independent communities (i.e., simulation replicates).
@@
 This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
-The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals [@satakeStockingCaptivebredFish2012].
+The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, confirming the previous theoretical prediction [@satakeStockingCaptivebredFish2012].
 Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure 1A**).
@@
 
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive release (**Figure 1B**).
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with intensive release (**Figure 1B**).
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
+Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure 2**; see **Methods** for "effective" release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
 This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6-S8** for full statistics).
@@
 
-To gain better insights into the driving mechanisms, we fitted a multi-species Ricker model to a subset of our time-series data at nine sites with few missing observations and no intentional release (**Methods**).
-The parameter estimates of this model are thus directly comparable to those used in the theoretical Ricker model.
+To gain better insights into the driving mechanisms, we fitted a multi-species Ricker model to a subset of our time-series data (nine sites with few missing observations and no intentional release; **Methods**).
+The parameter estimates of this model are directly comparable to those used in the theoretical Ricker model.
 The estimated competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure 3**), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
 Our statistical inference is supported by previous studies.
-For example, interference competition between masu salmon and other salmonid species is well documented [@miyasakaFoodHabitDivergence2003; @hasegawaComparisonCompetitiveAbility2004a].
-Diets of salmonid species are innately overlapped (e.g., drift terrestrial insects), such that they interfere with each other for preferable foraging microhabitats [@hasegawaComparisonCompetitiveAbility2004a].
+For example, interference competition between masu salmon and other salmonid species is well documented [@miyasakaFoodHabitDivergence2003; @hasegawaComparisonCompetitiveAbility2004].
+Diets of salmonid species are innately overlapped (e.g., drift terrestrial insects), such that they interfere with each other for profitable foraging spots [@hasegawaComparisonCompetitiveAbility2004].
 Exploitative competition between masu salmon and benthic fish (e.g., sculpins and stone loaches in our study system) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014], which are dominant prey items for many benthic fish species [@natsumedaEvaluationEcologicalFeatures2010; @natsumedaDietFoodSelectivity2012].
 Importantly, hatchery masu salmon may intensify intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
-Hatchery salmons are larger and more aggressive than wild individuals at a comparable life stage, increasing the likelihood of intense intra- and interspecific competition [@weberInteractionsHatcheryWild2003].
+Hatchery salmons are larger and more aggressive than wild individuals of a comparable life stage, increasing the likelihood of intense intra- and interspecific competition [@weberInteractionsHatcheryWild2003].
 Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
@@
 Like other salmonids, masu salmon exhibits a life history of partial migration [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013].
-In our study region, almost all females and the majority of males migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @moritaTemperaturedependentVariationAlternative2014].
-It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress].
+In our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @moritaTemperaturedependentVariationAlternative2014].
+It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may exacerbate exponentially as the number of generations in captivity increases [@arakiGeneticEffectsCaptive2007].
+Typically, hatchery masu salmon is reared in captivity for two to four generations; thus, the fitness decline may be substantial.
 In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003].
-The fitness disadvantage may add to negative density dependence to influence community stability.
+The multiple fitness disadvantages may add to negative density dependence to influence community stability.
 
-Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities.
+Importantly, socioeconomic factors control the number of releases.
+The hatchery program aims to produce and release a constant number of hatchery masu salmon every year, although uncontrollable factors (e.g., diseases in a hatchery, budget allocation) generate considerable variation in release number among years.
+Therefore, the number of releases is determined without accounting for the current conditions of the recipient ecosystem.
 As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
-XXX -
 
@@
 For example, 0.5 -- 1.2 million juveniles of Black sea bream are released annually in the Kagoshima bay, Japan, where substantial declines of genetic diversity and wild individuals have been reported [@kitadaRigorousMonitoringLargescale2019].
+Similarly, three to four millions of Red-legged partridge are released for sports hunting in rural Spain [@villanuaSanitaryRisksRedlegged2008].
+Therefore, our results should not be viewed as an extreme scenario.
 Importantly, a meta-analysis focusing on fishery resources revealed that only a few of these massive release programs led to increased abundance of the enhanced species [@arakiHatcheryStockingHelp2010].
-Hence, the patterns observed in the protected watersheds are likely to be general, although none of those studies quantified the community-level impact of massive releases.
+Hence, the reduced abundance of enhanced species may be general, although none of those studies quantified the community-level impact of massive releases.
 Future studies addressing this knowledge gap is therefore highly valuable.

### 2022-10-17 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 However, such external inputs may disrupt the sensitive balance of species interactions that allows competing species to coexist, potentially compromising the long-term community stability.
-Here, we use theory and long-term data of stream fish communities to show that intentional release triggers community collapse with little demographic benefit to the enhanced species.
+Here, we use theory and long-term data of stream fish communities to show that intentional release destabilizes community dynamics with a limited demographic benefit to the enhanced species.
 Our theory predicted that intentional release intensifies interspecific competition, facilitating competitive exclusion of unenhanced species that otherwise stablely coexist.
@@
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure 2**; see **Methods** for "effective" release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
+Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure 2**; see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
 This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6-S8** for full statistics).
@@
 Importantly, socioeconomic factors control the number of releases.
-The hatchery program aims to produce and release a constant number of hatchery masu salmon every year, although uncontrollable factors (e.g., diseases in a hatchery, budget allocation) generate considerable variation in release number among years.
+The hatchery program aims to produce and release a constant number of hatchery masu salmon every year, although uncontrollable factors (e.g., diseases, budget allocation) generate considerable variation in the release number among years.
 Therefore, the number of releases is determined without accounting for the current conditions of the recipient ecosystem.
@@
 Therefore, our results should not be viewed as an extreme scenario.
-Importantly, a meta-analysis focusing on fishery resources revealed that only a few of these massive release programs led to increased abundance of the enhanced species [@arakiHatcheryStockingHelp2010].
-Hence, the reduced abundance of enhanced species may be general, although none of those studies quantified the community-level impact of massive releases.
+We also must mention that a meta-analysis focusing on fishery resources revealed that only a few of massive release programs led to increased abundance of the enhanced species [@arakiHatcheryStockingHelp2010].
+The reduced abundance of enhanced species may be general, although none of those studies statistically quantified the community-level impact of massive releases.
 Future studies addressing this knowledge gap is therefore highly valuable.
@@
 The near-intact environment of the protected watersheds with strict regulations of human activities (**Figure S10**) may have helped uncover the qualitative agreement between theory and empirical patterns.
-For example, any form of exploitation, including angling, is strictly prohibited for any fish species in the protected watersheds.
+For example, any form of exploitation, including angling, is prohibited for any species in the protected watersheds.
 In addition, an exclusive permission is required to physically alter in-stream and riparian habitats (e.g., construction of river-crossing structures).
@@
 Nevertheless, our results must be viewed with caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research.
-Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics if sufficient time-series data are available.
+Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics if sufficient time-series data are available (a minimum of \> 30 temporal replicates).
 
@@
 Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the stable delivery of ecosystem services [@cardinaleBiodiversityLossIts2012].
-While more sophisticated analysis is required to provide detailed guidance on how to improve release programs, it is clear from our analysis that habitat conservation should be prioritized with a broader scope of ecosystem management for the sustainability of natural resources.
-Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of intentional release by compromising the environmental capacity.
+While socioeconomic analysis is required to provide detailed guidance on how to improve release programs, it is clear for the natural resources sustainability that habitat conservation should be prioritized with a broader scope of ecosystem management.
+Such efforts are particularly important in the Anthropocene because habitat degradation may facilitate the undesired influence of intentional release by compromising the environmental capacity.
 Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation.
-For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022].
+For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022].
 Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018].

### 2022-10-18 rmd/manuscript.Rmd
rmd

@@
    toc: false
+   number_sections: false
   #bookdown::word_document2:
@@
 Massive releases of captive-bred native species ("intentional release") is a pervasive method to enhance wild populations of commercial and recreational species.
-However, such external inputs may disrupt the sensitive balance of species interactions that allows competing species to coexist, potentially compromising the long-term community stability.
+However, such external inputs may disrupt the sensitive species interactions that allow competing species to coexist, potentially compromising long-term community stability.
 Here, we use theory and long-term data of stream fish communities to show that intentional release destabilizes community dynamics with a limited demographic benefit to the enhanced species.
-Our theory predicted that intentional release intensifies interspecific competition, facilitating competitive exclusion of unenhanced species that otherwise stablely coexist.
+Our theory predicted that intentional release intensifies interspecific competition, facilitating the competitive exclusion of unenhanced species that otherwise stably coexist.
 In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition.
-Consequently, the ecological community with intentional release is predicted to show reduced community density with unstable temporal dynamics.
+Consequently, the ecological community with the intentional release is predicted to show reduced community density with unstable temporal dynamics.
 Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery salmon - a major fishery resource worldwide.
@@
 
-Intentional release of captive-bred individuals is a common practice for conservation and natural resource management.
+The intentional release of captive-bred individuals is a common practice for conservation and natural resource management.
 However, we know little about its potential consequences for the whole ecological community.
-Here, we show that intentional release undermines community stability with little demographic benefit to the enhanced species.
-Theory and data agreed that intentional release destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species.
-The effect size of intentional release was striking in its magnitude, doubling temporal fluctuations of enhanced communities compared to those with no intentional release.
+Here, we show that the intentional release undermines community stability with little demographic benefit to the enhanced species.
+Theory and data agree that intentional release destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species.
+The effect size of the intentional release was striking in its magnitude, doubling temporal fluctuations of enhanced communities compared to those with no intentional release.
 Our findings point to major limitations of intentional release as a primary tool for biodiversity conservation and sustainability.
 
-**Key words:** coexistence theory, competition, resilience, ecological modeling, fishery
+**Keywords:** coexistence theory, competition, resilience, ecological modeling, fishery
 
@@
 Yet, this method is still pervasive in natural resource management owing to the significant economic benefit [@malkamakiSystematicReviewSocioeconomic2018; @davidEconomicFeasibilityIntensification2018; @rutledgeCostBenefitHatcheryreared1990; @kitadaEconomicEcologicalGenetic2018].
-For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed economic performance of release programs for 12 major fishery resources across the globe.
+For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed the economic performance of release programs for 12 major fishery resources across the globe.
 The gross monetary yield exceeded the seed-production cost in nine species, suggesting that release programs are economically profitable in general.
@@
 Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability.
-The community-wide impact may be particularly serious in release programs for fishery resources as many of them release millions of hatchery individuals into a single water body (e.g., a watershed) every year.
 Evidence for this hypothesis is lacking, however.
@@
 Once released as fry, masu salmon stay in freshwater for at least one year before sea migration and compete for resources with other stream-dwelling species.
-Therefore, this system serves as an excellent model to study the community-wide impact of intentional release.
+Therefore, this system serves as an excellent model for studying the community-wide impact of intentional release.
 Our integrative approach provides strong evidence for the destabilizing effect of intentional release on ecological communities.
@@
 
-We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the intentional release of a constituent species (species 1).
+We employed a multi-species Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the intentional release of a constituent species (species 1).
 Specifically, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
@@
 
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $\text{Normal}(0,\sigma_{\varepsilon}^2)$.
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ ($\alpha_{ii} = 1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $\text{Normal}(0,\sigma_{\varepsilon}^2)$.
 The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:
@@
 
-Prior to our full-community analysis, we analyzed a two species community to understand the model behavior.
+Prior to our full-community analysis, we analyzed a two-species community to understand the model behavior.
 The prior analysis revealed distinct parameter spaces predicting destabilizing, neutral, and stabilizing effects of intentional release on community dynamics (**Figures S1 and S2**).
-In general, intentional release had a neutral to destabilizing effect in a community with slow-growing species ($r_i < 1.5$).
+In general, the intentional release had a neutral to destabilizing effect in a community with slow-growing species ($r_i < 1.5$).
 Meanwhile, for higher values of $r_i$ ($\ge 1.5$), intentional release stabilized community dynamics by dampening limit cycles or chaos.
@@
 This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
-The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, confirming the previous theoretical prediction [@satakeStockingCaptivebredFish2012].
+The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012].
 Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure 1A**).
@@
 The destabilizing effect emerges because intentional release affects the balance of species interactions that underpins community stability.
-In theory, the stable coexistence requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a].
+In theory, stable coexistence requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a].
 Under this condition, competing species can grow from small populations because dominant species undergo stronger intraspecific competition [@carrollNicheFitnessDifferences2011a].
-Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multispecies community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$).
-However, intentional release is externally controlled, and the number of releases is not subject to density-dependent regulation.
+Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multi-species community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$).
+However, the intentional release is externally controlled, and the number of releases is not subject to density-dependent regulation.
 Therefore, released individuals impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.
 
-Intentional release, however, had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S7-S10**).
+The intentional release had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S7-S10**).
 In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S7**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective.
-Our result is reasonable because some of the best evidence for successful intentional release comes from re-introduction/translocation programs of extirpated species or population enhancement of long-lived endangered species [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021].
-In the Sado island (Japan), for example, the endangered Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008 [@okahisaEvaluationOngoingCrested2022].
+The weak-competition scenario is likely in re-introduction programs of extirpated species or population enhancement of long-lived endangered species.
+In fact, some of the best evidence for successful intentional release comes from re-introduction efforts [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021].
+In the Sado island (Japan), for example, the once-extirpated Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial re-introduction of ten captive-bred individuals in 2008 [@okahisaEvaluationOngoingCrested2022].
 Similarly, translocations of Humpback chub, a federally-listed fish species in the US, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River [@yackulicAssessingPopulationImpacts2021].
-Two common features exist in these successful cases.
-First, the receiving ecosystem supports suitable habitats (i.e., high carrying capacity).
-Second, the number of releases in these conservation-oriented programs is rather small (several tens to hundreds) [@fischerAssessmentPublishedResults2000] in comparison to release programs for commercial and recreational species (up to several tens of millions).
-These conditions meet the theoretical assumptions with which intentional release led to increased abundance of the enhanced species.
-However, the preponderance of unsuccessful reintroduction programs implies that these conditions are not always sufficed [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019].
-Indeed, non-negligible numbers of projects seem to release captive-bred individuals into the wild without knowing whether the release habitat is suitable for the focal species [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012].
-Our analysis suggests that pre-release examination and restoration of environmental capacity may be a key to successful release programs with minimal impacts on other community members.
+However, the preponderance of unsuccessful re-introduction programs implies that the theoretical requirements for successful intentional release are not always met [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019].
+Indeed, non-negligible numbers of projects seem to release captive-bred individuals into unsuitable habitats with compromised carrying capacities [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012].
+Our analysis suggests that such programs could rather impair biodiversity without noticeable demographic benefit to the enhanced species.
+Pre-release examination and restoration of environmental capacity may be key to successful release programs with minimal impacts on other community members.
 
@@
 In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records.
-The release of masu salmon began in 1950s, with the annual average ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019.
-The majority of release occurs in spring at fish survey locations, after which salmon fry stay in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
+The release of masu salmon began in the 1950s, with the annual average ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019.
+The majority of release occurs in spring at fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
 We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria).
-Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for potential effects of climates and local abiotic factors.
+Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for the potential effects of climates and local abiotic factors.
 
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with intensive release (**Figure 1B**).
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure 1B**).
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
@@
 This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6-S8** for full statistics).
-In the meantime, the SDs had vague relationships with intentional release (**Figures 1B and 2**).
+In the meantime, the SDs had vague relationships with the intentional release (**Figures 1B and 2**).
 
@@
 The parameter estimates of this model are directly comparable to those used in the theoretical Ricker model.
-The estimated competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure 3**), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
+The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure 3**), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
 Our statistical inference is supported by previous studies.
@@
 Diets of salmonid species are innately overlapped (e.g., drift terrestrial insects), such that they interfere with each other for profitable foraging spots [@hasegawaComparisonCompetitiveAbility2004].
-Exploitative competition between masu salmon and benthic fish (e.g., sculpins and stone loaches in our study system) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014], which are dominant prey items for many benthic fish species [@natsumedaEvaluationEcologicalFeatures2010; @natsumedaDietFoodSelectivity2012].
+Exploitative competition between masu salmon and benthic fish (e.g., sculpins and stone loaches in our study system) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014] that many benthic fish species prey on [@natsumedaEvaluationEcologicalFeatures2010; @natsumedaDietFoodSelectivity2012].
 Importantly, hatchery masu salmon may intensify intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
@@
 The reduced fitness of hatchery masu salmon may also play a role in the observed response.
-Like other salmonids, masu salmon exhibits a life history of partial migration [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013].
-In our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @moritaTemperaturedependentVariationAlternative2014].
-It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may exacerbate exponentially as the number of generations in captivity increases [@arakiGeneticEffectsCaptive2007].
-Typically, hatchery masu salmon is reared in captivity for two to four generations; thus, the fitness decline may be substantial.
+Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014].
+It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate as the number of generations in captivity increases [@arakiGeneticEffectsCaptive2007].
+Typically, hatchery masu salmon are reared in captivity for two to four generations.
+Thus, the fitness decline may be substantial.
 In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003].
@@
 
-Importantly, socioeconomic factors control the number of releases.
-The hatchery program aims to produce and release a constant number of hatchery masu salmon every year, although uncontrollable factors (e.g., diseases, budget allocation) generate considerable variation in the release number among years.
-Therefore, the number of releases is determined without accounting for the current conditions of the recipient ecosystem.
+External control of intentional release is a theoretical premise for the destabilizing effect to emerge, and this is exactly how the release of masu salmon is operated.
+The hatchery program aims to produce and release a constant number of hatchery masu salmon every year, although uncontrollable factors (e.g., disease, budget allocation) generate some variation in the release number between years.
+Therefore, the number of releases is determined without accounting for the current condition of the recipient ecosystem.
 As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.
@@
 It is noteworthy that the magnitude of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is comparable or even smaller when compared with those for other commercial and recreational species [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018].
-For example, 0.5 -- 1.2 million juveniles of Black sea bream are released annually in the Kagoshima bay, Japan, where substantial declines of genetic diversity and wild individuals have been reported [@kitadaRigorousMonitoringLargescale2019].
-Similarly, three to four millions of Red-legged partridge are released for sports hunting in rural Spain [@villanuaSanitaryRisksRedlegged2008].
+For example, 0.5 -- 1.2 million juveniles of Black sea bream are released annually in Kagoshima bay, Japan, where substantial declines in genetic diversity and wild individuals have been reported [@kitadaRigorousMonitoringLargescale2019].
+Similarly, three to four millions of Red-legged partridges are introduced repeatedly for sports hunting in rural Spain [@villanuaSanitaryRisksRedlegged2008].
 Therefore, our results should not be viewed as an extreme scenario.
-We also must mention that a meta-analysis focusing on fishery resources revealed that only a few of massive release programs led to increased abundance of the enhanced species [@arakiHatcheryStockingHelp2010].
-The reduced abundance of enhanced species may be general, although none of those studies statistically quantified the community-level impact of massive releases.
-Future studies addressing this knowledge gap is therefore highly valuable.
+We also must mention that a meta-analysis focusing on fishery resources revealed that only a few massive release programs led to an increased abundance of the enhanced species [@arakiHatcheryStockingHelp2010].
+Yet, none of those studies statistically quantified the community-level impact of massive releases.
+Future studies addressing this knowledge gap are therefore highly valuable.
 
-The near-intact environment of the protected watersheds with strict regulations of human activities (**Figure S10**) may have helped uncover the qualitative agreement between theory and empirical patterns.
-For example, any form of exploitation, including angling, is prohibited for any species in the protected watersheds.
-In addition, an exclusive permission is required to physically alter in-stream and riparian habitats (e.g., construction of river-crossing structures).
+Human activities are strictly regulated in the protected watersheds, and the near-intact environment (**Figure S10**) may have helped uncover the qualitative agreement between theory and empirical patterns.
+For example, any form of exploitation, including angling, is prohibited in these areas.
+In addition, exclusive permission is required to physically alter in-stream and riparian habitats.
 Therefore, unmeasured human influences should have minimal influences on the observed relationships.
@@
 Nevertheless, our results must be viewed with caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research.
-Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics if sufficient time-series data are available (a minimum of \> 30 temporal replicates).
+Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018; @suzukiDecomposingPredictabilityIdentify2022] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics.
+Unfortunately, these methods were not applicable to our data because they require a longer and non-sparse time series to yield robust results.
+
+## Implications
 
 Despite the significant attention to the fate of captive-bred individuals [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996], current schemes rarely consider the self-regulation process of biodiversity.
-Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the stable delivery of ecosystem services [@cardinaleBiodiversityLossIts2012].
-While socioeconomic analysis is required to provide detailed guidance on how to improve release programs, it is clear for the natural resources sustainability that habitat conservation should be prioritized with a broader scope of ecosystem management.
+Our results suggest that ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the stable delivery of ecosystem services [@cardinaleBiodiversityLossIts2012].
+While socioeconomic analysis is required to provide detailed guidance on how to improve release programs, it is clear for the sustainability of the natural resources that habitat conservation should be prioritized with a broader scope of ecosystem management.
 Such efforts are particularly important in the Anthropocene because habitat degradation may facilitate the undesired influence of intentional release by compromising the environmental capacity.
-Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation.
+Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is integral to achieving successful conservation.
 For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022].
@@
 
-We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Genki Sahashi and Masato Yamamichi for helpful discussion on this manuscript.
+We are grateful to the people involved in the long-term monitoring program at the protected watersheds in Hokkaido.
+We thank Genki Sahashi and Masato Yamamichi for the helpful discussion on this manuscript.
 

### 2022-10-18 rmd/reply_r1.Rmd
rmd

---
title: "Reply to: 2022-05603 Intentional release of native species undermines ecological stability"
output:
  bookdown::pdf_document2:
   latex_engine: xelatex
   toc: false
   number_sections: false
csl: https://www.zotero.org/styles/pnas
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
mainfont: "Times New Roman"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Dear Editor,

Thank you for giving us the opportunity to revise our manuscript. The comments were very helpful to improve our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:

1.  **Improve the introduction and implications**: both reviewers noted an absence of context in the previous manuscript. We agree with this comment. To address this issue, we revised the text to better contextualize our work. In particular, we have carefully reviewed cases to which our findings may apply, and discussed the relevance of our work to those systems.
2.  **Two-species simulation.** The Editor suggested to include a two-species simulation to guide the full community model. We really appreciate this suggestion and were able to draw deeper insights into our theoretical analysis. This improvement helped address the concern raised by the reviewer 2 (they pointed the lack of depth in theoretical analysis). We revised Methods and Results in accordance with this change. In particular, we removed the old sensitivity analysis as it was redundant with two-species simulations.
3.  **Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed that the interpretation of our empirical analysis is superficial -- we agree with this comment too. We have carefully enriched the text related to this issue. We have greatly increased the number of citations and discussed more carefully possible mechanisms that may produce the observed patterns. In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities. The estimated parameter indicated that competition among species certainly exists.
4.  **Life history of masu salmon.** Lastly, we enriched the text for life history of masu salmon and how release programs for this species are operated.

We appended a point-by-point response below. We hope our manuscript is now suitable for publication in your journal.

Sincerely,

Akira Terui on behalf of the authors

\clearpage

## Point-by-point response

**NOTE: original comments from reviewers and editor are italicized**

### Response to editor

*Because the Ricker model can yield damped oscillations, limit cycles, and even chaos depending on intrinsic growth rate, I would have first understood the impact of population supplementation analytically in a deterministic two species system. This is straightforward and relevant since the tendency to experience fluctuations without stochasticity is the baseline for your model. Moreover, this analysis can illuminate how you organize any exploration of parameter space. In particular, I would vary intrinsic rate of increase so that it captured monotonic convergence to equilibrium, damped oscillations en route to equilibrium, limit cycle, and chaos....The results reported from the model lack depth - especially considering the many possible parameter combinations. Since the Ricker model can produce fluctuations deterministically, the tendency to fluctuate deterministically (which is governed by intrinsic rate of increase) should be used to organize the simulation results. A more systematic examination of results would cross varying levels of K with varying r's, where the r's selected capture the different dynamical possibilities of the deterministic model.*

> Thank you for this constructive comment! We followed this direction, analyzing the model in a two-species community to guide a whole community analysis. As we detailed in the maintext, the different combinations of $r$ and $K$ produced distinct parameter spaces where intentional release had destabilizing, neutral, and stabilizing effects. Stabilizing effects appeared when the community shows limit cycles or chaos; otherwise, intentional release had destabilizing effects in general. We have clarified this point in the revised manuscript (see section **Theoretical prediction**).

*Second, for figure 1, it is important to use estimated Ricker parameters for salmon (several have been published) for the simulations. If there are no published estimates for masu salmon, there are estimates for other species in the same genus. Pairing model simulations with empirical plots has greater merit if the parameters used in the simulations are related to the species being released.*

> XXX

*Obviously species do not go extinct in your simulations (since populations can never go to zero or become negative). You contrive extinction to be an N = .01 or lower. In your words "the number of species persist (defied as 𝑁𝑖 \> 0.01 at 𝑡 = 1600)". Apart from the typo it is not clear to me if you:\
\
1) at t= 1600, you simply tally up all N's less than .01 and call that an extinction. or, alternatively,\
\
2) whenever a species' population falls below .01 during the course of the potential 1600 time steps, that species is considered extinct. So if at time step 634, N fell to .005, that would then be an absorbing boundary and the species is removed from the simulation.\
\
It is essential that you make clear whether it is #1 or #2 above that accounts for the loss of species.*

> XXX

*Both reviewers noted an absence of context, and literature cited that might better provide a framework for this study. What other species might this apply to? What are levels of supplementation in other salmon systems? The discussion does not place the work in the context of general research regarding captive breeding for enhancement, salmon hatcheries, and salmon conservation.*

> XXX

*The discussion of the masu data is too superficial. You need to include more about their life history and the supplementation systems. To what extent do the released salmon overlap with other species in space and time?*

> XXX

*I am not sure "collapse" is the appropriate word. Because extinction is the result of an absorbing boundary at N= .01, really it is fluctuations and mean community density that you are examining. The extinctions that generate what you call "collapse" are the result of fluctuations that take populations down to the absorbing boundary.*

> XXX

### Response to Reviewer 1

*Is the subject sufficiently general? Hatchery supplementation of salmonid populations is common practice globally. However, are there other taxa where this issue pertains? Though the authors a couple of citations, I worry this system may be a bit niche for readers of PNAS. I recommend the authors describe specific case studies in the Discussion where similar dynamics may apply and point to the types of additional research needed to determine if similar inferences may apply in those systems. Also, it would be helpful to include (widely available) estimates of the extent of salmonid hatchery supplementation in North America, and to contextualize the dynamics estimated in the state space model for masu salmon relative to these other well-studied populations.*

> XXX

*The authors employ a state of the art space-state model for the empirical portion of their paper, but I believe other interpretations of the data are possible. The empirical results shown here are consistent with the theoretical model, but a correlative statistical model does not allow direct causal inference. So I recommend the authors review their interpretations of their state space model and revise causal language in the text with this in mind.*

> Agreed. We have revised the paragraph stating the limitation of our work (the last paragraph of section **Empirical evidence**)

*How much time do they spend in the freshwater life stage?*

> Masu salmon spend at least one year before sea migration (they show partial migration, and some males stay in freshwater for their entire life). We have clarified details of masu salmon's life history.

*Marine life stage before spawning? How does this map to the AR1 process assumed in the state space model?*

> Thank you - we have given a deep thought on this. Masu salmon has a 1-year marine life stage (typically). However, many other species are also diadromous, and some of them return freshwater in a couple of months (e.g., amphidromous). Given the complexity of this system, we reconsidered our state-space model to account for up to AR3 process (fish species in our system typically 1-3 years of life-span). The results were qualitatively similar.

*If hatchery releases began in the 1950s, how has the proportion of natural origin fish changed over time?*

> XXX

*What other species are part of the masu salmon stream communities? Are they subject to supplementation, exploitation, or other factors that may also influence temporal variability and other aspects of these communities?*

> We have detailed species information in Table S2. Masu salmon often co-occur with white-spotted charr, sculpins, and stone loaches. Since our watersheds are "protected" watersheds, any form of exploitation (including angling) is not allowed (regardless of fish species). Therefore, other factors are very unlikely to shape the observed patterns of temporal community variability. Please note that we have statistically accounted for natural variation in land use, watershed size, climate etc.

### Response to Reviewer 2

*The general model seems logical in that there is a non-linear response to numbers of releases. It does not seem too surprising that when releases are 5x carrying capacity that there is a negative impact, especially given a fairly large alpha.*

> We agree that our results are not surprising -- we are not surprised either. However, we strongly believe that our result is important and worth publishing because to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long-term. Also, and perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system EVERY YEAR** (clarified in the revised manuscript)! This magnitude is way larger than the release program in our study system. Therefore, release numbers of $5\times$ carrying capacity seem even conservative to us. Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative scenario, rather than an extreme, unrealistic scenario.
>
> Regarding the competition coefficient, please note that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition, i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species). The values in our simulation (0.25 or 0.50 in the revised manusucript) are thus weak enough to allow species co-existence in the absence of intentional release. Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions. In the revised text, we have also provided empirical estimates of species interactions -- the median value was 0.29, so our simulation setup is reasonable.

*But in the mean* $\mu$ *panel in Figure 1A, the enhanced population shows no effect of releases until about 2x carrying capacity, which seems significant. This appears to occur at the same time there is steep decline of the unenhanced species, even when the number of releases is below.*

> Thank you for this comment. We agree that this pattern is important, and we do acknowledge that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**). However, our focus here is not the influence of intentional release on the enhanced species -- we are interested in how unenhanced species respond to the intentional release. This is the knowledge gap we are trying to fill, as no study has focused on this "side-effect" of intentional release so far. We hope the reviewer will understand the significance of this finding.

*In general, I found the results reported from this model to be lacking depth, especially given the many variations of model output in the supplemental material.*

> Thank you for this critical comment. Following the editor's suggestion, we have greatly improved the analysis by introducing two-species simulations (see our response to editor).

*Although the model is general, it is motivated by salmon. As a salmon model, it may lack the nuance needed to really explore the impacts of hatchery releases on salmon or communities. In particular, I wonder if a life-cycle model would provide a better insight of the potential impacts of hatchery releases on the enhanced species and community. **Table s9 shows the importance of ocean productivity and forest cover for mean*** $\mu$ ***in salmon, for example.** This makes sense for an anadromous species, but also highlights that the species occurs in multiple habitats with potentially different and asynchronously varying capacities. The model does not address this important life history trait. Consequently, results of the model may or may not be relevant to fishery managers - does it matter to the enhanced species or the community if releases are 5x K, when ocean productivity is high, for example.*

> Thank you, we agree that a detailed life-history model will provide useful insights into salmon management. However, we decided not to perform this analysis for the following reasons. First, given the readership of PNAS, as well as the suggestions from reviewer 1 and editor, we believe it is important to keep our model as general as possible. In fact, as clarified in the revised manuscript, there are a number of cases where our phenomenological model may apply. Second, a detailed life-history model has already been developed by Morita et al. [@moritaTemperaturedependentVariationAlternative2014]. The readers interested in specifics of masu salmon can refer to this article. We have cited it in the revised manuscript. Lastly, we believe the reviewer has misread our results in the previous manuscript. Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best. This result remains the same in the improved analysis in the revised manuscript. Therefore, there is little evidence supporting the importance of detailed life-history processes in explaining long-term population dynamics for our dataset.

*We are not provided with any life history or hatchery-operation detail of Masu salmon or the other species examined. It is difficult to discern, for instance, how much hatchery salmon would overlap with other species in space or time.*

> We are glad that the reviewer caught this issue. We improved as follows:
>
> \- enriched the text explaining masu salmon's life history
>
> \- added species traits to Table S2
>
> \- added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix)
>
> As we clarified in the revised text, we are pretty sure that (hatchery) masu salmon interact with other species. Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches). In addition, there are numerous research documenting competition between masu salmon and other stream fish species. We have clarified these points in the revised manuscript.

*I did not see any attempt to estimate a competition coefficient among species (perhaps from diet and spatial overlap). This would also make the statistical analysis more compatible with the model.*

> Thank you, this is very important. To address this issue, we have developed a Bayesian Ricker model to estimate competition coefficients in our data (note: we used a subset of data because it requires non-sparse data to estimate parameters reliably). The results were very promising, supporting the considerable interspecific competition among stream fishes. We chose this approach to make it directly comparable with theoretical parameters. As the reviewer suggests, spatial/diet overlap may be useful, but it does not necessarily translate into "population" level interactions (in fact, estimated competition coefficients are varied greatly among sites for a given species pair). Therefore, our approach would give stronger evidence for interspecific competition occurring in natural systems.

*The Introduction of the paper does not set up the problem well. There is a large literature about captive breeding for enhancement, and an especially large literature for salmonids. For example, the paper suggests in line 45 that "use of captive breeding is perhaps because of the myth that the demographic benefits of released individuals may exceed the associated risks." This statement highlights that the introduction is not well grounded in the vast literature regarding the science and politics of hatcheries. Similarly, the discussion of the paper does not place this work in the larger body of scholarship around captive breeding for enhancement , salmon hatcheries, and salmon conservation.*

> XXX

\clearpage

# References

### 2022-10-19 rmd/reply_r1.Rmd
reply

@@
 Though the authors a couple of citations, I worry this system may be a bit niche for readers of PNAS.
-I recommend the authors describe specific case studies in the Discussion where similar dynamics may apply and point to the types of additional research needed to determine if similar inferences may apply in those systems.
-Also, it would be helpful to include (widely available) estimates of the extent of salmonid hatchery supplementation in North America, and to contextualize the dynamics estimated in the state space model for masu salmon relative to these other well-studied populations.*
+I recommend the authors describe specific case studies in the Discussion where similar dynamics may apply and point to the types of additional research needed to determine if similar inferences may apply in those systems.*
+
+> XXX
+
+*Also, it would be helpful to include (widely available) estimates of the extent of salmonid hatchery supplementation in North America, and to contextualize the dynamics estimated in the state space model for masu salmon relative to these other well-studied populations.*
 
@@
 > Thank you - we have given a deep thought on this.
-Masu salmon has a 1-year marine life stage (typically).
+Masu salmon has a 1-year marine life stage.
 However, many other species are also diadromous, and some of them return freshwater in a couple of months (e.g., amphidromous).
-Given the complexity of this system, we reconsidered our state-space model to account for up to AR3 process (fish species in our system typically 1-3 years of life-span).
+Given the complexity of this system, we reconsidered our state-space model to account for up to AR3 process (fish species in our system typically 1-3 years of life-span; see Methods for the revised model).
 The results were qualitatively similar.
@@
 However, we strongly believe that our result is important and worth publishing because to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long-term.
-Also, and perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system EVERY YEAR** (clarified in the revised manuscript)!
+Also, and perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)!
 This magnitude is way larger than the release program in our study system.
 Therefore, release numbers of $5\times$ carrying capacity seem even conservative to us.
-Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative scenario, rather than an extreme, unrealistic scenario.
+Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative scenario, rather than an unrealistic extreme scenario.
 >
-> Regarding the competition coefficient, please note that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition, i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species).
-The values in our simulation (0.25 or 0.50 in the revised manusucript) are thus weak enough to allow species co-existence in the absence of intentional release.
+> Regarding the competition coefficient, please find that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition -- i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species).
+The values in our simulation (0.25 or 0.50 in the revised manuscript) are thus weak enough to allow species co-existence in the absence of intentional release.
 Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions.
@@
 
-*But in the mean* $\mu$ *panel in Figure 1A, the enhanced population shows no effect of releases until about 2x carrying capacity, which seems significant.
+*...in the mean* $\mu$ *panel in Figure 1A, the enhanced population shows no effect of releases until about 2x carrying capacity, which seems significant.
 This appears to occur at the same time there is steep decline of the unenhanced species, even when the number of releases is below.*
@@
 We have cited it in the revised manuscript.
-Lastly, we believe the reviewer has misread our results in the previous manuscript.
+Lastly, we believe the reviewer misread our results in the previous manuscript.
 Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best.
@@
 >
-> \- enriched the text explaining masu salmon's life history
+> \- Enriched the text explaining masu salmon's life history; they spend at least one year in freshwater.
 >
-> \- added species traits to Table S2
+> \- Added species traits to Table S2.
 >
-> \- added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix)
+> \- Added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix).
 >
@@
 We chose this approach to make it directly comparable with theoretical parameters.
-As the reviewer suggests, spatial/diet overlap may be useful, but it does not necessarily translate into "population" level interactions (in fact, estimated competition coefficients are varied greatly among sites for a given species pair).
+As the reviewer suggests, spatial/diet overlap may be useful, but it does not necessarily translate into "population" level interactions (in fact, estimated competition coefficients varied greatly among sites for a given species pair).
 Therefore, our approach would give stronger evidence for interspecific competition occurring in natural systems.
@@
 
-> XXX
+> We appreciate the careful reading by the reviewer.
+We agree, and we have substantially improved the introduction and discussion to address this issue.
+Specifically, we now recognized that there are a number of cases where stock enhancement is economically successful -- we have mentioned these examples to properly develop a context.
+Also, where applicable, we have softened the language throughout the manuscript.
+If there are information/issues that we have missed, please let us know and we will address them too.
+This insightful comment helped a lot to avoid delivering wrong messages.
 

### 2022-10-19 rmd/manuscript.Rmd
rmd

@@
 Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@villanuaSanitaryRisksRedlegged2008; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
+In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [\@]negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
 There is growing awareness that intentional release entails ecological risks, including the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007], the spread of diseases in wild populations [@krkosekDecliningWildSalmon2007], and the intensification of intraspecific competition within the enhanced species [@kitadaLessonsLearnedJapanese2006].
@@
 
-It is noteworthy that the magnitude of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is comparable or even smaller when compared with those for other commercial and recreational species [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018].
-For example, 0.5 -- 1.2 million juveniles of Black sea bream are released annually in Kagoshima bay, Japan, where substantial declines in genetic diversity and wild individuals have been reported [@kitadaRigorousMonitoringLargescale2019].
-Similarly, three to four millions of Red-legged partridges are introduced repeatedly for sports hunting in rural Spain [@villanuaSanitaryRisksRedlegged2008].
-Therefore, our results should not be viewed as an extreme scenario.
-We also must mention that a meta-analysis focusing on fishery resources revealed that only a few massive release programs led to an increased abundance of the enhanced species [@arakiHatcheryStockingHelp2010].
-Yet, none of those studies statistically quantified the community-level impact of massive releases.
-Future studies addressing this knowledge gap are therefore highly valuable.
+It is noteworthy that the scale of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is fairly small when compared with those for other fishery resources [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018].
+For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017].
+Similarly, large-scale releases of Black sea bream (on average, 0.64 million juveniles annually) has been conducted in Kagoshima Bay since 1974 with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019].
+Although we do not know the carrying capacities of the recipient systems, it is clear that our results should not be viewed as an exceptional case.
+In support of this view, a meta-analysis revealed that only a few massive release programs led to an increased abundance of fishery resources [@arakiHatcheryStockingHelp2010].
+Yet, none of those studies statistically quantified the community-level impact.
+Future studies addressing this knowledge gap are therefore desired to generalize our findings.
 
@@
 Our results suggest that ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the stable delivery of ecosystem services [@cardinaleBiodiversityLossIts2012].
-While socioeconomic analysis is required to provide detailed guidance on how to improve release programs, it is clear for the sustainability of the natural resources that habitat conservation should be prioritized with a broader scope of ecosystem management.
-Such efforts are particularly important in the Anthropocene because habitat degradation may facilitate the undesired influence of intentional release by compromising the environmental capacity.
+We anticipate that the detrimental community-level consequence is not rare, or even pervasive, because many release programs are designed to aid declining populations [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019; @hilbornEconomicPerformanceMarine1998].
+In rural Spain, two million individuals of reared red-legged partridge, the most important game bird in this area, are introduced into the wild every year to overcome the regional decline of this species [@negroRAPDAnalysisDetection2001].
+In the US, a nation-wide initiative exists to augment populations of freshwater mussels, which are rapidly disappearing for enigmatic reasons over the past decades [@haagNorthAmericanFreshwater2012].
+The exact causes behind such population declines are often unknown or controversial, yet it is reasonable to assume that those habitats are no longer suitable and can support limited numbers of individuals (i.e., low carrying capacity).
+As such, the phenomenon observed in our study streams may be occurring broadly across taxa and ecosystems.
+
+While socioeconomic analysis is required to provide detailed guidance on release programs, it is clear that habitat conservation should be prioritized for the sustainability of the natural resources.
 Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is integral to achieving successful conservation.

### 2022-10-19 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [\@]negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
+In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
 There is growing awareness that intentional release entails ecological risks, including the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007], the spread of diseases in wild populations [@krkosekDecliningWildSalmon2007], and the intensification of intraspecific competition within the enhanced species [@kitadaLessonsLearnedJapanese2006].

### 2022-10-19 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
-There is growing awareness that intentional release entails ecological risks, including the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007], the spread of diseases in wild populations [@krkosekDecliningWildSalmon2007], and the intensification of intraspecific competition within the enhanced species [@kitadaLessonsLearnedJapanese2006].
+There is growing awareness that intentional release entails ecological risks, such as the accumulation of deleterious alleles and the intensified competition within the [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007; @kitadaLessonsLearnedJapanese2006].
 Yet, this method is still pervasive in natural resource management owing to the significant economic benefit [@malkamakiSystematicReviewSocioeconomic2018; @davidEconomicFeasibilityIntensification2018; @rutledgeCostBenefitHatcheryreared1990; @kitadaEconomicEcologicalGenetic2018].

### 2022-10-20 rmd/manuscript.Rmd
rmd

@@
 suppressMessages(source(here::here("code/set_rmd.R")))
+df_sim <- list_sim[[2]]
 
@@
 
-When carrying capacity was small ($K=$ `r min(list_param[[2]]$k)`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
-This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
+When carrying capacity was small ($K=$ `r min(list_param[[2]]$k)`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure** \@ref(fig:figure-layout)**A**).
+This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** \@ref(fig:figure-layout)**A**).
 The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure 1A**).
-Combined, the total community density decreased more sharply than individual species groups (**Figure 1A**).
-The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure 1A**).
+Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** \@ref(fig:figure-layout)**A**).
+Combined, the total community density decreased more sharply than individual species groups (**Figure** \@ref(fig:figure-layout)**A**).
+The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** \@ref(fig:figure-layout)**A**).
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
 These patterns were qualitatively similar across ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S3-S6**).
+
+```{r figure-layout, fig.cap= paste0("Theory and empirical observations agree that intentional release destabilizes community dynamics.
+In A and B, panels and colors distinguish response variables and species groups.
+(A) Theoretical predictions.
+Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and 50% prediction intervals (light shade).
+Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ ", round(na.omit(unique(df_sim$r1)), 2), ", average interspecific competition $\\bar{\\alpha}=$ ", round(na.omit(unique(df_sim$alpha)), 2), ", carrying capacity $K=$ ", round(na.omit(unique(df_sim$k)), 2), ", environmental stochasticity $\\sigma_{\\epsilon}=$ ", round(na.omit(unique(df_sim$sd_env)), 2), ", relative fitness of captive-bred individuals $f_R=$ ", round(na.omit(unique(df_sim$phi)), 2), ".
+These parameter values are comparable to the estimates of the multi-species Ricker model.
+(B) Empirical evidence.
+Dots represent observations at 97 sites within 31 watersheds.
+Lines and shades are the predicted values and their 95% credible intervals of the regression models, and line types correspond to the coefficient's posterior probabilities.
+Effective release is a latent explanatory variable estimated in our hierarchical Baysian model.
+See Methods for details.
+Full statistics were reported in Tables S6-8.
+(C) Map of sampling sites (black dots) in Hokkaido, Japan.
+(D) Example of a protected watershed (Okushibetsu).
+(E) Masu salmon *Oncorhynchus masou*.
+Photo credit: Akira Terui")}
+
+knitr::include_graphics(here::here("output/figure_theory_obs.pdf"))
+
+```
 
@@
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure** \@ref(fig:figure-layout)**E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
 In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records.
@@
 
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure 1B**).
+```{r figure-coef, fig.cap="Posterior distributions for the standardized regression coefficients of intentional release.
+Y-axis represents different response variables grouped by colors distinguishing species groups (whole community, enhanced species [masu salmon], and unenhanced species).
+Triangles indicate median estimates."}
+
+knitr::include_graphics(here::here("output/figure_coef.pdf"))
+
+```
+
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** \@ref(fig:figure-layout)**B**).
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure 2**; see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
-This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6-S8** for full statistics).
-In the meantime, the SDs had vague relationships with the intentional release (**Figures 1B and 2**).
+Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** \@ref(fig:figure-coef); see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
+This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)**;** see **Tables S6-S8** for full statistics).
+In the meantime, the SDs had vague relationships with the intentional release (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)).
 
@@
 The parameter estimates of this model are directly comparable to those used in the theoretical Ricker model.
-The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure 3**), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
+The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure** \@ref(fig:figure-alpha)), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
 Our statistical inference is supported by previous studies.
-For example, interference competition between masu salmon and other salmonid species is well documented [@miyasakaFoodHabitDivergence2003; @hasegawaComparisonCompetitiveAbility2004].
-Diets of salmonid species are innately overlapped (e.g., drift terrestrial insects), such that they interfere with each other for profitable foraging spots [@hasegawaComparisonCompetitiveAbility2004].
-Exploitative competition between masu salmon and benthic fish (e.g., sculpins and stone loaches in our study system) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014] that many benthic fish species prey on [@natsumedaEvaluationEcologicalFeatures2010; @natsumedaDietFoodSelectivity2012].
+For example, competition between masu salmon and other salmonid species is well documented, and its form can be interference or exploitative [@miyasakaFoodHabitDivergence2003; @hasegawaComparisonCompetitiveAbility2004; @moritaImpactExoticTrout2004a].
+Diets of salmonid species are innately overlapped, and they interfere with each other to claim profitable foraging spots for drift insects [@hasegawaComparisonCompetitiveAbility2004] or cruise over a large area in search of prey [@hasegawaEffectFlowRegime2010].
+Exploitation competition between masu salmon and benthic fish (e.g., sculpins and stone loaches in our study system) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014] that many benthic fish species prey on [@natsumedaEvaluationEcologicalFeatures2010; @natsumedaDietFoodSelectivity2012].
 Importantly, hatchery masu salmon may intensify intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
@@
 For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017].
-Similarly, large-scale releases of Black sea bream (on average, 0.64 million juveniles annually) has been conducted in Kagoshima Bay since 1974 with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019].
+Similarly, large-scale releases of Black sea bream (on average, 0.64 million juveniles annually) has been conducted in Kagoshima Bay (Japan) since 1974 with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019].
 Although we do not know the carrying capacities of the recipient systems, it is clear that our results should not be viewed as an exceptional case.
-In support of this view, a meta-analysis revealed that only a few massive release programs led to an increased abundance of fishery resources [@arakiHatcheryStockingHelp2010].
+In support of this view, a meta-analysis revealed that only a few massive release programs in fisheries led to an increased abundance of the focal species [@arakiHatcheryStockingHelp2010].
 Yet, none of those studies statistically quantified the community-level impact.
@@
 For example, any form of exploitation, including angling, is prohibited in these areas.
-In addition, exclusive permission is required to physically alter in-stream and riparian habitats.
+In addition, exclusive permission from a governer of Hokkaido is required to physically alter in-stream and riparian habitats.
 Therefore, unmeasured human influences should have minimal influences on the observed relationships.
@@
 Unfortunately, these methods were not applicable to our data because they require a longer and non-sparse time series to yield robust results.
+
+```{r figure-alpha, fig.cap="Estimated competition coefficients of the multi-species Ricker model.
+Dots represent a given pair of taxa, and box plots show median (vertical center line) and quartiles (box limits) with whiskers extending up to the most extreme data points that are within ±1.5 interquartile range.
+The density plot on the top shows the overall distribution of the competition coefficient.
+Colors distinguish taxa."}
+
+source(here::here("code/si_figure_species_int.R"))
+
+knitr::include_graphics(here::here("output/figure_alpha_dist.pdf"))
+```
 
@@
 In rural Spain, two million individuals of reared red-legged partridge, the most important game bird in this area, are introduced into the wild every year to overcome the regional decline of this species [@negroRAPDAnalysisDetection2001].
-In the US, a nation-wide initiative exists to augment populations of freshwater mussels, which are rapidly disappearing for enigmatic reasons over the past decades [@haagNorthAmericanFreshwater2012].
+In the US, a nation-wide initiative exists to augment populations of freshwater mussels, which are rapidly disappearing over the past decades for enigmatic reasons [@haagNorthAmericanFreshwater2012].
 The exact causes behind such population declines are often unknown or controversial, yet it is reasonable to assume that those habitats are no longer suitable and can support limited numbers of individuals (i.e., low carrying capacity).
-As such, the phenomenon observed in our study streams may be occurring broadly across taxa and ecosystems.
+As long as this important theoretical condition of limited carrying capacity holds true, the phenomenon observed in our study streams may occur broadly across taxa and ecosystems.
 

### 2022-10-20 code/set_rmd.R

@@ -55,7 +55,7 @@ list_param <- list_sim %>%
 source(here::here("code/data_fmt_fishdata.R"))
 source(here::here("code/data_fmt_reg.R"))
 source(here::here("code/data_fmt_stock.R")) # call `df_stock_mu`
-source(here::here("code/figure_obs_stock.R")) # call `df_beta`
+source(here::here("code/figure_layout.R")) # call `df_sim`, `df_beta`
 source(here::here("code/si_figure_species_int.R")) # call `df_pd`
 
 df_stock_stage <- df_stock %>% 

### 2022-10-20 code/figure_obs_coef.R
figure

@@ -81,5 +81,5 @@ g_coef <- df_mcmc %>%
 
 ggsave(g_coef,
        filename = here::here("output/figure_coef.pdf"),
-       width = 8,
-       height = 6)
+       width = 7,
+       height = 4.5)

### 2022-10-20 code/figure_theory.R

@@ -9,7 +9,7 @@ source(here::here("code/library.R"))
 ## call `sim_result`
 sim_result <- readRDS(file = here::here("output/result_ricker.rds"))
 
-df0 <- sim_result %>% 
+df_sim <- sim_result %>% 
   mutate(cv = sd_density / mean_density) %>% 
   pivot_longer(cols = mean_density:cv,
                names_to = "response",
@@ -41,7 +41,7 @@ df0 <- sim_result %>%
                                            "SD~sigma~(ind.)")))
 
 ## loess prediction with prediction intervals
-df1 <- df0 %>% 
+df1 <- df_sim %>% 
   filter(status != "dummy") %>% 
   group_by(status,
            group_id,
@@ -75,7 +75,7 @@ df_plot <- lapply(seq_len(nrow(df1)),
 source(here::here("code/set_figure_theme.R"))
 theme_set(plt_theme)
 
-g_theory <- df0 %>% 
+g_theory <- df_sim %>% 
   ggplot(aes(y = value,
              x = stock,
              color = group_id,
@@ -89,13 +89,13 @@ g_theory <- df0 %>%
                   ymax = upper),
               alpha = 0.4,
               color = grey(0, alpha = 0)) +
-  # geom_point(data = df0 %>% filter(status == "enhanced"),
+  # geom_point(data = df_sim %>% filter(status == "enhanced"),
   #            size = pt_size,
   #            color = hue_pal(h.start = hs[2], l = lum, c = con)(1)) +
-  # geom_point(data = df0 %>% filter(status == "unenhanced"),
+  # geom_point(data = df_sim %>% filter(status == "unenhanced"),
   #            size = pt_size,
   #            color = hue_pal(h.start = hs[3], l = lum, c = con)(1)) +
-  # geom_point(data = df0 %>% filter(status == "all"),
+  # geom_point(data = df_sim %>% filter(status == "all"),
   #            size = pt_size,
   #            color = hue_pal(h.start = hs[1], l = lum, c = con)(1)) +
   geom_smooth(size= 0.5,

### 2022-10-20 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{\sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
+(\#eq:ricker0)
 \end{align}
@@
 ```
-Equation \@ref(eq:ricker-ssm) is equivalent to Equation \@ref(eq:ricker) except the scale of competition coefficients $\alpha'_{ij}$ ($\frac{\alpha'_{ij}}{\alpha'_{ii}}=\alpha_{ij}$, where $\alpha'_{ii}=\frac{r_i}{K_i}$).
+Equation \@ref(eq:ricker-ssm) is equivalent to Equation \@ref(eq:ricker0) except the scale of competition coefficients $\alpha'_{ij}$ ($\frac{\alpha'_{ij}}{\alpha'_{ii}}=\alpha_{ij}$, where $\alpha'_{ii}=\frac{r_i}{K_i}$).
 We used sparse priors for $\alpha'_{ij}$ to reduce the risk of over-fitting [@mutshindaWhatDrivesCommunity2009]:

### 2022-10-20 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 suppressMessages(source(here::here("code/set_rmd.R")))
-df_sim <- list_sim[[2]]
 
@@
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
-These patterns were qualitatively similar across ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S3-S6**).
+These patterns were qualitatively similar across ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S3 -- S6**).
 
@@
 
-The intentional release had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S7-S10**).
+The intentional release had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S7 -- S10**).
 In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S7**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective.
@@
 
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** \@ref(fig:figure-layout)**B**).
+The effect was striking in its magnitude, almost doubling the CV at the highest release level.
+Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** \@ref(fig:figure-coef); see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
+This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)**;** see **Tables S6 -- S8** for full statistics).
+In the meantime, the SDs had vague relationships with the intentional release (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)).
+
 ```{r figure-coef, fig.cap="Posterior distributions for the standardized regression coefficients of intentional release.
@@
 ```
-
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** \@ref(fig:figure-layout)**B**).
-The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** \@ref(fig:figure-coef); see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
-This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)**;** see **Tables S6-S8** for full statistics).
-In the meantime, the SDs had vague relationships with the intentional release (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)).
 
@@
 For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017].
-Similarly, large-scale releases of Black sea bream (on average, 0.64 million juveniles annually) has been conducted in Kagoshima Bay (Japan) since 1974 with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019].
+Similarly, the large-scale release of Black sea bream has been conducted in Kagoshima Bay (Japan) since 1974 (the yearly-average of 0.64 million juveniles) with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019].
 Although we do not know the carrying capacities of the recipient systems, it is clear that our results should not be viewed as an exceptional case.
@@
 The density plot on the top shows the overall distribution of the competition coefficient.
-Colors distinguish taxa."}
+Colors distinguish taxa.
+The vertical broken line denotes the overall median value."}
 

### 2022-10-20 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Our statistical inference is supported by previous studies.
-For example, competition between masu salmon and other salmonid species is well documented, and its form can be interference or exploitative [@miyasakaFoodHabitDivergence2003; @hasegawaComparisonCompetitiveAbility2004; @moritaImpactExoticTrout2004a].
+For example, competition between masu salmon and other salmonid species is well documented, and its form can be interference or exploitative [@miyasakaFoodHabitDivergence2003; @hasegawaComparisonCompetitiveAbility2004; @moritaImpactExoticTrout2004].
 Diets of salmonid species are innately overlapped, and they interfere with each other to claim profitable foraging spots for drift insects [@hasegawaComparisonCompetitiveAbility2004] or cruise over a large area in search of prey [@hasegawaEffectFlowRegime2010].

### 2022-10-20 rmd/manuscript.Rmd
rmd

@@
 (A) Theoretical predictions.
-Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and 50% prediction intervals (light shade).
-Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ ", round(na.omit(unique(df_sim$r1)), 2), ", average interspecific competition $\\bar{\\alpha}=$ ", round(na.omit(unique(df_sim$alpha)), 2), ", carrying capacity $K=$ ", round(na.omit(unique(df_sim$k)), 2), ", environmental stochasticity $\\sigma_{\\epsilon}=$ ", round(na.omit(unique(df_sim$sd_env)), 2), ", relative fitness of captive-bred individuals $f_R=$ ", round(na.omit(unique(df_sim$phi)), 2), ".
-These parameter values are comparable to the estimates of the multi-species Ricker model.
+Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and prediction intervals (light shade).
+Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ ", round(na.omit(unique(df_sim$r1)), 2), ", average interspecific competition $\\bar{\\alpha}=$ ", round(na.omit(unique(df_sim$alpha)), 2), ", carrying capacity $K=$ ", round(na.omit(unique(df_sim$k)), 2), ", environmental stochasticity $\\sigma_{\\varepsilon}=$ ", round(na.omit(unique(df_sim$sd_env)), 2), ", relative fitness of captive-bred individuals $f_R=$ ", round(na.omit(unique(df_sim$phi)), 2), ".
+These parameter values are comparable to those estimated in the empirical Ricker model.
 (B) Empirical evidence.
@@
 Typically, hatchery masu salmon are reared in captivity for two to four generations.
-Thus, the fitness decline may be substantial.
-In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003].
-The multiple fitness disadvantages may add to negative density dependence to influence community stability.
+Given the duration of the extensive release program (\> 60 years), it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines.
+This effect may add to negative density dependence to influence community stability.
 
@@
 ```{r figure-alpha, fig.cap="Estimated competition coefficients of the multi-species Ricker model.
-Dots represent a given pair of taxa, and box plots show median (vertical center line) and quartiles (box limits) with whiskers extending up to the most extreme data points that are within ±1.5 interquartile range.
+Dots represent a given pair of taxa, and box plots show median (vertical center line) and quartiles (box limits) with whiskers extending up to the most extreme data points that are within $\\pm 1.5$ interquartile range.
 The density plot on the top shows the overall distribution of the competition coefficient.

### 2022-10-20 rmd/reply_r1.Rmd
rmd

@@
 
-Dear Editor,
+Dear editor,
 
-Thank you for giving us the opportunity to revise our manuscript.
-The comments were very helpful to improve our manuscript.
-When revising the manuscript, we have put a particular emphasis on the following points:
+Thank you for allowing us to revise our manuscript. The comments were very helpful in improving our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:
 
@@
 We agree with this comment.
-To address this issue, we revised the text to better contextualize our work.
-In particular, we have carefully reviewed cases to which our findings may apply, and discussed the relevance of our work to those systems.
+We revised the text to contextualize our work better to address this issue.
+In particular, we have carefully reviewed cases to which our findings may apply and discussed the relevance of our work to those systems.
 2.
-**Two-species simulation.** The Editor suggested to include a two-species simulation to guide the full community model.
-We really appreciate this suggestion and were able to draw deeper insights into our theoretical analysis.
-This improvement helped address the concern raised by the reviewer 2 (they pointed the lack of depth in theoretical analysis).
-We revised Methods and Results in accordance with this change.
+**Two-species simulation.** The Editor suggested including a two-species simulation to guide the full community model.
+We appreciated this suggestion and were able to draw deeper insights into our theoretical analysis.
+This improvement helped address the concern raised by reviewer 2 (they pointed out the lack of depth in theoretical analysis).
+We revised the Methods and Results following this change.
 In particular, we removed the old sensitivity analysis as it was redundant with two-species simulations.
 3.
-**Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed that the interpretation of our empirical analysis is superficial -- we agree with this comment too.
+**Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed out that the interpretation of our empirical analysis is superficial -- we agree with this comment too.
 We have carefully enriched the text related to this issue.
-We have greatly increased the number of citations and discussed more carefully possible mechanisms that may produce the observed patterns.
+We have greatly increased the number of citations and discussed possible mechanisms that may produce the observed patterns more carefully.
 In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities.
 The estimated parameter indicated that competition among species certainly exists.
-4.  **Life history of masu salmon.** Lastly, we enriched the text for life history of masu salmon and how release programs for this species are operated.
+4.  **Life history of masu salmon.** Lastly, we enriched the text for the life history of masu salmon and how release programs for this species are operated.
 
@@
 
-Akira Terui on behalf of the authors
+Akira Terui, on behalf of the authors
 
@@
 
-*Because the Ricker model can yield damped oscillations, limit cycles, and even chaos depending on intrinsic growth rate, I would have first understood the impact of population supplementation analytically in a deterministic two species system.
+*Because the Ricker model can yield damped oscillations, limit cycles, and even chaos depending on the intrinsic growth rate, I would have first understood the impact of population supplementation analytically in a deterministic two species system.
 This is straightforward and relevant since the tendency to experience fluctuations without stochasticity is the baseline for your model.
 Moreover, this analysis can illuminate how you organize any exploration of parameter space.
-In particular, I would vary intrinsic rate of increase so that it captured monotonic convergence to equilibrium, damped oscillations en route to equilibrium, limit cycle, and chaos....The results reported from the model lack depth - especially considering the many possible parameter combinations.
+In particular, I would vary the intrinsic rate of increase so that it captured monotonic convergence to equilibrium, damped oscillations en route to equilibrium, limit cycle, and chaos....The results reported from the model lack depth - especially considering the many possible parameter combinations.
 Since the Ricker model can produce fluctuations deterministically, the tendency to fluctuate deterministically (which is governed by intrinsic rate of increase) should be used to organize the simulation results.
@@
 We followed this direction, analyzing the model in a two-species community to guide a whole community analysis.
-As we detailed in the maintext, the different combinations of $r$ and $K$ produced distinct parameter spaces where intentional release had destabilizing, neutral, and stabilizing effects.
-Stabilizing effects appeared when the community shows limit cycles or chaos; otherwise, intentional release had destabilizing effects in general.
+As we detailed in the main text, the different combinations of $r$ and $K$ produced distinct parameter spaces where intentional release had destabilizing, neutral, and stabilizing effects.
+Stabilizing effects appeared when the community showed limit cycles or chaos; otherwise, the intentional release had destabilizing effects in general.
 We have clarified this point in the revised manuscript (see section **Theoretical prediction**).
@@
 
-> XXX
+> We have now used relevant values in the simulation.
+Myer et al @myersMaximumReproductiveRate1999 has provided a comprehensive list of ricker model parameters, so we referenced this work.
+Specifically, r = 1.5 seems a reasonable proxy for masu salmon and other salmonid species.
+Also, we changed the value of competition to make it comparable to our estimates of $\alpha_{ij}$ ($\approx 0.25$).
+The value of $\sigma_{\varepsilon}$ in the original analysis was also comparable.
 
@@
 You contrive extinction to be an N = .01 or lower.
-In your words "the number of species persist (defied as 𝑁𝑖 \> 0.01 at 𝑡 = 1600)".
+In your words "the number of species persist (defined as N \> 0.01 at t = 1600)".
 Apart from the typo it is not clear to me if you:\
@@
 2) whenever a species' population falls below .01 during the course of the potential 1600 time steps, that species is considered extinct.
-So if at time step 634, N fell to .005, that would then be an absorbing boundary and the species is removed from the simulation.\
-\
+So if at time step 634, N fell to .005, that would then be an absorbing boundary and the species is removed from the simulation.
 It is essential that you make clear whether it is #1 or #2 above that accounts for the loss of species.*
 
-> XXX
+> Although we used #1 in the previous version, we thought this was not the best - in the revised manuscript, we used #2. We clarified this point in the revised Methods.
 
-*Both reviewers noted an absence of context, and literature cited that might better provide a framework for this study.
+*Both reviewers noted an absence of context and literature cited that might better provide a framework for this study.
 What other species might this apply to?
 What are levels of supplementation in other salmon systems?
-The discussion does not place the work in the context of general research regarding captive breeding for enhancement, salmon hatcheries, and salmon conservation.*
+The Discussion does not place the work in the context of general research regarding captive breeding for enhancement, salmon hatcheries, and salmon conservation.*
 
-> XXX
+> Agreed.
+We have greatly improved the introduction and Discussion (paragraph L184 --, paragraph L208 --).
+We have clarified that our findings seem quite general for two reasons.
+(1) the scale of other release programs (mussels, crustaceans, birds, insects, and other fish) is generally way larger than our release program.
+For example, the largest release program for pink salmon in Alaska releases \> 600 million fish year^-1^ (note: our program releases only 0.24 million fish per year at the most intense site).
+(2) Most release programs aim to help declining populations in degraded habitats.
+In these habitats, the carrying capacities are likely compromised - a theoretical premise for the destabilizing effect to emerge.
 
-*The discussion of the masu data is too superficial.
+*The Discussion of the masu data is too superficial.
 You need to include more about their life history and the supplementation systems.
@@
 
-> XXX
+> We have addressed the concerns raised by the reviewers.
+Please see our response to specific comments.
+Also, we have improved our regression analysis to account for the spatial overlap of hatchery salmon and other wild fishes.
+Since we do not have exact information on where hatchery fish are released (we have partial information -- updated our map to include this information; see Figure 1C), we performed the *post hoc* estimation of spatial overlap within the regression model (see Methods, "effective release").
+We believe this will increase the validity of our results as it enabled us to use 97 site replicates fully to estimate the effect of releases.
 
@@
 
-> XXX
+> We have rephrased.
 
@@
 
-> XXX
+> Thank you for the great comment!
+As you can see in our response to the editor's comment, we have greatly improved the introduction and Discussion (paragraph L208 --).
+We believe our findings are broadly applicable across taxa and ecosystems.
 
@@
 
-> XXX
+> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (paragraph L184 --).
 
@@
 > Masu salmon spend at least one year before sea migration (they show partial migration, and some males stay in freshwater for their entire life).
-We have clarified details of masu salmon's life history.
+We have clarified the details of masu salmon's life history.
 
@@
 
-> Thank you - we have given a deep thought on this.
+> Thank you - we have given deep thought to this.
 Masu salmon has a 1-year marine life stage.
-However, many other species are also diadromous, and some of them return freshwater in a couple of months (e.g., amphidromous).
-Given the complexity of this system, we reconsidered our state-space model to account for up to AR3 process (fish species in our system typically 1-3 years of life-span; see Methods for the revised model).
+However, many other species are also diadromous; some return freshwater in a couple of months (e.g., amphidromous).
+Given the complexity of this system, we reconsidered our state-space model to account for up to the AR3 process (fish species in our system typically have 1-3 years of lifespan; see Methods for the revised model).
 The results were qualitatively similar.
@@
 
-> XXX
+> Good point -- unfortunately, we do not have any data to show quantitative patterns.
+The "hatchery" gene has likely spread within the wild populations, given the duration of the extensive release programs.
+We have briefly mentioned this in the revised text (paragraph L169 --).
 
@@
 Since our watersheds are "protected" watersheds, any form of exploitation (including angling) is not allowed (regardless of fish species).
-Therefore, other factors are very unlikely to shape the observed patterns of temporal community variability.
-Please note that we have statistically accounted for natural variation in land use, watershed size, climate etc.
+Therefore, other factors are unlikely to shape the observed patterns of temporal community variability.
+Please note that we have statistically accounted for natural variations in land use, watershed size, climate etc.
 
@@
 
-*The general model seems logical in that there is a non-linear response to numbers of releases.
+*The general model seems logical in that there is a non-linear response to the number of releases.
 It does not seem too surprising that when releases are 5x carrying capacity that there is a negative impact, especially given a fairly large alpha.*
@@
 > We agree that our results are not surprising -- we are not surprised either.
-However, we strongly believe that our result is important and worth publishing because to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long-term.
-Also, and perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)!
+However, we strongly believe that our result is important and worth publishing because, to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long term.
+Also, perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)!
 This magnitude is way larger than the release program in our study system.
-Therefore, release numbers of $5\times$ carrying capacity seem even conservative to us.
-Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative scenario, rather than an unrealistic extreme scenario.
+Therefore, release numbers of $5\times$ carrying capacity seem conservative to us.
+Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative rather than an unrealistic extreme scenario.
 >
 > Regarding the competition coefficient, please find that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition -- i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species).
-The values in our simulation (0.25 or 0.50 in the revised manuscript) are thus weak enough to allow species co-existence in the absence of intentional release.
+The values in our simulation (0.25 or 0.50 in the revised manuscript) are thus weak enough to allow species co-existence without intentional release.
 Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions.
@@
 *...in the mean* $\mu$ *panel in Figure 1A, the enhanced population shows no effect of releases until about 2x carrying capacity, which seems significant.
-This appears to occur at the same time there is steep decline of the unenhanced species, even when the number of releases is below.*
+This appears to occur at the same time there is a steep decline of the unenhanced species, even when the number of releases is below.*
 
 > Thank you for this comment.
-We agree that this pattern is important, and we do acknowledge that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**).
+We agree that this pattern is important, and we acknowledge that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**).
 However, our focus here is not the influence of intentional release on the enhanced species -- we are interested in how unenhanced species respond to the intentional release.
-This is the knowledge gap we are trying to fill, as no study has focused on this "side-effect" of intentional release so far.
+This is the knowledge gap we are trying to fill, as no study has focused on this "side-effect" of intentional release.
 We hope the reviewer will understand the significance of this finding.
@@
 
-> Thank you for this critical comment. Following the editor's suggestion, we have greatly improved the analysis by introducing two-species simulations (see our response to editor).
+> Thank you for this critical comment. Following the editor's suggestion, we have greatly improved the analysis by introducing two-species simulations (see our response to the editor).
 
@@
 However, we decided not to perform this analysis for the following reasons.
-First, given the readership of PNAS, as well as the suggestions from reviewer 1 and editor, we believe it is important to keep our model as general as possible.
-In fact, as clarified in the revised manuscript, there are a number of cases where our phenomenological model may apply.
-Second, a detailed life-history model has already been developed by Morita et al.
-[@moritaTemperaturedependentVariationAlternative2014].
-The readers interested in specifics of masu salmon can refer to this article.
+First, given the readership of PNAS and the suggestions from reviewer 1 and the editor, we believe it is important to keep our model as general as possible.
+In fact, as clarified in the revised manuscript, there are many cases where our phenomenological model may apply.
+Second, Morita et al.
+have already developed a detailed life-history model [@moritaTemperaturedependentVariationAlternative2014].
+Readers interested in the specifics of masu salmon can refer to this article.
 We have cited it in the revised manuscript.
@@
 Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches).
-In addition, there are numerous research documenting competition between masu salmon and other stream fish species.
+In addition, numerous research documents competition between masu salmon and other stream fish species.
 We have clarified these points in the revised manuscript.
@@
 We chose this approach to make it directly comparable with theoretical parameters.
-As the reviewer suggests, spatial/diet overlap may be useful, but it does not necessarily translate into "population" level interactions (in fact, estimated competition coefficients varied greatly among sites for a given species pair).
+As the reviewer suggests, spatial/diet overlap may be useful.
+However, it does not necessarily translate into "population" level interactions (estimated competition coefficients varied greatly among sites for a given species pair).
 Therefore, our approach would give stronger evidence for interspecific competition occurring in natural systems.
@@
 *The Introduction of the paper does not set up the problem well.
-There is a large literature about captive breeding for enhancement, and an especially large literature for salmonids.
-For example, the paper suggests in line 45 that "use of captive breeding is perhaps because of the myth that the demographic benefits of released individuals may exceed the associated risks." This statement highlights that the introduction is not well grounded in the vast literature regarding the science and politics of hatcheries.
-Similarly, the discussion of the paper does not place this work in the larger body of scholarship around captive breeding for enhancement , salmon hatcheries, and salmon conservation.*
+There is a large literature about captive breeding for enhancement and an especially large literature for salmonids.
+For example, the paper suggests in line 45 that the "use of captive breeding is perhaps because of the myth that the demographic benefits of released individuals may exceed the associated risks." This statement highlights that the introduction is not well grounded in the vast literature regarding the science and politics of hatcheries.
+Similarly, the Discussion of the paper does not place this work in the larger body of scholarship around captive breeding for enhancement, salmon hatcheries, and salmon conservation.*
 
 > We appreciate the careful reading by the reviewer.
-We agree, and we have substantially improved the introduction and discussion to address this issue.
-Specifically, we now recognized that there are a number of cases where stock enhancement is economically successful -- we have mentioned these examples to properly develop a context.
+This insightful comment helped a lot to avoid delivering the wrong messages.
+We agree and have substantially improved the introduction and Discussion to address this issue.
+Specifically, we now recognize that there are many cases where stock enhancement is economically successful -- we have mentioned these examples to develop a context properly.
 Also, where applicable, we have softened the language throughout the manuscript.
-If there are information/issues that we have missed, please let us know and we will address them too.
-This insightful comment helped a lot to avoid delivering wrong messages.
+If there are information/issues that we have missed, please let us know, and we will address them too.
 

### 2022-10-20 code/run_simulation_analytical.R
Update run_simulation_analytical.R

@@ -17,7 +17,7 @@ df_param <- expand.grid(n_timestep = 1000,
                         k = seq(50, 500, length = 20),
                         r_type = "constant",
                         r1 = seq(0.5, 3.5, length = 20),
-                        sd_env = c(0, 0.75),
+                        sd_env = c(0, 0.5),
                         phi = 1,
                         int_type = "constant",
                         alpha = c(0.25, 0.5),
@@ -46,6 +46,10 @@ result <- foreach(x = iter(df_param, by = 'row'),
                     df_set <- foreach(j = seq_len(n_rep),
                                       .combine = "bind_rows") %do% {
                                         
+                                        ## for reproducibility
+                                        set.seed(j)
+                                        
+                                        ## simulation
                                         dyn <- cdynsim(n_timestep = x$n_timestep,
                                                        n_warmup = x$n_warmup,
                                                        n_burnin = x$n_burnin,

### 2022-10-20 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
-There is growing awareness that intentional release entails ecological risks, such as the accumulation of deleterious alleles and the intensified competition within the [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007; @kitadaLessonsLearnedJapanese2006].
+There is growing awareness that intentional release entails ecological risks, such as the accumulation of deleterious alleles and the intensified competition within the enhanced species [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007; @kitadaLessonsLearnedJapanese2006].
 Yet, this method is still pervasive in natural resource management owing to the significant economic benefit [@malkamakiSystematicReviewSocioeconomic2018; @davidEconomicFeasibilityIntensification2018; @rutledgeCostBenefitHatcheryreared1990; @kitadaEconomicEcologicalGenetic2018].

### 2022-10-21 rmd/reply_r1.Rmd
Update reply_r1.Rmd

@@
 2.
-**Two-species simulation.** The Editor suggested including a two-species simulation to guide the full community model.
+**Two-species simulation.** The editor suggested including a two-species simulation to guide the full community model.
 We appreciated this suggestion and were able to draw deeper insights into our theoretical analysis.
-This improvement helped address the concern raised by reviewer 2 (they pointed out the lack of depth in theoretical analysis).
+At the same time, this improvement helped address the concern raised by reviewer 2 (they pointed out the lack of depth in theoretical analysis).
 We revised the Methods and Results following this change.
@@
 3.
-**Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed out that the interpretation of our empirical analysis is superficial -- we agree with this comment too.
-We have carefully enriched the text related to this issue.
-We have greatly increased the number of citations and discussed possible mechanisms that may produce the observed patterns more carefully.
+**Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed out that the interpretation of our empirical analysis is superficial; we agree with this comment.
+We have enriched the text pertinent to this issue.
+We have greatly increased the number of citations and discussed possible mechanisms (e.g., diet overlap, exploitative competition) that may produce the observed patterns more carefully.
 In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities.
@@
 
-We appended a point-by-point response below. We hope our manuscript is now suitable for publication in your journal.
+In summary, the improved text/analysis provided clearer evidence that intentional release has destabilizing effects and clarified its broader relevance to other systems.
+We appended a point-by-point response below.
+We hope our manuscript is now suitable for publication in your journal.
 
@@
 Stabilizing effects appeared when the community showed limit cycles or chaos; otherwise, the intentional release had destabilizing effects in general.
-We have clarified this point in the revised manuscript (see section **Theoretical prediction**).
+We have clarified this point in the revised manuscript (see section **Theoretical prediction**; see also **Figures S1 and S2**).
 
@@
 > Agreed.
-We have greatly improved the introduction and Discussion (paragraph L184 --, paragraph L208 --).
+We have greatly improved the introduction and Discussion (paragraph L185 --, paragraph L209 --).
 We have clarified that our findings seem quite general for two reasons.

### 2022-10-21 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
-These patterns were qualitatively similar across ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S3 -- S6**).
+These patterns were qualitatively similar across ecological contexts with the low carrying capacity (**Figures S3 -- S6**), but except for the scenario in which the enhanced species exhibits chaos ($r_1=$ `r max(list_param[[2]]$r1)`).
 
@@
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** \@ref(fig:figure-coef); see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**).
+Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** \@ref(fig:figure-coef); see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob) %>% round(2), 2)` (**Table S6**).
 This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)**;** see **Tables S6 -- S8** for full statistics).
@@
 
-It is noteworthy that the scale of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is fairly small when compared with those for other fishery resources [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018].
+It is noteworthy that the scale of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is comparable or even smaller when compared with those for other fishery resources [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018].
 For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017].
@@
 For example, any form of exploitation, including angling, is prohibited in these areas.
-In addition, exclusive permission from a governer of Hokkaido is required to physically alter in-stream and riparian habitats.
+In addition, exclusive permission from the governer of Hokkaido is required to physically alter in-stream and riparian habitats.
 Therefore, unmeasured human influences should have minimal influences on the observed relationships.

### 2022-10-21 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 mainfont: "Times New Roman"
-fontsize: 11pt
+fontsize: 10.5pt
 knit: (function(inputFile, encoding) {
@@
 **Fish release.** The release of masu salmon began in the 1950s.
+Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years.
 Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage).
-Although the fish release occurs at multiple locations within a watershed, the release information is available only at the watershed level.
-For each release stage, we assembled annual records of intentional release (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
+Most fish are released near the fish survey sites.
+However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable.
+For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
 During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
@@
 \begin{split}
-R'_s &= \eta_{w,s'} R_w\\
-\sum_{s'}^{S_w + 1} \eta_{w,s'} &= 1
+R'_s = \eta_{w,s'} R_w~\text{where}~
+\sum_{s'}^{S_w + 1} \eta_{w,s'} = 1
 (\#eq:effr)
@@
 \begin{split}
-N_{i,t} \sim \text{Poisson}(\lambda_{i,t} A_{t})\\
-\lambda_{s,t} = n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})
+N_{i,t} &\sim \text{Poisson}(\lambda_{i,t} A_{t})\\
+\lambda_{s,t} &= n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})
 \end{split}
@@
 
-The analysis of a two-species community revealed the distinct parameter space predicting a stabilizing, neutral, or destabilizing effect of intentional release.
+The analysis of a two-species community revealed the distinct parameter spaces predicting a stabilizing, neutral, or destabilizing effect of intentional release.
 The left column in **Figure S**\@ref(fig:fig-2sp-w)**A** shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`).
 For lower values of intrinsic growth rate $r_i$ ($<1.5$), intentional release had neutral (with higher $K$) to destabilizing effects (with lower $K$) on community dynamics.
-In the meantime, stabilization with intentional release occurred for higher values of $r_i$ ($\ge 1.5$) by dampening limit cycles or chaos (**Figure S**\@ref(fig:fig-2sp-s)), which is reflected in decreased SD $\sigma$ (**Figure S**\@ref(fig:fig-2sp-w)).
+In the meantime, stabilization with intentional release occurred for higher values of $r_i$ ($\ge 1.5$) by dampening limit cycles or chaos (**Figure S**\@ref(fig:fig-2sp-w)), which is reflected in decreased SD $\sigma$ (**Figure S**\@ref(fig:fig-2sp-w)).
 However, the long-term mean of community density $\mu$ consistently decreased with intentional release in almost all cases except for only a few combinations of $r_i$ and $K$ (**Figure S**\@ref(fig:fig-2sp-w)).

### 2022-10-21 rmd/manuscript.Rmd
rmd

@@
 Consequently, the ecological community with the intentional release is predicted to show reduced community density with unstable temporal dynamics.
-Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery salmon - a major fishery resource worldwide.
-Our findings alarm that the current overreliance on intentional release may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.
+Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery salmon -- a major fishery resource worldwide.
+Our findings alarm that the current overreliance on intentional release may accelerate global biodiversity loss with undesired consequences for the provisioning of ecosystem services.
 
@@
 However, we know little about its potential consequences for the whole ecological community.
-Here, we show that the intentional release undermines community stability with little demographic benefit to the enhanced species.
+Here, we show that the intentional release undermines community stability with limited demographic benefit to the enhanced species.
 Theory and data agree that intentional release destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species.
 The effect size of the intentional release was striking in its magnitude, doubling temporal fluctuations of enhanced communities compared to those with no intentional release.
-Our findings point to major limitations of intentional release as a primary tool for biodiversity conservation and sustainability.
+Our findings point to major limitations of intentional release as a primary tool for conservation and sustainability.
 
@@
 Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
+In particular, the magnitude of intentional release for commercial and recreational species is massive [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018] -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (crustaceans, bivalves, insects) [@kitadaEconomicEcologicalGenetic2018; @ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
 There is growing awareness that intentional release entails ecological risks, such as the accumulation of deleterious alleles and the intensified competition within the enhanced species [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007; @kitadaLessonsLearnedJapanese2006].
@@
 The release of masu salmon began in the 1950s, with the annual average ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019.
-The majority of release occurs in spring at fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
+The majority of release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
@@
 Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014].
-It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate as the number of generations in captivity increases [@arakiGeneticEffectsCaptive2007].
-Typically, hatchery masu salmon are reared in captivity for two to four generations.
-Given the duration of the extensive release program (\> 60 years), it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines.
+It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007].
+Typically, masu salmon are reared in captivity for two to four generations.
+In light of the 60-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines.
 This effect may add to negative density dependence to influence community stability.

### 2022-10-21 rmd/reply_r1.Rmd
rmd

@@
 1.
-**Improve the introduction and implications**: both reviewers noted an absence of context in the previous manuscript.
+**Improve the Introduction and implications**: both reviewers noted an absence of context in the previous manuscript.
 We agree with this comment.
-We revised the text to contextualize our work better to address this issue.
+We revised the text to contextualize our work better.
 In particular, we have carefully reviewed cases to which our findings may apply and discussed the relevance of our work to those systems.
@@
 
-In summary, the improved text/analysis provided clearer evidence that intentional release has destabilizing effects and clarified its broader relevance to other systems.
+In summary, the improved text/analysis provides clearer evidence that intentional release has destabilizing effects and clarifies its broader relevance to other systems.
 We appended a point-by-point response below.
@@
 
-> Agreed.
-We have greatly improved the introduction and Discussion (paragraph L185 --, paragraph L209 --).
-We have clarified that our findings seem quite general for two reasons.
-(1) the scale of other release programs (mussels, crustaceans, birds, insects, and other fish) is generally way larger than our release program.
-For example, the largest release program for pink salmon in Alaska releases \> 600 million fish year^-1^ (note: our program releases only 0.24 million fish per year at the most intense site).
-(2) Most release programs aim to help declining populations in degraded habitats.
-In these habitats, the carrying capacities are likely compromised - a theoretical premise for the destabilizing effect to emerge.
+> Agreed. We followed your guidance to improve the Introduction and Discussion (**paragraph L185 --, paragraph L209 --**). In short, we have clarified the following point:
+>
+> Introduction -- We have included representative works that report the scale of intentional release for commercial and recreational species.
+The release programs included plants, insects, mollusks, crustaceans, fish, birds, and others.
+The magnitude was enormous, releasing several tens of thousands to \> 10 millions of individuals annually.
+Thus, our system certainly represents a typical scenario of release programs (our program releases 0.24 million fish per year at the most intense watershed).
+>
+> Discussion -- Given the scale of other release programs, our results should represent a conservative estimate of community-level impacts.
+In addition, many programs release individuals into "unsuitable" habitats to aid declining populations -- these programs are likely to cause the destabilizing effect of the intentional release because the carrying capacities of such habitats are likely compromised.
+We have clarified this point in the revised manuscript.
+>
+> Discussion -- We have also clarified that our findings align with previous work on other hatchery programs (including salmons and other fisheries).
+The decline of wild stocks has been repeatedly observed after intensive stocking (consistent with our theoretical predictions and empirical patterns).
+We have cited an important meta-analysis [@arakiHatcheryStockingHelp2010] along with several specific examples (e.g., pink salmon in Alaska, where \> 600 million fish year^-1^ are released).
 
@@
 
-> We have addressed the concerns raised by the reviewers.
-Please see our response to specific comments.
-Also, we have improved our regression analysis to account for the spatial overlap of hatchery salmon and other wild fishes.
-Since we do not have exact information on where hatchery fish are released (we have partial information -- updated our map to include this information; see Figure 1C), we performed the *post hoc* estimation of spatial overlap within the regression model (see Methods, "effective release").
+> Agreed. We have included more information on our study system. Please see our response to reviewer comments.
+>
+> Also, we have improved our regression analysis to account for the spatial overlap of hatchery salmon and other wild fishes.
+Since we do not have exact information on where and how many hatchery fish are released within a watershed (we are sure they are released near the fish survey sites though), we performed the *post hoc* estimation of spatial overlap within the regression model (see Methods, "effective release").
 We believe this will increase the validity of our results as it enabled us to use 97 site replicates fully to estimate the effect of releases.
@@
 > Thank you for the great comment!
-As you can see in our response to the editor's comment, we have greatly improved the introduction and Discussion (paragraph L208 --).
+As you can see in our response to the editor's comment, we have greatly improved the Introduction and Discussion.
 We believe our findings are broadly applicable across taxa and ecosystems.
@@
 
-> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (paragraph L184 --).
+> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (**paragraph L185 --**).
 
@@
 
-> Good point -- unfortunately, we do not have any data to show quantitative patterns.
+> Good point -- however, we do not have any data to show quantitative patterns.
 The "hatchery" gene has likely spread within the wild populations, given the duration of the extensive release programs.
-We have briefly mentioned this in the revised text (paragraph L169 --).
+We have briefly mentioned this in the revised text (**paragraph L170 --**).
 
@@
 
-> We have detailed species information in Table S2.
+> We have detailed species information in Table S2 and have provided a co-occurrence matrix in Fig S16.
 Masu salmon often co-occur with white-spotted charr, sculpins, and stone loaches.
-Since our watersheds are "protected" watersheds, any form of exploitation (including angling) is not allowed (regardless of fish species).
-Therefore, other factors are unlikely to shape the observed patterns of temporal community variability.
-Please note that we have statistically accounted for natural variations in land use, watershed size, climate etc.
+Since our watersheds are "protected", any form of exploitation (including angling) is not allowed (regardless of species).
+Therefore, intentional release is the most likely explanation for the observed pattern.
+Please note that we have statistically accounted for natural variations in land use, watershed size, climate etc -- the effect size of these factors were smaller compared with the release effect.
 
@@
 > We agree that our results are not surprising -- we are not surprised either.
-However, we strongly believe that our result is important and worth publishing because, to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long term.
+However, we believe that our result is important and worth publishing because, to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long term.
 Also, perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)!
-This magnitude is way larger than the release program in our study system.
 Therefore, release numbers of $5\times$ carrying capacity seem conservative to us.
-Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative rather than an unrealistic extreme scenario.
+Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a typical scenario of release programs.
 >
@@
 > Thank you for this comment.
-We agree that this pattern is important, and we acknowledge that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**).
+We agree that this pattern is important, and we acknowledged that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**).
 However, our focus here is not the influence of intentional release on the enhanced species -- we are interested in how unenhanced species respond to the intentional release.
@@
 
-> Thank you, we agree that a detailed life-history model will provide useful insights into salmon management.
+> We agree that a detailed life-history model will provide useful insights into salmon management.
+We appreciate this comment.
 However, we decided not to perform this analysis for the following reasons.
@@
 We have cited it in the revised manuscript.
-Lastly, we believe the reviewer misread our results in the previous manuscript.
+Lastly, we believe the reviewer misread our results in the previous manuscript (correct us if we misunderstood something).
 Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best.
@@
 Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches).
-In addition, numerous research documents competition between masu salmon and other stream fish species.
+In addition, numerous research document competition between masu salmon and other stream fish species.
 We have clarified these points in the revised manuscript.
@@
 This insightful comment helped a lot to avoid delivering the wrong messages.
-We agree and have substantially improved the introduction and Discussion to address this issue.
+We agree and have substantially improved the Introduction and Discussion to address this issue.
 Specifically, we now recognize that there are many cases where stock enhancement is economically successful -- we have mentioned these examples to develop a context properly.

### 2022-10-21 rmd/supporting_info.Rmd
rmd

@@
   - \usepackage{amsmath,fancyhdr, caption}
-  - \captionsetup{width=1.3\linewidth, labelfont={bf}}
+  - \captionsetup{width=1.35\linewidth, labelfont={bf}}
 bibliography: reference.bib
@@
 **Fish release.** The release of masu salmon began in the 1950s.
+Hatchery fish are reared in captivity for zero (wild origin) to seven generations (the majority is two to four generations).
 Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years.

### 2022-10-21 rmd/manuscript.Rmd
rmd

@@
 Typically, masu salmon are reared in captivity for two to four generations.
-In light of the 60-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines.
+In light of the 70-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines.
 This effect may add to negative density dependence to influence community stability.

### 2022-10-21 rmd/supporting_info.Rmd
rmd
Update supporting_info.Rmd

@@
 **Fish release.** The release of masu salmon began in the 1950s.
-Hatchery fish are reared in captivity for zero (wild origin) to seven generations (the majority is two to four generations).
+The duration of captivity ranged from zero (wild origin) to seven generations, and the majority is released at two to four generations in captivity.
 Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years.
@@
 knitr::kable(df_prior,
+             align = rep("l", 3),
              format = "markdown",
@@
 
+```{=tex}
+\fancyhead[L]{Terui et al.}
+\fancyhead[C]{}
+\fancyhead[R]{}
+```
 # References

### 2022-10-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
   - \pagenumbering{gobble}
-  - \usepackage{amsmath,fancyhdr, caption}
+  - \usepackage{amsmath, fancyhdr, caption, booktabs}
   - \captionsetup{width=1.35\linewidth, labelfont={bf}}
@@
 suppressMessages(source(here::here("code/set_rmd.R")))
+
 ```
@@
 \fancyhead[C]{}
-\setlength{\headheight}{13.7pt}
 \pagenumbering{arabic}
@@
 knitr::kable(df_param,
-             format = "markdown",
-             caption = "Parameter values used in the whole community simulation.")
+             escape = FALSE,
+             booktabs = TRUE,
+             caption = "Parameter values used in the whole community simulation.") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 
@@
 knitr::kable(df_sp_list,
-             format = "markdown",
-             caption = "Fish species found in the study watersheds.
-Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge.
-Body size is coded as follows: maximum total length (TL) $< 100$ mm (S), $100\\le$  TL $\\le 200$ (M), and TL $> 200$ (L).")
+             booktabs = TRUE,
+             escape = FALSE,
+             caption = "Fish species found in the study watersheds. Body size is coded as follows: maximum total length (TL) $< 100$ mm (S), $100\\le$  TL $\\le 200$ (M), and TL $> 200$ (L).") %>% 
+  kableExtra::kable_styling(latex_options = c("HOLD_position",
+                                              "scale_down"))
 ```
+
+Note: Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975; @gotoLifeHistoryDistibution1981; @ministryofenvironmentofjapanThreatenedWildlifeJapan2014; @natsumedaEvaluationEcologicalFeatures2010; @fishbaseFishBaseHttpsWww] and expert knowledge.
 
@@
              align = rep("l", 3),
-             format = "markdown",
-             caption = "Prior distributions used in the Bayesian models.
-See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
-The parameter $\\pmb{\\omicron}$ is a vector of prior scales ($\\pmb{\\omicron}=2.5,...,2.5$).")
+             escape = FALSE,
+             booktabs = TRUE,
+             caption = "Prior distributions used in the Bayesian models. The parameter $\\pmb{\\omicron}$ is a vector of prior scales ($\\pmb{\\omicron}=2.5,...,2.5$).") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 
 ```
+
+See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
 
@@
              align = c(rep("l", 2), rep("r", 2)),
-             format = "markdown",
-             caption = "Median estimates for key parameters of the state-space autoregressive model. Site-specific parameters were excluded due to a large number of parameters.")
+             escape = FALSE,
+             booktabs = TRUE,
+             caption = "Median estimates for key parameters of the state-space autoregressive model. Site-specific parameters were excluded due to a large number of parameters.") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 
@@
              align = c(rep("l", 2), rep("r", 2)),
-             format = "markdown",
-             caption = "Median estimates for key parameters of the state-space Ricker model. Site-specific parameters were excluded due to a large number of parameters.")
+             escape = FALSE,
+             booktabs = TRUE,
+             caption = "Median estimates for key parameters of the state-space Ricker model. Site-specific parameters were excluded due to a large number of parameters.") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 
@@
                              align = c(rep('l', 2), rep('r', 4)),
-                             format = 'markdown',
-                             caption = table_legend[",i,"])
+                             escape = FALSE,
+                             booktabs = TRUE,
+                             caption = table_legend[",i,"]) %>% 
+  kableExtra::kable_styling(latex_options = 'HOLD_position')
+
                        \n\n

### 2022-10-22 rmd/manuscript.Rmd
rmd

@@
   # reference_docx: word_format.docx
+  # number_sections: false
 csl: https://www.zotero.org/styles/pnas
@@
 
-When carrying capacity was small ($K=$ `r min(list_param[[2]]$k)`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure** \@ref(fig:figure-layout)**A**).
+When small carrying capacity was combined with a low to modest intrinsic growth rate ($K=$ `r min(list_param[[2]]$k)`, $r_1 \le 2.5$), our model predicted a destabilizing effect of intentional release on ecological communities, as illustrated by increased CV with increasing numbers of releases (**Figure** \@ref(fig:figure-layout)**A**).
 This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** \@ref(fig:figure-layout)**A**).

### 2022-10-22 rmd/reply_r1.Rmd
rmd

@@
 
-Thank you for allowing us to revise our manuscript. The comments were very helpful in improving our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:
+This is a re-submission of a manuscript: "2022­05603 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript.
+The comments were very helpful in improving our manuscript.
+When revising the manuscript, we have put a particular emphasis on the following points:
 
 1.
-**Improve the Introduction and implications**: both reviewers noted an absence of context in the previous manuscript.
+**Improve the Introduction and broad implications**: both reviewers noted an absence of context in the previous manuscript.
 We agree with this comment.
@@
 
-> Agreed. We followed your guidance to improve the Introduction and Discussion (**paragraph L185 --, paragraph L209 --**). In short, we have clarified the following point:
+> Agreed. We followed your guidance to improve the Introduction and Discussion (**paragraph L186 --, paragraph L210 --**). In short, we have clarified the following point:
 >
@@
 
-> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (**paragraph L185 --**).
+> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (**paragraph L186 --**).
 

### 2022-10-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd
rmd

@@
 Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`).
+We used $r_{max}=$ `r unique(list_param[[2]]$r_max)` because the intrinsic growth rate higher than this value was rarely observed in nature [@myersMaximumReproductiveRate1999].
 This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.
@@
 
-See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
+Note: see Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
 

### 2022-10-22 rmd/supporting_info.Rmd
text{max}

--- 2022-10-22 rmd/supporting_info.Rmd
@@
 ```
-In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim \text{Exp}(1/\bar{\alpha})$), respectively.
+In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,r_{\text{max}})$) and an exponential distribution ($\alpha_{ij} \sim \text{Exp}(1/\bar{\alpha})$), respectively.
 We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
@@
 We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs.
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`).
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`).
+We used $r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)` because the intrinsic growth rate higher than this value was rarely observed in nature [@myersMaximumReproductiveRate1999].
 This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.
@@
 Other parameters are: ",
-                       "number of species $S$ = ", df_param$n_species[i], "; intrinsic growth rate of an enhanced species $r_1$ = ", df_param$r1[i], "; maximum intrinsic growth rate of unenhanced species $r_{max}$ = ", df_param$r_max[i], "; environmental stochasticity $\\sigma_{\\varepsilon}$ = ", df_param$sd_env[i], "; carrying capacity $K$ = ", df_param$k[i], ".")
+                       "number of species $S$ = ", df_param$n_species[i], "; intrinsic growth rate of an enhanced species $r_1$ = ", df_param$r1[i], "; maximum intrinsic growth rate of unenhanced species $r_{\\text{max}}$ = ", df_param$r_max[i], "; environmental stochasticity $\\sigma_{\\varepsilon}$ = ", df_param$sd_env[i], "; carrying capacity $K$ = ", df_param$k[i], ".")
 

### 2022-10-22 code/table_param_set.R

@@ -40,7 +40,7 @@ df_param <- sim_result %>%
     Parameter = case_when(Parameter == "n_species" ~ "$S$",
                           Parameter == "k" ~ "$K$",
                           Parameter == "r1" ~ "$r_1$",
-                          Parameter == "r_max" ~ "$r_{max}$",
+                          Parameter == "r_max" ~ "$r_{\\text{max}}$",
                           Parameter == "sd_env" ~ "$\\sigma_{\\varepsilon}$",
                           Parameter == "phi" ~ "$f_R$",
                           Parameter == "alpha" ~ "$\\bar{\\alpha}$")

### 2022-10-22 rmd/manuscript.Rmd
rmd

@@
 
-Massive releases of captive-bred native species ("intentional release") is a pervasive method to enhance wild populations of commercial and recreational species.
+The massive release of captive-bred native species ("intentional release") is a pervasive method to enhance wild populations of commercial and recreational species.
 However, such external inputs may disrupt the sensitive species interactions that allow competing species to coexist, potentially compromising long-term community stability.

### 2022-10-25 rmd/README.Rmd
readme

@@
 
-Title: Intentional release of native species undermines ecological stability
-Authors: Akira Terui, Hirokazu Urabe, Masayuki Senzaki, Bungo Nishizawa
+**Title:** Intentional release of native species undermines ecological stability
+
+**Authors:** Akira Terui, Hirokazu Urabe, Masayuki Senzaki, Bungo Nishizawa
 
@@
 ```{r}
+source(here::here("code/library.R"))
 sessionInfo()

### 2022-10-25 code/set_readme.R

@@ -9,6 +9,8 @@ pacman::p_load(tidyverse)
 
 tbl_readme <- tibble(name = list.files(here::here("code")),
                      dir = "code") %>% 
+  bind_rows(tibble(name = list.files(here::here("data_fmt")),
+                   dir = "data_fmt")) %>% 
   filter(name != "readme.R") %>% 
   mutate(class = case_when(str_detect(name, "analysis_") ~ "analysis",
                            str_detect(name, "^figure_|^si_figure_") ~ "figure",
@@ -17,12 +19,9 @@ tbl_readme <- tibble(name = list.files(here::here("code")),
                            str_detect(name, "model_|run_jags") ~ "jags",
                            str_detect(name, "run_simulation") ~ "simulation",
                            str_detect(name, "table_") ~ "table",
-                           str_detect(name, "set_") ~ "set")
-  ) %>% 
-  bind_rows(tibble(name = list.files(here::here("data_fmt")),
-                   dir = "data_fmt")) %>%
-  # bind_rows(tibble(name = list.files(here::here("data_raw")),
-  #                  dir = "data_raw")) %>% 
+                           str_detect(name, "set_") ~ "set",
+                           str_detect(name, "data_") ~ "data")
+  ) %>%
   relocate(dir, class) %>% 
   arrange(dir, class, name) %>% 
   mutate(description = case_when(str_detect(class, "analysis") ~ "correlation for sensitivity analysis of theoretical model",
@@ -34,12 +33,14 @@ tbl_readme <- tibble(name = list.files(here::here("code")),
                                  str_detect(class, "gis") ~ ifelse(str_detect(name, "watershed"),
                                                                    "delineate watersheds",
                                                                    paste("extract layer data for", str_extract(name, "environment|ocean"))
-                                 ),
+                                                                   ),
                                  str_detect(class, "jags") & str_detect(name, "model") ~ "jags model for joint state-space (`_joint`), multi-species ricker (`_multi_ricker_sparse`), and regression (`_reg`)",
                                  str_detect(class, "jags") & str_detect(name, "run") ~ "run corresponding jags models",
                                  str_detect(class, "simulation") ~ "run simulation model for species rich (no postfix) and 2-species community (`_analytical`) or sensitivity analysis (`_stvy`)",
[…]

### 2022-10-26 rmd/supporting_info.Rmd
edit: supporting info

@@
 csl: https://www.zotero.org/styles/pnas
-nocite: |
-  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
 ---
@@
 ```
-# Methods
-
-## Theory
-
-### Model
-
-We employed a multi-species Ricker model [@fowlerSpeciesDynamicsAlter2012].
-In the basic formula without intentional release, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{\sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
-(\#eq:ricker0)
-\end{align}
-```
-where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey a normal distribution $\text{Normal}(0, \sigma_{\varepsilon}^2)$.
-We modified this formula to include the effects of intentional release (species 1) on reproduction and competition as follows:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\varepsilon_{i,t})
-(\#eq:ricker)
-\end{align}
-```
-$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
-
-```{=tex}
-\begin{align}
-\phi_i = 
-\left\{
-\begin{array}{cc}
-f_R & (i = 1)\\
-0 & (i \ne 1)
-\end{array}
-\right.
-\end{align}
-```
-$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation \@ref(eq:ricker) can be reorganized to:
-
-```{=tex}
-\begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t) ~ \exp \left[r_i \left(1-\frac{\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
-\end{align}
-```
-In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,r_{\text{max}})$) and an exponential distribution ($\alpha_{ij} \sim \text{Exp}(1/\bar{\alpha})$), respectively.
-We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
-
-### Model analysis
-
-First, we analyzed a two-species community to gain insights into the model behavior and to guide the N-species analysis.
-Specifically, we examined the release effect with $20$ parameter values of intrinsic population growth rate $r_i$ ($0.5$ to $3.5$ with an equal interval) and carrying capacity $K$ ($50$ to $500$ with an equal interval), resulting in $400$ parameter combinations.
-In a single-species Ricker model, the chosen range of $r_i$ can generate stable equilibrium, damped oscillations, limit cycle, and chaos [@sunDynamicBehaviorsRicker2000].
-For simplicity, we assumed $r_1 = r_2$.
-We crossed this parameter setup with environmental stochasticity ($\sigma_{\varepsilon} =$ `r unique(list_param[[1]]$sd_env)`) and competition strength ($\alpha_{ij} =$ `r unique(list_param[[1]]$alpha)`) and generated `r nrow(list_param[[1]])` simulation scenarios ($400 \times 2 \times 2$).
-
-Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` timesteps of community dynamics for $100$ values of release level $R$ ($0$ to $500$ with an equal interval).
-We introduced $50$ individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` timesteps (initialization).
-After the initialization period, we released $R$ individuals of the enhanced species every timestep over the next `r unique(list_sim[[1]]$n_burnin)` timesteps to reach a new equilibrium with the intentional release (burn-in period).
-We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` timesteps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$ ($S$: the number of species): the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
-The results of the two-species system were reported in [Supplementary Text].
-
-We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`).
-We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs.
-Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`).
-We used $r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)` because the intrinsic growth rate higher than this value was rarely observed in nature [@myersMaximumReproductiveRate1999].
-This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.
-
-As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` timesteps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
-In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community.
-In addition, we defined a threshold density ($N_i = 0.01$) below which species are removed from the simulation (i.e., an absorbing condition) and are recorded as "extinct".
-The rest of the simulation procedure is identical to the two-species model.
-We summarized values of simulation parameters in **Table S**\@ref(tab:tab-para).
-
-## Empirical analysis
-
-### Data
-
-**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
-The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterfisheriesresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
-The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
-Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
-We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds ten years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
-As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019.
-The summed abundance of first and second passes was used in the following analysis.
-**Table S**\@ref(tab:tab-splist) summarizes observed species in these watersheds.
-
-**Fish release.** The release of masu salmon began in the 1950s.
-The duration of captivity ranged from zero (wild origin) to seven generations, and the majority is released at two to four generations in captivity.
-Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years.
-Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage).
-Most fish are released near the fish survey sites.
-However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable.
-For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
-During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
-
-**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]).
-We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site.
-We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
-Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
-We extracted annual data of chlorophyll *a* concentration (2002 -- 2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
-We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
-
-### Statistical analysis
-
-**Community dynamics comparison.** Our goal is to compare temporal community dynamics across sites.
-However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
-To confront this challenge, we developed a Bayesian state-space model for two species groups separately: (i) enhanced species, the abundance of masu salmon, and (ii) unenhanced species, the summed abundance of all species except masu salmon.
-A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
-The model is composed of observation and state models, as described below.
-
-In the observation model, we model observation processes. Fish abundance at site $s$ in year $t$ (either enhanced or unenhanced species), $N_{s,t}$, was assumed to follow a Poisson distribution:
-
-```{=tex}
-\begin{align}
-N_{s,t} \sim \text{Poisson}(\lambda_{s,t} A_{s,t})
-\end{align}
-```
-where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
-Since fish sampling was conducted after the spring release of masu salmon, captured fish may include individuals released in the observation year.
-We explicitly modeled this observation process to avoid biases in estimating temporal community trends:
-
-```{=tex}
-\begin{align}
-\lambda_{s,t} = n_{s,t}\exp(\varepsilon_{s,t}^{\text{obs}}) + \psi \beta_s~Fry_{w(s),t}
-\end{align}
-```
-$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released (unit: million fish) in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
-The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\theta_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
-The parameter $\varepsilon_{s,t}^{\text{obs}}$ is the error term that follows a normal distribution $\text{Normal}(0, \sigma_{\text{obs},s}^2)$.
-The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
-When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
-
-In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
-
-```{=tex}
-\begin{align}
-\begin{split}
-&\ln n_{s,t} = \xi_{1,s} + \xi_{2,s} \ln n'_{s,t-1} + \varepsilon_{s,t}^{\text{state}}\\
-&\ln n'_{s,t-1} = \frac{\sum_{q=1}^Q (\tau^{q} \ln n_{s,t-q})}{\sum_{q=1}^Q \tau^{q}}
-\end{split}
-(\#eq:state)
-\end{align}
-```
-where $\xi_{1,s}$ is the site-specific constant at site $s$, $\xi_{2,s}$ the parameter characterizing an autoregressive (AR) process, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
-The parameters $\xi_{1,s}$ and $\xi_{2,s}$ were drawn from a multivariate normal distribution as $\pmb{\xi} \sim \text{MVN}(\pmb{\theta_{\xi}}, \pmb{\Omega_{\xi}})$, where $\pmb{\xi}$ is the matrix of $\xi_{1,s}$ and $\xi_{2,s}$.
-Equation \@ref(eq:state) is structurally equivalent to a $Q$-order AR model; however, we expressed the part of AR parameters as a geometric-series $\tau^q$ to reduce the number of parameters (our model has two AR parameters $\xi_{2,s}$ and $\tau$ regardless of order $Q$).
-The parameter $\tau$ controls how fast the density influence attenuates towards the past [@takagiTimescaleDependencyHost2015].
-In this study, we set $Q=3$ given the life span of the study species (typically 1 -- 3 years).
-We used median estimates of fish density $n_{s,t}$ to calculate the temporal CV, mean ($\mu$), and SD ($\sigma$) for each site.
-For a whole community, we summed the densities of enhanced and unenhanced species.
-We summarized the reconstructed community dynamics in **Figures S**\@ref(fig:fig-d1) -- **S**\@ref(fig:fig-d3).
-
-We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0 --1 and indicates over- (\~0.00), under- (\~1.00), or suitable-fitting (\~0.50) to the data.
-A Bayesian p-value for our state-space models was `r op(round(df_bp$mean, 2))`, indicating that our model specification is appropriate.
-
-We used linear regression to quantify the impact of the intentional release on community dynamics.
-Although our focus is intentional release, each model included climatic and local abiotic variables to account for important environmental differences among sites.
-Specifically, we developed the following linear regression model taking either species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$.
-
-```{=tex}
-\begin{align}
-\left\{
-\begin{aligned}
-y_s &\sim \text{Poisson}(\lambda_{y,s} \exp(\varepsilon_{\lambda,s})) &&\text{for species richness}\\
-\ln \pmb{y_s} &\sim \text{MVN}(\pmb{\theta_{y,s}}, \pmb{\Omega_y}) &&\text{for mean and SD}
-\end{aligned}
-\right.
- (\#eq:reg)
-\end{align}
-```
-In the poisson model for species richness, $\exp(\varepsilon_{\lambda,s})$ is the error term accounting for overdispersion ($\varepsilon_{\lambda,s} \sim \text{Normal}(0, \sigma_{\lambda}^2)$).
-In the multivariate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multivariate normal distribution with the variance-covariance matrix $\pmb{\Omega_y}$.
-The expected means $\lambda_{y,s}$ and $\pmb{\theta_s}$ were related to linear predictors as follows:
-
-```{=tex}
-\begin{align}
-\left\{
-\begin{aligned}
-\ln \lambda_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}\\
-\theta_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_k x_{k,s} &&\text{for mean and SD}
-\end{aligned}
-\right.
-(\#eq:model)
-\end{align}
-```
-$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k = 1,2,...)$ is the $k^\text{th}$ regression coefficient [effective release of masu salmon $R'_s$ ($k = 1$) and other site-level predictors $x_k$ ($k \ge 2$)].
-$R'_s$ is the product of the average yearly release at watershed $w$ ($R_w$; fry + juvenile + smolt, averaged for 1999 -- 2019) and the site-specific weight factor $\eta_{w,s'}$ ($s'=1,...,S_w + 1$, where $S_w$ is the number of sites within watershed $w$):
-
-```{=tex}
-\begin{align}
-\begin{split}
-R'_s = \eta_{w,s'} R_w~\text{where}~
-\sum_{s'}^{S_w + 1} \eta_{w,s'} = 1
-(\#eq:effr)
-\end{split}
-\end{align}
-```
-In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$.
-The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas.
-Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **model fitting**).
-Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
-Urban and agricultural land use was omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)).
-The watershed-specific intercept was related to a watershed-level predictor as:
-
-```{=tex}
-\begin{align}
-\begin{split}
-\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\
-\theta_{\gamma,w} &= \gamma'_0 + \gamma'_1 x'_{w}
-\end{split}
-\end{align}
-```
-$\gamma'_{0}$ is the global intercept and $\gamma'_1$ is the regression coefficient of ocean productivity $\gamma'_{w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019).
-Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
-The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictor cannot capture.
-
-Since the CV is an additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation \@ref(eq:model):
-
-```{=tex}
-\begin{align}
-\text{E}(\ln CV_s) = \text{E}(\ln y_s^{(\sigma)}) - \text{E}(\ln y_s^{(\mu)})
-\end{align}
-```
-Considering that $\text{E}(\ln y_s^{(\sigma)}) = \theta_{y,s}^{(\sigma)}$ and $\text{E}(\ln y_s^{(\mu)}) = \theta_{y,s}^{(\mu)}$,
-
-```{=tex}
-\begin{align}
-\text{E}(\ln CV_s) = (\gamma_{0,w(s)}^{(\sigma)} - \gamma_{0,w(s)}^{(\mu)}) + (\gamma_{1}^{(\sigma)} - \gamma_{1}^{(\mu)})R'_s + \sum_k (\gamma_{k}^{(\sigma)} - \gamma_{k}^{(\mu)})x_{k,s}
-\end{align}
-```
-All predictors were standardized (mean = 0, SD = 1) before the analysis.
-
-**Species interaction.** We analyzed a subset of our data to estimate the strength of interspecific interactions among stream fishes.
-In this analysis, we focused on `r n_distinct(df_complete$site_id)` sites with $>16$ years of observations and no intentional release of masu salmon.
-Further, at each site, we confined our analysis to species that occurred more than four times.
-These additional constraints were necessary to estimate parameters in a complex multi-species model within a state-space modeling framework.
-
-We fitted the following state-space model to the data for each site separately. In the observation model, we modeled fish abundance $N_{i,t}$ for species $i$ at year $t$ as:
-
-```{=tex}
-\begin{align}
-\begin{split}
-N_{i,t} &\sim \text{Poisson}(\lambda_{i,t} A_{t})\\
-\lambda_{s,t} &= n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})
-\end{split}
-\end{align}
-```
-where $\varepsilon_{i,t}^{\text{obs}} \sim \text{Normal}(0, \sigma_{\text{obs},i})$. In the state model, we described a multi-species Ricker model for fish density $n_{i,t}$:
-
-```{=tex}
-\begin{align}
-\ln n_{i,t} = \ln n_{i,t-1} + r_{i} - \sum_{j=1}^S\alpha'_{ij} n_{i,t-1} + \varepsilon_{i,t}^{\text{state}}
-(\#eq:ricker-ssm)
-\end{align}
-```
-Equation \@ref(eq:ricker-ssm) is equivalent to Equation \@ref(eq:ricker0) except the scale of competition coefficients $\alpha'_{ij}$ ($\frac{\alpha'_{ij}}{\alpha'_{ii}}=\alpha_{ij}$, where $\alpha'_{ii}=\frac{r_i}{K_i}$).
-We used sparse priors for $\alpha'_{ij}$ to reduce the risk of over-fitting [@mutshindaWhatDrivesCommunity2009]:
-
-```{=tex}
-\begin{align}
-\begin{split}
-\alpha'_{ij} \sim \text{Half-normal}(0, \sigma^2_{\alpha, ij})\\
-\sigma_{\alpha,ij}^2 = z_{ij}c_1 + (1-z_{ij})c_0
-\end{split}
-(\#eq:sparse)
-\end{align}
-```
-In Equation \@ref(eq:sparse), the latent variable $z_{ij}$ is drawn from a Bernoulli distribution and controls the prior for $\alpha'_{ij}$.
-We used $c_1 = 1$ and $c_0 = 0.01$ so that $\alpha'_{ij}$ is freely estimated when $z_{ij}$ equals one ($\sigma^2_{\alpha} = 1$).
-Otherwise, the probability density of $\alpha'_{ij}$ would be concentrated around zero ($\sigma^2_{\alpha} = 0.01$), effectively omitting the parameter from the model [@mutshindaWhatDrivesCommunity2009].
-We assigned different "inclusion" probabilities to diagonal (intraspecific competition) and off-diagonal elements (interspecific competition) as $z_{ii} \sim \text{Bernoulli}(p_{\alpha}^{\text{intra}})$ and $z_{ij,i \ne j} \sim \text{Bernoulli}(p_{\alpha}^{\text{inter}})$.
-
-We assumed that environmental noise $\varepsilon_{i,t}^{\text{state}}$ is correlated among species by introducing the variance-covariance matrix $\pmb{\Omega_{\varepsilon}}$.
-The matrix $\pmb{\Omega_{\varepsilon}}$ was modeled with the aid of latent factors $\zeta_{t,d}$ and factor loadings $\delta_{d,i}$:
-
-```{=tex}
-\begin{align}
-\varepsilon_{i,t}^{\text{state}}=\sum_{d}^{D}\zeta_{t,d}\delta_{d,i} + I_{ij}\epsilon_{i,t}
-\end{align}
-```
-where $D$ is the number of latent factors, $\epsilon_{i,t} \sim \text{Normal}(0, \sigma_{\epsilon,i}^2)$, and $I_{ij}$ is the identity matrix ($I_{ii}=1$ and $I_{ij, i \ne j} = 0$).
-With this formulation, the matrix $\pmb{\Omega_{\varepsilon}}$ can be described as $\pmb{\Omega_{\varepsilon}}=\pmb{\Delta}^T\pmb{\Delta} + \text{diag}(\sigma_{\epsilon,i}^2)$, where $\pmb{\Delta}$ is the matrix of factor loadings $\delta_{d,i}$.
-This model structure with multiplicative gamma priors on factor loadings [@duranteNoteMultiplicativeGamma2017] has the merit of the reduced number of parameters while capturing the correlated nature of species responses to environmental fluctuations [@ovaskainenHowAreSpecies2017].
-We set $D=2$ in our model.
-We reported the estimates of $\alpha_{ij}$, so the values are comparable to those used in the theoretical analysis.
-
-**Model fitting.** We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
-We assigned vague or weakly informative priors to parameters (**Table S**\@ref(tab:tab-prior)).
-Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
-The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc)` to `r max(df_mcmc$n_total_mcmc)`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period.
-Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached $<1.1$ [@gelmanDataAnalysisUsing2007].
-Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021].
-Parameter estimates were summarized in **Tables S**\@ref(tab:tab-ssm-ar) -- **S**\@ref(tab:tab-reg3).
-
-\newpage
-
 # Supplementary Text

### 2022-10-26 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 mainfont: "Times New Roman"
-fontsize: 10.5pt
+fontsize: 11pt
 knit: (function(inputFile, encoding) {

### 2022-10-26 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 
+# Methods
+
+## Theory
+
+### Model
+
+We employed a multi-species Ricker model [@fowlerSpeciesDynamicsAlter2012].
+In the basic formula without intentional release, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{\sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
+(\#eq:ricker0)
+\end{align}
+```
+where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey a normal distribution $\text{Normal}(0, \sigma_{\varepsilon}^2)$.
+We modified this formula to include the effects of intentional release (species 1) on reproduction and competition as follows:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\varepsilon_{i,t})
+(\#eq:ricker)
+\end{align}
+```
+$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
+
+```{=tex}
+\begin{align}
+\phi_i = 
+\left\{
+\begin{array}{cc}
+f_R & (i = 1)\\
+0 & (i \ne 1)
+\end{array}
+\right.
+\end{align}
+```
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation \@ref(eq:ricker) can be reorganized to:
+
+```{=tex}
+\begin{align}
+N_{i,t+1} = (N_{i,t}+\phi_i R_t) ~ \exp \left[r_i \left(1-\frac{\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
+\end{align}
+```
+In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,r_{\text{max}})$) and an exponential distribution ($\alpha_{ij} \sim \text{Exp}(1/\bar{\alpha})$), respectively.
+We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.
+
+### Model analysis
+
+First, we analyzed a two-species community to gain insights into the model behavior and to guide the N-species analysis.
+Specifically, we examined the release effect with $20$ parameter values of intrinsic population growth rate $r_i$ ($0.5$ to $3.5$ with an equal interval) and carrying capacity $K$ ($50$ to $500$ with an equal interval), resulting in $400$ parameter combinations.
+In a single-species Ricker model, the chosen range of $r_i$ can generate stable equilibrium, damped oscillations, limit cycle, and chaos [@sunDynamicBehaviorsRicker2000].
+For simplicity, we assumed $r_1 = r_2$.
+We crossed this parameter setup with environmental stochasticity ($\sigma_{\varepsilon} =$ `r unique(list_param[[1]]$sd_env)`) and competition strength ($\alpha_{ij} =$ `r unique(list_param[[1]]$alpha)`) and generated `r nrow(list_param[[1]])` simulation scenarios ($400 \times 2 \times 2$).
+
+Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` timesteps of community dynamics for $100$ values of release level $R$ ($0$ to $500$ with an equal interval).
+We introduced $50$ individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` timesteps (initialization).
+After the initialization period, we released $R$ individuals of the enhanced species every timestep over the next `r unique(list_sim[[1]]$n_burnin)` timesteps to reach a new equilibrium with the intentional release (burn-in period).
+We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` timesteps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$ ($S$: the number of species): the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
+The results of the two-species system were reported in [Supplementary Text].
+
+We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`).
+We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs.
+Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`).
+We used $r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)` because the intrinsic growth rate higher than this value was rarely observed in nature [@myersMaximumReproductiveRate1999].
+This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.
+
+As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` timesteps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario.
+In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community.
+In addition, we defined a threshold density ($N_i = 0.01$) below which species are removed from the simulation (i.e., an absorbing condition) and are recorded as "extinct".
+The rest of the simulation procedure is identical to the two-species model.
+We summarized values of simulation parameters in **Table S**\@ref(tab:tab-para).
+
+## Empirical analysis
+
+### Data
+
+**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan.
+The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterfisheriesresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
+The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
+Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).
+We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds ten years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period.
+As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019.
+The summed abundance of first and second passes was used in the following analysis.
+**Table S**\@ref(tab:tab-splist) summarizes observed species in these watersheds.
+
+**Fish release.** The release of masu salmon began in the 1950s.
+The duration of captivity ranged from zero (wild origin) to seven generations, and the majority is released at two to four generations in captivity.
+Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years.
+Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage).
+Most fish are released near the fish survey sites.
+However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable.
+For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
+During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
+
+**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]).
+We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site.
+We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018].
+We extracted annual data of chlorophyll *a* concentration (2002 -- 2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
+We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
+
+### Statistical analysis
+
+**Community dynamics comparison.** Our goal is to compare temporal community dynamics across sites.
+However, the data are not comparable because of observation errors (e.g., different observers) and missing observations.
+To confront this challenge, we developed a Bayesian state-space model for two species groups separately: (i) enhanced species, the abundance of masu salmon, and (ii) unenhanced species, the summed abundance of all species except masu salmon.
+A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012].
+The model is composed of observation and state models, as described below.
+
+In the observation model, we model observation processes. Fish abundance at site $s$ in year $t$ (either enhanced or unenhanced species), $N_{s,t}$, was assumed to follow a Poisson distribution:
+
+```{=tex}
+\begin{align}
+N_{s,t} \sim \text{Poisson}(\lambda_{s,t} A_{s,t})
+\end{align}
+```
+where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
+Since fish sampling was conducted after the spring release of masu salmon, captured fish may include individuals released in the observation year.
+We explicitly modeled this observation process to avoid biases in estimating temporal community trends:
+
+```{=tex}
+\begin{align}
+\lambda_{s,t} = n_{s,t}\exp(\varepsilon_{s,t}^{\text{obs}}) + \psi \beta_s~Fry_{w(s),t}
+\end{align}
+```
+$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released (unit: million fish) in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
+The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\theta_{\beta}$ and hyper-variance $\sigma_{\beta}^2$.
+The parameter $\varepsilon_{s,t}^{\text{obs}}$ is the error term that follows a normal distribution $\text{Normal}(0, \sigma_{\text{obs},s}^2)$.
+The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors.
+When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.
+
+In the state model, we model temporal dynamics of fish density $n_{s,t}$ as follows:
+
+```{=tex}
+\begin{align}
+\begin{split}
+&\ln n_{s,t} = \xi_{1,s} + \xi_{2,s} \ln n'_{s,t-1} + \varepsilon_{s,t}^{\text{state}}\\
+&\ln n'_{s,t-1} = \frac{\sum_{q=1}^Q (\tau^{q} \ln n_{s,t-q})}{\sum_{q=1}^Q \tau^{q}}
+\end{split}
+(\#eq:state)
+\end{align}
+```
+where $\xi_{1,s}$ is the site-specific constant at site $s$, $\xi_{2,s}$ the parameter characterizing an autoregressive (AR) process, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
+The parameters $\xi_{1,s}$ and $\xi_{2,s}$ were drawn from a multivariate normal distribution as $\pmb{\xi} \sim \text{MVN}(\pmb{\theta_{\xi}}, \pmb{\Omega_{\xi}})$, where $\pmb{\xi}$ is the matrix of $\xi_{1,s}$ and $\xi_{2,s}$.
+Equation \@ref(eq:state) is structurally equivalent to a $Q$-order AR model; however, we expressed the part of AR parameters as a geometric-series $\tau^q$ to reduce the number of parameters (our model has two AR parameters $\xi_{2,s}$ and $\tau$ regardless of order $Q$).
+The parameter $\tau$ controls how fast the density influence attenuates towards the past [@takagiTimescaleDependencyHost2015].
+In this study, we set $Q=3$ given the life span of the study species (typically 1 -- 3 years).
+We used median estimates of fish density $n_{s,t}$ to calculate the temporal CV, mean ($\mu$), and SD ($\sigma$) for each site.
+For a whole community, we summed the densities of enhanced and unenhanced species.
+We summarized the reconstructed community dynamics in **Figures S**\@ref(fig:fig-d1) -- **S**\@ref(fig:fig-d3).
+
+We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0 --1 and indicates over- (\~0.00), under- (\~1.00), or suitable-fitting (\~0.50) to the data.
+A Bayesian p-value for our state-space models was `r op(round(df_bp$mean, 2))`, indicating that our model specification is appropriate.
+
+We used linear regression to quantify the impact of the intentional release on community dynamics.
+Although our focus is intentional release, each model included climatic and local abiotic variables to account for important environmental differences among sites.
+Specifically, we developed the following linear regression model taking either species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$.
+
+```{=tex}
+\begin{align}
+\left\{
+\begin{aligned}
+y_s &\sim \text{Poisson}(\lambda_{y,s} \exp(\varepsilon_{\lambda,s})) &&\text{for species richness}\\
+\ln \pmb{y_s} &\sim \text{MVN}(\pmb{\theta_{y,s}}, \pmb{\Omega_y}) &&\text{for mean and SD}
+\end{aligned}
+\right.
+ (\#eq:reg)
+\end{align}
+```
+In the poisson model for species richness, $\exp(\varepsilon_{\lambda,s})$ is the error term accounting for overdispersion ($\varepsilon_{\lambda,s} \sim \text{Normal}(0, \sigma_{\lambda}^2)$).
+In the multivariate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multivariate normal distribution with the variance-covariance matrix $\pmb{\Omega_y}$.
+The expected means $\lambda_{y,s}$ and $\pmb{\theta_s}$ were related to linear predictors as follows:
+
+```{=tex}
+\begin{align}
+\left\{
+\begin{aligned}
+\ln \lambda_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}\\
+\theta_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_k x_{k,s} &&\text{for mean and SD}
+\end{aligned}
+\right.
+(\#eq:model)
+\end{align}
+```
+$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k = 1,2,...)$ is the $k^\text{th}$ regression coefficient [effective release of masu salmon $R'_s$ ($k = 1$) and other site-level predictors $x_k$ ($k \ge 2$)].
+$R'_s$ is the product of the average yearly release at watershed $w$ ($R_w$; fry + juvenile + smolt, averaged for 1999 -- 2019) and the site-specific weight factor $\eta_{w,s'}$ ($s'=1,...,S_w + 1$, where $S_w$ is the number of sites within watershed $w$):
+
+```{=tex}
+\begin{align}
+\begin{split}
+R'_s = \eta_{w,s'} R_w~\text{where}~
+\sum_{s'}^{S_w + 1} \eta_{w,s'} = 1
+(\#eq:effr)
+\end{split}
+\end{align}
+```
+In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$.
+The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas.
+Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **model fitting**).
+Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
+Urban and agricultural land use was omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)).
+The watershed-specific intercept was related to a watershed-level predictor as:
+
+```{=tex}
+\begin{align}
+\begin{split}
+\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\
+\theta_{\gamma,w} &= \gamma'_0 + \gamma'_1 x'_{w}
+\end{split}
+\end{align}
+```
+$\gamma'_{0}$ is the global intercept and $\gamma'_1$ is the regression coefficient of ocean productivity $\gamma'_{w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019).
+Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
+The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictor cannot capture.
+
+Since the CV is an additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation \@ref(eq:model):
+
+```{=tex}
+\begin{align}
+\text{E}(\ln CV_s) = \text{E}(\ln y_s^{(\sigma)}) - \text{E}(\ln y_s^{(\mu)})
+\end{align}
+```
+Considering that $\text{E}(\ln y_s^{(\sigma)}) = \theta_{y,s}^{(\sigma)}$ and $\text{E}(\ln y_s^{(\mu)}) = \theta_{y,s}^{(\mu)}$,
+
+```{=tex}
+\begin{align}
+\text{E}(\ln CV_s) = (\gamma_{0,w(s)}^{(\sigma)} - \gamma_{0,w(s)}^{(\mu)}) + (\gamma_{1}^{(\sigma)} - \gamma_{1}^{(\mu)})R'_s + \sum_k (\gamma_{k}^{(\sigma)} - \gamma_{k}^{(\mu)})x_{k,s}
+\end{align}
+```
+All predictors were standardized (mean = 0, SD = 1) before the analysis.
+
+**Species interaction.** We analyzed a subset of our data to estimate the strength of interspecific interactions among stream fishes.
+In this analysis, we focused on `r n_distinct(df_complete$site_id)` sites with $>16$ years of observations and no intentional release of masu salmon.
+Further, at each site, we confined our analysis to species that occurred more than four times.
+These additional constraints were necessary to estimate parameters in a complex multi-species model within a state-space modeling framework.
+
+We fitted the following state-space model to the data for each site separately. In the observation model, we modeled fish abundance $N_{i,t}$ for species $i$ at year $t$ as:
+
+```{=tex}
+\begin{align}
+\begin{split}
+N_{i,t} &\sim \text{Poisson}(\lambda_{i,t} A_{t})\\
+\lambda_{s,t} &= n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})
+\end{split}
+\end{align}
+```
+where $\varepsilon_{i,t}^{\text{obs}} \sim \text{Normal}(0, \sigma_{\text{obs},i})$. In the state model, we described a multi-species Ricker model for fish density $n_{i,t}$:
+
+```{=tex}
+\begin{align}
+\ln n_{i,t} = \ln n_{i,t-1} + r_{i} - \sum_{j=1}^S\alpha'_{ij} n_{i,t-1} + \varepsilon_{i,t}^{\text{state}}
+(\#eq:ricker-ssm)
+\end{align}
+```
+Equation \@ref(eq:ricker-ssm) is equivalent to Equation \@ref(eq:ricker0) except the scale of competition coefficients $\alpha'_{ij}$ ($\frac{\alpha'_{ij}}{\alpha'_{ii}}=\alpha_{ij}$, where $\alpha'_{ii}=\frac{r_i}{K_i}$).
+We used sparse priors for $\alpha'_{ij}$ to reduce the risk of over-fitting [@mutshindaWhatDrivesCommunity2009]:
+
+```{=tex}
+\begin{align}
+\begin{split}
+\alpha'_{ij} \sim \text{Half-normal}(0, \sigma^2_{\alpha, ij})\\
+\sigma_{\alpha,ij}^2 = z_{ij}c_1 + (1-z_{ij})c_0
+\end{split}
+(\#eq:sparse)
+\end{align}
+```
+In Equation \@ref(eq:sparse), the latent variable $z_{ij}$ is drawn from a Bernoulli distribution and controls the prior for $\alpha'_{ij}$.
+We used $c_1 = 1$ and $c_0 = 0.01$ so that $\alpha'_{ij}$ is freely estimated when $z_{ij}$ equals one ($\sigma^2_{\alpha} = 1$).
+Otherwise, the probability density of $\alpha'_{ij}$ would be concentrated around zero ($\sigma^2_{\alpha} = 0.01$), effectively omitting the parameter from the model [@mutshindaWhatDrivesCommunity2009].
+We assigned different "inclusion" probabilities to diagonal (intraspecific competition) and off-diagonal elements (interspecific competition) as $z_{ii} \sim \text{Bernoulli}(p_{\alpha}^{\text{intra}})$ and $z_{ij,i \ne j} \sim \text{Bernoulli}(p_{\alpha}^{\text{inter}})$.
+
+We assumed that environmental noise $\varepsilon_{i,t}^{\text{state}}$ is correlated among species by introducing the variance-covariance matrix $\pmb{\Omega_{\varepsilon}}$.
+The matrix $\pmb{\Omega_{\varepsilon}}$ was modeled with the aid of latent factors $\zeta_{t,d}$ and factor loadings $\delta_{d,i}$:
+
+```{=tex}
+\begin{align}
+\varepsilon_{i,t}^{\text{state}}=\sum_{d}^{D}\zeta_{t,d}\delta_{d,i} + I_{ij}\epsilon_{i,t}
+\end{align}
+```
+where $D$ is the number of latent factors, $\epsilon_{i,t} \sim \text{Normal}(0, \sigma_{\epsilon,i}^2)$, and $I_{ij}$ is the identity matrix ($I_{ii}=1$ and $I_{ij, i \ne j} = 0$).
+With this formulation, the matrix $\pmb{\Omega_{\varepsilon}}$ can be described as $\pmb{\Omega_{\varepsilon}}=\pmb{\Delta}^T\pmb{\Delta} + \text{diag}(\sigma_{\epsilon,i}^2)$, where $\pmb{\Delta}$ is the matrix of factor loadings $\delta_{d,i}$.
+This model structure with multiplicative gamma priors on factor loadings [@duranteNoteMultiplicativeGamma2017] has the merit of the reduced number of parameters while capturing the correlated nature of species responses to environmental fluctuations [@ovaskainenHowAreSpecies2017].
+We set $D=2$ in our model.
+We reported the estimates of $\alpha_{ij}$, so the values are comparable to those used in the theoretical analysis.
+
+**Model fitting.** We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
+We assigned vague or weakly informative priors to parameters (**Table S**\@ref(tab:tab-prior)).
+Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
+The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc)` to `r max(df_mcmc$n_total_mcmc)`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period.
+Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached $<1.1$ [@gelmanDataAnalysisUsing2007].
+Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021].
+Parameter estimates were summarized in **Tables S**\@ref(tab:tab-ssm-ar) -- **S**\@ref(tab:tab-reg3).
+
 # Acknowledgements

### 2022-10-28 rmd/manuscript.Rmd
Update manuscript.Rmd
fig reference

@@
 The rest of the simulation procedure is identical to the two-species model.
-We summarized values of simulation parameters in **Table S**\@ref(tab:tab-para).
+We summarized values of simulation parameters in **Table S**1.
 
@@
 The summed abundance of first and second passes was used in the following analysis.
-**Table S**\@ref(tab:tab-splist) summarizes observed species in these watersheds.
+**Table S**2 summarizes observed species in these watersheds.
 
@@
 For a whole community, we summed the densities of enhanced and unenhanced species.
-We summarized the reconstructed community dynamics in **Figures S**\@ref(fig:fig-d1) -- **S**\@ref(fig:fig-d3).
+We summarized the reconstructed community dynamics in **Figures S**11 -- **S**13.
 
@@
 Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
-Urban and agricultural land use was omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)).
+Urban and agricultural land use was omitted because of either a limited value range (**Figure S**14) or a strong correlation with forest land use (**Figure S**15).
 The watershed-specific intercept was related to a watershed-level predictor as:
@@
 **Model fitting.** We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016].
-We assigned vague or weakly informative priors to parameters (**Table S**\@ref(tab:tab-prior)).
+We assigned vague or weakly informative priors to parameters (**Table S**3).
 Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
@@
 Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021].
-Parameter estimates were summarized in **Tables S**\@ref(tab:tab-ssm-ar) -- **S**\@ref(tab:tab-reg3).
+Parameter estimates were summarized in **Tables S**4 -- **S**8.
 

### 2022-10-28 rmd/manuscript.Rmd
edit

@@
 Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014].
-It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007].
+It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoost2022], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007].
 Typically, masu salmon are reared in captivity for two to four generations.
@@
 We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` timesteps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$ ($S$: the number of species): the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$).
-The results of the two-species system were reported in [Supplementary Text].
+The results of the two-species system were reported in **Supplementary Text**.
 

### 2022-10-28 rmd/manuscript.Rmd
edit

@@
 However, such external inputs may disrupt the sensitive species interactions that allow competing species to coexist, potentially compromising long-term community stability.
-Here, we use theory and long-term data of stream fish communities to show that intentional release destabilizes community dynamics with a limited demographic benefit to the enhanced species.
+Here, we use theory and long-term data of stream fish communities to show that intentional release destabilizes community dynamics with limited demographic benefit to the enhanced species.
 Our theory predicted that intentional release intensifies interspecific competition, facilitating the competitive exclusion of unenhanced species that otherwise stably coexist.

### 2022-10-28 rmd/supporting_info.Rmd
edit

@@
   - \usepackage{amsmath, fancyhdr, caption, booktabs}
-  - \captionsetup{width=1.35\linewidth, labelfont={bf}}
+  - \setlength{\headheight}{13.6pt}
 bibliography: reference.bib

### 2022-12-21 rmd/manuscript.Rmd
edit: text

@@
 The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterfisheriesresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021].
-The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net).
+The program began in 1963, but an effective, standardized sampling method has been implemented since 1999; at all sampling sites, a combination of electrofishing and cast net (two-pass) was used to effectively catch both benthic and water-column species (see **Supplementary Text**).
 Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^).

### 2022-12-21 rmd/supporting_info.Rmd
edit: text

@@
 Increasing the competition coefficient $\bar{\alpha}$ shifted the region with the destabilizing effects to higher carrying capacities ($\bar{\alpha}=$ `r max(list_param[[1]]$alpha)`, **Figure S**\@ref(fig:fig-2sp-s)); otherwise, general patterns were similar to the weak competition scenario.
+
+## Fish sampling
+
+In the monitoring program, a two-pass sampling method was employed at all sampling sites.
+In each pass, a combination of electrofishing and cast net (two-pass) was used to effectively catch both benthic and water-column species in a given area.
+The number of cast-net throws was determined as the sampled area divided by $4.5~\text{m}^2$ (the area covered by a cast net).
+Thus, this sampling method has a constant sampling effort per unit area across sites.
 

### 2022-12-23 rmd/manuscript.Rmd
edit: manuscript
anchor: changing to word output

@@
 output:
-  bookdown::pdf_document2:
-   latex_engine: xelatex
-   toc: false
+  # bookdown::pdf_document2:
+  #  latex_engine: xelatex
+  #  toc: false
+  #  number_sections: false
+  bookdown::word_document2:
+    reference_docx: word_format.docx
     number_sections: false
-  #bookdown::word_document2:
-  # reference_docx: word_format.docx
-  # number_sections: false
+    pandoc_args: ["-Fpandoc-crossref"]
 csl: https://www.zotero.org/styles/pnas
@@
 
-When small carrying capacity was combined with a low to modest intrinsic growth rate ($K=$ `r min(list_param[[2]]$k)`, $r_1 \le 2.5$), our model predicted a destabilizing effect of intentional release on ecological communities, as illustrated by increased CV with increasing numbers of releases (**Figure** \@ref(fig:figure-layout)**A**).
-This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** \@ref(fig:figure-layout)**A**).
+When small carrying capacity was combined with a low to modest intrinsic growth rate ($K=$ `r min(list_param[[2]]$k)`, $r_1 \le 2.5$), our model predicted a destabilizing effect of intentional release on ecological communities, as illustrated by increased CV with increasing numbers of releases (**Figure** 1)**A**).
+This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** 1)**A**).
 The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** \@ref(fig:figure-layout)**A**).
-Combined, the total community density decreased more sharply than individual species groups (**Figure** \@ref(fig:figure-layout)**A**).
-The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** \@ref(fig:figure-layout)**A**).
+Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** 1)**A**).
+Combined, the total community density decreased more sharply than individual species groups (**Figure** 1)**A**).
+The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** 1)**A**).
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
 These patterns were qualitatively similar across ecological contexts with the low carrying capacity (**Figures S3 -- S6**), but except for the scenario in which the enhanced species exhibits chaos ($r_1=$ `r max(list_param[[2]]$r1)`).
-
-```{r figure-layout, fig.cap= paste0("Theory and empirical observations agree that intentional release destabilizes community dynamics.
-In A and B, panels and colors distinguish response variables and species groups.
-(A) Theoretical predictions.
-Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and prediction intervals (light shade).
-Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ ", round(na.omit(unique(df_sim$r1)), 2), ", average interspecific competition $\\bar{\\alpha}=$ ", round(na.omit(unique(df_sim$alpha)), 2), ", carrying capacity $K=$ ", round(na.omit(unique(df_sim$k)), 2), ", environmental stochasticity $\\sigma_{\\varepsilon}=$ ", round(na.omit(unique(df_sim$sd_env)), 2), ", relative fitness of captive-bred individuals $f_R=$ ", round(na.omit(unique(df_sim$phi)), 2), ".
-These parameter values are comparable to those estimated in the empirical Ricker model.
-(B) Empirical evidence.
-Dots represent observations at 97 sites within 31 watersheds.
-Lines and shades are the predicted values and their 95% credible intervals of the regression models, and line types correspond to the coefficient's posterior probabilities.
-Effective release is a latent explanatory variable estimated in our hierarchical Baysian model.
-See Methods for details.
-Full statistics were reported in Tables S6-8.
-(C) Map of sampling sites (black dots) in Hokkaido, Japan.
-(D) Example of a protected watershed (Okushibetsu).
-(E) Masu salmon *Oncorhynchus masou*.
-Photo credit: Akira Terui")}
-
-knitr::include_graphics(here::here("output/figure_theory_obs.pdf"))
-
-```
 
@@
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure** \@ref(fig:figure-layout)**E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure** 1)**E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
 In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records.
@@
 
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** \@ref(fig:figure-layout)**B**).
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** 1)**B**).
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** \@ref(fig:figure-coef); see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob) %>% round(2), 2)` (**Table S6**).
-This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)**;** see **Tables S6 -- S8** for full statistics).
-In the meantime, the SDs had vague relationships with the intentional release (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)).
-
-```{r figure-coef, fig.cap="Posterior distributions for the standardized regression coefficients of intentional release.
-Y-axis represents different response variables grouped by colors distinguishing species groups (whole community, enhanced species [masu salmon], and unenhanced species).
-Triangles indicate median estimates."}
-
-knitr::include_graphics(here::here("output/figure_coef.pdf"))
-
-```
+Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** 2; see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob) %>% round(2), 2)` (**Table S6**).
+This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** 1)**B and** 2), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** 1)**B and** 2**;** see **Tables S6 -- S8** for full statistics).
+In the meantime, the SDs had vague relationships with the intentional release (**Figures** 1)**B and** 2).
 
@@
 The parameter estimates of this model are directly comparable to those used in the theoretical Ricker model.
-The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure** \@ref(fig:figure-alpha)), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
+The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure** 3)), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
 Our statistical inference is supported by previous studies.
@@
 Importantly, hatchery masu salmon may intensify intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
-Hatchery salmons are larger and more aggressive than wild individuals of a comparable life stage, increasing the likelihood of intense intra- and interspecific competition [@weberInteractionsHatcheryWild2003].
+Hatchery salmon are larger and more aggressive than wild individuals of a comparable life stage, increasing the likelihood of intense intra- and interspecific competition [@weberInteractionsHatcheryWild2003].
 Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
@@
 
-```{r figure-alpha, fig.cap="Estimated competition coefficients of the multi-species Ricker model.
-Dots represent a given pair of taxa, and box plots show median (vertical center line) and quartiles (box limits) with whiskers extending up to the most extreme data points that are within $\\pm 1.5$ interquartile range.
-The density plot on the top shows the overall distribution of the competition coefficient.
-Colors distinguish taxa.
-The vertical broken line denotes the overall median value."}
-
-source(here::here("code/si_figure_species_int.R"))
-
-knitr::include_graphics(here::here("output/figure_alpha_dist.pdf"))
-```
-
 ## Implications
@@
 In the basic formula without intentional release, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:
+
+$$N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{\sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})$${#eq:ricker0}
 

### 2022-12-23 rmd/figure_caption.Rmd
Create figure_caption.Rmd

--- 2022-03-12 rmd/figures.Rmd
@@
 ---
+title: "Figure captions"
 output:
-  pdf_document:
-    latex_engine: xelatex
+  bookdown::word_document2:
+    reference_docx: word_format.docx
+    number_sections: false
 knit: (function(inputFile, encoding) {
-        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
+        rmarkdown::render(inputFile,
+                          encoding = encoding, 
+                          output_dir = "document_output")
       })
-header-includes:
-  \pagenumbering{gobble}
+fontsize: 11pt
+mainfont: "Times New Roman"
 ---
-
-```{r setup, include=FALSE}
-
-knitr::opts_chunk$set(echo = FALSE,
-                      message = FALSE,
-                      warning = FALSE)
-
-```
-
-```{r figure_1, fig.width=9, fig.height=11}
-
-source(here::here("code/figure_theory_obs.R"))
-
-print(g)
-
-```
 
@@
 (A) Theoretical predictions.
-Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and 95% confidence intervals.
-Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`.
+Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and prediction intervals (light shade).
+Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ `r round(na.omit(unique(df_sim$r1)), 2)` average interspecific competition $\bar{\alpha}=$ `r round(na.omit(unique(df_sim$alpha)), 2)`, carrying capacity $K=$ `round(na.omit(unique(df_sim$k)), 2)`, environmental stochasticity $\sigma_{\varepsilon}=$ `r round(na.omit(unique(df_sim$sd_env)), 2)`, relative fitness of captive-bred individuals $f_R=$ `r round(na.omit(unique(df_sim$phi)), 2)`.
+These parameter values are comparable to those estimated in the empirical Ricker model.
 (B) Empirical evidence.
-Dots represent geometric means of site-level observations in 31 watersheds.
-Lines are the predicted values of the regression models, and line types correspond to the coefficient's posterior probabilities.
-See Tables S8-10 for full statistics.
+Dots represent observations at 97 sites within 31 watersheds.
+Lines and shades are the predicted values and their 95% credible intervals of the regression models, and line types correspond to the coefficient's posterior probabilities.
+Effective release is a latent explanatory variable estimated in our hierarchical Baysian model.
+See Methods for details.
+Full statistics were reported in Tables S6 -- 8.
 (C) Map of sampling sites (black dots) in Hokkaido, Japan.
-(D) Example of a protected watershed (Okushibetsu).
-(E) Masu salmon *Oncorhynchus masou masou*.
-Photo credit: Akira Terui.
-
-\newpage
-
-```{r figure2, fig.width=8, fig.height=6}
-
-source(here::here("code/figure_coef.R"))
-
-print(g_coef)
-
-```
+(E) Masu salmon *Oncorhynchus masou*.
+Photo credit: Akira Terui
 
@@
 Y-axis represents different response variables grouped by colors distinguishing species groups (whole community, enhanced species [masu salmon], and unenhanced species).
+Triangles indicate median estimates.
+
+**Figure 3** Estimated competition coefficients of the multi-species Ricker model.
+Dots represent a given pair of taxa, and box plots show median (vertical center line) and quartiles (box limits) with whiskers extending up to the most extreme data points that are within $\pm 1.5$ interquartile range.
+The density plot on the top shows the overall distribution of the competition coefficient.
+Colors distinguish taxa.
+The vertical broken line denotes the overall median value.

### 2022-12-23 rmd/manuscript.Rmd
edit: update equation form to word

@@
 
-```{=tex}
-\begin{align}
-N_{i,t+1} = N_{i,t}~\exp\left[r_i \left(1-\frac{\sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
-(\#eq:ricker0)
-\end{align}
-```
 where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\varepsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey a normal distribution $\text{Normal}(0, \sigma_{\varepsilon}^2)$.
@@
 
-```{=tex}
-\begin{align}
-N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\varepsilon_{i,t})
-(\#eq:ricker)
-\end{align}
-```
+$$N_{i,t+1} = (N_{i,t}+\phi_i R_t)~\exp \left[r_i \left\{1-\frac{\alpha_{i1} (N_{1,t} + R_t) + \sum_{j=2}^S \alpha_{ij}N_{j,t}}{K_i} \right\} \right]\exp(\varepsilon_{i,t})$${#eq:ricker}
+
 $R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 \phi_i =
@@
 \right.
-\end{align}
-```
+\end{aligned}
+$${#eq:phi}
+
 $f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation \@ref(eq:ricker) can be reorganized to:
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 N_{i,t+1} = (N_{i,t}+\phi_i R_t) ~ \exp \left[r_i \left(1-\frac{\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
-\end{align}
-```
+\end{aligned}
+$${#eq:ricker1}
+
 In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,r_{\text{max}})$) and an exponential distribution ($\alpha_{ij} \sim \text{Exp}(1/\bar{\alpha})$), respectively.
@@
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 N_{s,t} \sim \text{Poisson}(\lambda_{s,t} A_{s,t})
-\end{align}
-```
+\end{aligned}
+$${#eq:ssm-obs1}
+
 where $\lambda_{s,t}$ is the expected fish density (individual m^-2^) and $A_{s,t}$ the sampling area (m^2^).
@@
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 \lambda_{s,t} = n_{s,t}\exp(\varepsilon_{s,t}^{\text{obs}}) + \psi \beta_s~Fry_{w(s),t}
-\end{align}
-```
+\end{aligned}
+$${#eq:ssm-obs2}
+
 $n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released (unit: million fish) in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density.
@@
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 \begin{split}
@@
 \end{split}
-(\#eq:state)
-\end{align}
-```
+\end{aligned}
+$${#eq:state}
+
 where $\xi_{1,s}$ is the site-specific constant at site $s$, $\xi_{2,s}$ the parameter characterizing an autoregressive (AR) process, and $\varepsilon_{s,t}^{\text{state}}$ the process error that follows a normal distribution as $\varepsilon_{s,t}^{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state},s}^2)$.
@@
 
-```{=tex}
-\begin{align}
-\left\{
+$$\left\{
 \begin{aligned}
@@
 \end{aligned}
-\right.
- (\#eq:reg)
-\end{align}
-```
+\right.$${#eq:reg}
+
 In the poisson model for species richness, $\exp(\varepsilon_{\lambda,s})$ is the error term accounting for overdispersion ($\varepsilon_{\lambda,s} \sim \text{Normal}(0, \sigma_{\lambda}^2)$).
@@
 \end{aligned}
-\right.
-(\#eq:model)
-\end{align}
-```
+\right.$${#eq:model}
+
 $\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k = 1,2,...)$ is the $k^\text{th}$ regression coefficient [effective release of masu salmon $R'_s$ ($k = 1$) and other site-level predictors $x_k$ ($k \ge 2$)].
@@
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 \begin{split}
-R'_s = \eta_{w,s'} R_w~\text{where}~
-\sum_{s'}^{S_w + 1} \eta_{w,s'} = 1
-(\#eq:effr)
+R'_s = \eta_{w,s'} R_w~\text{where}~\sum_{s'}^{S_w + 1} \eta_{w,s'} = 1
 \end{split}
-\end{align}
-```
+\end{aligned}
+$${#eq:effr}
+
 In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$.
 The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas.
-Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **model fitting**).
+Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **Model fitting**).
 Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
@@
 
-```{=tex}
-\begin{align}
-\begin{split}
-\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\
-\theta_{\gamma,w} &= \gamma'_0 + \gamma'_1 x'_{w}
-\end{split}
-\end{align}
-```
+$$
+\begin{aligned}\begin{split}\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\\theta_{\gamma,w} &= \gamma'_0 + \gamma'_1 x'_{w}\end{split}\end{aligned}
+$${#eq:random-eff}
+
 $\gamma'_{0}$ is the global intercept and $\gamma'_1$ is the regression coefficient of ocean productivity $\gamma'_{w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019).
@@
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 \text{E}(\ln CV_s) = \text{E}(\ln y_s^{(\sigma)}) - \text{E}(\ln y_s^{(\mu)})
-\end{align}
-```
+\end{aligned}
+$${#eq:cv-convert1}
+
 Considering that $\text{E}(\ln y_s^{(\sigma)}) = \theta_{y,s}^{(\sigma)}$ and $\text{E}(\ln y_s^{(\mu)}) = \theta_{y,s}^{(\mu)}$,
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 \text{E}(\ln CV_s) = (\gamma_{0,w(s)}^{(\sigma)} - \gamma_{0,w(s)}^{(\mu)}) + (\gamma_{1}^{(\sigma)} - \gamma_{1}^{(\mu)})R'_s + \sum_k (\gamma_{k}^{(\sigma)} - \gamma_{k}^{(\mu)})x_{k,s}
-\end{align}
-```
+\end{aligned}
+$${#eq:cv-convert2}
+
 All predictors were standardized (mean = 0, SD = 1) before the analysis.
@@
 
-```{=tex}
-\begin{align}
-\begin{split}
-N_{i,t} &\sim \text{Poisson}(\lambda_{i,t} A_{t})\\
-\lambda_{s,t} &= n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})
-\end{split}
-\end{align}
-```
+$$
+\begin{aligned}\begin{split}N_{i,t} &\sim \text{Poisson}(\lambda_{i,t} A_{t})\\\lambda_{s,t} &= n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})\end{split}\end{aligned}
+$${#eq:ricker-ssm-obs}
+
 where $\varepsilon_{i,t}^{\text{obs}} \sim \text{Normal}(0, \sigma_{\text{obs},i})$. In the state model, we described a multi-species Ricker model for fish density $n_{i,t}$:
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 \ln n_{i,t} = \ln n_{i,t-1} + r_{i} - \sum_{j=1}^S\alpha'_{ij} n_{i,t-1} + \varepsilon_{i,t}^{\text{state}}
-(\#eq:ricker-ssm)
-\end{align}
-```
+\end{aligned}
+$${#eq:ricker-ssm}
+
 Equation \@ref(eq:ricker-ssm) is equivalent to Equation \@ref(eq:ricker0) except the scale of competition coefficients $\alpha'_{ij}$ ($\frac{\alpha'_{ij}}{\alpha'_{ii}}=\alpha_{ij}$, where $\alpha'_{ii}=\frac{r_i}{K_i}$).
@@
 
-```{=tex}
-\begin{align}
+$$
+\begin{aligned}
 \begin{split}
-\alpha'_{ij} \sim \text{Half-normal}(0, \sigma^2_{\alpha, ij})\\
-\sigma_{\alpha,ij}^2 = z_{ij}c_1 + (1-z_{ij})c_0
+\alpha'_{ij} \sim \text{Half-normal}(0, \sigma^2_{\alpha, ij})\\\sigma_{\alpha,ij}^2 = z_{ij}c_1 + (1-z_{ij})c_0
 \end{split}
-(\#eq:sparse)
-\end{align}
-```
+\end{aligned}
+$${#eq:sparse}
+
 In Equation \@ref(eq:sparse), the latent variable $z_{ij}$ is drawn from a Bernoulli distribution and controls the prior for $\alpha'_{ij}$.
@@
 
-```{=tex}
-\begin{align}
-\varepsilon_{i,t}^{\text{state}}=\sum_{d}^{D}\zeta_{t,d}\delta_{d,i} + I_{ij}\epsilon_{i,t}
-\end{align}
-```
+$$
+\begin{aligned}\varepsilon_{i,t}^{\text{state}}=\sum_{d}^{D}\zeta_{t,d}\delta_{d,i} + I_{ij}\epsilon_{i,t}\end{aligned}
+$${#eq:ricker-ssm-fa}
+
 where $D$ is the number of latent factors, $\epsilon_{i,t} \sim \text{Normal}(0, \sigma_{\epsilon,i}^2)$, and $I_{ij}$ is the identity matrix ($I_{ii}=1$ and $I_{ij, i \ne j} = 0$).

### 2022-12-23 rmd/manuscript.Rmd
edit: add text for additional predictors

@@
 Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **Model fitting**).
-Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use.
+Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, forest land use, and the number of observation years.
+The number of observation years was included as a control factor given the potential influence on the estimates of temporal community variability.
 Urban and agricultural land use was omitted because of either a limited value range (**Figure S**14) or a strong correlation with forest land use (**Figure S**15).
@@
 $$
-\begin{aligned}\begin{split}\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\\theta_{\gamma,w} &= \gamma'_0 + \gamma'_1 x'_{w}\end{split}\end{aligned}
+\begin{aligned}\begin{split}\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\\theta_{\gamma,w} &= \gamma'_0 + \sum_k \gamma'_k x'_{k,w}\end{split}\end{aligned}
 $${#eq:random-eff}
 
-$\gamma'_{0}$ is the global intercept and $\gamma'_1$ is the regression coefficient of ocean productivity $\gamma'_{w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019).
+$\gamma'_{0}$ is the global intercept and $\gamma'_k$ is the regression coefficients of ocean productivity $\gamma'_{1,w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019) and standard deviation of elevation (SD elevation) within an entire watershed $\gamma'_{2,w}$.
 Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).
-The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictor cannot capture.
+SD elevation is a landscape-level variable that may dictate long-term flow dynamics.
+The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
 

### 2022-12-23 rmd/manuscript.Rmd
edit: correct cross-reference

@@
 
-$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation \@ref(eq:ricker) can be reorganized to:
+$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation (2) can be reorganized to:
 
@@
 The parameters $\xi_{1,s}$ and $\xi_{2,s}$ were drawn from a multivariate normal distribution as $\pmb{\xi} \sim \text{MVN}(\pmb{\theta_{\xi}}, \pmb{\Omega_{\xi}})$, where $\pmb{\xi}$ is the matrix of $\xi_{1,s}$ and $\xi_{2,s}$.
-Equation \@ref(eq:state) is structurally equivalent to a $Q$-order AR model; however, we expressed the part of AR parameters as a geometric-series $\tau^q$ to reduce the number of parameters (our model has two AR parameters $\xi_{2,s}$ and $\tau$ regardless of order $Q$).
+Equation (7) is structurally equivalent to a $Q$-order AR model; however, we expressed the part of AR parameters as a geometric-series $\tau^q$ to reduce the number of parameters (our model has two AR parameters $\xi_{2,s}$ and $\tau$ regardless of order $Q$).
 The parameter $\tau$ controls how fast the density influence attenuates towards the past [@takagiTimescaleDependencyHost2015].
@@
 
-In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$.
+In Equation (10), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$.
 The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas.
@@
 
-Since the CV is an additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation \@ref(eq:model):
+Since the CV is an additive function of mean $\mu$ and SD $\sigma$ in a log scale, we can derive the effects of environmental factors on the CV from Equation (9):
 
@@
 
-Equation \@ref(eq:ricker-ssm) is equivalent to Equation \@ref(eq:ricker0) except the scale of competition coefficients $\alpha'_{ij}$ ($\frac{\alpha'_{ij}}{\alpha'_{ii}}=\alpha_{ij}$, where $\alpha'_{ii}=\frac{r_i}{K_i}$).
+Equation (15) is equivalent to Equation (1) except the scale of competition coefficients $\alpha'_{ij}$ ($\frac{\alpha'_{ij}}{\alpha'_{ii}}=\alpha_{ij}$, where $\alpha'_{ii}=\frac{r_i}{K_i}$).
 We used sparse priors for $\alpha'_{ij}$ to reduce the risk of over-fitting [@mutshindaWhatDrivesCommunity2009]:
@@
 
-In Equation \@ref(eq:sparse), the latent variable $z_{ij}$ is drawn from a Bernoulli distribution and controls the prior for $\alpha'_{ij}$.
+In Equation (16), the latent variable $z_{ij}$ is drawn from a Bernoulli distribution and controls the prior for $\alpha'_{ij}$.
 We used $c_1 = 1$ and $c_0 = 0.01$ so that $\alpha'_{ij}$ is freely estimated when $z_{ij}$ equals one ($\sigma^2_{\alpha} = 1$).

### 2022-12-23 rmd/manuscript.Rmd
edit: manuscript correct typo

@@
 
-When small carrying capacity was combined with a low to modest intrinsic growth rate ($K=$ `r min(list_param[[2]]$k)`, $r_1 \le 2.5$), our model predicted a destabilizing effect of intentional release on ecological communities, as illustrated by increased CV with increasing numbers of releases (**Figure** 1)**A**).
-This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** 1)**A**).
+When small carrying capacity was combined with a low to modest intrinsic growth rate ($K=$ `r min(list_param[[2]]$k)`, $r_1 \le 2.5$), our model predicted a destabilizing effect of intentional release on ecological communities, as illustrated by increased CV with increasing numbers of releases (**Figure** 1**A**).
+This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** 1**A**).
 The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** 1)**A**).
-Combined, the total community density decreased more sharply than individual species groups (**Figure** 1)**A**).
-The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** 1)**A**).
+Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** 1**A**).
+Combined, the total community density decreased more sharply than individual species groups (**Figure** 1**A**).
+The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** 1**A**).
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
@@
 
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** 1)**B**).
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** 1**B**).
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
 Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** 2; see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob) %>% round(2), 2)` (**Table S6**).
-This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** 1)**B and** 2), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** 1)**B and** 2**;** see **Tables S6 -- S8** for full statistics).
-In the meantime, the SDs had vague relationships with the intentional release (**Figures** 1)**B and** 2).
+This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** 1**B and** 2), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** 1**B and** 2**;** see **Tables S6 -- S8** for full statistics).
+In the meantime, the SDs had vague relationships with the intentional release (**Figures** 1**B and** 2).
 
@@
 The parameter estimates of this model are directly comparable to those used in the theoretical Ricker model.
-The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure** 3)), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
+The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure** 3), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
 Our statistical inference is supported by previous studies.

### 2022-12-24 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010].
-In particular, the magnitude of intentional release for commercial and recreational species is massive [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018] -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (crustaceans, bivalves, insects) [@kitadaEconomicEcologicalGenetic2018; @ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
+In particular, the magnitude of intentional release for commercial and recreational species is massive [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018] -- large-scale programs release thousands to millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (crustaceans, bivalves, insects) [@kitadaEconomicEcologicalGenetic2018; @ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually.
 There is growing awareness that intentional release entails ecological risks, such as the accumulation of deleterious alleles and the intensified competition within the enhanced species [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007; @kitadaLessonsLearnedJapanese2006].
 Yet, this method is still pervasive in natural resource management owing to the significant economic benefit [@malkamakiSystematicReviewSocioeconomic2018; @davidEconomicFeasibilityIntensification2018; @rutledgeCostBenefitHatcheryreared1990; @kitadaEconomicEcologicalGenetic2018].
-For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed the economic performance of release programs for 12 major fishery resources across the globe.
+For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed the economic performance of release programs for 12 major fishery species across the globe.
 The gross monetary yield exceeded the seed-production cost in nine species, suggesting that release programs are economically profitable in general.
 
-Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of intentional release.
-Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
+The intentional release, however, can have far-reaching consequences than previously thought, as the impacts can propagate through a diversity of ecological interactions [@careyNativeInvadersChallenges2012].
+This recognition has stimulated a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019].
+Yet, current debates overlook the fact that we lack a quantitative assessment of the community-wide impact in the long-term.
+Ecological theory suggests that the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
 Intentional release may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@laikreCompromisingGeneticDiversity2010; @careyNativeInvadersChallenges2012; @kitadaEconomicEcologicalGenetic2018].
@@
 In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S7**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective.
-The weak-competition scenario is likely in re-introduction programs of extirpated species or population enhancement of long-lived endangered species.
-In fact, some of the best evidence for successful intentional release comes from re-introduction efforts [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021].
-In the Sado island (Japan), for example, the once-extirpated Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial re-introduction of ten captive-bred individuals in 2008 [@okahisaEvaluationOngoingCrested2022].
+The weak-competition scenario is likely in reintroduction programs that aim to replenish populations of extirpated species or long-lived endangered species.
+In fact, some of the best evidence for successful intentional release comes from reintroduction efforts for such species [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021].
+In the Sado island (Japan), for example, the once-extirpated Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008 [@okahisaEvaluationOngoingCrested2022].
 Similarly, translocations of Humpback chub, a federally-listed fish species in the US, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River [@yackulicAssessingPopulationImpacts2021].
-However, the preponderance of unsuccessful re-introduction programs implies that the theoretical requirements for successful intentional release are not always met [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019].
+However, the preponderance of unsuccessful reintroduction programs implies that the theoretical requirements for successful intentional release are not always met [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019].
 Indeed, non-negligible numbers of projects seem to release captive-bred individuals into unsuitable habitats with compromised carrying capacities [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012].
@@
 The majority of release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
+Several of the watersheds are not subject to intentional release aiming to preserve regional populations of masu salmon, while the release numbers at other watersheds vary due mainly to logistical reasons.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.

### 2022-12-24 rmd/reply_r2.Rmd
Create reply_r2.Rmd

---
title: "Reply to: 2022-05603 Intentional release of native species undermines ecological stability"
output:
  bookdown::pdf_document2:
   latex_engine: xelatex
   toc: false
   number_sections: false
csl: https://www.zotero.org/styles/pnas
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
mainfont: "Times New Roman"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Dear editor,

This is a re-submission of a manuscript: "2022­05603 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript. The comments were very helpful in improving our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:

In summary, the improved text/analysis provides clearer evidence that intentional release has destabilizing effects and clarifies its broader relevance to other systems. We appended a point-by-point response below. We hope our manuscript is now suitable for publication in your journal.

Sincerely,

Akira Terui, on behalf of the authors

\clearpage

## Point-by-point response

### Editor

### Reviewer 1

*The authors have done a terrific job of responding to the editor and reviewer comments.*

> Thank you!

### Reviewer 3

*The empirical results are intriguing to me. It is an impressive data set and intriguing results, but I do worry quite a bit that the results are spurious. In particular, interannual stability (CV) of the aggregate population feels like many factors could influence it. I have a series of questions with corresponding suggestions to address some of these concerns.*

> Thank you for your careful reading. Please see our response below.

*Sampling. Effective sampling of stream fishes is quite challenging. Cast net and e-fishing would likely have very strong influence on the catch composition (e.g., benthic fishes will be less catchable by cast net). Was sampling methodology included as a factor in the analysis?*

> Thank you. This is perhaps because of our unclear writing. At all sites, a combination of electrofishing and cast net was used to capture both benthic and water-column species effectively. We have clarified this in the revised MS (L XXX). In addition, we have added some text to clarify that the sampling has constant sampling effort per unit area. Therefore, our analysis is robust to this issue.

*Sampling interval. I am concerned that there were irregular sampling intervals ("1- to 3-year intervals"), especially given that variability was one of the response variables. I understand that the state-space approach estimates true abundance, but I think it is important that a secondary analysis be performed on just the sites with all years.*

> The secondary analysis at sites with no missing data would be insightful for sure. However, it introduces the issue of sample size. To address reviewer's concern more appropriately, we included "the number of observation years" as a covariate in the regression model. This approach is suitable because it keeps the sample size as original while accounting for potential influences of observation intervals. The results were qualitatively similar.

*Are the empirical results robust if the strong outlier on the far right is removed? It sure looks like this point would have strong leverage.*

> Thank you for your careful reading. However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from analysis. Although the figure was shown in an ordinary scale, the analysis was carried out in a log-scale (see Methods). When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below). Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for outliers in both response (log CV) and predictor variables (effective release). We hope this ameliorates reviewer's concern.

```{r outlier, echo = TRUE}

# setup -------------------------------------------------------------------
source(here::here("code/library.R"))

# data --------------------------------------------------------------------

## raw data for cv, mean, sd
suppressMessages(source(here::here("code/data_fmt_reg.R")))

## select cv
df_m <- df_ssm %>%
  filter(group == "all",
         response == "cv")

## regression data
df_reg <- list.files(path = here::here("output"),
                     full.names = TRUE,
                     pattern = "summary_reg") %>% 
  readRDS() %>% 
  mutate(y = response)

## join weighted stock
df_m <- df_reg %>% 
  filter(str_detect(parameter, "ef_stock")) %>%
  dplyr::select(site_id_numeric,
         ef_stock = median) %>% 
  right_join(df_m,
             by = "site_id_numeric")

# check outlier influence -------------------------------------------------

# outlier check for log-cv
## log(df_m$value) is log-transformed cv
outliers::grubbs.test(log(df_m$value))

# check robustness with MM method
## MM method accounts for outliers in both y and x
## log(value) - log-tranformed CV
## ef_stock - effective release of masu salmon
MASS::rlm(log(value) ~ scale(ef_stock),
          method = "MM",
          df_m) %>% 
  summary()

```

*Relatively community composition could drive patterns of variability through time, as different species many have different intrinsic patterns of variability. I was struck by the diversity of life-histories in the fish community, ranging from smelt to lamprey to loach to salmonids.*

> XXX

*Elevation range or mean elevation of the watersheds should be included as a factor in the model. The current factors were positive, but none of them really had any proxies for the inherent dynamics of stream ecosystems or flow regime variability.*

> We appreciate this suggestion! We included SD Elevation as an additional covariate in the regression model. The results were qualitatively similar.

*What policy factors have led to different levels of stocking across the systems? Perhaps I missed it, but this information would be helpful for the reader to understand what factors might be associated (or not) with the large "experimental" treatment.*

> Some of the watersheds (e.g. Shimonaefutoro) do not receive stocking for the purpose of regional population conservation. The rest of variation across watersheds are due largely to logistical reasons (e.g., accessibility). We have briefly mentioned this in the revised MS.

*Line 38-39. I question whether this is accurate as written. There is a single release program that releases millions of plants, fish, invertebrates, etc? Perhaps I am wrong, but when I skimmed a few of the provided references it looked like those stats were for multiple programs.*

> We are glad that the reviewer caught this! Yes, the reviewer is right - different programes release plants, insects, birds, fish etc. We have revised the text.

*Line 44-46. I think the "nine species" refers to the "12 major fishery resources". In order to align these statistics, perhaps change "fishery resources" to "fishery species".*

> Thank you, we have corrected.

*Lines 47-48. I agree with the general phrase that the community impacts of hatchery releases have been underappreciated. From a community perspective, the role of hatchery fish in influencing predators is also important. It would be worth mentioning these other potential types of community interactions. For example, if we consider people and fisheries to be interacting species, there is some work on how hatcheries can enable increased harvest rates on wild stocks. Hatchery fish also subsidize predators that could then have higher predation on shared prey (hyperpredation). This has been hypothesized to be an issue with marine mammals and hatchery Pacific salmon in western North America.*

*Fig 1d doesn't offer much meaningful. I suggest removing the example watershed map.*

> Agree. We have removed the panel.

*Line 167. Change "salmons" to "salmon".*

> Corrected.

*Figure 3. Genus should be included for all species. It would be nice to add species silhouettes to this figure.*

> Thank you, we have modified the figure as suggested.

*In places in the manuscript, I think a bit more precision is needed to acknowledge that reintroduction approaches likely have multiple motivations. For instance, I think it is quite feasible that many reintroduction programs are basically trying to create opportunities for harvest.*

\clearpage

# References

### 2022-12-24 rmd/manuscript.Rmd
edit: manuscript

@@
 The intentional release, however, can have far-reaching consequences than previously thought, as the impacts can propagate through a diversity of ecological interactions [@careyNativeInvadersChallenges2012].
-This recognition has stimulated a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019].
+This recognition has stimulated a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019; @cucheroussetAreDomesticatedFreshwater2020].
 Yet, current debates overlook the fact that we lack a quantitative assessment of the community-wide impact in the long-term.
@@
 In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S7**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective.
-The weak-competition scenario is likely in reintroduction programs that aim to replenish populations of extirpated species or long-lived endangered species.
-In fact, some of the best evidence for successful intentional release comes from reintroduction efforts for such species [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021].
+The weak-competition scenario is likely in reintroduction of extirpated species or long-lived endangered species.
+In fact, some of the best evidence for successful intentional release comes from conservation programs of such species [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021].
 In the Sado island (Japan), for example, the once-extirpated Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008 [@okahisaEvaluationOngoingCrested2022].
 Similarly, translocations of Humpback chub, a federally-listed fish species in the US, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River [@yackulicAssessingPopulationImpacts2021].
-However, the preponderance of unsuccessful reintroduction programs implies that the theoretical requirements for successful intentional release are not always met [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019].
+However, the preponderance of unsuccessful reintroduction in conservation implies that the theoretical requirements for successful intentional release are not always met [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019].
 Indeed, non-negligible numbers of projects seem to release captive-bred individuals into unsuitable habitats with compromised carrying capacities [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012].
@@
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure** 1)**E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure** 1**E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
 In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records.
-The release of masu salmon began in the 1950s, with the annual average ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019.
+The release of masu salmon began in the 1950s; the release numbers at other watersheds vary due mainly to logistical reasons, while several of the watersheds are not subject to intentional release to preserve regional populations.
+This resulted in the average annual release ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019.
 The majority of release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
-Several of the watersheds are not subject to intentional release aiming to preserve regional populations of masu salmon, while the release numbers at other watersheds vary due mainly to logistical reasons.
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
@@
 Diets of salmonid species are innately overlapped, and they interfere with each other to claim profitable foraging spots for drift insects [@hasegawaComparisonCompetitiveAbility2004] or cruise over a large area in search of prey [@hasegawaEffectFlowRegime2010].
-Exploitation competition between masu salmon and benthic fish (e.g., sculpins and stone loaches in our study system) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014] that many benthic fish species prey on [@natsumedaEvaluationEcologicalFeatures2010; @natsumedaDietFoodSelectivity2012].
+Exploitation competition between masu salmon and benthic fish (e.g., sculpins and stone loach in our study system) is also likely because subordinate masu salmon in the dominance hierarchy consumes benthic macroinvertebrates [@satoStagespecificFunctionalResponses2014] that many benthic fish species prey on [@natsumedaEvaluationEcologicalFeatures2010; @natsumedaDietFoodSelectivity2012].
 Importantly, hatchery masu salmon may intensify intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022].
@@
 
-Human activities are strictly regulated in the protected watersheds, and the near-intact environment (**Figure S10**) may have helped uncover the qualitative agreement between theory and empirical patterns.
-For example, any form of exploitation, including angling, is prohibited in these areas.
+Two unique strengths in our dataset may have helped uncover the qualitative agreement between theory and empirical patterns.
+First, human activities are strictly regulated in the protected watersheds (**Figure S10**).
+Any form of exploitation, including angling, is prohibited in these areas.
 In addition, exclusive permission from the governer of Hokkaido is required to physically alter in-stream and riparian habitats.
 Therefore, unmeasured human influences should have minimal influences on the observed relationships.
-Further, we have statistically controlled natural variation in environmental factors (see **Methods**).
-Nevertheless, our results must be viewed with caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research.
+As such, we were able to confine potential confounding factors to natural environmental variation, which were properly accounted in our statistical model (see **Methods**).
+Second, the sampling method in this monitoring program (a combination of cast net and electrofishing) is carefully chosen to capture stream fishes with different microhabitat preference (e.g., water-column vs.
+bottom).
+Thus, our data is robust to potential bias caused by sampling methods.
+Nevertheless, our results must be viewed with some caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research.
 Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018; @suzukiDecomposingPredictabilityIdentify2022] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics.
@@
 Most fish are released near the fish survey sites.
-However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable.
+However, the number of fish released was reported as an aggregate for each watershed, and the site-specific information of release is unavailable.
 For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute.
@@
 Although our focus is intentional release, each model included climatic and local abiotic variables to account for important environmental differences among sites.
-Specifically, we developed the following linear regression model taking either species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$.
+Specifically, we developed the following linear regression model taking either taxonomic richness (the number of taxa present during the observation period), mean, or SD as a response variable $y_s$.
 
@@
 Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
-The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc)` to `r max(df_mcmc$n_total_mcmc)`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period.
+The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc) %>% as.character()` to `r max(df_mcmc$n_total_mcmc) %>% as.character()`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period.
 Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached $<1.1$ [@gelmanDataAnalysisUsing2007].

### 2022-12-24 rmd/manuscript.Rmd
edit: manuscript

@@
 
-The intentional release, however, can have far-reaching consequences than previously thought, as the impacts can propagate through a diversity of ecological interactions [@careyNativeInvadersChallenges2012].
-This recognition has stimulated a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019; @cucheroussetAreDomesticatedFreshwater2020].
-Yet, current debates overlook the fact that we lack a quantitative assessment of the community-wide impact in the long-term.
+The intentional release, however, can have wide-ranging consequences than previously thought, as the impacts can propagate through a diversity of ecological interactions [@careyNativeInvadersChallenges2012].
+This recognition has sparked a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019; @cucheroussetAreDomesticatedFreshwater2020].
+Yet, current debates overlook the fact that we rarely assessed the community-wide impact in the long-term.
 Ecological theory suggests that the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].

### 2022-12-24 rmd/manuscript.Rmd
edit: add terra

@@
 We extracted annual data of chlorophyll *a* concentration (2002 -- 2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
-We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*
+We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018], *terra* [@hijmansTerraSpatialData2022], *exactextractr* [@bastonExactextractrFastExtraction2020], *stars* [@pebesmaStarsSpatiotemporalArrays2020], *whitebox* [@lindsayWhiteboxGATCase2016]*.*
 

### 2022-12-24 rmd/manuscript.Rmd
edit: ms minor

@@
 Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged.
-The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc) %>% as.character()` to `r max(df_mcmc$n_total_mcmc) %>% as.character()`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period.
+The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc) %>% op(0)` to `r max(df_mcmc$n_total_mcmc) %>% op(0)`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period.
 Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached $<1.1$ [@gelmanDataAnalysisUsing2007].

### 2022-12-24 code/si_figure_cor.R
Update si_figure_cor.R

@@ -14,15 +14,17 @@ source(here::here("code/data_fmt_reg.R"))
 M <- df_env %>%
   left_join(df_stock_mu, by = "river") %>% 
   left_join(df_ocean, by = "river") %>% 
+  left_join(df_n_obs, by = "river") %>% 
   dplyr::select('Forest fraction' = frac_forest,
                 'Agriculture fraction' = frac_agri,
                 'Urban fraction' = frac_urban,
                 'Temperature' = temp,
                 'Precipitation' = ppt,
                 'Watershed area' = wsd_area,
+                'Number of observation years' = n_obs,
                 'Number of fish released' = mean_stock,
                 'Chlorophyll a' = chr_a,
-                'SD Elevation' = sd_elev) %>% 
+                'SD elevation' = sd_elev) %>% 
   cor(method = "spearman")
 
 corrplot(M,

### 2022-12-24 rmd/figure_caption.Rmd
Update figure_caption.Rmd

@@
 
+```{r setup, include=FALSE}
+
+suppressMessages(source(here::here("code/set_functions.R")))
+suppressMessages(source(here::here("code/set_rmd.R")))
+
+```
+
 **Figure 1** Theory and empirical observations agree that intentional release destabilizes community dynamics.
@@
 Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and prediction intervals (light shade).
-Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ `r round(na.omit(unique(df_sim$r1)), 2)` average interspecific competition $\bar{\alpha}=$ `r round(na.omit(unique(df_sim$alpha)), 2)`, carrying capacity $K=$ `round(na.omit(unique(df_sim$k)), 2)`, environmental stochasticity $\sigma_{\varepsilon}=$ `r round(na.omit(unique(df_sim$sd_env)), 2)`, relative fitness of captive-bred individuals $f_R=$ `r round(na.omit(unique(df_sim$phi)), 2)`.
+Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ `r round(na.omit(unique(df_sim$r1)), 2)` average interspecific competition $\bar{\alpha}=$ `r round(na.omit(unique(df_sim$alpha)), 2)`, carrying capacity $K=$ `r round(na.omit(unique(df_sim$k)), 2)`, environmental stochasticity $\sigma_{\varepsilon}=$ `r round(na.omit(unique(df_sim$sd_env)), 2)`, relative fitness of captive-bred individuals $f_R=$ `r round(na.omit(unique(df_sim$phi)), 2)`.
 These parameter values are comparable to those estimated in the empirical Ricker model.
@@
 Lines and shades are the predicted values and their 95% credible intervals of the regression models, and line types correspond to the coefficient's posterior probabilities.
-Effective release is a latent explanatory variable estimated in our hierarchical Baysian model.
+Effective release is a latent explanatory variable estimated in our hierarchical Bayesian model.
 See Methods for details.
@@
 (C) Map of sampling sites (black dots) in Hokkaido, Japan.
-(E) Masu salmon *Oncorhynchus masou*.
+(D) Masu salmon *Oncorhynchus masou masou*.
 Photo credit: Akira Terui

### 2022-12-24 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 
-When small carrying capacity was combined with a low to modest intrinsic growth rate ($K=$ `r min(list_param[[2]]$k)`, $r_1 \le 2.5$), our model predicted a destabilizing effect of intentional release on ecological communities, as illustrated by increased CV with increasing numbers of releases (**Figure** 1**A**).
-This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** 1**A**).
+When small carrying capacity was combined with a low to modest intrinsic growth rate ($K=$ `r min(list_param[[2]]$k)`, $r_1 \le 2.5$), our model predicted a destabilizing effect of intentional release on ecological communities, as illustrated by increased CV with increasing numbers of releases (**Figure 1A**).
+This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**).
 The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012].
-Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** 1**A**).
-Combined, the total community density decreased more sharply than individual species groups (**Figure** 1**A**).
-The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** 1**A**).
+Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure 1A**).
+Combined, the total community density decreased more sharply than individual species groups (**Figure 1A**).
+The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure 1A**).
 Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV.
@@
 
-To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure** 1**E**) on the long-term stability of stream fish communities in Hokkaido, Japan.
-In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records.
+To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure 1D**) on the long-term stability of stream fish communities in Hokkaido, Japan.
+In the protected watersheds (all separated by the ocean; **Figure 1C**), a long-term program exists to monitor stream fish communities along with the official release records.
 The release of masu salmon began in the 1950s; the release numbers at other watersheds vary due mainly to logistical reasons, while several of the watersheds are not subject to intentional release to preserve regional populations.
@@
 
-As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** 1**B**).
+As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure 1B**).
 The effect was striking in its magnitude, almost doubling the CV at the highest release level.
-Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** 2; see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob) %>% round(2), 2)` (**Table S6**).
-This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** 1**B and** 2), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** 1**B and** 2**;** see **Tables S6 -- S8** for full statistics).
-In the meantime, the SDs had vague relationships with the intentional release (**Figures** 1**B and** 2).
+Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure 2**; see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob) %>% round(2), 2)` (**Table S6**).
+This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6 -- S8** for full statistics).
+In the meantime, the SDs had vague relationships with the intentional release (**Figures 1B and 2**).
 
@@
 The parameter estimates of this model are directly comparable to those used in the theoretical Ricker model.
-The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure** 3), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
+The estimates of interspecific competition coefficients $\alpha_{ij}$ ranged `r op(min(df_pd$alpha_prime), 2)` -- `r op(max(df_pd$alpha_prime), 2)` with the median of `r op(median(df_pd$alpha_prime), 2)` (**Figure 3**), suggesting that competition is a likely mechanism as our theory assumes (see **Figure S17** for all pairwise estimates).
 Our statistical inference is supported by previous studies.

### 2022-12-24 rmd/manuscript.Rmd
edit: minor

@@
 In the protected watersheds (all separated by the ocean; **Figure 1C**), a long-term program exists to monitor stream fish communities along with the official release records.
-The release of masu salmon began in the 1950s; the release numbers at other watersheds vary due mainly to logistical reasons, while several of the watersheds are not subject to intentional release to preserve regional populations.
+The release of masu salmon began in the 1950s; the release numbers vary due mainly to logistical reasons, while several of the watersheds are not subject to intentional release to preserve regional populations.
 This resulted in the average annual release ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019.

### 2022-12-24 rmd/supporting_info.Rmd
edit: minor

@@
 ---
+title: |
+  ![](images/logo.png){width=4in}  
 output:
@@
 
-In the monitoring program, a two-pass sampling method was employed at all sampling sites.
+The monitoring program employed a two-pass sampling method at all sampling sites.
 In each pass, a combination of electrofishing and cast net (two-pass) was used to effectively catch both benthic and water-column species in a given area.

### 2022-12-24 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 This recognition has sparked a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019; @cucheroussetAreDomesticatedFreshwater2020].
-Yet, current debates overlook the fact that we rarely assessed the community-wide impact in the long-term.
+Yet, current debates overlook the fact that we have rarely assessed the community-wide impact in the long-term.
 Ecological theory suggests that the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004].
@@
 bottom).
-Thus, our data is robust to potential bias caused by sampling methods.
+Thus, our data is robust to potential sampling bias.
 Nevertheless, our results must be viewed with some caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research.

### 2022-12-24 code/table_reg.R
Update table_reg.R

@@ -30,7 +30,7 @@ list_reg <- lapply(group, FUN = function(x) {
                                 id1 == 6 & param_name == "a" ~ "Forest fraction",
                                 id1 == 7 & param_name == "a" ~ "Number of observations",
                                 id1 == 1 & param_name == "b" ~ "Ocean productivity",
-                                id1 == 2 & param_name == "b" ~ "SD Elevation"),
+                                id1 == 2 & param_name == "b" ~ "SD elevation"),
            response = case_when(response == "species_richness" ~ "Species richness",
                                 response == "cv" ~ "CV",
                                 response == "mu" ~ "Mean $\\mu$",

### 2022-12-24 rmd/reply_r2.Rmd
Update reply_r2.Rmd

@@
 
-This is a re-submission of a manuscript: "2022­05603 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript.
-The comments were very helpful in improving our manuscript.
-When revising the manuscript, we have put a particular emphasis on the following points:
-
-In summary, the improved text/analysis provides clearer evidence that intentional release has destabilizing effects and clarifies its broader relevance to other systems.
-We appended a point-by-point response below.
-We hope our manuscript is now suitable for publication in your journal.
+This is a revision of a manuscript: "2022­18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript.
+We have refined our analysis and text in light of comments from the reviewer 3.
+We hope the manuscript is suitable for publication in PNAS.
 
@@
 
-\clearpage
-
 ## Point-by-point response
@@
 ### Editor
+
+*This revision does a superb job addressing previous concerns that were raised in the review process.
+These improvements along with the significant content of this research have resulted in an excellent contribution.*
+
+> Thank you!
+
+*Before publication, however, the authors need to clarify the text commented on by reviewer #3 (lines 38-39, 44-46, 47-48, 167, and include the Genus for all species.*
+
+> Thank you for your careful reading. We have addressed these concerns. Please see our response to reviewer 3.
+
+*I also recommend a bit more discussion relating to sampling method and its implications for estimated variability (the point raised by reviewer #3).*
+
+> We appreciate your recommendation. We believe our unclear writing has caused a confusion -- please let us clarify.
+>
+> First, the sampling method in the protected watersheds are consistent across all sites and years, so there is no need to include the sampling method as a control factor in the statistical model (clarified in Methods).
+Further, the sampling method (a combination of cast net and electrofishing) was carefully chosen to catch both water-column and benthic fish species effectively (clarified and mentioned in Discussion; L.
+227 --).
+Therefore, we believe our data are robust to sampling bias.
+>
+> Second, we appreciate reviewer's comment on irregular sampling interval.
+In the revised analysis, we have included the number of observation years as an additional covariate to address reviewer's concern.
+The results were qualitatively similar.
+Please see also our response to reviewer 3.
+>
+> Overall, we confirmed that our results were robust to concerns raised by reviewer 3.
 
@@
 At all sites, a combination of electrofishing and cast net was used to capture both benthic and water-column species effectively.
-We have clarified this in the revised MS (L XXX).
-In addition, we have added some text to clarify that the sampling has constant sampling effort per unit area.
+We have clarified this in the revised MS (L 333 --).
+In addition, we have added some text to clarify that the sampling has constant sampling effort per unit area (see **Supplementary text**).
 Therefore, our analysis is robust to this issue.
@@
 This approach is suitable because it keeps the sample size as original while accounting for potential influences of observation intervals.
-The results were qualitatively similar.
+The results were qualitatively similar, confirming the robustness of our results.
 
@@
 When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below).
-Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for outliers in both response (log CV) and predictor variables (effective release).
+Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release).
 We hope this ameliorates reviewer's concern.
@@
 
-> XXX
+> Thank you for this comment.
+We agree with this opinion.
+However, we believe our analysis has already accounted for this aspect.
+The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$).
+Therefore, the point raised by the reviewer is already accounted in our model, albeit implicitly.
+Also, we wanted to remind the reviewer that our results indicated that the community SD was not influenced by intentional release.
+Although we cannot exclude the possible importance of relative community composition, our data suggest that it has a minimal influence on the dynamics (at least in our system).
 
@@
 
-> We appreciate this suggestion! We included SD Elevation as an additional covariate in the regression model. The results were qualitatively similar.
+> We appreciate this suggestion -- We included "SD elevation" as an additional covariate in the regression model. The results were qualitatively similar.
 
@@
 The rest of variation across watersheds are due largely to logistical reasons (e.g., accessibility).
-We have briefly mentioned this in the revised MS.
+We have briefly mentioned this in the revised MS (L.
+158 --).
 
@@
 
+> Thank you for the important suggestion.
+We agree that different types of interactions may be important to understand ecosystem-wide impacts of intentional release.
+We have clarified this point in the revised manuscript.
+In the meantime, we believe our research is unique and significant in that we have quantified "long-term" impact at the community level.
+As the reviewer suggested, there are some discussion on the community-level impact of intentional release (very few though).
+However, none of them evaluated the long-term impact.
+We have improved the description about the knowledge gap addressed in this study (L51 --)
+
 *Fig 1d doesn't offer much meaningful. I suggest removing the example watershed map.*
@@
 
-\clearpage
-
-# References
+> We understood that the reviewer commented on the last paragraph of "theoretical prediction." We have clarified that we are linking our results to reintroduction programs in conservation (paragraph starting at L135).

### 2022-12-24 rmd/manuscript.Rmd
edit: grammar

@@
 
-The intentional release, however, can have wide-ranging consequences than previously thought, as the impacts can propagate through a diversity of ecological interactions [@careyNativeInvadersChallenges2012].
+The intentional release, however, can have wider-ranging consequences than previously thought, as the impacts can propagate through a diversity of ecological interactions [@careyNativeInvadersChallenges2012].
 This recognition has sparked a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019; @cucheroussetAreDomesticatedFreshwater2020].
@@
 In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S7**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective.
-The weak-competition scenario is likely in reintroduction of extirpated species or long-lived endangered species.
+The weak-competition scenario is likely in the reintroduction of extirpated species or long-lived endangered species.
 In fact, some of the best evidence for successful intentional release comes from conservation programs of such species [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021].
@@
 This resulted in the average annual release ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019.
-The majority of release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
+Most release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset).
 Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions.
@@
 Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014].
-It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoost2022], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007].
+It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoost2022], and such genetic effects may accumulate during successive generations in captivity [@arakiGeneticEffectsCaptive2007].
 Typically, masu salmon are reared in captivity for two to four generations.
@@
 For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017].
-Similarly, the large-scale release of Black sea bream has been conducted in Kagoshima Bay (Japan) since 1974 (the yearly-average of 0.64 million juveniles) with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019].
+Similarly, the large-scale release of Black sea bream has been conducted in Kagoshima Bay (Japan) since 1974 (a yearly average of 0.64 million juveniles) with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019].
 Although we do not know the carrying capacities of the recipient systems, it is clear that our results should not be viewed as an exceptional case.
@@
 Any form of exploitation, including angling, is prohibited in these areas.
-In addition, exclusive permission from the governer of Hokkaido is required to physically alter in-stream and riparian habitats.
+In addition, exclusive permission from the governor of Hokkaido is required to physically alter in-stream and riparian habitats.
 Therefore, unmeasured human influences should have minimal influences on the observed relationships.
-As such, we were able to confine potential confounding factors to natural environmental variation, which were properly accounted in our statistical model (see **Methods**).
-Second, the sampling method in this monitoring program (a combination of cast net and electrofishing) is carefully chosen to capture stream fishes with different microhabitat preference (e.g., water-column vs.
+As such, we were able to confine potential confounding factors to natural environmental variation, which were properly accounted for in our statistical model (see **Methods**).
+Second, the sampling method in this monitoring program (a combination of cast net and electrofishing) is carefully chosen to capture stream fishes with different microhabitat preferences (e.g., water-column vs.
 bottom).
@@
 In rural Spain, two million individuals of reared red-legged partridge, the most important game bird in this area, are introduced into the wild every year to overcome the regional decline of this species [@negroRAPDAnalysisDetection2001].
-In the US, a nation-wide initiative exists to augment populations of freshwater mussels, which are rapidly disappearing over the past decades for enigmatic reasons [@haagNorthAmericanFreshwater2012].
+In the US, a nationwide initiative exists to augment populations of freshwater mussels, which have been rapidly disappearing over the past decades for enigmatic reasons [@haagNorthAmericanFreshwater2012].
 The exact causes behind such population declines are often unknown or controversial, yet it is reasonable to assume that those habitats are no longer suitable and can support limited numbers of individuals (i.e., low carrying capacity).
@@
 
-While socioeconomic analysis is required to provide detailed guidance on release programs, it is clear that habitat conservation should be prioritized for the sustainability of the natural resources.
+While socioeconomic analysis is required to provide detailed guidance on release programs, it is clear that habitat conservation should be prioritized for the sustainability of natural resources.
 Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is integral to achieving successful conservation.
@@
 We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`).
-We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs.
+We also varied the relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs.
 Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`).
@@
 In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community.
-In addition, we defined a threshold density ($N_i = 0.01$) below which species are removed from the simulation (i.e., an absorbing condition) and are recorded as "extinct".
-The rest of the simulation procedure is identical to the two-species model.
-We summarized values of simulation parameters in **Table S**1.
+In addition, we defined a threshold density ($N_i = 0.01$) below which species are removed from the simulation (i.e., an absorbing condition) and are recorded as "extinct." The rest of the simulation procedure is identical to the two-species model.
+We summarized the values of simulation parameters in **Table S**1.
 
@@
 We extracted annual data of chlorophyll *a* concentration (2002 -- 2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth.
-We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018], *terra* [@hijmansTerraSpatialData2022], *exactextractr* [@bastonExactextractrFastExtraction2020], *stars* [@pebesmaStarsSpatiotemporalArrays2020], *whitebox* [@lindsayWhiteboxGATCase2016]*.*
+We used the following R packages to perform the geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018], *terra* [@hijmansTerraSpatialData2022], *exactextractr* [@bastonExactextractrFastExtraction2020], *stars* [@pebesmaStarsSpatiotemporalArrays2020], *whitebox* [@lindsayWhiteboxGATCase2016]*.*
 
@@
 
-$\gamma'_{0}$ is the global intercept and $\gamma'_k$ is the regression coefficients of ocean productivity $\gamma'_{1,w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019) and standard deviation of elevation (SD elevation) within an entire watershed $\gamma'_{2,w}$.
+$\gamma'_{0}$ is the global intercept, and $\gamma'_k$ is the regression coefficients of ocean productivity $\gamma'_{1,w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019) and standard deviation of elevation (SD elevation) within an entire watershed $\gamma'_{2,w}$.
 Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous).

### 2022-12-24 rmd/reply_r2.Rmd
edit: grammar

@@
 This is a revision of a manuscript: "2022­18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript.
-We have refined our analysis and text in light of comments from the reviewer 3.
+We have refined our analysis and text in light of comments from reviewer 3.
 We hope the manuscript is suitable for publication in PNAS.
@@
 
-> We appreciate your recommendation. We believe our unclear writing has caused a confusion -- please let us clarify.
+> We appreciate your recommendation. Our unclear writing has caused confusion -- please let us clarify.
 >
-> First, the sampling method in the protected watersheds are consistent across all sites and years, so there is no need to include the sampling method as a control factor in the statistical model (clarified in Methods).
+> First, the sampling method in the protected watersheds is consistent across all sites and years, so there is no need to include the sampling method as a controlling factor in the statistical model (clarified in Methods).
 Further, the sampling method (a combination of cast net and electrofishing) was carefully chosen to catch both water-column and benthic fish species effectively (clarified and mentioned in Discussion; L.
 227 --).
-Therefore, we believe our data are robust to sampling bias.
+Therefore, our data are robust to sampling bias.
 >
-> Second, we appreciate reviewer's comment on irregular sampling interval.
-In the revised analysis, we have included the number of observation years as an additional covariate to address reviewer's concern.
+> Second, we appreciate the reviewer's comment on irregular sampling intervals.
+In the revised analysis, we have included the number of observation years as an additional covariate to address the reviewer's concern.
 The results were qualitatively similar.
@@
 We have clarified this in the revised MS (L 333 --).
-In addition, we have added some text to clarify that the sampling has constant sampling effort per unit area (see **Supplementary text**).
+In addition, we have added some text to explain that the sampling has constant sampling effort per unit area (see **Supplementary text**).
 Therefore, our analysis is robust to this issue.
@@
 However, it introduces the issue of sample size.
-To address reviewer's concern more appropriately, we included "the number of observation years" as a covariate in the regression model.
+To address the reviewer's concern more appropriately, we included "the number of observation years" as a covariate in the regression model.
 This approach is suitable because it keeps the sample size as original while accounting for potential influences of observation intervals.
@@
 > Thank you for your careful reading.
-However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from analysis.
-Although the figure was shown in an ordinary scale, the analysis was carried out in a log-scale (see Methods).
+However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from the analysis.
+Although the figure was shown on an ordinary scale, the analysis was carried out on a log-scale (see Methods).
 When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below).
 Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release).
-We hope this ameliorates reviewer's concern.
+We hope this ameliorates the reviewer's concern.
 
@@
 The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$).
-Therefore, the point raised by the reviewer is already accounted in our model, albeit implicitly.
+Therefore, the point raised by the reviewer is already accounted for in our model, albeit implicitly.
 Also, we wanted to remind the reviewer that our results indicated that the community SD was not influenced by intentional release.
@@
 Shimonaefutoro) do not receive stocking for the purpose of regional population conservation.
-The rest of variation across watersheds are due largely to logistical reasons (e.g., accessibility).
+The rest of the variation across watersheds is due largely to logistical reasons (e.g., accessibility).
 We have briefly mentioned this in the revised MS (L.
@@
 
-> We are glad that the reviewer caught this! Yes, the reviewer is right - different programes release plants, insects, birds, fish etc. We have revised the text.
+> We are glad that the reviewer caught this! Yes, the reviewer is right - different programs release plants, insects, birds, fish etc. We have revised the text.
 
@@
 > Thank you for the important suggestion.
-We agree that different types of interactions may be important to understand ecosystem-wide impacts of intentional release.
+We agree that different types of interactions may be important to understand the ecosystem-wide impacts of intentional release.
 We have clarified this point in the revised manuscript.
 In the meantime, we believe our research is unique and significant in that we have quantified "long-term" impact at the community level.
-As the reviewer suggested, there are some discussion on the community-level impact of intentional release (very few though).
+As the reviewer suggested, there is some discussion about the community-level effects of intentional release (very few, though).
 However, none of them evaluated the long-term impact.
-We have improved the description about the knowledge gap addressed in this study (L51 --)
+We have improved the description of the knowledge gap addressed in this study (L51 --)
 

### 2022-12-24 rmd/reply_r2.Rmd
edit: minor

@@
 ---
-title: "Reply to: 2022-05603 Intentional release of native species undermines ecological stability"
+title: "Reply to: 2022-18044 Intentional release of native species undermines ecological stability"
 output:
@@
 
-This is a revision of a manuscript: "2022­18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript.
+This is a revision of a manuscript: "2022-18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript.
 We have refined our analysis and text in light of comments from reviewer 3.

### 2022-12-25 rmd/reply_r2.Rmd
Update reply_r2.Rmd

@@
 > Thank you for your careful reading.
-However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from the analysis.
-Although the figure was shown on an ordinary scale, the analysis was carried out on a log-scale (see Methods).
+Give this comment, we checked whether this point strongly affects the overall pattern.
 When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below).
-Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release).
-We hope this ameliorates the reviewer's concern.
+Please note that, although the figure was shown on an ordinary scale, the analysis was carried out on a log-scale (see Methods).
+>
+> Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release).
+>
+> We hope this ameliorates the reviewer's concern.
 
@@
 > Thank you for this comment.
-We agree with this opinion.
-However, we believe our analysis has already accounted for this aspect.
+We agree with this opinion; therefore, our analysis was designed to account for this aspect.
 The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$).
-Therefore, the point raised by the reviewer is already accounted for in our model, albeit implicitly.
-Also, we wanted to remind the reviewer that our results indicated that the community SD was not influenced by intentional release.
-Although we cannot exclude the possible importance of relative community composition, our data suggest that it has a minimal influence on the dynamics (at least in our system).
+As such, the point raised by the reviewer is already accounted for in our model, albeit implicitly.
+>
+> Also, we wanted to remind the reviewer that the relative community composition & species richness are the pathways through which intentional release affects community stability (see Theoretical predictions).
+**Intentional release changes relative abundance of unenhanced species, as our theory suggests.** Therefore, although our regression model does not include the effects of relative community composition explicitly, it is the part of the effect of intentional release.
+Due to the tight correlation between intentional release and community composition/richness, including both factors into a single model will create an issue of multicollinearity.
+>
+> In summary, we have already accounted for the point raised by the reviewer. We appreciate the input though!
 

### 2022-12-25 rmd/supporting_info.Rmd
edit: add header to SI

@@
 ---
-title: |
-  ![](images/logo.png){width=4in}  
 output:
@@
 header-includes:
+  - \usepackage{amsmath, fancyhdr, caption, booktabs}
+  - \pagestyle{fancy}
+  - \renewcommand{\headrulewidth}{0pt}
+  - \fancyhead[L]{\includegraphics[width=5cm]{images/logo.png}}
+  - \fancyhead[C]{}
   - \pagenumbering{gobble}
-  - \usepackage{amsmath, fancyhdr, caption, booktabs}
   - \setlength{\headheight}{13.6pt}
@@
 The monitoring program employed a two-pass sampling method at all sampling sites.
-In each pass, a combination of electrofishing and cast net (two-pass) was used to effectively catch both benthic and water-column species in a given area.
+In each pass, a combination of electrofishing and cast net was used to effectively catch both benthic and water-column species in a given area.
 The number of cast-net throws was determined as the sampled area divided by $4.5~\text{m}^2$ (the area covered by a cast net).

### 2022-12-25 rmd/manuscript.Rmd
edit: minor
edit: maintext

@@
 bottom).
-Thus, our data is robust to potential sampling bias.
+Thus, our data are robust to potential sampling bias.
 Nevertheless, our results must be viewed with some caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research.
@@
 In rural Spain, two million individuals of reared red-legged partridge, the most important game bird in this area, are introduced into the wild every year to overcome the regional decline of this species [@negroRAPDAnalysisDetection2001].
-In the US, a nationwide initiative exists to augment populations of freshwater mussels, which have been rapidly disappearing over the past decades for enigmatic reasons [@haagNorthAmericanFreshwater2012].
+In the US, a nationwide initiative exists to augment populations of freshwater mussels, which have rapidly disappeared over the past decades for enigmatic reasons [@haagNorthAmericanFreshwater2012].
 The exact causes behind such population declines are often unknown or controversial, yet it is reasonable to assume that those habitats are no longer suitable and can support limited numbers of individuals (i.e., low carrying capacity).

### 2022-12-25 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@
 \fancyhead[C]{}
+\renewcommand{\headrulewidth}{0.5pt}
 \pagenumbering{arabic}
@@
 ```{r fig-env, fig.width=11, fig.height=8, fig.cap="Distribution of environmental variables in the protected watershed.
-Note that the number of fish released and ocean productivity (chlorophyll a) are measured at the watershed level while others are measured at the site level."}
+Note that the number of fish released, ocean productivity (chlorophyll a), and SD elevation are measured at the watershed level while others are measured at the site level."}
 

### 2022-12-26 rmd/reply_r2.Rmd
edit: minor change

@@
 > Thank you for your careful reading.
-Give this comment, we checked whether this point strongly affects the overall pattern.
+Given this comment, we checked whether this data point strongly affects the overall pattern.
 When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below).
@@
 
-```{r outlier, echo = TRUE}
+```{r, include = FALSE}
 
@@
              by = "site_id_numeric")
+```
+
+```{r outlier, echo = TRUE}
 
@@
 > Also, we wanted to remind the reviewer that the relative community composition & species richness are the pathways through which intentional release affects community stability (see Theoretical predictions).
-**Intentional release changes relative abundance of unenhanced species, as our theory suggests.** Therefore, although our regression model does not include the effects of relative community composition explicitly, it is the part of the effect of intentional release.
-Due to the tight correlation between intentional release and community composition/richness, including both factors into a single model will create an issue of multicollinearity.
+Our theory predicts that **intentional release changes relative abundance of unenhanced species.** Therefore, although our regression model does not include the effects of relative community composition explicitly, it is the part of the effect of intentional release.
 >

### 2022-12-26 rmd/supporting_info.Rmd
edit: minor change

@@
 
-```{r fig-env, fig.width=11, fig.height=8, fig.cap="Distribution of environmental variables in the protected watershed.
+```{r fig-env, fig.width=11, fig.height=8, fig.cap="Distribution of environmental variables in protected watersheds.
 Note that the number of fish released, ocean productivity (chlorophyll a), and SD elevation are measured at the watershed level while others are measured at the site level."}
@@
 
-```{r fig-cor, fig.width=11, fig.height=11, fig.cap="Correlation plot among environmental variables in the protected watersheds. Numbers indicate Spearman's rank correlations."}
+```{r fig-cor, fig.width=11, fig.height=11, fig.cap="Correlation plot among environmental variables in  protected watersheds. Numbers indicate Spearman's rank correlations."}
 

### 2022-12-26 code/figure_species_int.R

@@ -84,17 +84,18 @@ g_alpha <- df_plot %>%
                         levels = taxon_ordered)) %>% 
   ggplot(aes(y = lbs.y,
              x = value)) +
+  geom_vline(aes(xintercept = median(value)),
+             col = grey(0.8),
+             size = 0.5,
+             linetype = "dashed") +
+  geom_jitter(height = 0.1,
+              width = 0,
+              size = 1,
+              color = grey(0.5)) +
   geom_boxplot(aes(fill = lbs.y),
                color = grey(0.4),
                alpha = 0.75,
                outlier.colour = NA) +
-  geom_jitter(height = 0.1,
-              width = 0,
-              size = 1,
-              color = grey(0.2)) +
-  geom_vline(aes(xintercept = median(value)),
-             col = grey(0.5),
-             linetype = "dashed") +
   geom_xsidedensity(aes(fill = lbs.y),
                     color = NA,
                     alpha = 0.8,
@@ -122,17 +123,16 @@ fish <- list.files(here::here("data_raw/image"),
 yp <- seq(0.34, length = 10, by = -0.075)
 xp <- -0.18
 
-g_alpha_img <- ggdraw() +
-  draw_image(fish[1], x = xp, y = yp[1], scale = 0.06) +
-  draw_image(fish[2], x = xp, y = yp[2], scale = 0.06) +
-  draw_image(fish[3], x = xp, y = yp[3], scale = 0.06) +
-  draw_image(fish[4], x = xp, y = yp[4], scale = 0.06) +
-  draw_image(fish[5], x = xp, y = yp[5], scale = 0.06) +
-  draw_image(fish[6], x = xp, y = yp[6], scale = 0.06) +
-  draw_image(fish[7], x = xp, y = yp[7], scale = 0.06) +
-  draw_image(fish[8], x = xp, y = yp[8], scale = 0.06) +
-  draw_image(fish[9], x = xp, y = yp[9], scale = 0.06) +
-  draw_image(fish[10], x = xp, y = yp[10], scale = 0.06) +
+g_alpha_img <- ggdraw()
+
+for(i in 1:length(fish)) {
+  
+  g_alpha_img <- g_alpha_img +
+    draw_image(fish[i], x = xp, y = yp[i], scale = 0.06)
+    
+}
+
+g_alpha_img <- g_alpha_img +
   draw_plot(g_alpha)
 
 

### 2022-12-26 rmd/reply_r2.Rmd
Update reply_r2.Rmd

@@
 
-This is a revision of a manuscript: "2022-18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript.
+This is a revision of "2022-18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript.
 We have refined our analysis and text in light of comments from reviewer 3.
@@
 
-> Thank you for this comment.
-We agree with this opinion; therefore, our analysis was designed to account for this aspect.
-The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$).
-As such, the point raised by the reviewer is already accounted for in our model, albeit implicitly.
+> Thank you for this comment. We agree with this opinion; the main response variable in our analysis (CV of summed density across species) can be expressed as:
 >
-> Also, we wanted to remind the reviewer that the relative community composition & species richness are the pathways through which intentional release affects community stability (see Theoretical predictions).
-Our theory predicts that **intentional release changes relative abundance of unenhanced species.** Therefore, although our regression model does not include the effects of relative community composition explicitly, it is the part of the effect of intentional release.
+> $$
+> CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}
+> $$
+>
+> where $\mu_i$ and $\sigma_i$ are the mean and SD for species $i$.
+As such, the point raised by the reviewer is relevant for our analysis; fortunately, we have naturally accounted for it, as explained below.
+>
+> Our theory predicts that intentional release changes relative abundance of unenhanced species (and some species are competitively excluded as part of this process).
+The relative community composition & species richness are therefore the pathways through which intentional release affects community stability (see Theoretical predictions).
+Consequently, the effect of community composition is naturally integrated into the effect of intentional release, statistically speaking.
+>
+> Please note that, in our causal scenario, the inclusion of community composition in our regression model causes a problem called "over-control bias." (see @arifPredictiveModelsAren2022) The pathway through which intentional release affects community stability is, "intentional release (variable X1)" $\rightarrow$ "community composition (X2)" $\rightarrow$ "community stability (Y)." Statistical theory suggests that including both X1 and X2 to explain Y improperly underestimates (or overlooks) the effect of X1 on Y.
+Therefore, our model structure is appropriate from the perspective of statistical causal inference.
 >
@@
 > We understood that the reviewer commented on the last paragraph of "theoretical prediction." We have clarified that we are linking our results to reintroduction programs in conservation (paragraph starting at L135).
+
+# References

### 2022-12-26 rmd/reply_r2.Rmd
Update reply_r2.Rmd

@@
 >
-> Please note that, in our causal scenario, the inclusion of community composition in our regression model causes a problem called "over-control bias." (see @arifPredictiveModelsAren2022) The pathway through which intentional release affects community stability is, "intentional release (variable X1)" $\rightarrow$ "community composition (X2)" $\rightarrow$ "community stability (Y)." Statistical theory suggests that including both X1 and X2 to explain Y improperly underestimates (or overlooks) the effect of X1 on Y.
+> Please note that, in our causal scenario, the inclusion of community composition in our regression model causes a problem called "over-control bias." (see @arifPredictiveModelsAren2022).
+The pathway through which intentional release affects community stability is, "intentional release (variable X1)" $\rightarrow$ "community composition (X2)" $\rightarrow$ "community stability (Y)." Statistical theory suggests that including both X1 and X2 to explain Y improperly underestimates (or overlooks) the effect of X1 on Y.
 Therefore, our model structure is appropriate from the perspective of statistical causal inference.

### 2022-12-26 rmd/reply_r2.Rmd
Update reply_r2.Rmd

@@
 >
-> Please note that, in our causal scenario, the inclusion of community composition in our regression model causes a problem called "over-control bias." (see @arifPredictiveModelsAren2022).
-The pathway through which intentional release affects community stability is, "intentional release (variable X1)" $\rightarrow$ "community composition (X2)" $\rightarrow$ "community stability (Y)." Statistical theory suggests that including both X1 and X2 to explain Y improperly underestimates (or overlooks) the effect of X1 on Y.
+> Please note that, in our causal scenario, the inclusion of community composition in our regression model causes a problem called "over-control bias" (see [@arifPredictiveModelsAren2022] for details).
+The pathway through which intentional release affects community stability is, "intentional release (variable X1)" $\rightarrow$ "community composition (X2)" $\rightarrow$ "community stability (Y)." In this case, statistical theory suggests that including both X1 and X2 to explain Y improperly underestimates (or overlooks) the effect of X1 on Y [@arifPredictiveModelsAren2022].
 Therefore, our model structure is appropriate from the perspective of statistical causal inference.

### 2022-12-26 rmd/README.Rmd
readme

@@
 
+## Analysis flow
+
+### Theory
+
+**Two-species simulation** -- simulation with `cdyns::cdynsim()` (see R package https://github.com/aterui/cdyns).
+Run `run_simulation_analytical.R`.
+Simulation results are saved in `output/result_ricker_2sp.rds`.
+
+**Whole community simulation** -- simulation with `cdyns::cdynsim()` (see R package https://github.com/aterui/cdyns).
+Run `run_simulation.R`.
+Simulation results are saved in `output/result_ricker.rds`.
+
+### Empirical
+
+**State-space AR model** -- run `run_jags_model_ssm_ar.R`. Data sourced from `data_fmt_XXX.R` files. Model code is `model_ssm_ar.R`
+
+**Regression** -- run `run_jags_model_reg.R`. Data sourced from `data_fmt_XXX.R` files. Model code is `model_reg.R`
+
+**State-space Ricker model** -- run `run_jags_model_multi_ricker_sparse.R`. Data sourced from `data_fmt_XXX.R` files. Model code is `model_multi_ricker_sparse.R`
+
 ## Contents

### 2022-12-26 code/set_readme.R

@@ -24,7 +24,7 @@ tbl_readme <- tibble(name = list.files(here::here("code")),
   ) %>%
   relocate(dir, class) %>% 
   arrange(dir, class, name) %>% 
-  mutate(description = case_when(str_detect(class, "analysis") ~ "correlation for sensitivity analysis of theoretical model",
+  mutate(description = case_when(str_detect(class, "analysis") ~ "confirm Bayesian results with `glmmTMB()`",
                                  str_detect(class, "figure") & str_detect(name, "^figure_obs") ~ "figure codes for map (`_map`), coefficients (`_coef`), or stock effect (`_stock`)",
                                  str_detect(class, "figure") & str_detect(name, "theory") ~ "theoretical predictions for stocking & community dynamics in species-rich (no postfix) or 2-species scenarios (`_2sp`)",
                                  str_detect(class, "figure") & str_detect(name, "si_") ~ paste("supporting figure codes for correlations in environmental variables (`_cor`), histograms for environmental data (`_env`), observed community dynamics (`_obs_dyns`), pairwise species interactions (`_species_int`), and scenario simulations in a species-rich community (`_theory`)"),

### 2022-12-27 rmd/reply_r2.Rmd
Update reply_r2.Rmd

@@
    number_sections: false
-csl: https://www.zotero.org/styles/pnas
+csl: https://www.zotero.org/styles/ecology
 knit: (function(inputFile, encoding) {
@@
 We have refined our analysis and text in light of comments from reviewer 3.
+
+We also noticed a very minor error in our codes while double-checking (improper setup in .RNG seed). We have re-ran the simulations after correction just in case.
+
 We hope the manuscript is suitable for publication in PNAS.
@@
 At all sites, a combination of electrofishing and cast net was used to capture both benthic and water-column species effectively.
-We have clarified this in the revised MS (L 333 --).
+We have clarified this in the revised MS (L.
+333 --).
 In addition, we have added some text to explain that the sampling has constant sampling effort per unit area (see **Supplementary text**).
@@
 > Our theory predicts that intentional release changes relative abundance of unenhanced species (and some species are competitively excluded as part of this process).
-The relative community composition & species richness are therefore the pathways through which intentional release affects community stability (see Theoretical predictions).
+The relative community composition & species richness are therefore the pathways through which intentional release affects community stability (see Theoretical prediction).
 Consequently, the effect of community composition is naturally integrated into the effect of intentional release, statistically speaking.
 >
-> Please note that, in our causal scenario, the inclusion of community composition in our regression model causes a problem called "over-control bias" (see [@arifPredictiveModelsAren2022] for details).
+> Please note that, in our causal scenario, the inclusion of community composition in our regression model causes a problem called "over-control bias" (see @arifPredictiveModelsAren2022 for details).
 The pathway through which intentional release affects community stability is, "intentional release (variable X1)" $\rightarrow$ "community composition (X2)" $\rightarrow$ "community stability (Y)." In this case, statistical theory suggests that including both X1 and X2 to explain Y improperly underestimates (or overlooks) the effect of X1 on Y [@arifPredictiveModelsAren2022].
@@
 However, none of them evaluated the long-term impact.
-We have improved the description of the knowledge gap addressed in this study (L51 --)
+We have improved the description of the knowledge gap addressed in this study (L.
+51 --)
 
@@
 
-> We understood that the reviewer commented on the last paragraph of "theoretical prediction." We have clarified that we are linking our results to reintroduction programs in conservation (paragraph starting at L135).
+> We understood that the reviewer commented on the last paragraph of "theoretical prediction." We have clarified that we are linking our results to reintroduction programs in conservation (paragraph starting at L.
+135).
 

### 2022-12-27 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Therefore, unmeasured human influences should have minimal influences on the observed relationships.
-As such, we were able to confine potential confounding factors to natural environmental variation, which were properly accounted for in our statistical model (see **Methods**).
+As such, we were able to confine potential confounding factors to natural environmental variation, which was properly accounted for in our statistical model (see **Methods**).
 Second, the sampling method in this monitoring program (a combination of cast net and electrofishing) is carefully chosen to capture stream fishes with different microhabitat preferences (e.g., water-column vs.

### 2022-12-28 rmd/manuscript.Rmd
Update manuscript.Rmd

@@
 Consequently, the ecological community with the intentional release is predicted to show reduced community density with unstable temporal dynamics.
-Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery salmon -- a major fishery resource worldwide.
+Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer taxonomic richness in rivers with the intensive release of hatchery salmon -- a major fishery resource worldwide.
 Our findings alarm that the current overreliance on intentional release may accelerate global biodiversity loss with undesired consequences for the provisioning of ecosystem services.
@@
 \begin{aligned}
-y_s &\sim \text{Poisson}(\lambda_{y,s} \exp(\varepsilon_{\lambda,s})) &&\text{for species richness}\\
+y_s &\sim \text{Poisson}(\lambda_{y,s} \exp(\varepsilon_{\lambda,s})) &&\text{for taxonomic richness}\\
 \ln \pmb{y_s} &\sim \text{MVN}(\pmb{\theta_{y,s}}, \pmb{\Omega_y}) &&\text{for mean and SD}
@@
 
-In the poisson model for species richness, $\exp(\varepsilon_{\lambda,s})$ is the error term accounting for overdispersion ($\varepsilon_{\lambda,s} \sim \text{Normal}(0, \sigma_{\lambda}^2)$).
+In the poisson model for taxonomic richness, $\exp(\varepsilon_{\lambda,s})$ is the error term accounting for overdispersion ($\varepsilon_{\lambda,s} \sim \text{Normal}(0, \sigma_{\lambda}^2)$).
 In the multivariate normal model, $\pmb{y_s}$ represents a vector of mean and SD at site $s$, which is modeled as a random variable drawn from a multivariate normal distribution with the variance-covariance matrix $\pmb{\Omega_y}$.
@@
 \begin{aligned}
-\ln \lambda_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}\\
+\ln \lambda_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_kx_{k,s} &&\text{for taxonomic richness}\\
 \theta_{y,s} &= \gamma_{0,w(s)} + \gamma_1 R'_{s} + \sum_k \gamma_k x_{k,s} &&\text{for mean and SD}
